\end{RTL}

\newpage
\markright{{\T{}\bfseries{}Dictionary}}
\phantomsection{}\label{page:dictionary}
{
\T{}
\raggedright{}
\raggedbottom{}
\leftskip 0.25in
\parindent -0.25in

\begin{center}
{\Large{}Words}\phantomsection{}\label{page:dictionary:words}
\end{center}

\vspace{-2ex}
\textbf{ABDOMEN} Heb: {\large\H מעה} ma-ah Def: The gut, the internal organs of the lower torso, the seat of the unconscious mind. \{Strong's: 4577, 4578\}\hfill{}\\

\textbf{ABHOR (Verb)} Heb: {\large\H תעב} t.ah.b Def: To hate something that is disgusting. \{Strong's: 8581\}\hfill{}\\

\textbf{ABIDE (Verb)} Heb: {\large\H נוה} n.w.h Def: To dwell restfully and peacefully. \{Strong's: 5115\}\hfill{}\\

\textbf{ABODE} Heb: {\large\H נוה} na-weh Def: The dwelling place of man (home), god (mountain) or animal (pasture or stable). \{Strong's: 5116\}\hfill{}\\

\textbf{ABODE.OF.NINUS} Heb: {\large\H נינוה} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{ABOUNDING} Heb: {\large\H שפע} {[}X{]} Def: {[}X{]} \{Strong's: 8228\}\hfill{}\\

\textbf{ABRUPTLY} Heb: {\large\H פתע} {[}X{]} Def: As a wink of time. \{Strong's: 6621\}\hfill{}\\

\textbf{ABUNDANCE} Heb: {\large\H רוב} rov Def: An ample quantity of number (many) or plentiful supply of strength (great). \{Strong's: 7230\}\hfill{}\\

\textbf{ABUNDANT} Heb: {\large\H רב} rav \textbf{\textbackslash{}} {\large\H רבה} ra-bah Def: Great plenty or supply of numbers (many) or strength (great). One who is abundant in authority such as a master or teacher. Also, an archer as one abundant with arrows. \{Strong's: 7227, 7228, 7229\}\hfill{}\\

\textbf{ABUNDANT.ONE} Heb: {\large\H עצמון} ats-mon Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{ACACIA} Heb: {\large\H שטה} shit-tah Def: A thorny tree commonly found in the Near East. In its plural form can mean wood or boards from the tree. \{Strong's: 7848\}\hfill{}\\

\textbf{ACCEPT (Verb)} Heb: {\large\H רצה} r.ts.h Def: To receive from the messenger what is given as a message. \{Strong's: 7521\}\hfill{}\\

\textbf{ACCUMULATE (Verb)} Heb: {\large\H רכש} r.k.sh Def: To gather or pile up, especially little by little. \{Strong's: 7408\}\hfill{}\\

\textbf{ACQUIRED} Heb: {\large\H מקנה} miq-nah Def: What is accumulated in the sense of gathering to build a nest. What is obtained as one's own. Often used in the context of purchasing. \{Strong's: 4736\}\hfill{}\\

\textbf{ACQUIRING} Heb: {\large\H משך} {[}X{]} Def: In the sense of drawing something out. \{Strong's: 4901\}\hfill{}\\

\textbf{ACQUISITION} Heb: {\large\H משק} me-sheq Def: Something gained by purchase or exchange. \{Strong's: 4943\}\hfill{}\\

\textbf{ACQUIT (Verb)} Heb: {\large\H נקה} n.q.h Def: To declare one innocent of a crime or oath. \{Strong's: 5343, 5352\}\hfill{}\\

\textbf{ADD (Verb)} Heb: {\large\H יסף} y.s.p Def: To augment something by increasing it in amount or supply. The hiphil (causative) form means ``again.'' \{Strong's: 3254, 3255\}\hfill{}\\

\textbf{ADDER} Heb: {\large\H שפיפון} she-phi-phon Def: A species of viper, possibly an adder. \{Strong's: 8207\}\hfill{}\\

\textbf{ADHERE (Verb)} Heb: {\large\H דבק} d.b.q Def: To join or stick to someone or something. \{Strong's: 1692, 1693\}\hfill{}\\

\textbf{ADMINISTRATION} Heb: {\large\H כהונה} ke-hu-nah Def: The collective members from the tribe of Levi who administrate over the tent of meeting or the temple. \{Strong's: 3550\}\hfill{}\\

\textbf{ADMINISTRATOR} Heb: {\large\H כוהן} ko-heyn Def: One who manages the affairs and activities of an organization. The administrators (often translated as ``priest'') of Israel are Levites who manage the Tent of Meeting, and later the Temple, as well as teach the people the teachings and directions of YHWH, and perform other duties, such as the inspection of people and structures for disease. \{Strong's: 3548, 3549\}\hfill{}\\

\textbf{ADORATION} Heb: {\large\H תהילה} te-hi-lah Def: To praise or to be boastful. \{Strong's: 8416\}\hfill{}\\

\textbf{ADORN (Verb)} Heb: {\large\H כהן} k.h.n Def: To put on special ornaments or garments for a special office or event. (see Isaiah 61:10). \{Strong's: 3547\}\hfill{}\\

\textbf{ADORNMENT} Heb: {\large\H עדה} od Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{ADVANCE (Verb)} Heb: {\large\H עתק} ah.t.q Def: To bring or move forward; to raise to a higher rank; to make progress. \{Strong's: 6275\}\hfill{}\\

\textbf{ADVICE} Heb: {\large\H עוץ} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{AFFECTION} Heb: {\large\H אהבה} a-ha-vah Def: A moderate feeling or emotion. A tender attachment or fondness. \{Strong's: 160\}\hfill{}\\

\textbf{AFFLICT (Verb)} Heb: {\large\H ענה} ah.n.h Def: To oppress severely so as to cause persistent suffering or anguish in the sense of making dark. \{Strong's: 6031, 6033\}\hfill{}\\

\textbf{AFFLICTION} Heb: {\large\H עני} a-ni Def: The cause of persistent suffering, pain or distress. \{Strong's: 6040, 6041\}\hfill{}\\

\textbf{AFLAME} Heb: {\large\H חרחר} {[}X{]} Def: {[}X{]} \{Strong's: 2746\}\hfill{}\\

\textbf{AFRAID} Heb: {\large\H יגור} {[}X{]} Def: {[}X{]} \{Strong's: 3016\}\hfill{}\\

\textbf{AFTER} Heb: {\large\H אחרי} a-hhar-i Def: A time to come beyond another event. \{Strong's: 310, 311\}\hfill{}\\

\textbf{AFTER.GROWTH} Heb: {\large\H ספיח} {[}X{]} Def: What spreads out by itself rather than sown. \{Strong's: 5599\}\hfill{}\\

\textbf{AGATE} Heb: {\large\H שבו} she-vo Def: Probably the Agate, a variety of quartz that may be gray, light blue, orange, red or black in color. The Septuagint uses achates meaning Agate. \{Strong's: 7618\}\hfill{}\\

\textbf{AGE} Heb: {\large\H זוקן} zo-qen Def: The part of existence extending from the beginning to any given time; a period of time marked by a central figure or prominent feature. \{Strong's: 2207\}\hfill{}\\

\textbf{AGITATED} Heb: {\large\H גתר} {[}X{]} Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{AGITATION} Heb: {\large\H זועה} {[}X{]} Def: An object of terror that causes trembling. \{Strong's: 2113, 2189\}\hfill{}\\

\textbf{AGONY} Heb: {\large\H חיל} hhil \textbf{\textbackslash{}} {\large\H חילה} hhi-lah Def: A state of being in emotional or physical turmoil or pain. \{Strong's: 2427\}\hfill{}\\

\textbf{AGREE (Verb)} Heb: {\large\H אות} a.w.t Def: Two parties to be in concert or concurrence. \{Strong's: 225\}\hfill{}\\

\textbf{ALL} Heb: {\large\H כול} kol Def: The whole of a group. \{Strong's: 3605, 3606\}\hfill{}\\

\textbf{ALL.AROUND} Heb: {\large\H סביב} sa-viv \textbf{\textbackslash{}} {\large\H סביבה} se-vi-vah Def: On all sides; enclose so as to surround; in rotation or succession. A circling or bordering about the edge. \{Strong's: 5439\}\hfill{}\\

\textbf{ALLIED} Heb: {\large\H קהת} qe-hat Def: To be a part of. \{Strong's: n/a\}\hfill{}\\

\textbf{ALMOND} Heb: {\large\H שקד} sha-qeyd Def: The nut or the tree. From the nut’s shape like an open eye. \{Strong's: 8247\}\hfill{}\\

\textbf{ALOE} Heb: {\large\H אהל} {[}X{]} Def: The glistening oils of the plant. The oils or the tree. \{Strong's: 174\}\hfill{}\\

\textbf{ALONE} Heb: {\large\H בדד} {[}X{]} Def: {[}X{]} \{Strong's: 910\}\hfill{}\\

\textbf{ALONGSIDE} Heb: {\large\H עומת} u-mat Def: To stand with, or next to, someone or something. \{Strong's: 5980\}\hfill{}\\

\textbf{ALSO} Heb: {\large\H גם} gam Def: In addition to. The idea of a gathering of objects or ideas. \{Strong's: 1571\}\hfill{}\\

\textbf{ALTAR} Heb: {\large\H מזבח} miz-bey-ahh Def: The place of sacrifice. \{Strong's: 4196\}\hfill{}\\

\textbf{AMBER} Heb: {\large\H בדולח} be-du-lahh Def: A fossil gum resin. \{Strong's: 916\}\hfill{}\\

\textbf{AMBUSH} Heb: {\large\H צדיה} {[}X{]} Def: A laying down in wait. \{Strong's: 6660\}\hfill{}\\

\textbf{AMBUSH (Verb)} Heb: {\large\H ארב} a.r.b Def: To lay in wait of another to capture or do harm or injury. \{Strong's: 693\}\hfill{}\\

\textbf{AMETHYST} Heb: {\large\H אחלמה} ahh-la-mah Def: Probably the Amethyst, a violet form of quartz. The Septuagint uses Amethystos. \{Strong's: 306\}\hfill{}\\

\textbf{AMPLIFY (Verb)} Heb: {\large\H דגה} d.g.h Def: To expand, multiply or increase. \{Strong's: 1711\}\hfill{}\\

\textbf{ANCIENT} Heb: {\large\H עילם} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{ANGER} Heb: {\large\H כעס} {[}X{]} Def: {[}X{]} \{Strong's: 3708\}\hfill{}\\

\textbf{ANNOYANCE} Heb: {\large\H קללה} qe-la-lah Def: The act of disturbing or irritating. Something that is light in stature; considered worthless as compared with something of much greater value or importance. \{Strong's: 7045\}\hfill{}\\

\textbf{ANPHAH} Heb: {\large\H אנפה} {[}X{]} Def: An unknown type of bird, possibly from its nose or beak. \{Strong's: 601\}\hfill{}\\

\textbf{ANSWER (Verb)} Heb: {\large\H ענה} ah.n.h Def: Something written or spoken in reply to a question. \{Strong's: 6030, 6032\}\hfill{}\\

\textbf{ANSWERED} Heb: {\large\H ענה} a-nah Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{ANYTHING} Heb: {\large\H מאומה} me-u-mah Def: An indeterminate amount or thing. \{Strong's: 3972\}\hfill{}\\

\textbf{APART.FROM} Heb: {\large\H בילעדי} bil-a-dey Def: At a little distance; away from in space or time; holding different opinions. \{Strong's: 1107\}\hfill{}\\

\textbf{APPAREL} Heb: {\large\H שימלה} sim-lah Def: Something that clothes or adorns. As forming to the image of the body. \{Strong's: 8071\}\hfill{}\\

\textbf{APPEARANCE} Heb: {\large\H מראה} mar-e Def: What is seen or is in sight. \{Strong's: 4758\}\hfill{}\\

\textbf{APPOINT (Verb)} Heb: {\large\H יעד} y.ah.d Def: To arrange, fix or set in place, to determine a set place or time to meet. \{Strong's: 3259\}\hfill{}\\

\textbf{APPOINTED} Heb: {\large\H מועד} mo-eyd Def: A person, place, thing or time that is fixed or officially set. \{Strong's: 4150, 4151\}\hfill{}\\

\textbf{APPOINTED.TIME} Heb: {\large\H עת} eyt Def: A fixed or officially set event, occasion or date. \{Strong's: 6256\}\hfill{}\\

\textbf{APPROACH (Verb)} Heb: {\large\H אנה} a.n.h Def: To come near or nearer to. \{Strong's: 579\}\hfill{}\\

\textbf{ARCH} Heb: {\large\H גב} gav Def: A curved object. The bowing of the back as when digging. Also any high arched or convex thing such as the eyebrow or the rim of a wheel. \{Strong's: 1354, 1355, 1610\}\hfill{}\\

\textbf{AREA} Heb: {\large\H מקום} ma-qom Def: An indefinite region or expanse; a particular part of a surface or body. A place. \{Strong's: 4725\}\hfill{}\\

\textbf{ARM} Heb: {\large\H זרוע} ze-ro-a Def: The human upper limb as representing power. \{Strong's: 2220\}\hfill{}\\

\textbf{ARM.BAND} Heb: {\large\H כומז} ku-maz Def: An insignia or emblem showing loyalty or ownership. \{Strong's: 3558\}\hfill{}\\

\textbf{ARM.FOR.BATTLE (Verb)} Heb: {\large\H חמש} hh.m.sh Def: To grab weapons in preparation for battle. \{Strong's: 2571\}\hfill{}\\

\textbf{ARMAMENT} Heb: {\large\H כבוד} ka-vod Def: The arms and equipment of a soldier or military unit. From a root meaning ``heavy'' and often paralleled with other weapons. Figurative for power. \{Strong's: 3519\}\hfill{}\\

\textbf{ARMLET} Heb: {\large\H אצעדה} {[}X{]} Def: An ornament worn on the ankle or wrist that jingles when walking. \{Strong's: 685\}\hfill{}\\

\textbf{ARMY} Heb: {\large\H צבא} tse-va Def: A large organized group mustered together and armed for war or service. \{Strong's: 6635\}\hfill{}\\

\textbf{AROMA} Heb: {\large\H ריח} ri-ahh Def: A distinctive pervasive and usually pleasant or savory smell or odor. \{Strong's: 7381, 7382\}\hfill{}\\

\textbf{AROMATIC.SPICE} Heb: {\large\H סם} sam Def: A spice that is pleasing to the nose. \{Strong's: 5561\}\hfill{}\\

\textbf{AROUND.THE.CORNER} Heb: {\large\H פינון} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{ARRANGE (Verb)} Heb: {\large\H ערך} ah.r.k Def: To set something in order or into a correct or suitable configuration, sequence or adjustment. \{Strong's: 6186\}\hfill{}\\

\textbf{ARRANGEMENT} Heb: {\large\H ערך} ey-rekh Def: Set in a row or in order according to rank or age. In parallel. Arranged items in juxtaposition. \{Strong's: 6187\}\hfill{}\\

\textbf{ARRIVE (Verb)} Heb: {\large\H אתה} a.t.h Def: To arrive at a destination. \{Strong's: 857, 858\}\hfill{}\\

\textbf{ARROW} Heb: {\large\H חץ} hheyts Def: A missile weapon shot from a bow having a pointed head, slender shaft and feathers as a butt. \{Strong's: 2671\}\hfill{}\\

\textbf{ASCENT} Heb: {\large\H מעלה} {[}X{]} Def: A place of straight or stepped incline. \{Strong's: 4608\}\hfill{}\\

\textbf{ASH} Heb: {\large\H אפר} a-phar Def: The solid residue left when material is thoroughly burned. \{Strong's: 665, 666\}\hfill{}\\

\textbf{ASSEMBLY} Heb: {\large\H קהל} qa-hal \textbf{\textbackslash{}} {\large\H קהלה} {[}X{]} Def: A large group, as a gathering of the flock of sheep to the shepherd. \{Strong's: 6951, 3862, 6952\}\hfill{}\\

\textbf{ASSIGN (Verb)} Heb: {\large\H חלק} hh.l.q Def: To divide and mete out according to a plan among the appropriate recipients. \{Strong's: 2505\}\hfill{}\\

\textbf{ASSOCIATION} Heb: {\large\H חברון} hhev-ron Def: A relationship between two persons, places or objects that connects them together. \{Strong's: n/a\}\hfill{}\\

\textbf{ASTONISHMENT} Heb: {\large\H תמהון} {[}X{]} Def: In the sense of overfilled. \{Strong's: 8541\}\hfill{}\\

\textbf{AT} Heb: {\large\H את} et Def: A function word to indicate presence or occurrence, a goal of an implied or indicated action, etc. Commonly used as a grammatical tool to identify the direct object of a verb. \{Strong's: 853, 854, 3487\}\hfill{}\\

\textbf{AT.THAT.TIME} Heb: {\large\H אז} az Def: A specified moment or time. \{Strong's: 227\}\hfill{}\\

\textbf{AT.THIS.POINT} Heb: {\large\H הלום} ha-lom Def: To indicate a specific moment or place in time. \{Strong's: 1988\}\hfill{}\\

\textbf{ATONEMENT} Heb: {\large\H כיפור} ki-pur Def: An act of paying the price to release the debt or person. A covering over of transgression. \{Strong's: 3725\}\hfill{}\\

\textbf{ATTACH (Verb)} Heb: {\large\H חשק} hh.sh.q Def: To bring one's self into an association with another. To have an attachment to another. \{Strong's: 2836\}\hfill{}\\

\textbf{ATTACK (Verb)} Heb: {\large\H איב} a.y.b Def: To be antagonistic or unfriendly to another. An action taken by an enemy. \{Strong's: 340, 341\}\hfill{}\\

\textbf{AUNT} Heb: {\large\H דודה} do-dah Def: The sister of one's father or mother. One who is loved. \{Strong's: 1733\}\hfill{}\\

\textbf{AVENGE (Verb)} Heb: {\large\H נקם} n.q.m Def: To take vengeance for or on behalf of another; to gain satisfaction for a wrong by punishing the wrongdoer; to pursue and kill one who has murdered. \{Strong's: 5358\}\hfill{}\\

\textbf{AWAKE (Verb)} Heb: {\large\H יקץ} y.q.ts Def: To bring sleep to an end; to not be in a state of sleeping. \{Strong's: 3364\}\hfill{}\\

\textbf{AWE} Heb: {\large\H פחד} pa-hhad Def: As shaking when in the presence of an awesome sight. \{Strong's: 6343, 6344\}\hfill{}\\

\textbf{AWL} Heb: {\large\H מרצע} mar-tsey-a Def: A sharp pointed tool for piercing holes in leather or the skin. \{Strong's: 4836\}\hfill{}\\

\textbf{AXE} Heb: {\large\H גרזן} {[}X{]} Def: {[}X{]} \{Strong's: 1631\}\hfill{}\\

\textbf{AZNIYAH} Heb: {\large\H עזניה} {[}X{]} Def: An unknown bird of prey. \{Strong's: 5822\}\hfill{}\\

\textbf{BACK} Heb: {\large\H אחור} a-hhor Def: The part of the body that is behind. To be in the rear of or behind something. \{Strong's: 268\}\hfill{}\\

\textbf{BACK.OF.THE.NECK} Heb: {\large\H צואר} tsa-war Def: The nape between the shoulders and the head. \{Strong's: 6676, 6677\}\hfill{}\\

\textbf{BACKBONE} Heb: {\large\H עציון} e-tsi-on Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{BACKWARD} Heb: {\large\H אחורנית} a-hho-ra-niyt Def: With the back foremost; in a reverse or contrary way; i.e. To walk backward in the sense of being after oneself. \{Strong's: 322\}\hfill{}\\

\textbf{BAG} Heb: {\large\H כיס} {[}X{]} Def: {[}X{]} \{Strong's: 3599\}\hfill{}\\

\textbf{BAKE (Verb)} Heb: {\large\H אפה} a.p.h Def: To cook using dry heat, especially in an oven. \{Strong's: 644\}\hfill{}\\

\textbf{BAKED} Heb: {\large\H מאפה} {[}X{]} Def: What is baked. \{Strong's: 3989\}\hfill{}\\

\textbf{BALANCE} Heb: {\large\H מואזן} {[}X{]} Def: A pair of scales used for weighing. From the ear as the place where balance is determined. \{Strong's: 3976, 3977\}\hfill{}\\

\textbf{BALD} Heb: {\large\H קרח} {[}X{]} Def: {[}X{]} \{Strong's: 7142\}\hfill{}\\

\textbf{BALD.FOREHEAD} Heb: {\large\H גבח} gi-bey-ahh \textbf{\textbackslash{}} {\large\H גבחת} ga-ba-hhat Def: A lack of hair on the front part of the head. \{Strong's: 1371, 1372\}\hfill{}\\

\textbf{BALDING} Heb: {\large\H קורח} qo-rahh Def: The top of the head void of any hair. \{Strong's: n/a\}\hfill{}\\

\textbf{BALDNESS} Heb: {\large\H קרחה} {[}X{]} Def: {[}X{]} \{Strong's: 7144, 7146\}\hfill{}\\

\textbf{BALM} Heb: {\large\H צרי} tse-ri Def: An aromatic preparation for a healing ointment. A salve rubbed and pressed into the skin. \{Strong's: 6875\}\hfill{}\\

\textbf{BALSAM} Heb: {\large\H בשם} ba-sham Def: A sweet smelling spices. \{Strong's: 1313\}\hfill{}\\

\textbf{BAND} Heb: {\large\H גדוד} ge-dud Def: A gathering of men for attacking or raiding. \{Strong's: 1416\}\hfill{}\\

\textbf{BAND (Verb)} Heb: {\large\H גדד} g.d.d Def: To gather or assemble as a group for attacking or raiding. \{Strong's: 1413\}\hfill{}\\

\textbf{BANKS} Heb: {\large\H אשד} {[}X{]} Def: The banks of a river as a channel for the water. \{Strong's: 793\}\hfill{}\\

\textbf{BANNER} Heb: {\large\H דגל} {[}X{]} Def: {[}X{]} \{Strong's: 1714\}\hfill{}\\

\textbf{BANQUET} Heb: {\large\H משתה} mish-teh Def: An elaborate meal often accompanied by a ceremony. \{Strong's: 4960, 4961\}\hfill{}\\

\textbf{BAR} Heb: {\large\H מוט} {[}X{]} Def: The bent bar of the yoke that goes around the neck, also a branch that is used as pole. A slipping or wavering of the foot. \{Strong's: 4132\}\hfill{}\\

\textbf{BARE.ONE} Heb: {\large\H ערן} ey-ran Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{BARE.PLACE} Heb: {\large\H שפי} {[}X{]} Def: The desert as a place of serpents. \{Strong's: 8205\}\hfill{}\\

\textbf{BARE.SKIN} Heb: {\large\H ער} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{BARK (Verb)} Heb: {\large\H נבח} n.b.hh Def: Of a dog. \{Strong's: 5024\}\hfill{}\\

\textbf{BARLEY} Heb: {\large\H סעורה} se-o-rah Def: A grain, identified by its hairs, used as food, and for determining the month of Aviv. \{Strong's: 8184\}\hfill{}\\

\textbf{BARN} Heb: {\large\H אסם} {[}X{]} Def: {[}X{]} \{Strong's: 618\}\hfill{}\\

\textbf{BARREN} Heb: {\large\H ערירי} a-ri-ri Def: Incapable of bearing children. Childless in the sense of being naked of children. \{Strong's: 6185\}\hfill{}\\

\textbf{BARRENNESS} Heb: {\large\H און} a-wen Def: Action or thought that is vain or for an improper purpose. \{Strong's: 205\}\hfill{}\\

\textbf{BARTER (Verb)} Heb: {\large\H ערב} ah.r.b Def: To exchange an item or service for another. \{Strong's: 6148\}\hfill{}\\

\textbf{BASE} Heb: {\large\H כן} keyn Def: The bottom or foundation which provides support. A person's home or family as being a base. A species of gnat. \{Strong's: 3653\}\hfill{}\\

\textbf{BASTARD} Heb: {\large\H ממזר} {[}X{]} Def: {[}X{]} \{Strong's: 4464\}\hfill{}\\

\textbf{BAT} Heb: {\large\H עטלף} {[}X{]} Def: {[}X{]} \{Strong's: 5847\}\hfill{}\\

\textbf{BATHE (Verb)} Heb: {\large\H רחץ} r.hh.ts Def: To cleanse by being immersed in, or washing with, water. \{Strong's: 7364, 7365\}\hfill{}\\

\textbf{BATTERING.RAM} Heb: {\large\H מחי} {[}X{]} Def: In the sense of fat. An engine of war for battering down walls. \{Strong's: 4239\}\hfill{}\\

\textbf{BATTLE} Heb: {\large\H מלחמה} mil-hha-mah Def: A struggle between two armies. \{Strong's: 4421\}\hfill{}\\

\textbf{BE (Verb)} Heb: {\large\H הוה} h.w.h Def: To exist or have breath. That which exists has breath. In Hebrew thought the breath is the character of someone or something. Just as a man has character, so do objects. \{Strong's: 1933, 1934\}\hfill{}\\

\textbf{BE.A.HARLOT (Verb)} Heb: {\large\H זנה} z.n.h Def: A woman who practices promiscuous sexual behavior, especially for hire. \{Strong's: 2181\}\hfill{}\\

\textbf{BE.ABLE (Verb)} Heb: {\large\H יכל} y.k.l Def: To successfully prevail, overcome or endure. \{Strong's: 3201, 3202\}\hfill{}\\

\textbf{BE.ABUNDANT (Verb)} Heb: {\large\H עצם} ah.ts.m Def: To be strong in might or numbers. From the abundant number of bones in the body. \{Strong's: 6105\}\hfill{}\\

\textbf{BE.AFRAID (Verb)} Heb: {\large\H יגר} y.g.r Def: {[}X{]} \{Strong's: 3025\}\hfill{}\\

\textbf{BE.ALMOND.SHAPED (Verb)} Heb: {\large\H שקד} sh.q.d Def: An object that is in the form of an almond. \{Strong's: 8246\}\hfill{}\\

\textbf{BE.AMAZED (Verb)} Heb: {\large\H חדה} hh.d.h Def: To be overwhelmed with surprise or sudden wonder; astonished greatly. \{Strong's: 2302\}\hfill{}\\

\textbf{BE.AN.IN.LAW (Verb)} Heb: {\large\H חתן} hh.t.n Def: To have a relationship with another through marriage. \{Strong's: 2859\}\hfill{}\\

\textbf{BE.ANGRY (Verb)} Heb: {\large\H כעס} k.ah.s Def: A strong feeling of displeasure and belligerence aroused by a wrong. \{Strong's: 3707\}\hfill{}\\

\textbf{BE.ASHAMED (Verb)} Heb: {\large\H בוש} b.w.sh Def: Feeling shame, guilt or disgrace; to be dried up with shame. \{Strong's: 954\}\hfill{}\\

\textbf{BE.BITTER (Verb)} Heb: {\large\H מרר} m.r.r Def: Having a harsh, disagreeably acrid taste. One of the four basic taste sensations. \{Strong's: 4843\}\hfill{}\\

\textbf{BE.BOLD (Verb)} Heb: {\large\H עוז} ah.w.z Def: To be fearless and daring; courageous. \{Strong's: 5756\}\hfill{}\\

\textbf{BE.BRIGHT (Verb)} Heb: {\large\H יפע} y.p.ah Def: {[}X{]} \{Strong's: 3313\}\hfill{}\\

\textbf{BE.CHILDLESS (Verb)} Heb: {\large\H שכל} sh.k.l Def: To be without children through miscarriage, barrenness or loss of children. \{Strong's: 7921\}\hfill{}\\

\textbf{BE.CLEAN (Verb)} Heb: {\large\H טהר} t.h.r Def: Free from dirt, pollution or immorality; unadulterated, pure. \{Strong's: 2891\}\hfill{}\\

\textbf{BE.CRAFTY (Verb)} Heb: {\large\H נכל} n.k.l Def: The doing of a thing slyly or cunningly. \{Strong's: 5230\}\hfill{}\\

\textbf{BE.DELIGHTFUL (Verb)} Heb: {\large\H נעם} n.ah.m Def: One of the four basic taste sensations \{Strong's: 5276\}\hfill{}\\

\textbf{BE.DISTINCT (Verb)} Heb: {\large\H פלה} p.l.h Def: To be clearly distinguished. To have a marked difference. To be prominent; separated out completely. \{Strong's: 6395\}\hfill{}\\

\textbf{BE.DOUBLE (Verb)} Heb: {\large\H תאם} t.a.m Def: To have two identical pieces placed together. Also to bear twins as doubles. \{Strong's: 8382\}\hfill{}\\

\textbf{BE.DRUNK (Verb)} Heb: {\large\H שכר} sh.k.r Def: To be filled with intoxicating drink. \{Strong's: 7937\}\hfill{}\\

\textbf{BE.DYSFUNCTIONAL (Verb)} Heb: {\large\H רעע} r.ah.ah Def: Impaired or abnormal filling of purpose; to act wrongly by injuring or doing an evil action. \{Strong's: 4827, 7489\}\hfill{}\\

\textbf{BE.EMINENT (Verb)} Heb: {\large\H אדר} a.d.r Def: To be large in size or stature. \{Strong's: 142\}\hfill{}\\

\textbf{BE.FACE.TO.FACE (Verb)} Heb: {\large\H נגד} n.g.d Def: To face another. The hiphil (causative) form means ``tell'' in the sense of speaking face to face. \{Strong's: 5046, 5047\}\hfill{}\\

\textbf{BE.FAR (Verb)} Heb: {\large\H רחק} r.hh.q Def: To be distant, a long way off. \{Strong's: 7368\}\hfill{}\\

\textbf{BE.FILTHY (Verb)} Heb: {\large\H חנף} hh.n.p Def: To be polluted or dirty. Usually in the sense of immorality. \{Strong's: 2610\}\hfill{}\\

\textbf{BE.FRUITFUL (Verb)} Heb: {\large\H פרא} p.r.a Def: Abundantly productive. \{Strong's: 6500\}\hfill{}\\

\textbf{BE.GUILTY (Verb)} Heb: {\large\H אשם} a.sh.m Def: To commit an offense, especially consciously. \{Strong's: 816\}\hfill{}\\

\textbf{BE.HARD (Verb)} Heb: {\large\H קשה} q.sh.h Def: To be difficult; not easily penetrated; not easily yielding to pressure. \{Strong's: 7185\}\hfill{}\\

\textbf{BE.HEAVY (Verb)} Heb: {\large\H כבד} k.b.d Def: To be great in weight, wealth or importance. The piel (intensive) form means ``honor.'' \{Strong's: 3513\}\hfill{}\\

\textbf{BE.HIGH (Verb)} Heb: {\large\H גבה} g.b.h Def: To lift up to a greater elevation or stature. \{Strong's: 1361\}\hfill{}\\

\textbf{BE.HUNGRY (Verb)} Heb: {\large\H רעב} r.ah.b Def: To have an urgent craving for food; famished. \{Strong's: 7456\}\hfill{}\\

\textbf{BE.IMPATIENT (Verb)} Heb: {\large\H לאה} l.a.h Def: Exhausted in strength, endurance, vigor or freshness. \{Strong's: 3811\}\hfill{}\\

\textbf{BE.IN.MISERY (Verb)} Heb: {\large\H כאב} k.a.b Def: A state of suffering and want due to poverty or affliction. \{Strong's: 3510\}\hfill{}\\

\textbf{BE.LAVISH (Verb)} Heb: {\large\H זול} z.w.l Def: To shake out. \{Strong's: 2107\}\hfill{}\\

\textbf{BE.LESS (Verb)} Heb: {\large\H מעט} m.ah.t Def: To be fewer or diminished in size or amount. \{Strong's: 4591\}\hfill{}\\

\textbf{BE.LOW (Verb)} Heb: {\large\H מוך} m.w.k Def: To be brought down low in poverty. \{Strong's: 4134\}\hfill{}\\

\textbf{BE.NUMB (Verb)} Heb: {\large\H פוג} p.w.g Def: Devoid of sensation or emotion. \{Strong's: 6313\}\hfill{}\\

\textbf{BE.OLD (Verb)} Heb: {\large\H זקן} z.q.n Def: To be of an advanced age. \{Strong's: 2204\}\hfill{}\\

\textbf{BE.OUT.OF.SIGHT (Verb)} Heb: {\large\H עלם} ah.l.m Def: To be hidden or obscured from vision; to be beyond the horizon; to be covered or unknown. \{Strong's: 5956\}\hfill{}\\

\textbf{BE.OVERSHADOWED (Verb)} Heb: {\large\H צלל} ts.l.l Def: To be sunk down into a dark depth. \{Strong's: 6749, 6751\}\hfill{}\\

\textbf{BE.RED (Verb)} Heb: {\large\H אדם} a.d.m Def: To be ruddy. To have a dark reddish color. \{Strong's: 119\}\hfill{}\\

\textbf{BE.RICH (Verb)} Heb: {\large\H עשר} ah.sh.r Def: To be wealthy. \{Strong's: 6238\}\hfill{}\\

\textbf{BE.SAD (Verb)} Heb: {\large\H זעף} z.ah.p Def: To be in a state of depression. \{Strong's: 2196\}\hfill{}\\

\textbf{BE.SATISFIED (Verb)} Heb: {\large\H שבע} sh.b.ah Def: To be filled full or to overflowing; to have a complete amount. \{Strong's: 7646\}\hfill{}\\

\textbf{BE.SICK (Verb)} Heb: {\large\H חלה} hh.l.h Def: To be twisted through pain. \{Strong's: 2470\}\hfill{}\\

\textbf{BE.SILENT (Verb)} Heb: {\large\H דמם} d.m.m Def: To come to a standstill in speech or deed. To be quiet; refrain from speech or action. \{Strong's: 1826\}\hfill{}\\

\textbf{BE.SKILLED (Verb)} Heb: {\large\H חכם} hh.k.m Def: To be able to decide or discern between good and bad, right and wrong; to act correctly in thought and action. \{Strong's: 2449\}\hfill{}\\

\textbf{BE.SMALL (Verb)} Heb: {\large\H קטן} q.t.n Def: To have little size or slight dimensions; insignificant. \{Strong's: 6994\}\hfill{}\\

\textbf{BE.SOFT (Verb)} Heb: {\large\H רכך} r.k.k Def: To be soft. \{Strong's: 7401\}\hfill{}\\

\textbf{BE.SOUR (Verb)} Heb: {\large\H חמץ} hh.m.ts Def: To be fermented by adding leaven to bread. Also, sour in taste, thought or action. \{Strong's: 2556\}\hfill{}\\

\textbf{BE.SQUARE (Verb)} Heb: {\large\H רבע} r.b.ah Def: Any four sided object. Also, to go down on the hands and knees, to be on all fours. \{Strong's: 7250, 7251\}\hfill{}\\

\textbf{BE.STEADFAST (Verb)} Heb: {\large\H צדק} ts.d.q Def: To walk on the right path without losing the way. \{Strong's: 6663\}\hfill{}\\

\textbf{BE.STRAIGHT (Verb)} Heb: {\large\H ישר} y.sh.r Def: To be in a direct or correct line, path or thought. \{Strong's: 3474\}\hfill{}\\

\textbf{BE.STRANGE (Verb)} Heb: {\large\H זור} z.w.r Def: To be separated out from others; to be scattered abroad. \{Strong's: 2114\}\hfill{}\\

\textbf{BE.STRONG (Verb)} Heb: {\large\H אמץ} a.m.ts Def: To be mentally astute, firm, obstinate or courageous. Having or marked by great physical, moral or intellectual power. \{Strong's: 553\}\hfill{}\\

\textbf{BE.STUBBORN (Verb)} Heb: {\large\H סרר} s.r.r Def: To turn away from the correct path toward another direction. \{Strong's: 5637, 7786, 8323\}\hfill{}\\

\textbf{BE.SUPERFLUOUS (Verb)} Heb: {\large\H סרע} s.r.ah Def: {[}X{]} \{Strong's: 8311\}\hfill{}\\

\textbf{BE.THICK (Verb)} Heb: {\large\H עבה} ah.b.h Def: To be thick. Thick. \{Strong's: 5666\}\hfill{}\\

\textbf{BE.THREEFOLD (Verb)} Heb: {\large\H שלש} sh.l.sh Def: Being three times as great or as many. \{Strong's: 8027\}\hfill{}\\

\textbf{BE.UNCIRCUMCISED (Verb)} Heb: {\large\H ערל} ah.r.l Def: To be uncircumcised. \{Strong's: 6188\}\hfill{}\\

\textbf{BE.UNCLEAN (Verb)} Heb: {\large\H טמא} t.m.a Def: Physically or morally impure; dirty, filthy. \{Strong's: 2930\}\hfill{}\\

\textbf{BE.UNMINDFUL (Verb)} Heb: {\large\H שיה} sh.y.h Def: {[}X{]} \{Strong's: 7876\}\hfill{}\\

\textbf{BE.WARM (Verb)} Heb: {\large\H חמם} hh.m.m Def: To glow; project extreme heat. To be heated, either internally or externally, such as from the sun or a fire. \{Strong's: 2552\}\hfill{}\\

\textbf{BE.WHOLE (Verb)} Heb: {\large\H תמם} t.m.m Def: To be free of wound or injury, defect or impairment, disease or deformity; physically and mentally sound. \{Strong's: 8552\}\hfill{}\\

\textbf{BE.ZEALOUS (Verb)} Heb: {\large\H קנא} q.n.a Def: To be filled with eagerness and ardent interest in pursuit of something. \{Strong's: 7065\}\hfill{}\\

\textbf{BEAR.FIRSTLING (Verb)} Heb: {\large\H בכר} b.k.r Def: To be born or bear the first fruits. \{Strong's: 1069\}\hfill{}\\

\textbf{BEARD} Heb: {\large\H זקן} za-qeyn Def: The hair that grows on a man's face. A long beard as a sign of old age and wisdom. An elder as a bearded one. \{Strong's: 2205, 2206\}\hfill{}\\

\textbf{BEAST} Heb: {\large\H בהמה} be-hey-mah Def: An animal as distinguished from man or a plant. A tall or large creature. Also representative of wealth, as one who is exalted. \{Strong's: 929, 930\}\hfill{}\\

\textbf{BEAT (Verb)} Heb: {\large\H פעם} p.ah.m Def: To strike repeatedly in a rhythm such as a drum. \{Strong's: 6470\}\hfill{}\\

\textbf{BEAT.IN.PIECES (Verb)} Heb: {\large\H דקק} d.q.q Def: To crush or beat something into thin or small pieces. \{Strong's: 1854, 1855\}\hfill{}\\

\textbf{BEAT.OUT (Verb)} Heb: {\large\H דפק} d.p.q Def: To strike something with a sharp blow. \{Strong's: 1849\}\hfill{}\\

\textbf{BEATEN} Heb: {\large\H גרס} {[}X{]} Def: Grain that is crushed to make meal. \{Strong's: 1643\}\hfill{}\\

\textbf{BEATEN.WORK} Heb: {\large\H מקשה} miq-shah Def: To be shaped into a specific form by an outside force such as a hammer. \{Strong's: 4749\}\hfill{}\\

\textbf{BEAUTIFUL} Heb: {\large\H יפה} ya-pheh Def: Generally pleasing. Possessing the qualities of loveliness or functionality. \{Strong's: 3303, 3304\}\hfill{}\\

\textbf{BEAUTY} Heb: {\large\H חן} hheyn Def: The qualities in a person or thing that give pleasure to the senses. Someone or something that is desired, approved, favored or in agreement by another. \{Strong's: 2580\}\hfill{}\\

\textbf{BED} Heb: {\large\H מטה} mit-tah Def: A place for sleeping. Spread out sheet for sleeping. \{Strong's: 4296\}\hfill{}\\

\textbf{BEE} Heb: {\large\H דבורה} {[}X{]} Def: A colony of ordered insects. \{Strong's: 1682\}\hfill{}\\

\textbf{BEFORE} Heb: {\large\H טרם} te-rem Def: What precedes another event. \{Strong's: 2962\}\hfill{}\\

\textbf{BEHEAD (Verb)} Heb: {\large\H ערף} ah.r.p Def: To sever the neck from the body. Also, to break the neck. \{Strong's: 6202\}\hfill{}\\

\textbf{BEING} Heb: {\large\H נפש} ne-phesh Def: The whole of a person, god or creature including the body, mind, emotion, character and inner parts. \{Strong's: 5315\}\hfill{}\\

\textbf{BEING.LOW} Heb: {\large\H מכי} ma-khi Def: \{Strong's: n/a\}\hfill{}\\

\textbf{BELITTLE (Verb)} Heb: {\large\H קלל} q.l.l Def: To regard or portray as less impressive or important; to be light in weight; to curse or despise in the sense of making light. \{Strong's: 7043\}\hfill{}\\

\textbf{BELL} Heb: {\large\H פעמן} pa-a-mon Def: An instrument used to call to attention or to a warning. From its rhythmic ringing. \{Strong's: 6472\}\hfill{}\\

\textbf{BELLY} Heb: {\large\H גחון} ga-hhon Def: The undersurface of an animal; the stomach and other digestive organs. \{Strong's: 1512\}\hfill{}\\

\textbf{BELONGING} Heb: {\large\H פוט} put Def: To acquire ownership or authority over, something or someone owned by another. \{Strong's: n/a\}\hfill{}\\

\textbf{BELONGING.TO.NAT} Heb: {\large\H אסנת} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{BELOVED} Heb: {\large\H דוד} dod Def: One who is cherished by another. \{Strong's: 1730\}\hfill{}\\

\textbf{BEND.DOWN (Verb)} Heb: {\large\H שחה} sh.hh.h Def: To pay homage to another one by bowing low or getting on the knees with the face to the ground. \{Strong's: 7812\}\hfill{}\\

\textbf{BEND.THE.KNEE} Heb: {\large\H אברך} av-reykh Def: A kneeling down as a sign of respect to another. \{Strong's: 86\}\hfill{}\\

\textbf{BENEATH} Heb: {\large\H מטה} mat-tah Def: Below; in a lower place, position or state. As under a stretched out sheet. \{Strong's: 4295\}\hfill{}\\

\textbf{BENEFIT (Verb)} Heb: {\large\H סכן} s.k.n Def: To be of use, service or profit in order that one may benefit from it. \{Strong's: 5532, 5533\}\hfill{}\\

\textbf{BEQA} Heb: {\large\H בקע} be-qa Def: A dry weight measure equal to one-half shekel weight. \{Strong's: 1235\}\hfill{}\\

\textbf{BESIDE} Heb: {\large\H אצל} e-tsel Def: Being next to something. \{Strong's: 681\}\hfill{}\\

\textbf{BEST} Heb: {\large\H מיטב} may-tav Def: Excelling all others; most, largest; most productive or good, utility or satisfaction. \{Strong's: 4315\}\hfill{}\\

\textbf{BETROTH (Verb)} Heb: {\large\H ארש} a.r.sh Def: A promise or contract of impending marriage. To request a woman for marriage. \{Strong's: 781\}\hfill{}\\

\textbf{BETWEEN} Heb: {\large\H בין} beyn Def: In the time, space or interval that separates. \{Strong's: 996, 997, 1143\}\hfill{}\\

\textbf{BIND (Verb)} Heb: {\large\H עקד} ah.q.d Def: To make secure by tying; to confine, restrain or restrict as if with bonds. bind with a cord. \{Strong's: 6123\}\hfill{}\\

\textbf{BIND.UP (Verb)} Heb: {\large\H אלם} a.l.m Def: To tie something. The tying of the tongue, silence. \{Strong's: 481\}\hfill{}\\

\textbf{BINDER} Heb: {\large\H חשוק} hha-shuq Def: Attached around something. \{Strong's: 2838\}\hfill{}\\

\textbf{BIRD} Heb: {\large\H ציפור} tsi-por Def: A creature distinguished by a body covering of feathers and wings as forelimbs. \{Strong's: 6833\}\hfill{}\\

\textbf{BIRD.OF.PREY} Heb: {\large\H עיט} a-yit Def: A carnivorous bird that feeds on carrion or meat taken by hunting. \{Strong's: 5861\}\hfill{}\\

\textbf{BIRTH} Heb: {\large\H שגר} she-ger Def: What is brought forth from the womb. \{Strong's: 7698\}\hfill{}\\

\textbf{BIRTHED} Heb: {\large\H ילוד} yi-lud Def: What is given birth to; a baby human or animal that is brought from the womb into the open world. \{Strong's: 3209\}\hfill{}\\

\textbf{BIRTHING} Heb: {\large\H תולדה} tol-dah Def: The act or process of bringing forth offspring from the womb. Total of the children born within an era. \{Strong's: 8435\}\hfill{}\\

\textbf{BIRTHRIGHT} Heb: {\large\H בכורה} be-kho-rah Def: Rights, privileges or possessions to which a person is entitled by birth. The rights of the firstborn son (see Deut. 21:17). Also meaning the firstborn. \{Strong's: 1062\}\hfill{}\\

\textbf{BITE (Verb)} Heb: {\large\H נשך} n.sh.k Def: To seize especially with teeth or jaws; to sting, wound or pierce as with a fang. To give usury in the sense of a biting. \{Strong's: 5391\}\hfill{}\\

\textbf{BITTER} Heb: {\large\H מר} mar Def: A difficult taste or experience. \{Strong's: 4751, 4752\}\hfill{}\\

\textbf{BITTER (Verb)} Heb: {\large\H מרה} m.r.h Def: Having a harsh, disagreeably acrid taste; to be rebellious or disobedient. \{Strong's: 4784\}\hfill{}\\

\textbf{BITTER.HERBS} Heb: {\large\H ממרור} mam-ror Def: Edible plants, that when eaten brings tears to the eyes. \{Strong's: 4472\}\hfill{}\\

\textbf{BITTERNESS} Heb: {\large\H מרר} ma-rar Def: Having a harsh, disagreeably acrid taste. \{Strong's: n/a\}\hfill{}\\

\textbf{BLACK} Heb: {\large\H חום} hhum Def: As darkened from the heat of a fire. \{Strong's: 2345\}\hfill{}\\

\textbf{BLACKISH} Heb: {\large\H כוש} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{BLANKET (Verb)} Heb: {\large\H חפף} hh.p.p Def: {[}X{]} \{Strong's: 2653\}\hfill{}\\

\textbf{BLAST (Verb)} Heb: {\large\H שדף} sh.d.p Def: To blow heavily. \{Strong's: 7710\}\hfill{}\\

\textbf{BLASTING} Heb: {\large\H שדפה} {[}X{]} Def: A strong devastating wind. \{Strong's: 7711\}\hfill{}\\

\textbf{BLAZE (Verb)} Heb: {\large\H להט} l.h.t Def: {[}X{]} \{Strong's: 3857\}\hfill{}\\

\textbf{BLAZING} Heb: {\large\H להט} la-hat Def: To burn, flash or shine brightly. Also used for the magic of magicians. \{Strong's: 3858\}\hfill{}\\

\textbf{BLEMISH} Heb: {\large\H מאום} {[}X{]} Def: {[}X{]} \{Strong's: 3971\}\hfill{}\\

\textbf{BLIND} Heb: {\large\H עור} i-weyr Def: A darkness of the eye. \{Strong's: 5787\}\hfill{}\\

\textbf{BLIND (Verb)} Heb: {\large\H עור} ah.w.r Def: To become dark of site through blindness or the putting out of the eyes. \{Strong's: 5786\}\hfill{}\\

\textbf{BLINDNESS} Heb: {\large\H עורת} {[}X{]} Def: {[}X{]} \{Strong's: 5788\}\hfill{}\\

\textbf{BLOOD} Heb: {\large\H דם} dam Def: The red fluid that circulates through the body. \{Strong's: 1818\}\hfill{}\\

\textbf{BLOOM (Verb)} Heb: {\large\H צוץ} ts.w.ts Def: {[}X{]} \{Strong's: 6692\}\hfill{}\\

\textbf{BLOSSOM} Heb: {\large\H ציץ} tsits \textbf{\textbackslash{}} {\large\H ציצה} tsi-tsah Def: The flower of a plant, especially of one producing an edible fruit. \{Strong's: 6731, 6733\}\hfill{}\\

\textbf{BLOW (Verb)} Heb: {\large\H נשף} n.sh.p Def: To expel air from the mouth. \{Strong's: 5398\}\hfill{}\\

\textbf{BLOW.AWAY (Verb)} Heb: {\large\H פאה} p.a.h Def: To scatter something by blowing. \{Strong's: 6284\}\hfill{}\\

\textbf{BLOWN} Heb: {\large\H פואה} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{BLUE} Heb: {\large\H תכלת} te-khey-let Def: A color that is created with the use of a dye. \{Strong's: 8504\}\hfill{}\\

\textbf{BOARD} Heb: {\large\H קרש} qe-resh Def: A plank of wood often used to wall off an area or restrict access. \{Strong's: 7175\}\hfill{}\\

\textbf{BOARDED.UP (Verb)} Heb: {\large\H ספן} s.p.n Def: To cover as a ceiling or to hide. \{Strong's: 5603, 8226\}\hfill{}\\

\textbf{BODY} Heb: {\large\H גויה} ge-vi-yah Def: By extension, the physical form, either alive or dead; a corpse. \{Strong's: 1472\}\hfill{}\\

\textbf{BOIL (Verb)} Heb: {\large\H בשל} b.sh.l Def: To generate bubbles of vapor when heated; to cook a meat in water. The hiphil (causative) form means ``ripen.'' \{Strong's: 1310\}\hfill{}\\

\textbf{BOILED} Heb: {\large\H בשל} ba-sheyl Def: Meat or other edible that is cooked in water over a fire. \{Strong's: 1311\}\hfill{}\\

\textbf{BOILING.POT} Heb: {\large\H מרחשת} {[}X{]} Def: {[}X{]} \{Strong's: 4802\}\hfill{}\\

\textbf{BOILS} Heb: {\large\H שחין} she-hhin Def: A festering under the skin. Pits in the skin from disease. \{Strong's: 7822\}\hfill{}\\

\textbf{BOLDNESS} Heb: {\large\H עוז} oz Def: Knowing one's position or authority and standing in it. Strengthened and protected from danger. \{Strong's: 5797\}\hfill{}\\

\textbf{BOND} Heb: {\large\H איסר} {[}X{]} Def: {[}X{]} \{Strong's: 632\}\hfill{}\\

\textbf{BONDWOMAN} Heb: {\large\H אמה} a-mah Def: A female slave. One who is bound to another. \{Strong's: 519\}\hfill{}\\

\textbf{BONE} Heb: {\large\H עצם} e-tsem Def: The hard tissue of which the skeleton is chiefly composed. As a numerous amount. \{Strong's: 6106\}\hfill{}\\

\textbf{BONNET} Heb: {\large\H פאר} pe-eyr Def: A piece of cloth that is wound around the head as a decoration. \{Strong's: 6287\}\hfill{}\\

\textbf{BOOTH} Heb: {\large\H סוכה} su-kah Def: A temporary shelter; a small enclosure; dwelling place. \{Strong's: 5521\}\hfill{}\\

\textbf{BOOTY} Heb: {\large\H מלקוח} {[}X{]} Def: As tongs for taking food. What is taken \{Strong's: 4455\}\hfill{}\\

\textbf{BORDER} Heb: {\large\H גבול} ge-vul Def: The outer edge of a region. Also the area within the borders. \{Strong's: 1366\}\hfill{}\\

\textbf{BORE.OUT (Verb)} Heb: {\large\H נבב} n.b.b Def: To form by making something hollow. \{Strong's: 5014\}\hfill{}\\

\textbf{BORE.THROUGH (Verb)} Heb: {\large\H רצע} r.ts.ah Def: To pierce with a sharp object. \{Strong's: 7527\}\hfill{}\\

\textbf{BORN} Heb: {\large\H יליד} {[}X{]} Def: Brought forth, as if by birth. \{Strong's: 3211\}\hfill{}\\

\textbf{BOSOM} Heb: {\large\H חיק} hheyq Def: The human chest, especially the front side. \{Strong's: 2436\}\hfill{}\\

\textbf{BOTTOM} Heb: {\large\H קרקע} {[}X{]} Def: {[}X{]} \{Strong's: 7172\}\hfill{}\\

\textbf{BOTTOM.BASE} Heb: {\large\H יסוד} ye-sod \textbf{\textbackslash{}} {\large\H יסודה} ye-so-dah Def: A supporting and level base of a building or structure which lies on or in the ground. \{Strong's: 3246, 3247, 3248, 4328\}\hfill{}\\

\textbf{BOUGH} Heb: {\large\H ענף} {[}X{]} Def: {[}X{]} \{Strong's: 6056, 6057, 6058\}\hfill{}\\

\textbf{BOULDER} Heb: {\large\H צור} tsur Def: A large rock used as a weapon or a rock cliff used as a place of defense. Also flint, a very hard rock that when fractured forms a razor sharp edge and used for knives, spears or arrowheads. \{Strong's: 6697\}\hfill{}\\

\textbf{BOUND (Verb)} Heb: {\large\H גבל} g.b.l Def: To be defined by a border. \{Strong's: 1379\}\hfill{}\\

\textbf{BOUND.SHEAF} Heb: {\large\H אלום} a-lum Def: Stalks and ears of a cereal grass bound together. A sheaf of grain that is bound. \{Strong's: 485\}\hfill{}\\

\textbf{BOUND.UP (Verb)} Heb: {\large\H קוה} q.w.h Def: To be confined or hedged in together; to wait or to be held back in the sense of being bound up. \{Strong's: 6960\}\hfill{}\\

\textbf{BOUNDARY} Heb: {\large\H מגבלה} mig-be-let Def: Marks the outer edge, the end, of a definite area or region. Idiomatically used for an entire region. \{Strong's: 4020\}\hfill{}\\

\textbf{BOUNTY} Heb: {\large\H תנובה} {[}X{]} Def: {[}X{]} \{Strong's: 8570\}\hfill{}\\

\textbf{BOW} Heb: {\large\H קשת} qe-shet Def: A weapon made from a stiff branch to shoots arrows. A bow-shaped object such as a rainbow. \{Strong's: 7198, 7199\}\hfill{}\\

\textbf{BOW.THE.HEAD (Verb)} Heb: {\large\H קדד} q.d.d Def: To lower the head as a sign of respect. \{Strong's: 6915\}\hfill{}\\

\textbf{BOWELS} Heb: {\large\H רחם} re-hhem Def: The large intestines as encompassed about by the torso. Compassion as coming from the bowels. \{Strong's: 7356, 7358, 7359\}\hfill{}\\

\textbf{BOWL} Heb: {\large\H גביע} ga-vi-a Def: A concave vessel especially for holding liquids. As with high sides. \{Strong's: 1375\}\hfill{}\\

\textbf{BOX} Heb: {\large\H ארון} a-ron Def: A rigid rectangular receptacle often with a cover. Any box-shaped object. \{Strong's: 727\}\hfill{}\\

\textbf{BOY} Heb: {\large\H ילד} ye-led Def: A male child from birth to puberty. \{Strong's: 3206\}\hfill{}\\

\textbf{BRACELET} Heb: {\large\H צמיד} tsa-mid Def: An ornamental band or chain worn around the wrist. As the ends joined together. \{Strong's: 6781\}\hfill{}\\

\textbf{BRAID (Verb)} Heb: {\large\H ארג} a.r.g Def: To twist, entwine or weave several pieces together in parallel to become one. \{Strong's: 707\}\hfill{}\\

\textbf{BRAIDED.WORK} Heb: {\large\H שרד} se-red Def: Finely made articles of clothing made by weaving together fibers. \{Strong's: 8278, 8279\}\hfill{}\\

\textbf{BRAMBLE} Heb: {\large\H קוץ} qots Def: A rough, prickly vine or shrub. Thorn. \{Strong's: 6975\}\hfill{}\\

\textbf{BRAMBLE.THORN} Heb: {\large\H אטד} a-tad Def: {[}X{]} \{Strong's: 329\}\hfill{}\\

\textbf{BRANCH} Heb: {\large\H מטה} ma-teh Def: A branch used as a staff. Also, a tribe as a branch of the family. \{Strong's: 4294\}\hfill{}\\

\textbf{BRASS} Heb: {\large\H נחוש} na-hhush \textbf{\textbackslash{}} {\large\H נחושה} na-hhu-shah Def: From its shine. \{Strong's: 5153, 5154\}\hfill{}\\

\textbf{BRAVERY} Heb: {\large\H גבורה} ge-vo-rah Def: An act of defending one's property, convictions or beliefs. Control through physical strength. \{Strong's: 1369, 1370\}\hfill{}\\

\textbf{BRAWN} Heb: {\large\H עוצם} {[}X{]} \textbf{\textbackslash{}} {\large\H עצומה} {[}X{]} Def: From the strength of the bones. \{Strong's: 6108, 6110\}\hfill{}\\

\textbf{BREACH} Heb: {\large\H פרץ} pe-rets Def: A broken, ruptured or torn condition or area; a gap as in a wall made by battering. \{Strong's: 6556\}\hfill{}\\

\textbf{BREAD} Heb: {\large\H לחם} le-hhem Def: Baked and leavened bread primarily made of flour or meal. Also food in general. \{Strong's: 3899, 3900, 3901\}\hfill{}\\

\textbf{BREAD.CAKE} Heb: {\large\H עוג} og \textbf{\textbackslash{}} {\large\H עוגה} u-gah Def: Cakes baked on hot stones. \{Strong's: 5692\}\hfill{}\\

\textbf{BREAD.MEAL} Heb: {\large\H עריסה} {[}X{]} Def: Meaning dubious. \{Strong's: 6182\}\hfill{}\\

\textbf{BREAK (Verb)} Heb: {\large\H פרר} p.r.r Def: To throw something on the ground and break it by trampling. \{Strong's: 6565\}\hfill{}\\

\textbf{BREAK.DOWN (Verb)} Heb: {\large\H נתץ} n.t.ts Def: To demolish an elevated object; to tear down. \{Strong's: 5422\}\hfill{}\\

\textbf{BREAK.OUT (Verb)} Heb: {\large\H פרץ} p.r.ts Def: To be spread out wide or widespread. \{Strong's: 6555\}\hfill{}\\

\textbf{BREAST} Heb: {\large\H שד} shad Def: Milk-producing glandular organs situated on the chest in the female; the fore part of the body between the neck and the abdomen. Also a goat-idol from the teats of the goat. \{Strong's: 7699, 7700\}\hfill{}\\

\textbf{BREASTPLATE} Heb: {\large\H חושן} hho-shen Def: An ornamental plate worn by the High Priest that held stones representing the twelve tribes of Israel and the Urim and Thummim. \{Strong's: 2833\}\hfill{}\\

\textbf{BREATH} Heb: {\large\H נשמה} ne-shey-mah Def: Air inhaled or exhaled. The breath of man or god. The essence of life. \{Strong's: 5396, 5397\}\hfill{}\\

\textbf{BREATHE.DEEPLY (Verb)} Heb: {\large\H נפש} n.p.sh Def: To relax and breath in deeply to refresh oneself. To take a breather. \{Strong's: 5314\}\hfill{}\\

\textbf{BRIBE} Heb: {\large\H שחד} sha-hhad Def: To buy a favor or service that would be otherwise out of reach. \{Strong's: 7810\}\hfill{}\\

\textbf{BRICK} Heb: {\large\H לבנה} le-vey-nah Def: A building material typically rectangular and of moist clay hardened by heat. \{Strong's: 3840, 3843\}\hfill{}\\

\textbf{BRIDE.PRICE} Heb: {\large\H מוהר} mo-har Def: A payment given by or in behalf of a prospective husband to the bride's family. \{Strong's: 4119\}\hfill{}\\

\textbf{BRIGHT} Heb: {\large\H שפר} she-pher Def: A radiating or reflective light. As cheerful. \{Strong's: 8233\}\hfill{}\\

\textbf{BRIGHTNESS} Heb: {\large\H שיפרה} shiph-rah Def: Harmonized and in balance. Cheerful. \{Strong's: 8235\}\hfill{}\\

\textbf{BRIMSTONE} Heb: {\large\H גפרית} gaph-rit Def: A rock of sulfur that burns. \{Strong's: 1614\}\hfill{}\\

\textbf{BRING (Verb)} Heb: {\large\H יבל} y.b.l Def: {[}X{]} \{Strong's: 2986, 2987\}\hfill{}\\

\textbf{BRING.FORTH (Verb)} Heb: {\large\H ילד} y.l.d Def: To issue out; to bring forth children, either by the woman who bears them or the man who fathers them. The piel (intensive) form means ``act-as-midwife.'' \{Strong's: 3205\}\hfill{}\\

\textbf{BROKEN} Heb: {\large\H דכא} {[}X{]} Def: Something that is broken into pieces. \{Strong's: 1793\}\hfill{}\\

\textbf{BROODING} Heb: {\large\H דאבון} {[}X{]} Def: {[}X{]} \{Strong's: 1671\}\hfill{}\\

\textbf{BROTHER} Heb: {\large\H אח} ahh Def: A male who has the same parents as another or shares one parent with another. One who stands between the enemy and the family, a protector. \{Strong's: 251, 252, 1889\}\hfill{}\\

\textbf{BROTHER.IN.LAW} Heb: {\large\H יבם} {[}X{]} Def: {[}X{]} \{Strong's: 2993\}\hfill{}\\

\textbf{BROUGHT.OUT} Heb: {\large\H גרש} {[}X{]} Def: {[}X{]} \{Strong's: 1645\}\hfill{}\\

\textbf{BRUISER} Heb: {\large\H כית} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{BUCK} Heb: {\large\H איל} a-yil Def: The large males of a flock of sheep or heard of deer. By extension, anything of strength including a chief, pillar (as the strong support of a building), or oak tree (one of the strongest of the woods). \{Strong's: 352, 353, 354\}\hfill{}\\

\textbf{BUCKET} Heb: {\large\H דלי} {[}X{]} Def: Dangles from a rope to draw water and lifted out of the well. \{Strong's: 1805\}\hfill{}\\

\textbf{BUD} Heb: {\large\H פרח} pe-rahh Def: The beginning of a flower that bursts from the plant. \{Strong's: 6525\}\hfill{}\\

\textbf{BUDDING} Heb: {\large\H גיבעול} giv-ol Def: To sprout flowers or blooms. To come into a fullness. \{Strong's: 1392\}\hfill{}\\

\textbf{BUILD (Verb)} Heb: {\large\H בנה} b.n.h Def: To construct a building or home with wood, stone or other material or a family with sons. \{Strong's: 1124, 1129\}\hfill{}\\

\textbf{BUILD.UP (Verb)} Heb: {\large\H סלל} s.l.l Def: To raise the elevation of the bank of a river or a highway. To raise one up higher than others. \{Strong's: 5549\}\hfill{}\\

\textbf{BULK} Heb: {\large\H תועפה} {[}X{]} Def: {[}X{]} \{Strong's: 8443\}\hfill{}\\

\textbf{BULL} Heb: {\large\H פר} par Def: A large male un-castrated bovine. \{Strong's: 6499\}\hfill{}\\

\textbf{BULLOCK} Heb: {\large\H עגל} ey-gel Def: A young bull. Also, insinuating strength. \{Strong's: 5695\}\hfill{}\\

\textbf{BULRUSH} Heb: {\large\H גומא} go-me Def: A reed that grows in, or on the edge of, a pond or river. \{Strong's: 1573\}\hfill{}\\

\textbf{BUNCH} Heb: {\large\H אגודה} a-gu-dah Def: A group of men or things bound together. \{Strong's: 92\}\hfill{}\\

\textbf{BUNDLE (Verb)} Heb: {\large\H עמר} ah.m.r Def: {[}X{]} \{Strong's: 6014\}\hfill{}\\

\textbf{BURDEN} Heb: {\large\H סבלה} se-va-lah Def: The heavy load carried in bondage. \{Strong's: 5450\}\hfill{}\\

\textbf{BURIAL.PLACE} Heb: {\large\H קבורה} qe-vu-rah Def: The place of interment or deposit of a deceased body. \{Strong's: 6900\}\hfill{}\\

\textbf{BURN (Verb)} Heb: {\large\H בער} b.ah.r Def: To undergo rapid combustion or consume fuel in such a way as to give off heat, gases, and, usually, light; be on fire. \{Strong's: 1197\}\hfill{}\\

\textbf{BURN.BLACK (Verb)} Heb: {\large\H כמר} k.m.r Def: To char wood in a fire. A passion that burns for another. \{Strong's: 3648\}\hfill{}\\

\textbf{BURN.INCENSE (Verb)} Heb: {\large\H קטר} q.t.r Def: To light a sacrifice or aromatic plant on fire creating smoke, often aromatic. \{Strong's: 6999, 7000\}\hfill{}\\

\textbf{BURNING} Heb: {\large\H בערה} be-ey-rah Def: Something that is aflame with fire. \{Strong's: 1200\}\hfill{}\\

\textbf{BURNT} Heb: {\large\H גחם} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{BURNT.VALLEY} Heb: {\large\H געתם} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{BURST.OUT (Verb)} Heb: {\large\H פרח} p.r.hh Def: To be larger, fuller, or more crowded; to break out or break forth as a blooming flower or the wings of a bird. \{Strong's: 6524\}\hfill{}\\

\textbf{BURSTING} Heb: {\large\H פטר} pe-ter \textbf{\textbackslash{}} {\large\H פיטרה} {[}X{]} Def: A sudden and forceful release or issuing out. \{Strong's: 6363\}\hfill{}\\

\textbf{BURSTING.FORTH} Heb: {\large\H גיחון} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{BURY (Verb)} Heb: {\large\H קבר} q.b.r Def: To dispose of by depositing in the ground. \{Strong's: 6912\}\hfill{}\\

\textbf{BUSINESS} Heb: {\large\H מלאכה} me-la-khah Def: The principal occupation of one's life. A service. \{Strong's: 4399\}\hfill{}\\

\textbf{BUT} Heb: {\large\H אולם} u-lam Def: On the contrary. An outcome desired in the sense of joining. \{Strong's: 199\}\hfill{}\\

\textbf{BUTCHER (Verb)} Heb: {\large\H טבח} t.b.hh Def: One who slaughters animals or dresses their flesh. \{Strong's: 2873\}\hfill{}\\

\textbf{BUTTOCKS} Heb: {\large\H שת} {[}X{]} Def: As the place of sitting. \{Strong's: 8357\}\hfill{}\\

\textbf{BUTTRESS} Heb: {\large\H מקצוע} miq-tso-a Def: A support or prop. Wall or abutment built to support another wall on the outside, when very high or loaded with a heavy structure. \{Strong's: 4740\}\hfill{}\\

\textbf{BY} Heb: {\large\H עימד} i-mad Def: In proximity to. The sense of standing with another. \{Strong's: 5978\}\hfill{}\\

\textbf{CAKE} Heb: {\large\H דבלה} {[}X{]} Def: A cake of pressed figs. \{Strong's: 1690\}\hfill{}\\

\textbf{CALAMITY} Heb: {\large\H איד} eyd Def: A pile of rubble from a fire or other calamity. \{Strong's: 343\}\hfill{}\\

\textbf{CALCULATE (Verb)} Heb: {\large\H סכל} s.k.l Def: To determine by mathematical deduction or practical judgment; to comprehend and carefully consider a path or course of action. \{Strong's: 7919, 7920\}\hfill{}\\

\textbf{CALL.OUT (Verb)} Heb: {\large\H קרא} q.r.a Def: To raise one's voice or speak loudly and with urgency; to give, a name; to meet in the sense of being called to a meeting; to have an encounter by chance; to read in the sense of calling out words. \{Strong's: 7121, 7123\}\hfill{}\\

\textbf{CAMEL} Heb: {\large\H גמל} ga-mal Def: Either of two ruminant mammals used as draft animals in the desert. The produce of the fields were tied in large bundles and transported on camels. \{Strong's: 1581\}\hfill{}\\

\textbf{CAMP} Heb: {\large\H תחן} ta-han \textbf{\textbackslash{}} {\large\H תחנה} {[}X{]} Def: {[}X{]} \{Strong's: 8466\}\hfill{}\\

\textbf{CAMP (Verb)} Heb: {\large\H חנה} hh.n.h Def: To erect temporary shelters (as tents) together; to stop for the night and pitch the tents. \{Strong's: 2583\}\hfill{}\\

\textbf{CAMPSITE} Heb: {\large\H מחנה} me-hha-neh Def: A place suitable for or used as the location of a camp. The inhabitants of a camp. \{Strong's: 4264\}\hfill{}\\

\textbf{CANOPY} Heb: {\large\H מסך} ma-sak Def: The covering of a temporary shelter. \{Strong's: 4539\}\hfill{}\\

\textbf{CAPTAIN} Heb: {\large\H נשיא} na-si Def: A military leader; the commander of a unit or a body of troops. The leader of a family, tribe or people as one who carries the burdens of the people. \{Strong's: 5387\}\hfill{}\\

\textbf{CAPTIVE} Heb: {\large\H שבי} she-vi \textbf{\textbackslash{}} {\large\H שביה} {[}X{]} Def: A person who is enslaved or dominated. \{Strong's: 7628, 7633\}\hfill{}\\

\textbf{CAPTIVITY} Heb: {\large\H שבות} {[}X{]} Def: The state or period of being held, imprisoned, enslaved, or confined. \{Strong's: 7622\}\hfill{}\\

\textbf{CAPTURE (Verb)} Heb: {\large\H שבה} sh.b.h Def: The act of catching, winning, or gaining control by force, stratagem, or guile; to take one away from his homeland as an involuntary prisoner. \{Strong's: 7617\}\hfill{}\\

\textbf{CARAVAN} Heb: {\large\H אורחה} {[}X{]} Def: A traveling company that follows a prescribed path. \{Strong's: 735, 736\}\hfill{}\\

\textbf{CARNELIAN} Heb: {\large\H אודם} o-dem Def: Probably the Carnelian, a reddish brown gemstone. The Hebrew word is from a root meaning red or reddish. Another possible translation is Jasper. \{Strong's: 124\}\hfill{}\\

\textbf{CARRY (Verb)} Heb: {\large\H סבל} s.b.l Def: To transfer from one place to another; to transport as by vehicle. \{Strong's: 5445, 5446\}\hfill{}\\

\textbf{CART} Heb: {\large\H עגלה} a-ga-lah Def: A heavy, two-wheeled vehicle, animal-drawn, used for transporting freight or for farming. \{Strong's: 5699\}\hfill{}\\

\textbf{CARTILAGE} Heb: {\large\H גרם} ge-rem Def: Translucent elastic tissue that lines the joints of the bony skeleton. \{Strong's: 1634, 1635\}\hfill{}\\

\textbf{CARVE (Verb)} Heb: {\large\H חטב} hh.t.b Def: {[}X{]} \{Strong's: 2404\}\hfill{}\\

\textbf{CASSIA} Heb: {\large\H קידה} qi-dah Def: The tree, wood or spice which is used in anointing oils and perfumes. \{Strong's: 6916\}\hfill{}\\

\textbf{CAST.AWAY (Verb)} Heb: {\large\H געל} g.ah.l Def: {[}X{]} \{Strong's: 1602\}\hfill{}\\

\textbf{CAST.DOWN (Verb)} Heb: {\large\H הרס} h.r.s Def: To ruin or break into pieces by throwing or pulling down. \{Strong's: 2040\}\hfill{}\\

\textbf{CAST.IMAGE} Heb: {\large\H מסכה} ma-sey-khah Def: A molten metal that is poured in a cast to form images. \{Strong's: 4541\}\hfill{}\\

\textbf{CAST.OFF (Verb)} Heb: {\large\H נשל} n.sh.l Def: To remove with force and intention. \{Strong's: 5394\}\hfill{}\\

\textbf{CAST.OUT (Verb)} Heb: {\large\H גרש} g.r.sh Def: To drive out, expel, thrust away. \{Strong's: 1644\}\hfill{}\\

\textbf{CATARACT} Heb: {\large\H תבלול} {[}X{]} Def: The clouding color of the eyes that appear as a mixture. \{Strong's: 8400\}\hfill{}\\

\textbf{CATTLE} Heb: {\large\H בקר} ba-qar Def: Domesticated bovine animals. Strong beasts used to break the soil with plows. \{Strong's: 1165, 1241\}\hfill{}\\

\textbf{CAULDRON} Heb: {\large\H כיור} ki-or Def: A large kettle or boiler, of copper or other metal. A smelting pot. \{Strong's: 3595\}\hfill{}\\

\textbf{CAUSING.TO.OVERLOOK} Heb: {\large\H מנשה} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{CAVE} Heb: {\large\H מכרה} me-khey-rah Def: A natural underground chamber or series of chambers that open to the surface. A hole in the rock. \{Strong's: 4380, 4631\}\hfill{}\\

\textbf{CEASE (Verb)} Heb: {\large\H שבת} sh.b.t Def: To come to an end; to die out; to stop an activity for the purpose of rest or celebration. \{Strong's: 7673\}\hfill{}\\

\textbf{CEASING} Heb: {\large\H שבת} sha-bat Def: A stopping of work or activity; An activity curtailed before completion. The seventh day of the week (often translated as Sabbath) when all business ceases for rest and celebration. \{Strong's: 7674, 7676\}\hfill{}\\

\textbf{CEDAR} Heb: {\large\H ארז} {[}X{]} Def: A coniferous tree from the cyprus family having wide, spreading branches. The wood or tree or something made it. \{Strong's: 730\}\hfill{}\\

\textbf{CENTER} Heb: {\large\H חצות} hha-tsot Def: The middle of something. \{Strong's: 2676\}\hfill{}\\

\textbf{CEREAL} Heb: {\large\H דגן} da-gan Def: Relating to grain or plants that produce it. A plentiful crop. \{Strong's: 1715\}\hfill{}\\

\textbf{CHAIN} Heb: {\large\H שרשרה} shar-she-rah Def: A strand of linked metal loops. \{Strong's: 8331, 8333\}\hfill{}\\

\textbf{CHAMBER} Heb: {\large\H חדר} hhe-der Def: A bedroom; a natural or artificial enclosed space or cavity. Place surrounded by walls. An inner place as hidden or secret. \{Strong's: 2315\}\hfill{}\\

\textbf{CHANGE (Verb)} Heb: {\large\H שנה} sh.n.h Def: To make different in some particular; to make radically different; exchange one thing for another. To repeat in the sense of a second time. \{Strong's: 8132, 8133, 8138\}\hfill{}\\

\textbf{CHARGE} Heb: {\large\H משמרת} mish-me-ret Def: A person or thing committed to the care of another. What is given to be watched over and protected. \{Strong's: 4931\}\hfill{}\\

\textbf{CHARIOT} Heb: {\large\H מרכבה} mer-ka-vah Def: A light, two-wheeled battle vehicle for one or two persons, usually drawn by two horses and driven from a standing position. \{Strong's: 4818\}\hfill{}\\

\textbf{CHEESE} Heb: {\large\H חמאה} hhem-ah Def: A food consisting of the coagulated, compressed and usually ripened curd of milk separated from the whey. \{Strong's: 2529\}\hfill{}\\

\textbf{CHERISH (Verb)} Heb: {\large\H חבב} hh.b.b Def: {[}X{]} \{Strong's: 2245\}\hfill{}\\

\textbf{CHERISHED} Heb: {\large\H ידיד} {[}X{]} Def: One who is loved. \{Strong's: 3039\}\hfill{}\\

\textbf{CHEST} Heb: {\large\H חזה} hha-zeh Def: The breast containing heart. What is prominently visible. The breast of an animal used for a sacrifice. \{Strong's: 2373\}\hfill{}\\

\textbf{CHESTNUT} Heb: {\large\H ערמון} er-mon Def: Probably the chestnut tree but uncertain. \{Strong's: 6196\}\hfill{}\\

\textbf{CHEW (Verb)} Heb: {\large\H גרר} g.r.r Def: {[}X{]} \{Strong's: 1641\}\hfill{}\\

\textbf{CHEWED} Heb: {\large\H גרר} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{CHICK} Heb: {\large\H אפרח} {[}X{]} Def: A young bird that has burst out of the egg. \{Strong's: 667\}\hfill{}\\

\textbf{CHIEF} Heb: {\large\H אלוף} a-luph Def: Accorded highest rank or office; of greatest importance, significance, or influence. The military commander of a thousand men. One who is yoked to another to lead and teach. \{Strong's: 441\}\hfill{}\\

\textbf{CHILD} Heb: {\large\H ולד} wa-lad Def: A young person, especially between infancy and youth. \{Strong's: 2056\}\hfill{}\\

\textbf{CHILD.OF.THE.SUN} Heb: {\large\H רעמסס} ra-me-seys Def: A word of Egyptian origins. \{Strong's: n/a\}\hfill{}\\

\textbf{CHILDREN} Heb: {\large\H טף} taph Def: The offspring of the parent or descendents of a patron. More than one child. \{Strong's: 2945\}\hfill{}\\

\textbf{CHIMNEY} Heb: {\large\H ארובה} a-ru-bah Def: A vertical structure in a building and enclosing a flue or flues that carry off smoke. A hole in the roof where smoke escapes. \{Strong's: 699\}\hfill{}\\

\textbf{CHOICE.FRUIT} Heb: {\large\H זימרה} zim-rah Def: Having qualities that appeal to a cultivated taste. As plucked from the tree or vine. \{Strong's: 2173\}\hfill{}\\

\textbf{CHOICE.VINE} Heb: {\large\H סורק} so-reyq \textbf{\textbackslash{}} {\large\H סורקה} {[}X{]} Def: The best of the vine, the best grapes. \{Strong's: 8321\}\hfill{}\\

\textbf{CHOICE.VINEYARD} Heb: {\large\H מסרקה} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{CHOOSE (Verb)} Heb: {\large\H בחר} b.hh.r Def: To select freely and after consideration. \{Strong's: 977\}\hfill{}\\

\textbf{CHOSEN} Heb: {\large\H מבחר} miv-hhar Def: One who is the object of choice or of divine favor. \{Strong's: 4005\}\hfill{}\\

\textbf{CINNAMON} Heb: {\large\H קנמון} qi-na-mon Def: A spice from the bark of a small evergreen tree. The essential oil is of great price. \{Strong's: 7076\}\hfill{}\\

\textbf{CIRCUIT} Heb: {\large\H תקופה} te-qu-phah Def: A going around in a circle. To return to a starting point in the sense of going full circle. \{Strong's: 8622\}\hfill{}\\

\textbf{CIRCUMCISION} Heb: {\large\H מולה} mu-lah Def: The removal of the front part of the male sexual organ. \{Strong's: 4139\}\hfill{}\\

\textbf{CISTERN} Heb: {\large\H כור} kor Def: An artificial reservoir for storing water. A hole or well as dug out. \{Strong's: 953, 2352, 2356, 3564\}\hfill{}\\

\textbf{CITY} Heb: {\large\H עיר} ir Def: An inhabited place of greater size, population, or importance than a town or village. Usually protected by a wall. \{Strong's: 5892\}\hfill{}\\

\textbf{CITY.OF.JUSTICE} Heb: {\large\H פיתום} pi-tom Def: A word of Egyptian origins. \{Strong's: n/a\}\hfill{}\\

\textbf{CLAN} Heb: {\large\H משפחה} mish-pa-hhah Def: A group of persons of common ancestry. A group of people joined together by certain convictions or common affiliation. \{Strong's: 4940\}\hfill{}\\

\textbf{CLASP (Verb)} Heb: {\large\H ספק} s.p.q Def: {[}X{]} \{Strong's: 5606\}\hfill{}\\

\textbf{CLAYEY.SOIL} Heb: {\large\H גש} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{CLEANLINESS} Heb: {\large\H טוהר} to-har Def: The act of being free from dirt or immorality. Free from foreign elements. \{Strong's: 2892\}\hfill{}\\

\textbf{CLEANSING} Heb: {\large\H טהרה} {[}X{]} Def: {[}X{]} \{Strong's: 2893\}\hfill{}\\

\textbf{CLEAVE (Verb)} Heb: {\large\H פרס} p.r.s Def: To split in two as the hoofs of a clean animal. \{Strong's: 6536, 6537\}\hfill{}\\

\textbf{CLEAVE.IN.TWO (Verb)} Heb: {\large\H שסע} sh.s.ah Def: {[}X{]} \{Strong's: 8156\}\hfill{}\\

\textbf{CLEAVE.OPEN (Verb)} Heb: {\large\H בקע} b.q.ah Def: To divide by or as if by a cutting blow; to separate into distinct parts; to break, cut or divide something in half. \{Strong's: 1234\}\hfill{}\\

\textbf{CLEFT} Heb: {\large\H פיסגה} pis-gah Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{CLIFF} Heb: {\large\H סלע} {[}X{]} Def: A high rock, cliff or towering rock, as a place of defense. \{Strong's: 5553\}\hfill{}\\

\textbf{CLING (Verb)} Heb: {\large\H בטח} b.t.hh Def: To grab hold of someone or something that is secure and safe. \{Strong's: 982\}\hfill{}\\

\textbf{CLOAK} Heb: {\large\H מעיל} me-il Def: A loose outer garment worn over other clothes both by men and women. \{Strong's: 4598\}\hfill{}\\

\textbf{CLOD (Verb)} Heb: {\large\H רגב} r.g.b Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{CLOSE (Verb)} Heb: {\large\H קפץ} q.p.ts Def: To draw together to close or shut. \{Strong's: 7092\}\hfill{}\\

\textbf{CLOTHING} Heb: {\large\H לבוש} le-vush Def: Garments in general. \{Strong's: 3830, 3831\}\hfill{}\\

\textbf{CLOUD} Heb: {\large\H ענן} a-nan \textbf{\textbackslash{}} {\large\H עננה} {[}X{]} Def: A visible mass of particles of water or ice in the form of fog, mist, or haze suspended usually at a considerable height in the air. \{Strong's: 6050, 6051, 6053\}\hfill{}\\

\textbf{CLUSTER} Heb: {\large\H אשכול} esh-kol Def: A number of similar things growing together or of things or persons collected or grouped closely together. A cluster of grapes from the vine or flowers from the plant. \{Strong's: 811\}\hfill{}\\

\textbf{COAL} Heb: {\large\H שחור} {[}X{]} Def: The dim light before the rising of the sun. As dark in color. \{Strong's: 7838, 7815\}\hfill{}\\

\textbf{COAT} Heb: {\large\H סות} sut Def: An outer garment varying in length and style; the external growth on an animal. \{Strong's: 5497\}\hfill{}\\

\textbf{COHABITATION} Heb: {\large\H עון} on \textbf{\textbackslash{}} {\large\H עונה} o-nah Def: A place of residence. An abode. \{Strong's: 5772\}\hfill{}\\

\textbf{COLD} Heb: {\large\H קר} qar Def: A condition of low temperature. \{Strong's: 7119, 7120\}\hfill{}\\

\textbf{COLLAR} Heb: {\large\H תחרא} tahh-ra Def: The hole in the middle of a rectangular garment for the head to pass through. An area reinforced around the neck opening. \{Strong's: 8473\}\hfill{}\\

\textbf{COLLECT (Verb)} Heb: {\large\H קשש} q.sh.sh Def: To gather up straw, stubble or sticks. \{Strong's: 7197\}\hfill{}\\

\textbf{COLLECTION} Heb: {\large\H מקוה} miq-weh Def: An accumulation of objects or material. A collection of water (a pool, pond or sea) or horses (herd). \{Strong's: 4723\}\hfill{}\\

\textbf{COLT} Heb: {\large\H עייר} ai-yir Def: A young male horse; a young untried person. As dark in color. \{Strong's: 5895\}\hfill{}\\

\textbf{COME (Verb)} Heb: {\large\H בוא} b.w.a Def: To move toward something; approach; enter. This can be understood as to come or to go. The hiphil (causative) form means ``bring.'' \{Strong's: 935\}\hfill{}\\

\textbf{COME.NEAR (Verb)} Heb: {\large\H קרב} q.r.b Def: To come close by or near to. \{Strong's: 7126, 7127\}\hfill{}\\

\textbf{COME.TO.AN.END (Verb)} Heb: {\large\H אפס} a.p.s Def: To cease. Conclude. \{Strong's: 656\}\hfill{}\\

\textbf{COME.UP (Verb)} Heb: {\large\H זרח} z.r.hh Def: To rise up, as the sun does at the horizon. \{Strong's: 2224\}\hfill{}\\

\textbf{COMFORT (Verb)} Heb: {\large\H נחם} n.hh.m Def: Consolation in time of trouble or worry; to give solace in time of difficulty or sorrow. The niphal (passive) form means ``repent.'' \{Strong's: 5162\}\hfill{}\\

\textbf{COMMIT (Verb)} Heb: {\large\H מסר} m.s.r Def: {[}X{]} \{Strong's: 4560\}\hfill{}\\

\textbf{COMMIT.ADULTERY (Verb)} Heb: {\large\H נאף} n.a.p Def: To perform voluntary violation of the marriage bed. \{Strong's: 5003\}\hfill{}\\

\textbf{COMMUNITY} Heb: {\large\H לאום} la-um Def: A unified body of individuals; a group of people bound together. \{Strong's: 3816\}\hfill{}\\

\textbf{COMPANION} Heb: {\large\H רע} ra Def: One that accompanies another in the sense of a close companion or friend. \{Strong's: 7453\}\hfill{}\\

\textbf{COMPANY} Heb: {\large\H עדה} ey-dah Def: A group of persons or things for carrying on a project or undertaking; a group with a common testimony. May also mean a witness or testimony. \{Strong's: 5712, 5713\}\hfill{}\\

\textbf{COMPARE (Verb)} Heb: {\large\H סלא} s.l.a Def: {[}X{]} \{Strong's: 5537\}\hfill{}\\

\textbf{COMPARISON} Heb: {\large\H משל} {[}X{]} Def: An illustration of similitude. Often a parable or proverb as a story of comparisons. \{Strong's: 4912\}\hfill{}\\

\textbf{COMPASSIONATE} Heb: {\large\H רחום} ra-hhum Def: Being sympathetic, and understanding. A protecting from harm. \{Strong's: 7349\}\hfill{}\\

\textbf{COMPEL (Verb)} Heb: {\large\H אוץ} a.w.ts Def: To drive or urge forcefully or irresistibly. A pressing into an action or narrow place. \{Strong's: 213\}\hfill{}\\

\textbf{COMPLAIN (Verb)} Heb: {\large\H אנן} a.n.n Def: {[}X{]} \{Strong's: 596\}\hfill{}\\

\textbf{COMPLAINER} Heb: {\large\H אונן} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{COMPLETE} Heb: {\large\H שלם} she-lem \textbf{\textbackslash{}} {\large\H שלמה} she-ley-mah Def: Having all necessary parts, elements or steps. A state of being whole or full. Left unaltered and whole in its original functional state without removing or adding to it. To finish. A sacrifice or offering given to bring about peace. \{Strong's: 8001, 8002, 8003\}\hfill{}\\

\textbf{COMPLETENESS} Heb: {\large\H שלום} sha-lom Def: Something that has been finished or made whole. A state of being complete. \{Strong's: 7965\}\hfill{}\\

\textbf{COMPLETION} Heb: {\large\H כלה} ka-lah Def: The act or process of completing. This can be in a positive sense or negative, such as in a failure. \{Strong's: 3617\}\hfill{}\\

\textbf{COMPOUND (Verb)} Heb: {\large\H רקח} r.q.hh Def: The combining of two or more ingredients to achieve the desired substance. \{Strong's: 7543\}\hfill{}\\

\textbf{CONCEAL (Verb)} Heb: {\large\H צפן} ts.p.n Def: To hide to prevent discovery. \{Strong's: 6845\}\hfill{}\\

\textbf{CONCEIVE (Verb)} Heb: {\large\H הרה} h.r.h Def: To become pregnant with young. \{Strong's: 2029\}\hfill{}\\

\textbf{CONCERNING} Heb: {\large\H אודות} o-dot Def: Regarding. Marked interest or regard usually arising through a personal tie or relationship. A turning over and bringing together of a thought. \{Strong's: 182\}\hfill{}\\

\textbf{CONCLUDED} Heb: {\large\H גומר} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{CONCLUSION} Heb: {\large\H קץ} qeyts Def: To come to an end. The end of a time period or place or the end of something. The border of a country as its edges. \{Strong's: 7093\}\hfill{}\\

\textbf{CONCUBINE} Heb: {\large\H פילגש} {[}X{]} Def: Cohabitation of persons not legally married; a woman living in a socially recognized state of being a mistress. \{Strong's: 6370\}\hfill{}\\

\textbf{CONFERENCE} Heb: {\large\H עצרה} {[}X{]} Def: A special occasion as a temporary ceasing of normal activity. \{Strong's: 6116\}\hfill{}\\

\textbf{CONFIDENCE} Heb: {\large\H סוד} sod Def: Advice given in secret as a result of consultation. \{Strong's: 5475\}\hfill{}\\

\textbf{CONFIDENT (Verb)} Heb: {\large\H כסל} k.s.l Def: Always used in a negative sense such as foolish confidence. \{Strong's: 3688, 5528\}\hfill{}\\

\textbf{CONFIDENT.ONE} Heb: {\large\H כיסלון} kis-lon Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{CONFUSE (Verb)} Heb: {\large\H המם} h.m.m Def: To cause trouble and confusion through a great noise such as with trumpets. \{Strong's: 2000\}\hfill{}\\

\textbf{CONFUSED} Heb: {\large\H הימם} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{CONFUSION} Heb: {\large\H תוהו} to-hu Def: To bring to ruin; to make indistinct; to fail to differentiate from an often similar or related other. A barren place. Vanity as a state of waste. \{Strong's: 8414\}\hfill{}\\

\textbf{CONJURE (Verb)} Heb: {\large\H ענן} ah.n.n Def: To call or bring into existence. \{Strong's: 6049\}\hfill{}\\

\textbf{CONSENT (Verb)} Heb: {\large\H אבה} a.b.h Def: To give approval; to be in concord in opinion or sentiment; agreement as to action or opinion; to be willing to go somewhere or do something. \{Strong's: 14\}\hfill{}\\

\textbf{CONSISTENCY} Heb: {\large\H איתן} ey-tan Def: Agreement or harmony of parts or features; showing steady conformity to character, profession, belief, or custom. \{Strong's: 386\}\hfill{}\\

\textbf{CONSORT (Verb)} Heb: {\large\H חרף} hh.r.p Def: To pierce another with sharp words of reproach or scorn. (see Psalms 42:10). A nose ring is put in the piercing of the nose as a sign of betrothal (see Genesis 24:47). \{Strong's: 2778\}\hfill{}\\

\textbf{CONSUME (Verb)} Heb: {\large\H ספה} s.p.h Def: To eat or drink; with the lips. \{Strong's: 5595\}\hfill{}\\

\textbf{CONSUMPTION} Heb: {\large\H שחפת} {[}X{]} Def: A disease making one thin. \{Strong's: 7829\}\hfill{}\\

\textbf{CONTENTION} Heb: {\large\H מריבה} me-ri-vah Def: An act or instance of striving or struggling against great difficulty or opposition. \{Strong's: 4808\}\hfill{}\\

\textbf{CONTINUALLY} Heb: {\large\H תמיד} ta-mid Def: Happening without interruption or cessation; continuous in time. \{Strong's: 8548\}\hfill{}\\

\textbf{CONTINUE} Heb: {\large\H נון} nun Def: Maintain the action, to forge ahead with intention. \{Strong's: n/a\}\hfill{}\\

\textbf{CONTINUOUS} Heb: {\large\H מטרד} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{CONTRARY} Heb: {\large\H קרי} {[}X{]} Def: An opposition. \{Strong's: 7147\}\hfill{}\\

\textbf{CONTRIBUTION} Heb: {\large\H מתנה} mat-nah Def: What is given or supplied in common with others. \{Strong's: 4978, 4979\}\hfill{}\\

\textbf{CONVERT (Verb)} Heb: {\large\H מור} m.w.r Def: {[}X{]} \{Strong's: 4171\}\hfill{}\\

\textbf{CONVICT (Verb)} Heb: {\large\H יכח} y.k.hh Def: To find or prove to be guilty. \{Strong's: 3198\}\hfill{}\\

\textbf{COOKED} Heb: {\large\H תאופין} {[}X{]} Def: Something baked. \{Strong's: 8601\}\hfill{}\\

\textbf{COPPER} Heb: {\large\H נחושת} ne-hho-shet Def: A malleable, ductile, metallic element having a characteristic reddish-brown color. A precious metal. \{Strong's: 5178\}\hfill{}\\

\textbf{COPULATE (Verb)} Heb: {\large\H שגל} sh.g.l Def: {[}X{]} \{Strong's: 7693\}\hfill{}\\

\textbf{COPULATION} Heb: {\large\H שכובת} {[}X{]} Def: {[}X{]} \{Strong's: 7903\}\hfill{}\\

\textbf{CORAL} Heb: {\large\H ראמה} {[}X{]} Def: Lifted up as a highly prized item. \{Strong's: 7215\}\hfill{}\\

\textbf{CORD} Heb: {\large\H פתיל} pa-til Def: A long slender flexible material made of several strands woven or twisted together. Made of twisted fibers. \{Strong's: 6616\}\hfill{}\\

\textbf{CORIANDER} Heb: {\large\H גד} gad Def: A class of plants with seeds which are in the form of the size of a peppercorn. They are used medicinally and as a spice. Likened to the manna in its form and color. \{Strong's: 1407\}\hfill{}\\

\textbf{CORNER} Heb: {\large\H פינה} pin-nah Def: The point where two lines meet. \{Strong's: 6438\}\hfill{}\\

\textbf{CORNER.POST} Heb: {\large\H מקוצעה} me-quts-ah Def: The strongest point from where the rest of the structure is built from. As scraped out with a plane. \{Strong's: 4742\}\hfill{}\\

\textbf{CORPSE} Heb: {\large\H פגר} pe-ger Def: A dead body. \{Strong's: 6297\}\hfill{}\\

\textbf{CORRECT (Verb)} Heb: {\large\H יסר} y.s.r Def: To make a preferred change in direction through instruction or chastisement. \{Strong's: 3256\}\hfill{}\\

\textbf{COUCH} Heb: {\large\H יצוע} ya-tsu-a Def: An article of furniture for sitting or reclining. \{Strong's: 3326\}\hfill{}\\

\textbf{COUNSEL} Heb: {\large\H עצה} {[}X{]} Def: Advice given in the sense of being the firm support of the community. \{Strong's: 5843, 6098\}\hfill{}\\

\textbf{COUNT (Verb)} Heb: {\large\H ספר} s.p.r Def: To find the total number of units. Also to give an account on record. The piel (intensive) form means ``recount.'' \{Strong's: 5608\}\hfill{}\\

\textbf{COUNTRY.OF.TWO.RIVERS} Heb: {\large\H שינער} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{COUPLE} Heb: {\large\H חבר} {[}X{]} Def: A group bound together. \{Strong's: 2267, 2269, 2270, 2271\}\hfill{}\\

\textbf{COUPLE (Verb)} Heb: {\large\H חבר} hh.b.r Def: To bind by joining or coupling together. \{Strong's: 2266\}\hfill{}\\

\textbf{COUPLING} Heb: {\large\H חוברת} hho-be-ret Def: To bring together as a unit. \{Strong's: 2279\}\hfill{}\\

\textbf{COURAGEOUS} Heb: {\large\H גיבור} gi-bor Def: Having or characterized by mental or moral strength to venture, persevere, and withstand danger, fear or difficulty. \{Strong's: 1368\}\hfill{}\\

\textbf{COURTYARD} Heb: {\large\H חצר} hha-tser Def: The grounds of a building or group of buildings. Villages outside of the larger cities, as ``the yard of the city. '' A courtyard as outside the house. \{Strong's: 2691\}\hfill{}\\

\textbf{COVENANT} Heb: {\large\H ברית} be-rit Def: A solemn and binding agreement between two or more parties especially for the performance of some action. Often instituted through a sacrifice. \{Strong's: 1285\}\hfill{}\\

\textbf{COVER (Verb)} Heb: {\large\H כפר} k.p.r Def: To afford protection or security; to hide from sight or knowledge; to cover over as with a lid. \{Strong's: 3722\}\hfill{}\\

\textbf{COVER.OVER (Verb)} Heb: {\large\H כסה} k.s.h Def: To prevent disclosure or recognition of; to place out of sight; to completely cover over or hide. \{Strong's: 3680, 3780\}\hfill{}\\

\textbf{COVERING} Heb: {\large\H כופר} ko-pher Def: Something that covers or conceals. A covering such as pitch or a monetary covering such as a bribe or ransom. A ``village'' as a covering. \{Strong's: 3723, 3724\}\hfill{}\\

\textbf{COW} Heb: {\large\H פרה} pa-rah Def: The mature female of cattle. \{Strong's: 6510\}\hfill{}\\

\textbf{CRACK (Verb)} Heb: {\large\H שבר} sh.b.r Def: To break open, apart or into pieces. The piel (intensive) form means ``shatter.'' \{Strong's: 7665, 8406\}\hfill{}\\

\textbf{CRACK.OPEN} Heb: {\large\H לשע} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{CRAFTINESS} Heb: {\large\H נכל} {[}X{]} Def: {[}X{]} \{Strong's: 5231\}\hfill{}\\

\textbf{CRAFTSMAN} Heb: {\large\H חורש} {[}X{]} Def: One who engraves wood, stone or metal. \{Strong's: 2794\}\hfill{}\\

\textbf{CRASH (Verb)} Heb: {\large\H שאה} sh.a.h Def: To break violently and noisily. \{Strong's: 7582, 7583\}\hfill{}\\

\textbf{CRAVE (Verb)} Heb: {\large\H חמד} hh.m.d Def: To have a strong or inward desire for something. \{Strong's: 2530\}\hfill{}\\

\textbf{CRAVING (Verb)} Heb: {\large\H כסף} k.s.p Def: A great desire or longing. \{Strong's: 3700\}\hfill{}\\

\textbf{CREEK} Heb: {\large\H יובל} {[}X{]} Def: A flowing body of water. \{Strong's: 3105\}\hfill{}\\

\textbf{CREMATE (Verb)} Heb: {\large\H סרף} s.r.p Def: To reduce a dead body, or other object, to ashes by burning. \{Strong's: 5635, 8313\}\hfill{}\\

\textbf{CREMATING} Heb: {\large\H סרפה} se-rey-phah Def: The act of burning a dead body to ashes. \{Strong's: 8316\}\hfill{}\\

\textbf{CROCODILE} Heb: {\large\H תנין} ta-nin Def: A large creature that lives in the water (see Genesis 1:21) and the land (see Psalm 91:13). \{Strong's: 8565, 8577\}\hfill{}\\

\textbf{CROOKED} Heb: {\large\H עיקש} {[}X{]} Def: {[}X{]} \{Strong's: 6141\}\hfill{}\\

\textbf{CROP} Heb: {\large\H מוראה} {[}X{]} Def: What is closely watched for harvest time. \{Strong's: 4760\}\hfill{}\\

\textbf{CROP.OFF (Verb)} Heb: {\large\H קטף} q.t.p Def: {[}X{]} \{Strong's: 6998\}\hfill{}\\

\textbf{CROPLAND} Heb: {\large\H שדמה} she-dey-mah Def: A level field for growing crops. \{Strong's: 7709, 8309\}\hfill{}\\

\textbf{CROSS.OVER (Verb)} Heb: {\large\H עבר} ah.b.r Def: To pass from one side to the other; to go across a river or through a land; to transgress in the sense of crossing over. \{Strong's: 5668, 5674, 5675\}\hfill{}\\

\textbf{CROSSING} Heb: {\large\H מעבר} ma-a-var Def: A place or structure as on a street or over a river where pedestrians or vehicles pass from one side to the other. In the river for crossing. \{Strong's: 4569\}\hfill{}\\

\textbf{CROSSING.ONE} Heb: {\large\H עברון} ev-ron \textbf{\textbackslash{}} {\large\H עברונה} ev-ro-nah Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{CROWN} Heb: {\large\H נזר} ne-zer Def: An object showing Kingship or authority. Also, a sign upon the head as a sign of dedication. \{Strong's: 5145\}\hfill{}\\

\textbf{CRUEL} Heb: {\large\H אכזר} {[}X{]} Def: {[}X{]} \{Strong's: 393\}\hfill{}\\

\textbf{CRUMBLE (Verb)} Heb: {\large\H פתת} p.t.t Def: {[}X{]} \{Strong's: 6626\}\hfill{}\\

\textbf{CRUMBLED} Heb: {\large\H מרוח} {[}X{]} Def: In the sense of being rubbed. Meaning dubious. \{Strong's: 4790\}\hfill{}\\

\textbf{CRUSH (Verb)} Heb: {\large\H רצץ} r.ts.ts Def: To reduce to particles by pounding or grinding. Crush something to pieces. An oppression or struggle as crushing. \{Strong's: 7465, 7533, 7567\}\hfill{}\\

\textbf{CRUSHED} Heb: {\large\H מנכה} {[}X{]} Def: Pressed or squeezed with a force that destroys or deforms. Also a plague. \{Strong's: 4347\}\hfill{}\\

\textbf{CRY} Heb: {\large\H צעקה} tse-a-qah Def: To utter loudly; to shout; to shed tears, often noisily. A loud crying or calling out. \{Strong's: 6818\}\hfill{}\\

\textbf{CRY.OUT (Verb)} Heb: {\large\H צעק} ts.ah.q Def: To cry or call out loudly. \{Strong's: 6817\}\hfill{}\\

\textbf{CRYING} Heb: {\large\H אנקה} {[}X{]} Def: {[}X{]} \{Strong's: 603\}\hfill{}\\

\textbf{CUCUMBER} Heb: {\large\H קשוא} {[}X{]} Def: A hard vegetable. \{Strong's: 7180\}\hfill{}\\

\textbf{CUD} Heb: {\large\H גרה} ge-rah Def: The chewing of the cud by clean animals. \{Strong's: 1625\}\hfill{}\\

\textbf{CUP} Heb: {\large\H כוס} kos Def: A vessel for holding liquids, usually for drinking. \{Strong's: 3563\}\hfill{}\\

\textbf{CUPPED.HAND} Heb: {\large\H חופן} hho-phen Def: The cup shape of the palm. \{Strong's: 2651\}\hfill{}\\

\textbf{CURDLE (Verb)} Heb: {\large\H קפא} q.p.a Def: To change into curd; coagulate; congeal. To spoil; turn sour. \{Strong's: 7087\}\hfill{}\\

\textbf{CUSTODY} Heb: {\large\H משמר} mish-mar Def: Immediate charge and control exercised by a person or authority. A careful watching over as an office, guard or prison. \{Strong's: 4929\}\hfill{}\\

\textbf{CUSTOM} Heb: {\large\H חוק} hhuq \textbf{\textbackslash{}} {\large\H חוקה} hhu-qah Def: A usage or practice common to many or to a particular place or class or habitual with an individual. \{Strong's: 2706, 2708\}\hfill{}\\

\textbf{CUT (Verb)} Heb: {\large\H כרת} k.r.t Def: To penetrate with a sharp edged instrument. \{Strong's: 3772\}\hfill{}\\

\textbf{CUT.DOWN (Verb)} Heb: {\large\H גדע} g.d.ah Def: {[}X{]} \{Strong's: 1438\}\hfill{}\\

\textbf{CUT.IN.TWO (Verb)} Heb: {\large\H בתר} b.t.r Def: To sever into two pieces or parts. \{Strong's: 1334\}\hfill{}\\

\textbf{CUT.OFF (Verb)} Heb: {\large\H נמל} n.m.l Def: To discontinue or terminate. To sever the tip or end. \{Strong's: 5243\}\hfill{}\\

\textbf{CUT.PIECE} Heb: {\large\H בתר} be-ter Def: A sacrificial animal that has been cut into pieces. \{Strong's: 1335\}\hfill{}\\

\textbf{CUT.SHARPLY (Verb)} Heb: {\large\H חרץ} hh.r.ts Def: To divide or slice with a sharp instrument such as a potsherd or iron blade. To make a decision in the sense of dividing between two choices. To be diligent in the sense of a sharp action. \{Strong's: 2742, 2782\}\hfill{}\\

\textbf{CUT.THE.TAIL (Verb)} Heb: {\large\H זנב} z.n.b Def: To slap, strike or attack the rear. \{Strong's: 2179\}\hfill{}\\

\textbf{CUTTING} Heb: {\large\H גרן} ge-rez Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{CYMBAL} Heb: {\large\H זילזל} {[}X{]} Def: An instrument that vibrates when shaken. \{Strong's: 6767\}\hfill{}\\

\textbf{DA'AH} Heb: {\large\H דאה} {[}X{]} Def: An unknown bird of prey. \{Strong's: 1676\}\hfill{}\\

\textbf{DAMAGE (Verb)} Heb: {\large\H שחת} sh.hh.t Def: To bring to ruin by destruction; to destroy through disfigurement or corruption. \{Strong's: 7843, 7844\}\hfill{}\\

\textbf{DAMAGING} Heb: {\large\H משחית} mash-hhit Def: To completely destroy with force. To tear or bring down. \{Strong's: 4889\}\hfill{}\\

\textbf{DANCE} Heb: {\large\H מחולה} me-hho-lah Def: Twisting, skipping, or leaping with joy. To rejoice in expression of thanksgiving for religious worship or festivity. \{Strong's: 4246\}\hfill{}\\

\textbf{DANCING.AROUND} Heb: {\large\H גיל} {[}X{]} Def: A circle of rejoicing. \{Strong's: 1524\}\hfill{}\\

\textbf{DARK} Heb: {\large\H חשכה} hha-shey-khah Def: Devoid or partially devoid of light; not receiving, reflecting, transmitting, producing or radiating light. As the darkness of a moonless night. \{Strong's: 2824, 2825\}\hfill{}\\

\textbf{DARKEN (Verb)} Heb: {\large\H חשך} hh.sh.k Def: To be deprived of light. To be dark as night. \{Strong's: 2821\}\hfill{}\\

\textbf{DARKNESS} Heb: {\large\H חושך} hho-shekh Def: The state of being dark. As the darkness of a moonless night. \{Strong's: 2822\}\hfill{}\\

\textbf{DASH.TO.PIECES (Verb)} Heb: {\large\H רעץ} r.ah.ts Def: To shatter into pieces by force. \{Strong's: 7492\}\hfill{}\\

\textbf{DATE.PALM} Heb: {\large\H תמר} ta-mar Def: The tree that produces the date. An erect tree as a pillar. \{Strong's: 8558\}\hfill{}\\

\textbf{DAUGHTER} Heb: {\large\H בת} bat Def: A female having the relation of a child to parent. A village that resides outside of the city walls; as ``the daughter of the city.'' \{Strong's: 1323\}\hfill{}\\

\textbf{DAUGHTER.IN.LAW} Heb: {\large\H כללה} kal-lah Def: The wife of one’s son. Bride of the son, as brought into the camp, in the sense of making the man complete. \{Strong's: 3618\}\hfill{}\\

\textbf{DAWN} Heb: {\large\H שחר} sha-hhar Def: To begin to grow light as the sun rises in the east. The place of the rising sun. \{Strong's: 7837\}\hfill{}\\

\textbf{DAY} Heb: {\large\H יום} yom Def: The time of light between one dusk and the next one. Usually in the context of daylight hours but may also refer to the entire day or even a season. \{Strong's: 3117, 3118\}\hfill{}\\

\textbf{DAYTIME} Heb: {\large\H יומם} yo-mam Def: The time of the day when the sun is shining. \{Strong's: 3119\}\hfill{}\\

\textbf{DAY'YAH} Heb: {\large\H דאיה} {[}X{]} Def: An unknown bird of prey. \{Strong's: 1772\}\hfill{}\\

\textbf{DEAD} Heb: {\large\H רפא} {[}X{]} Def: {[}X{]} \{Strong's: 7496\}\hfill{}\\

\textbf{DEAD.BODY} Heb: {\large\H נבלה} {[}X{]} Def: The remains of a dead creature or person. \{Strong's: 5038\}\hfill{}\\

\textbf{DEAL.DECEITFULLY (Verb)} Heb: {\large\H התל} h.t.l Def: To give as one's portion by a false impression. \{Strong's: 2048\}\hfill{}\\

\textbf{DEAL.FALSELY (Verb)} Heb: {\large\H שקר} sh.q.r Def: {[}X{]} \{Strong's: 8266\}\hfill{}\\

\textbf{DEATH} Heb: {\large\H מות} mot Def: A permanent cessation of all vital functions; the end of life. \{Strong's: 4192, 4193, 4194\}\hfill{}\\

\textbf{DECEIT} Heb: {\large\H מרמה} mir-mah Def: The act or practice of not being honest. \{Strong's: 4820\}\hfill{}\\

\textbf{DECEIVE (Verb)} Heb: {\large\H נשא} n.sh.a Def: To cause to accept as true or valid what is false or invalid. Can also mean usury in the sense of a deception. In the participle form can mean creditor in the sense of imposition. \{Strong's: 5377, 5378, 5383\}\hfill{}\\

\textbf{DECIDE (Verb)} Heb: {\large\H שפט} sh.p.t Def: To make a determination in a dispute or wrong doing. \{Strong's: 8199, 8200\}\hfill{}\\

\textbf{DECISION} Heb: {\large\H משפט} mish-pat Def: A pronounced opinion. \{Strong's: 4941\}\hfill{}\\

\textbf{DECLARE (Verb)} Heb: {\large\H נאם} n.a.m Def: To make a formal proclamation. Often used for the words of God. \{Strong's: 5001, 5002\}\hfill{}\\

\textbf{DECLINE (Verb)} Heb: {\large\H רפך} r.p.k Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{DECORATE (Verb)} Heb: {\large\H פאר} p.a.r Def: To apply ornamentation to show distinguishment or distinction. To stand out; being seen in a good light. To boast, in the sense of decorating the self with words. \{Strong's: 6286\}\hfill{}\\

\textbf{DECORATED} Heb: {\large\H פארן} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{DECORATION} Heb: {\large\H תפארה} tiph-a-rah Def: Ornamentation that shows position, distinguishment or distinction. \{Strong's: 8597\}\hfill{}\\

\textbf{DECORATIVE.BAND} Heb: {\large\H חשב} hhey-shev Def: An adornment with designs used to decorate or tie an article of clothing. \{Strong's: 2805\}\hfill{}\\

\textbf{DEDICATE (Verb)} Heb: {\large\H נזר} n.z.r Def: To set something apart or apart from something for a special purpose. \{Strong's: 5144\}\hfill{}\\

\textbf{DEDICATED} Heb: {\large\H נזיר} na-zir Def: Devoted to the worship of God. \{Strong's: 5139\}\hfill{}\\

\textbf{DEDICATION} Heb: {\large\H חנוכה} {[}X{]} Def: Reserved for a specific use or purpose. \{Strong's: 2597, 2598\}\hfill{}\\

\textbf{DEED} Heb: {\large\H פועל} {[}X{]} Def: A work or action that is made. \{Strong's: 6467\}\hfill{}\\

\textbf{DEEP.BLACK} Heb: {\large\H אישון} {[}X{]} Def: The black of night or the pupil of the eye. In the sense of charring from a fire. \{Strong's: 380\}\hfill{}\\

\textbf{DEEP.BREATH} Heb: {\large\H נפיש} ne-phesh Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{DEEP.SEA} Heb: {\large\H תהום} te-hom Def: Extending far from some surface or area; in difficulty or distress. Deep and tumultuous water. A subterranean body of water. \{Strong's: 8415\}\hfill{}\\

\textbf{DEFEAT} Heb: {\large\H חלושה} hha-lu-shah Def: Overcome or weakened by an outside force. \{Strong's: 2476\}\hfill{}\\

\textbf{DEFENDER} Heb: {\large\H גון} {[}X{]} Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{DEFIANCE} Heb: {\large\H תנואה} {[}X{]} Def: {[}X{]} \{Strong's: 8569\}\hfill{}\\

\textbf{DEFORM (Verb)} Heb: {\large\H קלט} q.l.t Def: To be physically deformed in some manner which is usually covered. \{Strong's: 7038\}\hfill{}\\

\textbf{DELAY (Verb)} Heb: {\large\H אחר} a.hh.r Def: To stop, detain or hinder for a time. \{Strong's: 309\}\hfill{}\\

\textbf{DELICACY} Heb: {\large\H מטעם} mat-am Def: The quality or state of being luxurious. Flavorful meat. \{Strong's: 4303\}\hfill{}\\

\textbf{DELICATE} Heb: {\large\H אכד} {[}X{]} Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{DELIGHT (Verb)} Heb: {\large\H חפץ} hh.p.ts Def: To desire something out of pleasure or necessity; to have a high degree of gratification. \{Strong's: 2654\}\hfill{}\\

\textbf{DELIGHTFUL} Heb: {\large\H נעמה} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{DELIVER (Verb)} Heb: {\large\H נצל} n.ts.l Def: To set free; to take and hand over to or leave for another. \{Strong's: 5337, 5338\}\hfill{}\\

\textbf{DELIVER.UP (Verb)} Heb: {\large\H מגן} m.g.n Def: To hand over to another. \{Strong's: 4042\}\hfill{}\\

\textbf{DEMISE} Heb: {\large\H דובא} do-ve Def: Meaning dubious. \{Strong's: 1679\}\hfill{}\\

\textbf{DENY (Verb)} Heb: {\large\H כחש} k.hh.sh Def: To disclaim connection with or responsibility for. Withhold something from another or self as in a lie or submission. \{Strong's: 3584\}\hfill{}\\

\textbf{DEPART (Verb)} Heb: {\large\H רשע} r.sh.ah Def: To go astray from the correct path and become lost; to act against a law or teaching as one who has gone astray. The hiphil (causative) form means ``convict.'' \{Strong's: 7561\}\hfill{}\\

\textbf{DEPART.EARLY (Verb)} Heb: {\large\H שכם} sh.k.m Def: Literally, to put a load on the shoulder to go away or leave early. \{Strong's: 7925\}\hfill{}\\

\textbf{DEPOSIT} Heb: {\large\H מינחה} min-hhah Def: The act of making a gift or a free contribution. What is brought to another as a gift. \{Strong's: 4503, 4504\}\hfill{}\\

\textbf{DEPOSIT (Verb)} Heb: {\large\H ינח} y.n.hh Def: To place, especially for safekeeping or as a pledge; to be laid down; to sit down to rest or remain in place. \{Strong's: 3240\}\hfill{}\\

\textbf{DEPOSITED} Heb: {\large\H פקדון} piq-don Def: Valuables placed for safekeeping. Produce or other stores that are watched over. \{Strong's: 6487\}\hfill{}\\

\textbf{DEPRESSION} Heb: {\large\H כר} car Def: What is of a concave shape such as a saddle or pasture in a valley. Also, may mean the sheep of the pasture. \{Strong's: 3733\}\hfill{}\\

\textbf{DEPTH} Heb: {\large\H מצולה} me-tso-lah Def: The bottom of a deep body of water. \{Strong's: 4688\}\hfill{}\\

\textbf{DERIDE (Verb)} Heb: {\large\H נאץ} n.a.ts Def: {[}X{]} \{Strong's: 5006\}\hfill{}\\

\textbf{DERISION} Heb: {\large\H שימצה} shim-tsah Def: To talk in a low quiet voice. \{Strong's: 8103\}\hfill{}\\

\textbf{DESCENDER} Heb: {\large\H ירדן} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{DESERT} Heb: {\large\H ערבה} {[}X{]} Def: An expanse of land often barren of vegetation and people. \{Strong's: 6160\}\hfill{}\\

\textbf{DESERT.REGION} Heb: {\large\H תימא} {[}X{]} Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{DESIRABLE} Heb: {\large\H תירס} {[}X{]} Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{DESIRE} Heb: {\large\H אוה} a-wat Def: What is good or bad, that is desired. \{Strong's: 185\}\hfill{}\\

\textbf{DESIRED} Heb: {\large\H חמדן} {[}X{]} Def: Something that is desired. \{Strong's: n/a\}\hfill{}\\

\textbf{DESOLATE} Heb: {\large\H שממה} she-ma-mah Def: Vacant or void of required sources for life. \{Strong's: 8047, 8077\}\hfill{}\\

\textbf{DESOLATE (Verb)} Heb: {\large\H שמם} sh.m.m Def: To be devoid of inhabitants or visitors. \{Strong's: 8074, 8075\}\hfill{}\\

\textbf{DESOLATE.WILDERNESS} Heb: {\large\H ישימון} {[}X{]} Def: A desolate place. \{Strong's: 3452\}\hfill{}\\

\textbf{DESPAIRING} Heb: {\large\H למך} {[}X{]} Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{DESPISE (Verb)} Heb: {\large\H בוז} b.w.z Def: To look down on with contempt or aversion. \{Strong's: 936\}\hfill{}\\

\textbf{DESPISED} Heb: {\large\H בוז} {[}X{]} Def: {[}X{]} \{Strong's: 937\}\hfill{}\\

\textbf{DESTROY (Verb)} Heb: {\large\H שמד} sh.m.d Def: To bring to ruin a structure, existence, or condition. \{Strong's: 8045, 8046\}\hfill{}\\

\textbf{DESTRUCTION} Heb: {\large\H קטב} {[}X{]} Def: {[}X{]} \{Strong's: 6986\}\hfill{}\\

\textbf{DETEST (Verb)} Heb: {\large\H שקץ} sh.q.ts Def: To detest that which is filthy. \{Strong's: 8262\}\hfill{}\\

\textbf{DEVOTE (Verb)} Heb: {\large\H חנך} hh.n.k Def: To begin using something new. \{Strong's: 2596\}\hfill{}\\

\textbf{DEVOTED} Heb: {\large\H חנוך} hha-nokh Def: Immersed in activity for a specific task. \{Strong's: n/a\}\hfill{}\\

\textbf{DEVOUR (Verb)} Heb: {\large\H חסל} Def: {[}X{]} \{Strong's: 2628\}\hfill{}\\

\textbf{DEW} Heb: {\large\H טל} tal Def: Moisture condensed on the surfaces of cool bodies or objects, especially at night. \{Strong's: 2919, 2920\}\hfill{}\\

\textbf{DIE (Verb)} Heb: {\large\H מות} m.w.t Def: To pass from physical life; to pass out of existence; to come to an end through death. The hiphil (causative) form means ``kill.'' \{Strong's: 4191\}\hfill{}\\

\textbf{DIG (Verb)} Heb: {\large\H כרה} k.r.h Def: To break or loosen earth with an instrument or tool. To bargain in the sense of digging. \{Strong's: 3735, 3738, 3739\}\hfill{}\\

\textbf{DIG.OUT (Verb)} Heb: {\large\H חפר} hh.p.r Def: To dig something out of the ground. To dig into something as if searching. To confuse in the sense of being dug out. \{Strong's: 2658, 2659\}\hfill{}\\

\textbf{DIM (Verb)} Heb: {\large\H כהה} k.h.h Def: Emitting a limited or insufficient amount of light; seen indistinctly or without clear outlines or details.. To be dark in the eyes or knowledge. \{Strong's: 3543\}\hfill{}\\

\textbf{DIMINISH (Verb)} Heb: {\large\H חסר} hh.s.r Def: To make less or cause to appear less; to lessen the authority, dignity, or reputation of. Be lacking or to decrease. \{Strong's: 2637\}\hfill{}\\

\textbf{DIMNESS} Heb: {\large\H כהה} {[}X{]} Def: {[}X{]} \{Strong's: 3544\}\hfill{}\\

\textbf{DIP (Verb)} Heb: {\large\H טבל} t.b.l Def: To plunge or immerse momentarily or partially, as under the surface of a liquid, to moisten, cool, or coat. \{Strong's: 2881\}\hfill{}\\

\textbf{DIRECT (Verb)} Heb: {\large\H צוה} ts.w.h Def: To cause to turn, move, or point undeviatingly or to follow a straight course; give instructions or orders for a path to be taken. \{Strong's: 6680\}\hfill{}\\

\textbf{DIRECTIVE} Heb: {\large\H מצוה} mits-wah Def: The direction to go. Serving or intended to guide, govern, or influence; serving to point direction. \{Strong's: 4687\}\hfill{}\\

\textbf{DISCERNMENT} Heb: {\large\H דעת} da-at Def: The quality of being able to grasp and comprehend what is obscure. An intimacy with a person, idea or concept. Knowledge. \{Strong's: 1847\}\hfill{}\\

\textbf{DISCORD} Heb: {\large\H מדן} {[}X{]} Def: {[}X{]} \{Strong's: 4090\}\hfill{}\\

\textbf{DISDAIN (Verb)} Heb: {\large\H בזה} b.z.h Def: A feeling of contempt for what is beneath one; to look with scorn on; to treat something as spoiled or no longer of value. \{Strong's: 959\}\hfill{}\\

\textbf{DISEASE} Heb: {\large\H מדוה} mad-weh Def: What brings on an illness. \{Strong's: 4064\}\hfill{}\\

\textbf{DISGRACE} Heb: {\large\H חרפה} hher-pah Def: A scorn, taunting or reproach as a piercing. \{Strong's: 2781\}\hfill{}\\

\textbf{DISGUSTING} Heb: {\large\H תועבה} to-ey-vah Def: Something highly distasteful that arouses marked aversion in one. \{Strong's: 8441\}\hfill{}\\

\textbf{DISHON} Heb: {\large\H דישון} {[}X{]} Def: unknown clean animal. \{Strong's: 1788\}\hfill{}\\

\textbf{DISLOCATE (Verb)} Heb: {\large\H יקע} y.q.ah Def: To put out of place; to displace, as to dislocate a joint. Beheading by severing the neck.. \{Strong's: 3363\}\hfill{}\\

\textbf{DISMAY} Heb: {\large\H בהלה} {[}X{]} Def: {[}X{]} \{Strong's: 928\}\hfill{}\\

\textbf{DISPERSE (Verb)} Heb: {\large\H זרה} z.r.h Def: To separate or remove to a distance apart from each other; to diffuse or cause to break into different parts. \{Strong's: 2219\}\hfill{}\\

\textbf{DISPUTE} Heb: {\large\H ריב} riv Def: Bitter, sometimes violent conflict or dissension. \{Strong's: 7379\}\hfill{}\\

\textbf{DISPUTE (Verb)} Heb: {\large\H ריב} r.y.b Def: To engage in argument; to dispute or chide another in harassment or trial. \{Strong's: 7378\}\hfill{}\\

\textbf{DISSOLVE (Verb)} Heb: {\large\H מוג} m.w.g Def: To loose the bonds of something. To make something disappear. \{Strong's: 4127\}\hfill{}\\

\textbf{DISTANCE} Heb: {\large\H רחוק} ra-hhoq \textbf{\textbackslash{}} {\large\H רחוקה} re-hho-qah Def: Separation in space or time. A distant place or time. \{Strong's: 7350\}\hfill{}\\

\textbf{DISTANT} Heb: {\large\H עולם} o-lam Def: A far off place as hidden beyond the horizon. A far off time as hidden from the present; the distant past or future. A place or time that cannot be perceived. \{Strong's: 5769\}\hfill{}\\

\textbf{DISTRACTED} Heb: {\large\H פון} pun Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{DISTRACTED.ONE} Heb: {\large\H פונון} pu-non Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{DISTRESS (Verb)} Heb: {\large\H עצב} ah.ts.b Def: The state of being in great trouble, great physical or mental strain and stress. To be in pain from grief or heavy toil. \{Strong's: 6087, 6088\}\hfill{}\\

\textbf{DISTRESSING.PAIN} Heb: {\large\H עצב} e-tsev Def: Resulting from grief or heavy toil. This word can also mean an idol or image. \{Strong's: 6089, 6091, 6092\}\hfill{}\\

\textbf{DISTURB (Verb)} Heb: {\large\H עכר} ah.k.r Def: To interfere with; to destroy tranquility; to throw into disorder. Agitate or trouble, as when stirring water. \{Strong's: 5916\}\hfill{}\\

\textbf{DISTURBED.ONE} Heb: {\large\H עכרן} akh-ran Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{DIVE (Verb)} Heb: {\large\H דאה} d.a.h Def: {[}X{]} \{Strong's: 1675\}\hfill{}\\

\textbf{DIVIDE (Verb)} Heb: {\large\H חצה} hh.ts.h Def: To separate into two or more parts, areas or groups. To divide in half. \{Strong's: 2673\}\hfill{}\\

\textbf{DIVIDE.APART (Verb)} Heb: {\large\H פרד} p.r.d Def: To separate. \{Strong's: 6504\}\hfill{}\\

\textbf{DIVIDE.INTO.PIECES (Verb)} Heb: {\large\H נתח} n.t.hh Def: To sever or part into sections To distribute or to bestow in parts or shares. \{Strong's: 5408\}\hfill{}\\

\textbf{DIVIDED.PART} Heb: {\large\H גזר} ge-zer Def: A part of a whole that was divided and separated. \{Strong's: 1506\}\hfill{}\\

\textbf{DIVIDING} Heb: {\large\H חצצון} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{DIVINATION} Heb: {\large\H קסם} {[}X{]} Def: {[}X{]} \{Strong's: 7081\}\hfill{}\\

\textbf{DIVINE (Verb)} Heb: {\large\H קסם} q.s.m Def: To practice divination. \{Strong's: 7080\}\hfill{}\\

\textbf{DIVINER} Heb: {\large\H נחשון} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{DIVORCE} Heb: {\large\H כריתות} {[}X{]} Def: As cut off from the husband. \{Strong's: 3748\}\hfill{}\\

\textbf{DO (Verb)} Heb: {\large\H עשה} ah.sh.h Def: To bring to pass; to bring about; to act or make. \{Strong's: 6213\}\hfill{}\\

\textbf{DO.NOT} Heb: {\large\H אל} al Def: The negative of an alternative choice. To be without; to not be. \{Strong's: 408, 409, 3809\}\hfill{}\\

\textbf{DO.THE.MARRIAGE.DUTY (Verb)} Heb: {\large\H יבם} y.b.m Def: To perform the duty of the brother-in-law. When a brother dies, it is his brother's responsibility to marry his sister-in-law to provide his brother a child there-by, exalting the woman to her responsibility of bringing a child for her dead husband. \{Strong's: 2992\}\hfill{}\\

\textbf{DO.WELL (Verb)} Heb: {\large\H יטב} y.t.b Def: To do something necessary; to be good, in the sense of being ``functional.'' \{Strong's: 3190, 3191\}\hfill{}\\

\textbf{DOE} Heb: {\large\H אילה} ay-ya-lah Def: The adult female fallow deer. Feminine form of a strong one. \{Strong's: 355\}\hfill{}\\

\textbf{DOG} Heb: {\large\H כלב} ke-lev Def: An unclean four-footed animal. Also meaning contempt or reproach. \{Strong's: 3611\}\hfill{}\\

\textbf{DOING} Heb: {\large\H עסו} a-sah Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{DOMINATE (Verb)} Heb: {\large\H שטר} sh.t.r Def: To govern or prevail over as a magistrate; to be in ultimate control; to establish order. \{Strong's: 7860\}\hfill{}\\

\textbf{DONATION} Heb: {\large\H קורבן} {[}X{]} Def: Something given to another in devotion. \{Strong's: 7133\}\hfill{}\\

\textbf{DONKEY} Heb: {\large\H חמור} hha-mor Def: A male ass. \{Strong's: 2543, 2565\}\hfill{}\\

\textbf{DOOR} Heb: {\large\H דלת} de-let Def: A means of access; usually a swinging or sliding barrier by which an entry is closed and opened. \{Strong's: 1817\}\hfill{}\\

\textbf{DOORPOST} Heb: {\large\H מזוזה} me-zu-zah Def: The supporting frame or single post around a door or gate. \{Strong's: 4201\}\hfill{}\\

\textbf{DOORWAY} Heb: {\large\H נפתוח} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{DOUBLE} Heb: {\large\H משנה} mish-neh Def: To make twice as great or as many. As a second or a multiple of two. \{Strong's: 4932\}\hfill{}\\

\textbf{DOUBLE.OVER (Verb)} Heb: {\large\H כפל} k.p.l Def: To bend at the waist or middle. \{Strong's: 3717\}\hfill{}\\

\textbf{DOUBLED} Heb: {\large\H מכפלה} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{DOUGH} Heb: {\large\H בצק} ba-tseyq Def: A mass of flour and water that rises when yeast is added and is then baked into bread or cakes. \{Strong's: 1217\}\hfill{}\\

\textbf{DOVE} Heb: {\large\H יונה} yo-nah Def: Any of numerous species of birds, especially a small wild one. \{Strong's: 3123\}\hfill{}\\

\textbf{DOWRY} Heb: {\large\H זבד} zey-ved Def: The money, goods, or estate that a woman brings to her husband in marriage. \{Strong's: 2065\}\hfill{}\\

\textbf{DRAIN (Verb)} Heb: {\large\H מצה} m.ts.h Def: To squeeze out by wringing. \{Strong's: 4680\}\hfill{}\\

\textbf{DRAW (Verb)} Heb: {\large\H משך} m.sh.k Def: To pull up or out of a receptacle or place; to draw or pull something out; to prolong in the sense of drawing out time; to draw out a sound from a horn. \{Strong's: 4900\}\hfill{}\\

\textbf{DRAW.AWAY (Verb)} Heb: {\large\H נתק} n.t.q Def: To draw out or away as a bowstring or to draw a cord to its breaking point. \{Strong's: 5423\}\hfill{}\\

\textbf{DRAW.NEAR (Verb)} Heb: {\large\H נגש} n.g.sh Def: To bring close to another. \{Strong's: 5066\}\hfill{}\\

\textbf{DRAW.OUT (Verb)} Heb: {\large\H רוק} r.w.q Def: To empty. To arm oneself by unsheathing a sword in the sense of emptying the scabbard. Acting in vain; empty-handed. \{Strong's: 7324\}\hfill{}\\

\textbf{DRAW.UP (Verb)} Heb: {\large\H דלה} d.l.h Def: To bale up. To lift the bucket out of the well for drawing water. \{Strong's: 1802\}\hfill{}\\

\textbf{DRAW.WATER (Verb)} Heb: {\large\H שאב} sh.a.b Def: To bringing up water from a well, usually using a rope and a bucket. \{Strong's: 7579\}\hfill{}\\

\textbf{DRAWING.NEAR} Heb: {\large\H גושן} go-shen Def: To come or be brought close. \{Strong's: n/a\}\hfill{}\\

\textbf{DRAWN.OUT} Heb: {\large\H מש} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{DREAD} Heb: {\large\H חיתה} hhi-tah Def: Great fear, especially in the face of impending evil. \{Strong's: 2847\}\hfill{}\\

\textbf{DREAM} Heb: {\large\H חלום} hha-lom Def: A series of thoughts, images or emotions occurring during sleep. \{Strong's: 2472\}\hfill{}\\

\textbf{DRIED} Heb: {\large\H קלי} {[}X{]} Def: Dried foods, grains and meat, are carried by the shepherd. \{Strong's: 7039\}\hfill{}\\

\textbf{DRILL (Verb)} Heb: {\large\H חלל} hh.l.l Def: To run into or through as with a pointed weapon or tool; pierce a hole through; to begin in the sense of pressing in. \{Strong's: 2490\}\hfill{}\\

\textbf{DRILLED} Heb: {\large\H חלל} hha-lal \textbf{\textbackslash{}} {\large\H חללה} hha-la-lah Def: Having holes. \{Strong's: 2491\}\hfill{}\\

\textbf{DRINK (Verb)} Heb: {\large\H שקה} sh.q.h Def: To swallow liquid, whether of man or of the land. \{Strong's: 8248\}\hfill{}\\

\textbf{DRINKING} Heb: {\large\H משקה} mash-qeh Def: The act of swallowing water or other liquid. The drinking of the land in the sense of its being watered or irrigated. \{Strong's: 4945\}\hfill{}\\

\textbf{DRIP (Verb)} Heb: {\large\H דלף} d.l.p Def: {[}X{]} \{Strong's: 1811\}\hfill{}\\

\textbf{DRIVE (Verb)} Heb: {\large\H נהג} n.h.g Def: To set or keep in motion; to press or force into an activity, course, or direction. \{Strong's: 5090\}\hfill{}\\

\textbf{DROP.DOWN (Verb)} Heb: {\large\H נתך} n.t.k Def: To pour down, pour out to the ground or into a vessel. To pour out anger to another. \{Strong's: 5413\}\hfill{}\\

\textbf{DROVE} Heb: {\large\H עדר} ey-der Def: A group of animals driven or moving in a body. \{Strong's: 5739\}\hfill{}\\

\textbf{DROWN (Verb)} Heb: {\large\H טבע} t.b.ah Def: To fall, drop, or descend down to a lower level. \{Strong's: 2883\}\hfill{}\\

\textbf{DRUNKARD} Heb: {\large\H סבא} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{DRY (Verb)} Heb: {\large\H קלה} q.l.h Def: To dry foods, grains and meats, to preserve them. Dried foods are carried by the shepherd. To be light in stature, worthless. \{Strong's: 7033, 7034\}\hfill{}\\

\textbf{DRY.GROUND} Heb: {\large\H יבשה} ya-ba-shah Def: Land that has become dried, parched or void of water. \{Strong's: 3004\}\hfill{}\\

\textbf{DRY.LAND} Heb: {\large\H יבשת} ya-be-shet Def: An area void of water. \{Strong's: 3006, 3007\}\hfill{}\\

\textbf{DRY.OUT (Verb)} Heb: {\large\H יבש} y.b.sh Def: To be dried up as well as withered, ashamed or confused. \{Strong's: 3001\}\hfill{}\\

\textbf{DRY.UP (Verb)} Heb: {\large\H חרב} hh.r.b Def: To be a dry wasteland; to be laid waste and made desolate. \{Strong's: 2717, 2718\}\hfill{}\\

\textbf{DUG.OUT.WELL} Heb: {\large\H חפר} hhe-pher Def: \{Strong's: n/a\}\hfill{}\\

\textbf{DULL.RED} Heb: {\large\H חכלילי} hhakh-li-li Def: The color of blood and wine. \{Strong's: 2447\}\hfill{}\\

\textbf{DUNG} Heb: {\large\H פרש} pe-resh Def: The excrement of animals or humans. Manure or refuse. \{Strong's: 6569\}\hfill{}\\

\textbf{DUST} Heb: {\large\H אבק} a-vaq Def: Fine particles of earth or other material that are easily disturbed to create a cloud. \{Strong's: 80\}\hfill{}\\

\textbf{DWELL (Verb)} Heb: {\large\H שכן} sh.k.n Def: To remain for a time; to live as a resident; to stay or sit in one location for an indeterminate duration. \{Strong's: 7931, 7932\}\hfill{}\\

\textbf{DWELLER} Heb: {\large\H שכן} she-khen Def: The resident of a region. Also a habitation, the place of residence. \{Strong's: 7933, 7934\}\hfill{}\\

\textbf{DWELLING} Heb: {\large\H משכן} mish-kan Def: A place of habitation or residence. \{Strong's: 4907, 4908\}\hfill{}\\

\textbf{DYSFUNCTIONAL} Heb: {\large\H רע} ra Def: Impaired or abnormal action other than that for which a person or thing is intended. Something that does not function within its intended purpose. \{Strong's: 7451, 7455\}\hfill{}\\

\textbf{EAR} Heb: {\large\H אוזן} o-zen Def: The organ of hearing; so named from its broad shape. \{Strong's: 241\}\hfill{}\\

\textbf{EARTHENWARE} Heb: {\large\H כיר} {[}X{]} Def: A hollow box formed out of brick or clay for cooking. \{Strong's: 3600\}\hfill{}\\

\textbf{EAST} Heb: {\large\H קדם} qe-dem Def: The general direction of sunrise. As in front when facing the rising sun. Also, the ancient past. \{Strong's: 6924\}\hfill{}\\

\textbf{EAST.WIND} Heb: {\large\H קדים} qa-dim Def: The wind that comes from the east. Toward the east as the origin of the east wind. \{Strong's: 6921\}\hfill{}\\

\textbf{EASTERN} Heb: {\large\H קדמון} {[}X{]} Def: {[}X{]} \{Strong's: 6930\}\hfill{}\\

\textbf{EASTWARD} Heb: {\large\H קידמה} qid-mah Def: Toward the east. Before another space or time; as the east is in front when facing the rising sun. \{Strong's: 6926\}\hfill{}\\

\textbf{EAT (Verb)} Heb: {\large\H אכל} a.k.l Def: To consume food; to destroy. A devouring of a fire. \{Strong's: 398, 399\}\hfill{}\\

\textbf{EDGE} Heb: {\large\H פאה} pey-ah Def: The border or boundary of an object or a region. The thin cutting edge of a blade. \{Strong's: 6285\}\hfill{}\\

\textbf{EDGING} Heb: {\large\H גבלות} gav-lut Def: Furnished with a border or trim. Added to a garment for ornamentation. \{Strong's: 1383\}\hfill{}\\

\textbf{EGG} Heb: {\large\H ביצה} {[}X{]} Def: {[}X{]} \{Strong's: 1000\}\hfill{}\\

\textbf{EIGHT} Heb: {\large\H שמונה} she-mo-nah \textbf{\textbackslash{}} {\large\H שמונה} she-mo-neh Def: A cardinal number eight. May represent fullness from its connection to root meaning fat or rich. \{Strong's: 8083, 8084\}\hfill{}\\

\textbf{EIGHTH} Heb: {\large\H שמיני} she-mi-ni Def: An ordinal number. \{Strong's: 8066\}\hfill{}\\

\textbf{ELEVATED} Heb: {\large\H ראומה} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{ELEVATION} Heb: {\large\H סאת} se-eyt Def: The height to which something is raised. \{Strong's: 7613\}\hfill{}\\

\textbf{EMBER} Heb: {\large\H גחל} {[}X{]} Def: {[}X{]} \{Strong's: 1513\}\hfill{}\\

\textbf{EMBRACE (Verb)} Heb: {\large\H חבק} hh.b.q Def: To clasp in the arms; to cherish or love; to take in or include in a larger group or whole. \{Strong's: 2263\}\hfill{}\\

\textbf{EMBROIDER (Verb)} Heb: {\large\H רקם} r.q.m Def: To decorate with ornamental and colorful needlework. \{Strong's: 7551\}\hfill{}\\

\textbf{EMBROIDERY} Heb: {\large\H רקם} {[}X{]} \textbf{\textbackslash{}} {\large\H ריקמה} {[}X{]} Def: A decorative work of colorful needlework. \{Strong's: 7553\}\hfill{}\\

\textbf{EMERALD} Heb: {\large\H ברקת} ba-re-qet Def: Possibly the Emerald, a green variety of Beryl. The Hebrew word is from a root meaning to flash or shimmer, while the Septuagint uses Smaragdos meaning a green stone. Other possible translations are Beryl or Quartz.\hfill{}\\

 \{Strong's: 1304\}\hfill{}\\

\textbf{EMINENT} Heb: {\large\H אדיר} a-dir Def: What exerts power and status. Someone or something that is wide in authority or majesty. \{Strong's: 117, 155\}\hfill{}\\

\textbf{EMPIRE} Heb: {\large\H מלכות} {[}X{]} Def: The area under the control of a king; a kingdom. \{Strong's: 4437, 4438\}\hfill{}\\

\textbf{EMPTINESS} Heb: {\large\H ריקם} rey-qam Def: Lack of contents which should be present. Void of contents or purpose. \{Strong's: 7387\}\hfill{}\\

\textbf{EMPTY (Verb)} Heb: {\large\H ריק} riq Def: The lack of intelligence or significance in an action. An action or thought with no positive results. To empty by pouring out. \{Strong's: 7385, 7386\}\hfill{}\\

\textbf{EMPTY.OUT (Verb)} Heb: {\large\H בקק} b.q.q Def: To be drained away. \{Strong's: 1238\}\hfill{}\\

\textbf{ENCIRCLE (Verb)} Heb: {\large\H נקף} n.q.p Def: To go around to enclose or go about. \{Strong's: 5362\}\hfill{}\\

\textbf{ENCLOSURE} Heb: {\large\H גדר} {[}X{]} \textbf{\textbackslash{}} {\large\H גדרה} {[}X{]} Def: Any type of enclosure. \{Strong's: 1444, 1447, 1448\}\hfill{}\\

\textbf{ENCOMPASS (Verb)} Heb: {\large\H ענק} ah.n.q Def: {[}X{]} \{Strong's: 6059\}\hfill{}\\

\textbf{ENCOUNTER} Heb: {\large\H פגע} {[}X{]} Def: A chance meeting. \{Strong's: 6294\}\hfill{}\\

\textbf{ENCOUNTER (Verb)} Heb: {\large\H פגש} p.g.sh Def: To meet or come in contact with another person. A meeting between two hostile factions; to engage in conflict with. \{Strong's: 6298\}\hfill{}\\

\textbf{END} Heb: {\large\H אחרית} a-hha-rit Def: A final point that marks the extent of something. The latter time as coming after everything else. \{Strong's: 319, 320\}\hfill{}\\

\textbf{ENDOW (Verb)} Heb: {\large\H זבד} z.b.d Def: To furnish with a dower or payment for a bride. Pay the price for a bride. Give a natural gift. \{Strong's: 2064\}\hfill{}\\

\textbf{ENEMY} Heb: {\large\H ער} {[}X{]} Def: {[}X{]} \{Strong's: 6145, 6146\}\hfill{}\\

\textbf{ENGRAVE (Verb)} Heb: {\large\H חרת} hh.r.t Def: To mark, scratch, or scrape. To chisel or cut figures, letters, or devices on stone or metal. \{Strong's: 2801\}\hfill{}\\

\textbf{ENGRAVER} Heb: {\large\H חרש} hhe-resh Def: A sculptor or carver who engraves wood, stone or metal. \{Strong's: 2791, 2796\}\hfill{}\\

\textbf{ENGRAVING} Heb: {\large\H חרושת} hha-ro-shet Def: A scratching or carving in stone, metal or wood. \{Strong's: 2799\}\hfill{}\\

\textbf{ENGRAVING.TOOL} Heb: {\large\H חרט} hhe-ret Def: A tool making markings or inscriptions by carving on stone, metal or wood. A stylus for inscribing a clay tablet. \{Strong's: 2747\}\hfill{}\\

\textbf{ENQUIRE (Verb)} Heb: {\large\H שאל} sh.a.l Def: To ask about; to search into; to seek to understand what is not known. The hiphil (causative) form means ``grant.'' \{Strong's: 7592, 7593\}\hfill{}\\

\textbf{ENRAGE (Verb)} Heb: {\large\H זעם} z.ah.m Def: {[}X{]} \{Strong's: 2194\}\hfill{}\\

\textbf{ENSNARE (Verb)} Heb: {\large\H נקש} n.q.sh Def: {[}X{]} \{Strong's: 5367, 5368\}\hfill{}\\

\textbf{ENTANGLED (Verb)} Heb: {\large\H בוך} b.w.k Def: Twisted together or interwoven in a confused manner. Involved. \{Strong's: 943\}\hfill{}\\

\textbf{ENTIRELY} Heb: {\large\H כליל} ka-lil Def: A state of being complete. All of it. No missing parts; complete by including everything. \{Strong's: 3632\}\hfill{}\\

\textbf{ENTRANCE} Heb: {\large\H מבוא} ma-vo Def: A place of entering. Once (Zechariah 8:7) used for the west as the place where the sun enters the underworld. \{Strong's: 3996\}\hfill{}\\

\textbf{ENTRYWAY} Heb: {\large\H זוז} {[}X{]} Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{ENTWINE (Verb)} Heb: {\large\H פתל} p.t.l Def: To twist together or around; to become twisted. \{Strong's: 6617\}\hfill{}\\

\textbf{ENWRAP (Verb)} Heb: {\large\H עטה} ah.t.h Def: To tightly wrap something up. \{Strong's: 5844\}\hfill{}\\

\textbf{EPHOD} Heb: {\large\H אפוד} e-phod \textbf{\textbackslash{}} {\large\H אפודה} e-phu-dah Def: An apron-like vestment having two shoulder straps and ornamental attachments for securing the breastplate, worn with a waistband by the high priest. \{Strong's: 642, 646\}\hfill{}\\

\textbf{EPIDEMIC} Heb: {\large\H דבר} de-ver Def: A wide spread disease effecting man or animal. A pestilence. \{Strong's: 1698\}\hfill{}\\

\textbf{EQUAL} Heb: {\large\H שוה} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{EQUATE (Verb)} Heb: {\large\H שוה} sh.w.h Def: To make something like something else, or to compare it to something else. \{Strong's: 7737, 7738, 7739\}\hfill{}\\

\textbf{EQUATED} Heb: {\large\H שה} {[}X{]} Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{ERR (Verb)} Heb: {\large\H שגג} sh.g.g Def: {[}X{]} \{Strong's: 7683\}\hfill{}\\

\textbf{ERROR} Heb: {\large\H שגגה} {[}X{]} Def: {[}X{]} \{Strong's: 7684\}\hfill{}\\

\textbf{ERUPTION} Heb: {\large\H נתק} {[}X{]} Def: A disease of the skin which breaks open drawing out liquid. \{Strong's: 5424\}\hfill{}\\

\textbf{ESCAPED} Heb: {\large\H פליט} pa-lit \textbf{\textbackslash{}} {\large\H פליטה} pe-ley-tah Def: A getting away, especially from confinement. A person or animal that has gotten away. \{Strong's: 6412, 6413\}\hfill{}\\

\textbf{ESCAPING} Heb: {\large\H פלט} {[}X{]} Def: {[}X{]} \{Strong's: 6405\}\hfill{}\\

\textbf{ESTIMATE (Verb)} Heb: {\large\H כסס} k.s.s Def: To make an approximate count or reckoning. \{Strong's: 3699\}\hfill{}\\

\textbf{EUNUCH} Heb: {\large\H סריס} sa-ris Def: A castrated man. As eunuchs were used as officers, may also mean an officer. \{Strong's: 5631\}\hfill{}\\

\textbf{EVENING} Heb: {\large\H ערב} e-rev Def: The latter part and close of the day and the early part of the night. Dark of the evening or dark-skinned people. Also the willow from its dark color. \{Strong's: 6153, 6155\}\hfill{}\\

\textbf{EVENT} Heb: {\large\H קרה} {[}X{]} Def: {[}X{]} \{Strong's: 7137\}\hfill{}\\

\textbf{EVICTED} Heb: {\large\H גרשון} ger-shon Def: To be removed or thrown from with force. To dispossess, exile, dismiss. \{Strong's: n/a\}\hfill{}\\

\textbf{EVIDENCE} Heb: {\large\H עדות} ey-dut Def: That which proves or disproves something; something that makes plain or clear; an indication or sign. \{Strong's: 5715\}\hfill{}\\

\textbf{EWE} Heb: {\large\H רחל} ra-hheyl Def: A female sheep. \{Strong's: 7353\}\hfill{}\\

\textbf{EXAMINE (Verb)} Heb: {\large\H בחן} b.hh.n Def: To inspect closely; to test, try or scrutinize. \{Strong's: 974\}\hfill{}\\

\textbf{EXCEED (Verb)} Heb: {\large\H עדף} ah.d.p Def: Running over, filled beyond capacity. \{Strong's: 5736\}\hfill{}\\

\textbf{EXCEPT} Heb: {\large\H בילתי} bil-ti Def: With the exclusion of from the whole. The whole with the exception of one or more. \{Strong's: 1115\}\hfill{}\\

\textbf{EXCHANGE} Heb: {\large\H תמורה} {[}X{]} Def: {[}X{]} \{Strong's: 8545\}\hfill{}\\

\textbf{EXCHANGE (Verb)} Heb: {\large\H שבל} sh.b.l Def: The act of giving or taking one thing in return for another. To buy or sell produce, usually grain. Bartering. \{Strong's: 7666\}\hfill{}\\

\textbf{EXHALE (Verb)} Heb: {\large\H נפח} n.p.hh Def: To give out a breath. To blow on a fire or the boiling water in a pot as an exhale. \{Strong's: 5301\}\hfill{}\\

\textbf{EXIST (Verb)} Heb: {\large\H היה} h.y.h Def: To have real being whether material or spiritual; to have breath. \{Strong's: 1961\}\hfill{}\\

\textbf{EXISTING} Heb: {\large\H יה} yah Def: Set in place. To be fixed with permanence or continuance. To continue in being. \{Strong's: n/a\}\hfill{}\\

\textbf{EXPEL (Verb)} Heb: {\large\H נדח} n.d.hh Def: To forcefully send someone or something out or away; to drive an axe through wood. \{Strong's: 5080\}\hfill{}\\

\textbf{EXPERIENCED} Heb: {\large\H חניך} hha-nikh Def: Direct observation of or participation in events as a basis of knowledge. Something that is personally encountered, undergone or lived through in its use. \{Strong's: 2593\}\hfill{}\\

\textbf{EXPIRE (Verb)} Heb: {\large\H גוע} g.w.ah Def: To breathe one’s last breath; the last breath of death. \{Strong's: 1478\}\hfill{}\\

\textbf{EXPLAIN (Verb)} Heb: {\large\H באר} b.a.r Def: To provide a meaning. \{Strong's: 874\}\hfill{}\\

\textbf{EXPOSE} Heb: {\large\H מחסוף} mahh-soph Def: To cause to be visible or open to public view. In the sense of uncovering. \{Strong's: 4286\}\hfill{}\\

\textbf{EXTEND (Verb)} Heb: {\large\H נטה} n.t.h Def: To set up camp by stretching out the cover of the tent; to extend or stretch in length. \{Strong's: 5186\}\hfill{}\\

\textbf{EXTRACT (Verb)} Heb: {\large\H חלץ} hh.l.ts Def: To pull out or toward. To draw weapons for battle. \{Strong's: 2502\}\hfill{}\\

\textbf{EXTREME.OLD.AGE} Heb: {\large\H זקון} za-qun Def: A full and long life. \{Strong's: 2208\}\hfill{}\\

\textbf{EXTREMITY} Heb: {\large\H קצה} qa-tseh \textbf{\textbackslash{}} {\large\H קצה} qa-tsah Def: The most distant end of something; the corner or edge. \{Strong's: 7097, 7098\}\hfill{}\\

\textbf{EXUBERANT} Heb: {\large\H זרד} ze-red Def: \{Strong's: n/a\}\hfill{}\\

\textbf{EYE} Heb: {\large\H עין} a-yin Def: The organ of sight or vision that tears when a person weeps. Also a spring that weeps water out of the ground. \{Strong's: 5869, 5870\}\hfill{}\\

\textbf{EYPHAH} Heb: {\large\H איפה} ey-phah Def: A dry standard of measure equal to 3 se'ahs or 10 omers. The same as the liquid measure bath which is about 9 imperial gallons or 40 liters. \{Strong's: 374\}\hfill{}\\

\textbf{FACE} Heb: {\large\H פנה} pa-neh Def: The anterior part of the human head; outward appearance. One present, in the sense of being in the face of another. Always written in the plural form. \{Strong's: 3942, 6440\}\hfill{}\\

\textbf{FACE.TOWARD (Verb)} Heb: {\large\H קדם} q.d.m Def: To face another or meet face to face; to go before someone or something in space or time. \{Strong's: 6923\}\hfill{}\\

\textbf{FADE (Verb)} Heb: {\large\H נבל} n.b.l Def: To degrade a person, action or object. To droop or pass away. To wither away as a leaf. To wear out of strength. To act unproductively. \{Strong's: 5034\}\hfill{}\\

\textbf{FAIL (Verb)} Heb: {\large\H חטא} hh.t.a Def: To miss the target, whether a literal target or a goal that is aimed for. The piel (intensive) form means ``reconcile.'' \{Strong's: 2398\}\hfill{}\\

\textbf{FAILING} Heb: {\large\H כליון} {[}X{]} Def: A complete destruction or failure of something. \{Strong's: 3631\}\hfill{}\\

\textbf{FAILURE} Heb: {\large\H חטא} hha-ta \textbf{\textbackslash{}} {\large\H חטאה} hha-ta-a Def: An act or condition of ignorant or imprudent deviation from a code of behavior. A missing of the target in the sense of making a mistake. The sacrifice, which by transference, becomes the sin. \{Strong's: 2399, 2400, 2401, 2402, 2403\}\hfill{}\\

\textbf{FAINT} Heb: {\large\H מורך} {[}X{]} Def: From a blow to the loins. \{Strong's: 4816\}\hfill{}\\

\textbf{FAINT (Verb)} Heb: {\large\H להה} l.h.h Def: Lacking courage and spirit; weak, dizzy and likely to pass out. Lacking distinctness. \{Strong's: 3856\}\hfill{}\\

\textbf{FALL} Heb: {\large\H פל} pa-lal Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{FALL (Verb)} Heb: {\large\H נפל} n.p.l Def: To leave an erect position suddenly and involuntarily; to descend freely by the force of gravity. \{Strong's: 5307, 5308\}\hfill{}\\

\textbf{FALL.UPON (Verb)} Heb: {\large\H שוף} sh.w.p Def: To suddenly and forcefully crash upon someone or something. \{Strong's: 7779\}\hfill{}\\

\textbf{FALLEN.GRAPE} Heb: {\large\H פרט} {[}X{]} Def: As broken from the plant and scattered on the ground. \{Strong's: 6528\}\hfill{}\\

\textbf{FALSE} Heb: {\large\H שקר} she-qer Def: A deliberate lie. An expression of a non-truth. \{Strong's: 8267\}\hfill{}\\

\textbf{FALSENESS} Heb: {\large\H שוא} shu-a Def: Words or actions that are not true or are empty. A Deception. Lacking value and content. \{Strong's: 7723\}\hfill{}\\

\textbf{FAMILY.IDOL} Heb: {\large\H תרף} te-raph Def: A household idol of a god, possibly believed to have a healing power. \{Strong's: 8655\}\hfill{}\\

\textbf{FAMINE} Heb: {\large\H רעבון} ra-a-von Def: An extreme scarcity of food. \{Strong's: 7459\}\hfill{}\\

\textbf{FAR.BE.IT} Heb: {\large\H חלילה} hha-li-lah Def: Something least likely to happen. \{Strong's: 2486\}\hfill{}\\

\textbf{FAR.END} Heb: {\large\H אפס} {[}X{]} Def: The concluding part of an area or extremity. Also used for the conclusion of a thought; finally, however, but. \{Strong's: 657\}\hfill{}\\

\textbf{FASTEN (Verb)} Heb: {\large\H צמד} ts.m.d Def: To be joined to another as in a yoke. \{Strong's: 6775\}\hfill{}\\

\textbf{FASTENER} Heb: {\large\H דבק} {[}X{]} Def: What joins together. \{Strong's: 1694, 1695\}\hfill{}\\

\textbf{FAT} Heb: {\large\H חלב} hhe-lev Def: Animal tissue consisting of cells distended with greasy or oily matter; adipose tissue. The fat of an animal as the choicest part. Also milk; A white fatty liquid secreted by cows, sheep and goats, and used for food or as a source of butter, cheeses, yogurt, etc. \{Strong's: 2459, 2461\}\hfill{}\\

\textbf{FAT.TAIL} Heb: {\large\H אליה} al-yah Def: The fat part of a sheep's rump considered an Eastern delicacy. \{Strong's: 451\}\hfill{}\\

\textbf{FATHER} Heb: {\large\H אב} av Def: A man who has begotten a child. The provider and support to the household. The ancestor of a family line. The patron of a profession or art. \{Strong's: 1, 2\}\hfill{}\\

\textbf{FATHER.IN.LAW} Heb: {\large\H חם} hham Def: The father of ones wife or husband, father-in-law in the sense of passion \{Strong's: 2524\}\hfill{}\\

\textbf{FATNESS} Heb: {\large\H ממרא} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{FATTEN (Verb)} Heb: {\large\H ברא} b.r.a Def: To make more substantial, fleshy or plump; to fill up. The filling of the earth in Genesis 1 with the sun, moon, plants and animals. The filling of man with breath and the image of God. \{Strong's: 1254\}\hfill{}\\

\textbf{FATTENING} Heb: {\large\H ריבקה} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{FAVORED} Heb: {\large\H מהיטב} ya-tav Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{FEAR (Verb)} Heb: {\large\H ירא} y.r.a Def: To be afraid of; to have a strong emotion caused by anticipation or awareness of danger; the flowing, or quivering, of the gut from fear or awe; to dread what is terrible or revere what is respected. \{Strong's: 3372\}\hfill{}\\

\textbf{FEARFUL} Heb: {\large\H ירא} ya-rey Def: Full of fear or dread. \{Strong's: 3373\}\hfill{}\\

\textbf{FEARFULNESS} Heb: {\large\H יראה} yi-rah Def: Inclined to be afraid. \{Strong's: 3374\}\hfill{}\\

\textbf{FEARING} Heb: {\large\H מורא} {[}X{]} Def: To be afraid or apprehensive. \{Strong's: 4172\}\hfill{}\\

\textbf{FEAST} Heb: {\large\H חג} hhag Def: A commemoration of a special event with dancing, rejoicing, and sharing of food. A ceremony of joy and thanksgiving. A festival with a magnificent meal which is shared with a number of guests. \{Strong's: 2282\}\hfill{}\\

\textbf{FEATHER} Heb: {\large\H אברה} {[}X{]} Def: {[}X{]} \{Strong's: 84\}\hfill{}\\

\textbf{FED.FAT} Heb: {\large\H בריא} ba-ri \textbf{\textbackslash{}} {\large\H בריאה} {[}X{]} Def: A member of the livestock that has been fed grains to fatten it for the slaughter. \{Strong's: 1277, 1278\}\hfill{}\\

\textbf{FEED (Verb)} Heb: {\large\H רעה} r.ah.h Def: To give food to; to provide feed or pasture to the flock. Commonly used in the participle form meaning a feeder or shepherd. \{Strong's: 7462\}\hfill{}\\

\textbf{FEEDING.PLACE} Heb: {\large\H מרעה} mir-eh Def: A place of feeding or grazing. \{Strong's: 4829\}\hfill{}\\

\textbf{FEEL (Verb)} Heb: {\large\H ימש} y.m.sh Def: To handle or touch in order to examine, test or explore some quality. Reach out with the hand to touch. \{Strong's: 3237\}\hfill{}\\

\textbf{FEMALE} Heb: {\large\H נקבה} na-qey-vah Def: An individual that bears children. Designed with a hollow or groove into which a corresponding male part fits, as with a hole. \{Strong's: 5347\}\hfill{}\\

\textbf{FEMALE.OWNER} Heb: {\large\H גברת} ge-ve-ret Def: A female master overseeing slaves or servants. \{Strong's: 1404\}\hfill{}\\

\textbf{FEMALE.PROSTITUTE} Heb: {\large\H קדשה} qe-dey-shah Def: Devoted to corrupt purposes. A female prostitute set aside for a special purpose. \{Strong's: 6948\}\hfill{}\\

\textbf{FENCE} Heb: {\large\H מבצר} {[}X{]} Def: A walled place of protection and confinement. \{Strong's: 4013\}\hfill{}\\

\textbf{FENCE.AROUND (Verb)} Heb: {\large\H שכך} sh.k.k Def: To surround with a wall of protection or covering. To encompass completely. \{Strong's: 5526\}\hfill{}\\

\textbf{FENCE.IN (Verb)} Heb: {\large\H בצר} b.ts.r Def: A barrier intended to protect, prevent escape or intrusion, or to mark a boundary; to gather together and confine for protection. \{Strong's: 1219\}\hfill{}\\

\textbf{FEVER} Heb: {\large\H קדחת} {[}X{]} Def: {[}X{]} \{Strong's: 6920\}\hfill{}\\

\textbf{FEW} Heb: {\large\H מצער} miz-ar Def: Small in number. \{Strong's: 4213, 4705\}\hfill{}\\

\textbf{FIELD} Heb: {\large\H שדה} sa-deh Def: An open land area free of trees and buildings. A level plot of ground. \{Strong's: 7704\}\hfill{}\\

\textbf{FIFTH} Heb: {\large\H חמישי} hha-mi-shi Def: An ordinal number. \{Strong's: 2549\}\hfill{}\\

\textbf{FIFTH.PART} Heb: {\large\H חומש} hho-mesh Def: A fifth portion of five equal amounts. \{Strong's: 2569, 2570\}\hfill{}\\

\textbf{FIG} Heb: {\large\H תאן} te-eyn Def: An oblong or pear-shaped fruit from a tree of the fichus genus. \{Strong's: 8384\}\hfill{}\\

\textbf{FIGHT (Verb)} Heb: {\large\H לחם} l.hh.m Def: To make war; to battle as to destruction; to attempt to defeat, subdue, or destroy an enemy by blows or weapons. A struggle for victory. \{Strong's: 3898\}\hfill{}\\

\textbf{FIGHTING} Heb: {\large\H כדר} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{FIGURE} Heb: {\large\H סמל} {[}X{]} Def: {[}X{]} \{Strong's: 5566\}\hfill{}\\

\textbf{FILL (Verb)} Heb: {\large\H מלא} m.l.a Def: To occupy to the full capacity. The piel (intensive) form means ``fulfill.'' \{Strong's: 4390, 4391\}\hfill{}\\

\textbf{FILLING} Heb: {\large\H מלוא} me-lo Def: An act or instance of filling; something used to fill a cavity, container, or depression. \{Strong's: 4393\}\hfill{}\\

\textbf{FILTHINESS} Heb: {\large\H שיקוץ} {[}X{]} Def: A dirty, shameful, or detestable action, object or condition. Often used in the context of idols. \{Strong's: 8251\}\hfill{}\\

\textbf{FILTHY} Heb: {\large\H שקץ} {[}X{]} Def: {[}X{]} \{Strong's: 8263\}\hfill{}\\

\textbf{FIN} Heb: {\large\H סנפיר} {[}X{]} Def: The fins of a fish. \{Strong's: 5579\}\hfill{}\\

\textbf{FIND (Verb)} Heb: {\large\H מצא} m.ts.a Def: To come upon, often accidentally; to meet with; to discover and secure through searching. \{Strong's: 4291, 4672\}\hfill{}\\

\textbf{FINE (Verb)} Heb: {\large\H ענש} ah.n.sh Def: A financial penalty made for an offense or damages. \{Strong's: 6064\}\hfill{}\\

\textbf{FINE.DUST} Heb: {\large\H שחק} {[}X{]} Def: A pulverized powder. Also the clouds as a fine powder. \{Strong's: 7834\}\hfill{}\\

\textbf{FINGER} Heb: {\large\H אצבע} ets-ba Def: The extension of the hand. Can be used to point. \{Strong's: 676, 677\}\hfill{}\\

\textbf{FINGER.SPAN} Heb: {\large\H זרת} ze-ret Def: The span of the fingers, often used as a measurement. \{Strong's: 2239\}\hfill{}\\

\textbf{FINISH (Verb)} Heb: {\large\H כלה} k.l.h Def: To bring to an end; terminate; to complete an action, event. \{Strong's: 3615\}\hfill{}\\

\textbf{FIRE} Heb: {\large\H אש} eysh Def: The phenomenon of combustion manifested by heat, light and flame. \{Strong's: 784, 785\}\hfill{}\\

\textbf{FIRE.OFFERING} Heb: {\large\H אישה} i-sheh Def: A sacrifice that is placed in a fire as an offering. \{Strong's: 801\}\hfill{}\\

\textbf{FIRE.PAN} Heb: {\large\H מחתה} mahh-tah Def: A tray for carrying hot coals. \{Strong's: 4289\}\hfill{}\\

\textbf{FIRMLY.PRESSED} Heb: {\large\H מעכה} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{FIRMNESS} Heb: {\large\H אמון} ey-mun \textbf{\textbackslash{}} {\large\H אמונה} e-mu-nah Def: Securely fixed in place. \{Strong's: 529, 530\}\hfill{}\\

\textbf{FIRST} Heb: {\large\H ריאשון} ri-shon Def: The head of a time or position. \{Strong's: 7223\}\hfill{}\\

\textbf{FIRST.RAIN} Heb: {\large\H יורה} {[}X{]} Def: {[}X{]} \{Strong's: 3138\}\hfill{}\\

\textbf{FIRST.TIME} Heb: {\large\H תחילה} te-hhiy-lah Def: The spot to be drilled is first scored to make an indentation to accept the drill. The beginning of the drilling is the most difficult, as the drill can easily slip out. If the first drilling slips, it is difficult to begin a second time. \{Strong's: 8462\}\hfill{}\\

\textbf{FIRSTBORN} Heb: {\large\H בכור} be-khor Def: The firstborn offspring, usually a son, of a man or animal. The prominent one. \{Strong's: 1060\}\hfill{}\\

\textbf{FIRSTBORN.FEMALE} Heb: {\large\H בכירה} be-khi-rah Def: The firstborn daughter. The prominent one. \{Strong's: 1067\}\hfill{}\\

\textbf{FIRSTFRUIT} Heb: {\large\H ביכור} bi-khor Def: The first gathered fruits of a harvest; the first results of an undertaking. \{Strong's: 1061\}\hfill{}\\

\textbf{FISH} Heb: {\large\H דג} dag \textbf{\textbackslash{}} {\large\H דגה} da-gah Def: An aquatic animal. Only fish with scales and fins are considered fit for food (clean). \{Strong's: 1709, 1710\}\hfill{}\\

\textbf{FISSURE} Heb: {\large\H נקרה} nik-rah Def: A division, causing to become two pieces instead of one. A cleft or narrow chasm. \{Strong's: 5366\}\hfill{}\\

\textbf{FIST} Heb: {\large\H אגרוף} eg-roph Def: Clenched fingers into the palm of the hand. \{Strong's: 106\}\hfill{}\\

\textbf{FIVE} Heb: {\large\H חמשה} hha-mi-shah \textbf{\textbackslash{}} {\large\H חמש} hha-meysh Def: A cardinal number, from the number of fingers on a hand. \{Strong's: 2568, 2572\}\hfill{}\\

\textbf{FLAKE.OFF (Verb)} Heb: {\large\H חספס} hh.s.p Def: To scale off particles from an object. \{Strong's: 2636\}\hfill{}\\

\textbf{FLAME.OF.FIRE} Heb: {\large\H פילדש} {[}X{]} Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{FLAMING} Heb: {\large\H חרי} hha-ri Def: A visible fire, usually used in the sense of a fierce anger. \{Strong's: 2750\}\hfill{}\\

\textbf{FLAMING.WRATH} Heb: {\large\H חרון} hha-ron Def: A fierce anger. \{Strong's: 2740\}\hfill{}\\

\textbf{FLANK} Heb: {\large\H ירכה} yar-khah Def: The hollow of the loins between the legs. \{Strong's: 3410, 3411\}\hfill{}\\

\textbf{FLARE.UP (Verb)} Heb: {\large\H חרה} hh.r.h Def: To become suddenly excited or angry; to break out suddenly. Burn with a fierce anger. \{Strong's: 2734\}\hfill{}\\

\textbf{FLASH} Heb: {\large\H ברק} ba-raq Def: The bright light shining off the edge of a sword. The bright light of lightning. \{Strong's: 1300\}\hfill{}\\

\textbf{FLAT} Heb: {\large\H ריקוע} {[}X{]} Def: As hammered out flat. \{Strong's: 7555\}\hfill{}\\

\textbf{FLAVOR} Heb: {\large\H טעם} ta-am Def: The taste of a food or the perception of a person's behavior. \{Strong's: 2940, 2941, 2942\}\hfill{}\\

\textbf{FLAX} Heb: {\large\H פשתה} pish-teh Def: A plant in which its fibers are used in manufacturing articles of clothing. Also used to make wicks, cords, and bands. Linseed, linseed oil, and oilcake are useful products of the same plant. \{Strong's: 6593, 6594\}\hfill{}\\

\textbf{FLEE (Verb)} Heb: {\large\H נוס} n.w.s Def: To run away, often from danger or evil; to hurry toward a place of safety; to flee to any safe place such as a city or mountain. \{Strong's: 5127\}\hfill{}\\

\textbf{FLEE.AWAY (Verb)} Heb: {\large\H ברח} b.r.hh Def: To run away from. \{Strong's: 1272\}\hfill{}\\

\textbf{FLEECE} Heb: {\large\H גז} {[}X{]} Def: The shearing of sheep for its fleece. Also the grasses that are sheared off with a sickle in harvest. \{Strong's: 1488\}\hfill{}\\

\textbf{FLEEING} Heb: {\large\H מנוסה} {[}X{]} Def: {[}X{]} \{Strong's: 4499\}\hfill{}\\

\textbf{FLEET} Heb: {\large\H עירד} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{FLESH} Heb: {\large\H בשר} ba-sar Def: The soft parts of a human or animal, composed primarily of skeletal muscle. Skin and muscle or the whole of the person. Meat as food. \{Strong's: 1154, 1320, 1321\}\hfill{}\\

\textbf{FLINT} Heb: {\large\H יהלום} ya-ha-lom Def: Possibly the flint, a form of quartz of a brown, gray or black color. Other possible translations are onyx and diamond. \{Strong's: 3095\}\hfill{}\\

\textbf{FLOAT (Verb)} Heb: {\large\H זוף} z.w.p Def: {[}X{]} \{Strong's: 6687\}\hfill{}\\

\textbf{FLOCKS} Heb: {\large\H צון} tson \textbf{\textbackslash{}} {\large\H צון} tson Def: Groups of birds or animals assembled or herded together. \{Strong's: 6629, 6792\}\hfill{}\\

\textbf{FLOOD} Heb: {\large\H מבול} ma-bul Def: To cover with an overwhelming quantity or volume of water. \{Strong's: 3999\}\hfill{}\\

\textbf{FLOOR} Heb: {\large\H גורן} go-ren Def: The level base of a room, barn or threshing floor. \{Strong's: 1637\}\hfill{}\\

\textbf{FLOUR} Heb: {\large\H סולת} so-let Def: Finely ground meal of grain used for making bread. \{Strong's: 5560\}\hfill{}\\

\textbf{FLOURISHED} Heb: {\large\H נב} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{FLOURISHING} Heb: {\large\H רען} {[}X{]} Def: A green plant bearing fruit. Also prosperous. \{Strong's: 7487, 7488\}\hfill{}\\

\textbf{FLOW (Verb)} Heb: {\large\H נזל} n.z.l Def: To stream or gush a liquid substance. To run like water. \{Strong's: 5140\}\hfill{}\\

\textbf{FLOW.OUT (Verb)} Heb: {\large\H רור} r.w.r Def: {[}X{]} \{Strong's: 7325\}\hfill{}\\

\textbf{FLOWER} Heb: {\large\H ניצן} {[}X{]} Def: {[}X{]} \{Strong's: 5339\}\hfill{}\\

\textbf{FLUSH (Verb)} Heb: {\large\H שטף} sh.t.p Def: To flow over with copious amounts of water. \{Strong's: 7857\}\hfill{}\\

\textbf{FLUTTER (Verb)} Heb: {\large\H רחף} r.hh.p Def: To flap the wings rapidly. To move with quick wavering or flapping motions. Shake as a bird in the nest. \{Strong's: 7363\}\hfill{}\\

\textbf{FLY (Verb)} Heb: {\large\H עוף} ah.w.p Def: To move in or pass through the air with wings; to soar in the air. \{Strong's: 5774\}\hfill{}\\

\textbf{FLYER} Heb: {\large\H עוף} oph Def: A flying creature such as a bird or insect. \{Strong's: 5775, 5776\}\hfill{}\\

\textbf{FOLLOWING} Heb: {\large\H תשוקה} te-shu-qah Def: To go, proceed or come after. Being next in order or time. Subsequent to. As the river follows the path of its banks. \{Strong's: 8669\}\hfill{}\\

\textbf{FOLLY} Heb: {\large\H נבלה} ne-va-lah Def: Lack of good sense or prudence and foresight. In the sense of fading away. \{Strong's: 5039\}\hfill{}\\

\textbf{FOOD} Heb: {\large\H אכלה} akh-lah Def: Something that nourishes, sustains, or supplies. For giving sustenance and making one whole. \{Strong's: 402\}\hfill{}\\

\textbf{FOODSTUFF} Heb: {\large\H אוכל} o-khel Def: A substance that may be eaten for giving sustenance and making one whole. \{Strong's: 400\}\hfill{}\\

\textbf{FOOL} Heb: {\large\H נבל} {[}X{]} Def: In the sense of fading away. \{Strong's: 5036\}\hfill{}\\

\textbf{FOOLISH (Verb)} Heb: {\large\H ילא} y.l.a Def: To be without wisdom. \{Strong's: 2973\}\hfill{}\\

\textbf{FOOT} Heb: {\large\H רגל} re-gel Def: The terminal part of the leg upon which the human, animal or object stands. Also euphemistically for the leg. \{Strong's: 7271, 7272\}\hfill{}\\

\textbf{FOOTING} Heb: {\large\H אדן} e-den Def: Ground or basis for a firm foundation. That which sustains a stable position. \{Strong's: 134\}\hfill{}\\

\textbf{FOOTSTEP} Heb: {\large\H פעם} pa-am Def: A stroke of time as a rhythmic beating of time, one moment after the other. A moment in time. A foot or leg in the sense of stepping. \{Strong's: 6471\}\hfill{}\\

\textbf{FOR} Heb: {\large\H חלף} {[}X{]} Def: An exchange for something else. \{Strong's: 2500\}\hfill{}\\

\textbf{FORBID (Verb)} Heb: {\large\H נוא} n.w.a Def: {[}X{]} \{Strong's: 5106\}\hfill{}\\

\textbf{FORCE} Heb: {\large\H חיל} hha-yil Def: The pressure exerted to make a piercing. \{Strong's: 2428, 2429\}\hfill{}\\

\textbf{FORCEFUL} Heb: {\large\H חזק} hha-zaq \textbf{\textbackslash{}} {\large\H חזקה} hha-za-qah Def: A strong grip on something to refrain or support. Driven with force. Acting with power. \{Strong's: 2389, 2390, 2391\}\hfill{}\\

\textbf{FOREARM} Heb: {\large\H אמה} am-mah Def: A linear standard of measure equal to the length of the forearm. \{Strong's: 520\}\hfill{}\\

\textbf{FOREFRONT} Heb: {\large\H מול} mul Def: In front of or at the head of, in space or time. \{Strong's: 4136\}\hfill{}\\

\textbf{FOREHEAD} Heb: {\large\H מצח} mey-tsahh Def: The part of the face which extends from the hair on the top of the head to the eyes. Impudence, confidence, or assurance. The seat of boldness of speech and actions. \{Strong's: 4696\}\hfill{}\\

\textbf{FOREIGN} Heb: {\large\H נכרי} na-khri \textbf{\textbackslash{}} {\large\H נכריה} na-khri-yah Def: Situated outside one's own country. Alien in character. A strange person, place or thing as being unrecognized. \{Strong's: 5237\}\hfill{}\\

\textbf{FOREIGNER} Heb: {\large\H נכר} ney-khar Def: A person belonging to or owing allegiance to a foreign country. \{Strong's: 5235, 5236\}\hfill{}\\

\textbf{FORESKIN} Heb: {\large\H ערלה} ar-lah Def: A fold of skin that covers the end of the penis. \{Strong's: 6190\}\hfill{}\\

\textbf{FOREST} Heb: {\large\H יער} {[}X{]} Def: A dark place dense with trees. \{Strong's: 3264, 3293\}\hfill{}\\

\textbf{FORGET (Verb)} Heb: {\large\H שכח} sh.k.hh Def: To lose remembrance of; to cease remembering or noticing. \{Strong's: 7911, 7912\}\hfill{}\\

\textbf{FORGIVE (Verb)} Heb: {\large\H סלח} s.l.hh Def: To pardon; to overlook an offense and treat the offender as not guilty. \{Strong's: 5545\}\hfill{}\\

\textbf{FORK} Heb: {\large\H מזלג} maz-leyg \textbf{\textbackslash{}} {\large\H מזלגה} {[}X{]} Def: An implement, or tool with multiple prongs or tines. \{Strong's: 4207\}\hfill{}\\

\textbf{FORTIFIED} Heb: {\large\H כסלוח} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{FORTRESS.OF.ANU} Heb: {\large\H כלנה} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{FORTUNATE} Heb: {\large\H שון} shun Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{FORTUNE} Heb: {\large\H גד} gad Def: A store of material possessions. \{Strong's: 1409\}\hfill{}\\

\textbf{FORTUNES} Heb: {\large\H גדגד} gid-gad \textbf{\textbackslash{}} {\large\H גודגודה} gud-go-dah Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{FOUL} Heb: {\large\H פיגול} {[}X{]} Def: {[}X{]} \{Strong's: 6292\}\hfill{}\\

\textbf{FOUND (Verb)} Heb: {\large\H יסד} y.s.d Def: To lay a foundation of a house, place or plan. \{Strong's: 3245\}\hfill{}\\

\textbf{FOUNDATION} Heb: {\large\H מוסד} {[}X{]} \textbf{\textbackslash{}} {\large\H מוסדה} {[}X{]} Def: A supporting and level base of a building or structure which lies on or in the ground. \{Strong's: 4143, 4144, 4145, 4146\}\hfill{}\\

\textbf{FOUNTAIN} Heb: {\large\H מכור} {[}X{]} Def: A spring that comes out of a hole in the ground. The source of water necessary for life in the wilderness. \{Strong's: 4726\}\hfill{}\\

\textbf{FOUR} Heb: {\large\H ארבעה} ar-ba-ah \textbf{\textbackslash{}} {\large\H ארבע} ar-ba Def: A cardinal number. \{Strong's: 702, 703, 705\}\hfill{}\\

\textbf{FOURTH} Heb: {\large\H רביעי} re-vi-i Def: An ordinal number. \{Strong's: 7243, 7244\}\hfill{}\\

\textbf{FOURTH.GENERATION} Heb: {\large\H ריבע} ri-va Def: A great-great grandchild, as a descendant of the fourth generation. \{Strong's: 7256\}\hfill{}\\

\textbf{FOURTH.PART} Heb: {\large\H רובע} {[}X{]} Def: As fourth in the order. \{Strong's: 7255\}\hfill{}\\

\textbf{FRAGILE} Heb: {\large\H פרנך} par-nakh Def: Meaning dubious. \{Strong's: n/a\}\hfill{}\\

\textbf{FRAGMENT} Heb: {\large\H פת} pat Def: A part broken off, detached, or incomplete. The removal of a piece resulting in a hole. \{Strong's: 6595\}\hfill{}\\

\textbf{FRAGRANCE} Heb: {\large\H בסמת} {[}X{]} Def: A sweet smelling spice. \{Strong's: n/a\}\hfill{}\\

\textbf{FRAGRANT.ONE} Heb: {\large\H זיפרון} ziph-ron Def: \{Strong's: n/a\}\hfill{}\\

\textbf{FRAIL} Heb: {\large\H רפה} {[}X{]} Def: {[}X{]} \{Strong's: 7504\}\hfill{}\\

\textbf{FRANKINCENSE} Heb: {\large\H לבונה} le-vo-nah Def: A resin or gum that is a residue from the bark of a particular ash or fir tree. Used as incense, perfume, or with an offering. \{Strong's: 3828\}\hfill{}\\

\textbf{FREE} Heb: {\large\H חפשי} hhaph-shi Def: Released from bondage or burden of obligation. Emancipation. \{Strong's: 2670\}\hfill{}\\

\textbf{FREE (Verb)} Heb: {\large\H חפש} hh.p.sh Def: To be free from a master or obligation. \{Strong's: 2666\}\hfill{}\\

\textbf{FREE.FLOWING} Heb: {\large\H דרור} de-ror Def: To flow without hindrances. \{Strong's: 1865\}\hfill{}\\

\textbf{FREEDOM} Heb: {\large\H חופשה} {[}X{]} Def: {[}X{]} \{Strong's: 2668\}\hfill{}\\

\textbf{FREELY} Heb: {\large\H חינם} hhi-nam Def: Having no restrictions. A work or action that is performed without wages or without cause. \{Strong's: 2600\}\hfill{}\\

\textbf{FREEWILL.OFFERING} Heb: {\large\H נדבה} ne-da-vah Def: A voluntary or spontaneous gift as an offering out of respect or devotion. \{Strong's: 5071\}\hfill{}\\

\textbf{FRESH} Heb: {\large\H לשד} {[}X{]} Def: Something that is fresh and moist. \{Strong's: 3955\}\hfill{}\\

\textbf{FRESH.OIL} Heb: {\large\H יצהר} {[}X{]} Def: {[}X{]} \{Strong's: 3323\}\hfill{}\\

\textbf{FRESH.WINE} Heb: {\large\H תירוש} ti-rosh Def: Newly pressed wine as a desired possession. \{Strong's: 8492\}\hfill{}\\

\textbf{FRIEND} Heb: {\large\H רעות} re-ut Def: A female companion as one who is close. \{Strong's: 7468\}\hfill{}\\

\textbf{FRINGE} Heb: {\large\H ציצית} tsi-tsit Def: A tassel or lock of hair as blossoms. \{Strong's: 6734\}\hfill{}\\

\textbf{FROG} Heb: {\large\H צפרדע} tse-phar-dey-a Def: A four-legged amphibious animal. \{Strong's: 6854\}\hfill{}\\

\textbf{FROM} Heb: {\large\H מין} min Def: A function word indicating a starting point or origin. \{Strong's: 4480, 4481\}\hfill{}\\

\textbf{FRUIT.PRESS} Heb: {\large\H דמע} de-ma Def: The liquid that seeps out of the fruit and used in making oils and juices. \{Strong's: 1831\}\hfill{}\\

\textbf{FRUITFUL} Heb: {\large\H ריבלה} {[}X{]} Def: A noun of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{FRUITFULNESS} Heb: {\large\H פרת} pa-tar Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{FRY (Verb)} Heb: {\large\H רבך} r.b.k Def: {[}X{]} \{Strong's: 7246\}\hfill{}\\

\textbf{FULL} Heb: {\large\H מלא} ma-ley Def: Containing as much or as many as is possible or normal. \{Strong's: 4392\}\hfill{}\\

\textbf{FULL.AGE} Heb: {\large\H כלח} {[}X{]} Def: {[}X{]} \{Strong's: 3624\}\hfill{}\\

\textbf{FULL.STRENGTH} Heb: {\large\H תום} tom Def: Someone or something that is whole or complete. Full in power or force. One who is mature. \{Strong's: 8537\}\hfill{}\\

\textbf{FUNCTIONAL} Heb: {\large\H טוב} tov \textbf{\textbackslash{}} {\large\H טובה} to-vah Def: Fulfilling the action for which a person or thing is specially fitted or used, or for which a thing exists. A functioning within its intended purpose. \{Strong's: 2896, 2898\}\hfill{}\\

\textbf{FURNACE} Heb: {\large\H כיבשן} kiv-shan Def: An enclosed structure in which heat is produced. \{Strong's: 3536\}\hfill{}\\

\textbf{FURROW} Heb: {\large\H תלם} {[}X{]} Def: Made by oxen plowing a field. \{Strong's: 8525\}\hfill{}\\

\textbf{FURTHER} Heb: {\large\H הלאה} hal-ah Def: At a distance beyond the present place or time. \{Strong's: 1973\}\hfill{}\\

\textbf{FURY} Heb: {\large\H חמה} hha-mah Def: Intense, disordered, and often destructive rage. An intense heat from anger. \{Strong's: 2528, 2534\}\hfill{}\\

\textbf{GALBANUM} Heb: {\large\H חלבנה} hhel-be-nah Def: An odoriferous resin used in incense. A choice ingredient used in the Temple incense or oil. \{Strong's: 2464\}\hfill{}\\

\textbf{GALL} Heb: {\large\H מרורה} {[}X{]} Def: The bitter fluids of a serpent. \{Strong's: 4846\}\hfill{}\\

\textbf{GAME} Heb: {\large\H צייד} tsa-yid Def: Animals being pursued or taken in hunting. The produce of the hunt. \{Strong's: 6718\}\hfill{}\\

\textbf{GARDEN} Heb: {\large\H גן} gan Def: A plot of ground where crops are grown. A place for growing crops, and often surrounded by a rock wall or hedge to protect it from grazing animals. \{Strong's: 1588\}\hfill{}\\

\textbf{GARLIC} Heb: {\large\H שום} {[}X{]} Def: From its strong odor. \{Strong's: 7762\}\hfill{}\\

\textbf{GARMENT} Heb: {\large\H בגד} be-ged Def: An article of clothing for covering. \{Strong's: 899\}\hfill{}\\

\textbf{GATE} Heb: {\large\H שער} sha-ar Def: The opening in a wall or fence through which livestock or people pass. Can be the gatekeeper. Also sha'ar, a unit of measurement. \{Strong's: 8179, 8651, 8652\}\hfill{}\\

\textbf{GATHER (Verb)} Heb: {\large\H אסף} a.s.p Def: To bring together; to accumulate and place in readiness. \{Strong's: 622\}\hfill{}\\

\textbf{GATHER.FOOD (Verb)} Heb: {\large\H אגר} a.g.r Def: {[}X{]} \{Strong's: 103\}\hfill{}\\

\textbf{GATHER.TOGETHER (Verb)} Heb: {\large\H קבץ} q.b.ts Def: To come or bring into a group, mass or unit. \{Strong's: 6908, 6910\}\hfill{}\\

\textbf{GATHERED.UP} Heb: {\large\H לק} laq Def: To bring together. Acquire. \{Strong's: n/a\}\hfill{}\\

\textbf{GATHERING} Heb: {\large\H אסיף} a-siph Def: That which has been brought together. {[}. \{Strong's: 614\}\hfill{}\\

\textbf{GAZELLE} Heb: {\large\H צבי} {[}X{]} \textbf{\textbackslash{}} {\large\H צביה} {[}X{]} Def: An animal of a herd in the sense of an army. \{Strong's: 6643, 6646\}\hfill{}\\

\textbf{GENERATION} Heb: {\large\H דור} dor Def: A body of living beings constituting a single step in the line of descent from an ancestor. \{Strong's: 1755, 1859\}\hfill{}\\

\textbf{GENITALS} Heb: {\large\H מבוש} {[}X{]} Def: The feeling of shame when exposed. \{Strong's: 4016\}\hfill{}\\

\textbf{GENTLE} Heb: {\large\H ענו} {[}X{]} Def: A characterstic trait of being meek or humble. \{Strong's: 6035\}\hfill{}\\

\textbf{GERAH} Heb: {\large\H גרה} ge-rah Def: A dry weight measure equal to a 20th part of a shekel. \{Strong's: 1626\}\hfill{}\\

\textbf{GIFT} Heb: {\large\H מנתן} ma-ten Def: To endow with some power, quality, or attribute; the act, power or right of giving. What is given. \{Strong's: 4976\}\hfill{}\\

\textbf{GIFT.OFFERING} Heb: {\large\H הב} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{GIRD (Verb)} Heb: {\large\H אפד} a.p.d Def: To pull in closely to the body. To wrap around. To tie on the ephod. \{Strong's: 640\}\hfill{}\\

\textbf{GIRD.UP (Verb)} Heb: {\large\H חגר} hh.g.r Def: To bind the loose portions of clothing into a belt or sash to prepare to go to war; to be bound with arms for war. \{Strong's: 2296\}\hfill{}\\

\textbf{GIRL} Heb: {\large\H ילדה} yal-dah Def: A young, unmarried woman. \{Strong's: 3207\}\hfill{}\\

\textbf{GIVE (Verb)} Heb: {\large\H נתן} n.t.n Def: To make a present; to present a gift; to grant, allow or bestow by formal action. \{Strong's: 5414\}\hfill{}\\

\textbf{GIVE.A.TENTH (Verb)} Heb: {\large\H עסר} ah.s.r Def: To tithe; a tenth part of something given voluntarily for the support of a religious establishment. \{Strong's: 6237\}\hfill{}\\

\textbf{GIVE.ADVICE (Verb)} Heb: {\large\H יעץ} y.ah.ts Def: To assist another by providing wise counsel. \{Strong's: 3272, 3289\}\hfill{}\\

\textbf{GIVE.AN.EAR.TO (Verb)} Heb: {\large\H אזן} a.z.n Def: To pay attention to a voice or sound; to hear with thoughtful attention and obedience. \{Strong's: 238, 239\}\hfill{}\\

\textbf{GIVE.HONOR (Verb)} Heb: {\large\H הדר} h.d.r Def: Someone or something that is wide in size or majesty. To honor. To puff up. \{Strong's: 1921, 1922\}\hfill{}\\

\textbf{GIVE.MILK (Verb)} Heb: {\large\H גול} g.w.l Def: To provide nourishment to the young by the female. \{Strong's: 5763\}\hfill{}\\

\textbf{GIVEN.THAT} Heb: {\large\H כי} ki Def: Prone or disposed to according to what preceded. A reference to the previous or following context. \{Strong's: 3588\}\hfill{}\\

\textbf{GLEANINGS} Heb: {\large\H לקט} {[}X{]} Def: {[}X{]} \{Strong's: 3951\}\hfill{}\\

\textbf{GLIMMER} Heb: {\large\H להב} {[}X{]} Def: The flash of light from a fire or metal. \{Strong's: 3851\}\hfill{}\\

\textbf{GLIMMERING} Heb: {\large\H להבה} leh-ha-vah Def: The flash of light from a fire or metal. \{Strong's: 3827, 3852\}\hfill{}\\

\textbf{GLISTENING} Heb: {\large\H צוהר} tso-har Def: Emitting or reflecting light. From the glisten of olive oil. Something that shines brightly. Also, noon as the brightest part of the day. \{Strong's: 2096, 6672\}\hfill{}\\

\textbf{GLORIOUS.REST} Heb: {\large\H פענח} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{GLUTTON (Verb)} Heb: {\large\H זלל} z.l.l Def: A shaking from fear or overeating. \{Strong's: 2151, 6750\}\hfill{}\\

\textbf{GNAT} Heb: {\large\H כן} keyn Def: A small flying insect. \{Strong's: 3654\}\hfill{}\\

\textbf{GNAW (Verb)} Heb: {\large\H גרם} g.r.m Def: {[}X{]} \{Strong's: 1633\}\hfill{}\\

\textbf{GNAWED} Heb: {\large\H ערק} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{GO (Verb)} Heb: {\large\H שוט} sh.w.t Def: To go back an forth as a whip. \{Strong's: 7751\}\hfill{}\\

\textbf{GO.ABOUT} Heb: {\large\H סבתה} sa-mal Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{GO.AROUND (Verb)} Heb: {\large\H סבב} s.b.b Def: To circle completely around something. \{Strong's: 5437\}\hfill{}\\

\textbf{GO.ASIDE (Verb)} Heb: {\large\H סטה} s.t.h Def: To turn aside or away. \{Strong's: 7847\}\hfill{}\\

\textbf{GO.ASTRAY (Verb)} Heb: {\large\H שגה} sh.g.h Def: {[}X{]} \{Strong's: 7686\}\hfill{}\\

\textbf{GO.DOWN (Verb)} Heb: {\large\H ירד} y.r.d Def: To go or come lower from a higher place. The hiphil (causative) form means ``bring down.'' \{Strong's: 3381\}\hfill{}\\

\textbf{GO.OUT (Verb)} Heb: {\large\H יצא} y.ts.a Def: To go, come or issue forth. \{Strong's: 3318, 3319\}\hfill{}\\

\textbf{GO.RIGHT (Verb)} Heb: {\large\H ימן} y.m.n Def: To choose, turn or go to the right hand. \{Strong's: 541, 3231\}\hfill{}\\

\textbf{GO.UP (Verb)} Heb: {\large\H עלה} ah.l.h Def: To go, come or bring higher. The hiphil (causative) form means ``bring up.'' \{Strong's: 5924, 5927\}\hfill{}\\

\textbf{GOBLET} Heb: {\large\H אגן} a-nan Def: A cup for containing liquids. \{Strong's: 101\}\hfill{}\\

\textbf{GOING.OUT} Heb: {\large\H מוצא} {[}X{]} Def: Coming or issuing out, such as a spring or words from the mouth. \{Strong's: 4161\}\hfill{}\\

\textbf{GOINGS} Heb: {\large\H תוצאה} {[}X{]} Def: {[}X{]} \{Strong's: 8444\}\hfill{}\\

\textbf{GOLD} Heb: {\large\H זהב} za-hav Def: A malleable yellow metallic element that is used especially in coins, jewelry, and dentures. A precious metal. \{Strong's: 1722, 2091\}\hfill{}\\

\textbf{GOODS} Heb: {\large\H רכוש} re-khush Def: Something that has economic utility or satisfies an economic want; personal property having intrinsic value but usually excluding money, securities and negotiable instruments. \{Strong's: 7399\}\hfill{}\\

\textbf{GOPHER} Heb: {\large\H גופר} go-pher Def: Wood from an unknown tree. \{Strong's: 1613\}\hfill{}\\

\textbf{GORE (Verb)} Heb: {\large\H נגח} n.g.hh Def: To stab with the horns. \{Strong's: 5055\}\hfill{}\\

\textbf{GORER} Heb: {\large\H נגח} na-gahh Def: An ox that is known to gore with the horns. \{Strong's: 5056\}\hfill{}\\

\textbf{GOVERNOR} Heb: {\large\H שליט} sha-lit Def: An official elected or appointed to act as ruler, chief executive, or nominal head of a political unit. One who has dominion over another; also a rule or law as a master. \{Strong's: 7989, 7990\}\hfill{}\\

\textbf{GRAIN} Heb: {\large\H בר} bar Def: A seed or fruit of a cereal grass. The grain and the field as a place for growing grain. \{Strong's: 1250, 1251\}\hfill{}\\

\textbf{GRAIN.FLOUR} Heb: {\large\H קמח} qe-mahh Def: Usually finely ground seeds of wheat. \{Strong's: 7058\}\hfill{}\\

\textbf{GRAIN.SACK} Heb: {\large\H אמתחת} am-ta-hhat Def: A usually flexible container that may be closed for holding, storing, or carrying something; e.g. The mouth is spread apart to put something in or take something out. \{Strong's: 572\}\hfill{}\\

\textbf{GRAIN.SEEDS} Heb: {\large\H שבל} she-ver Def: A family of grasses used for food. As traded or sold. \{Strong's: 7668\}\hfill{}\\

\textbf{GRAIN.STALK} Heb: {\large\H קמה} qa-mah Def: The tall stem of cereal crops. \{Strong's: 7054\}\hfill{}\\

\textbf{GRAPE} Heb: {\large\H ענב} ey-nav Def: A smooth-skinned juicy greenish white to deep red or purple berry grown on a vine and eaten dried or fresh as a fruit or fermented to produce wine. \{Strong's: 6025\}\hfill{}\\

\textbf{GRAPE.BLOSSOM} Heb: {\large\H נץ} nets Def: The flower of a seed plant. From its bright color and shape as like a spark. Also, an unknown bird of prey. \{Strong's: 5322\}\hfill{}\\

\textbf{GRAPE.SKIN} Heb: {\large\H זג} {[}X{]} Def: {[}X{]} \{Strong's: 2085\}\hfill{}\\

\textbf{GRAPEVINE} Heb: {\large\H גפן} ge-phen Def: A woody vine that usually climbs by tendrils and produces fruits that are grapes. \{Strong's: 1612\}\hfill{}\\

\textbf{GRAPPLE (Verb)} Heb: {\large\H אבק} a.b.q Def: A hand-to-hand struggle. Rolling around in the dust when wrestling. \{Strong's: 79\}\hfill{}\\

\textbf{GRASP} Heb: {\large\H חוזק} hho-zeq Def: A firm hold or grip. \{Strong's: 2392\}\hfill{}\\

\textbf{GRASP (Verb)} Heb: {\large\H קמץ} q.m.ts Def: To grab with the hands, to grab a handful. \{Strong's: 7061\}\hfill{}\\

\textbf{GRASS} Heb: {\large\H דשא} de-she Def: Herbage suitable or used for grazing animals. Young green sprouts. \{Strong's: 1877, 1883\}\hfill{}\\

\textbf{GRASSHOPPER} Heb: {\large\H חגב} {[}X{]} Def: {[}X{]} \{Strong's: 2284\}\hfill{}\\

\textbf{GRATE} Heb: {\large\H מכבר} mikh-bar Def: An agricultural device, like a sieve, used to separate the grain form the stem. \{Strong's: 4345\}\hfill{}\\

\textbf{GRAVE} Heb: {\large\H קבר} qe-ver Def: An excavation for the burial of a body. \{Strong's: 6913\}\hfill{}\\

\textbf{GRAY} Heb: {\large\H קדר} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{GRAY.HEADED} Heb: {\large\H סיבה} si-vah Def: One who has gray hair from old age; an old man. \{Strong's: 7872\}\hfill{}\\

\textbf{GREAT} Heb: {\large\H גדול} ga-dol \textbf{\textbackslash{}} {\large\H גדולה} ge-do-lah Def: Something with increased size, power or authority. \{Strong's: 1419\}\hfill{}\\

\textbf{GREAT.AMOUNT} Heb: {\large\H תרבות} {[}X{]} Def: {[}X{]} \{Strong's: 8635\}\hfill{}\\

\textbf{GREAT.HOUSE} Heb: {\large\H פרעוה} par-o Def: A word of Egyptian origins. \{Strong's: n/a\}\hfill{}\\

\textbf{GREAT.NUMBER} Heb: {\large\H מרבית} {[}X{]} Def: {[}X{]} \{Strong's: 4768\}\hfill{}\\

\textbf{GREAT.TREE} Heb: {\large\H אלון} a-lon Def: The strongest of the woods. \{Strong's: 436, 437\}\hfill{}\\

\textbf{GREEN} Heb: {\large\H ירק} ye-req Def: A color somewhat less yellow than that of fresh growing grass and of that part of the spectrum between blue and yellow. The color of grasses and herbs as thin. \{Strong's: 3418, 3419\}\hfill{}\\

\textbf{GREEN.GRAIN} Heb: {\large\H אביב} a-viv Def: Fresh young stalks of standing grain. Also the name of a month in the Hebrew calendar. \{Strong's: 24\}\hfill{}\\

\textbf{GREENISH} Heb: {\large\H ירקרק} {[}X{]} Def: {[}X{]} \{Strong's: 3422\}\hfill{}\\

\textbf{GRIEF} Heb: {\large\H מורה} mo-rah Def: Deep and poignant distress caused by or as if by bereavement. As an exchange. \{Strong's: 4786\}\hfill{}\\

\textbf{GRIND (Verb)} Heb: {\large\H טחן} t.hh.n Def: To reduce to fine particles through abrasion. \{Strong's: 2912\}\hfill{}\\

\textbf{GROANING} Heb: {\large\H נאקה} ne-a-qah Def: To voice a deep, inarticulate sound, as of pain, grief, or displeasure. \{Strong's: 5009\}\hfill{}\\

\textbf{GROPE (Verb)} Heb: {\large\H משש} m.sh.sh Def: To feel about blindly or uncertainly in search of something. A groping around in the darkness to find something. \{Strong's: 4184, 4959\}\hfill{}\\

\textbf{GROUND} Heb: {\large\H אדמה} a-da-mah Def: The surface of the earth. From its reddish color. \{Strong's: 127\}\hfill{}\\

\textbf{GROUND.TO.PIECES (Verb)} Heb: {\large\H דוך} d.w.k Def: {[}X{]} \{Strong's: 1743, 1751\}\hfill{}\\

\textbf{GROUSE} Heb: {\large\H דוכיפת} {[}X{]} Def: {[}X{]} \{Strong's: 1744\}\hfill{}\\

\textbf{GROVE} Heb: {\large\H אשרה} a-shey-rah Def: An area of planted trees. Trees planted in a straight line. \{Strong's: 842\}\hfill{}\\

\textbf{GROW (Verb)} Heb: {\large\H שבן} sh.b.n Def: {[}NOTE: Dictionary entry needs attention{]}. \{Strong's: n/a\}\hfill{}\\

\textbf{GROW.FAT (Verb)} Heb: {\large\H שמן} sh.m.n Def: To be fat or full of oil. \{Strong's: 8080\}\hfill{}\\

\textbf{GUARD} Heb: {\large\H שימרון} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{GUIDE (Verb)} Heb: {\large\H נחה} n.hh.h Def: One who leads or directs another in his way. \{Strong's: 5148\}\hfill{}\\

\textbf{GUILT} Heb: {\large\H אשם} a-sham Def: The fact of having committed a breach of conduct especially violating law and involving a penalty; the state of one who has committed an offense, especially consciously. \{Strong's: 817, 818\}\hfill{}\\

\textbf{GUILTINESS} Heb: {\large\H אשמה} {[}X{]} Def: {[}X{]} \{Strong's: 819\}\hfill{}\\

\textbf{GULP (Verb)} Heb: {\large\H שתה} sh.t.h Def: To drink plentifully; to swallow hurriedly or greedily or in one swallow. \{Strong's: 8354, 8355\}\hfill{}\\

\textbf{GUST (Verb)} Heb: {\large\H נשב} n.sh.b Def: A sudden brief rush of wind. The strong blowing of a wind. The wind of a bird's wing when taking flight. \{Strong's: 5380\}\hfill{}\\

\textbf{GUZZLE (Verb)} Heb: {\large\H גמא} g.m.a Def: To drink greedily, continually, or habitually. A drinking of water as from a pond. \{Strong's: 1572\}\hfill{}\\

\textbf{HABITATION} Heb: {\large\H מעון} {[}X{]} \textbf{\textbackslash{}} {\large\H מעונה} {[}X{]} Def: The dwelling place of a god (temple), man (home) or animal (den). Also a retreat. \{Strong's: 4583, 4585\}\hfill{}\\

\textbf{HAILSTONES} Heb: {\large\H ברד} ba-rad Def: A precipitation in the form of irregular pellets or balls of ice. \{Strong's: 1259\}\hfill{}\\

\textbf{HAIR} Heb: {\large\H סער} sey-ar \textbf{\textbackslash{}} {\large\H סערה} {[}X{]} Def: The covering of filaments on a human head or the body of an animal. \{Strong's: 8177, 8181, 8185\}\hfill{}\\

\textbf{HAIRY} Heb: {\large\H סעיר} sa-ir \textbf{\textbackslash{}} {\large\H סעירה} {[}X{]} Def: Being of an unusual amount of hair, often in reference to a goat. \{Strong's: 8163, 8166\}\hfill{}\\

\textbf{HALF} Heb: {\large\H חצי} hha-tsi Def: An equal part of something divided into two pieces. \{Strong's: 2677\}\hfill{}\\

\textbf{HALF.THE.SPOILS} Heb: {\large\H מחצה} me-hhe-tsat Def: {[}X{]} \{Strong's: 4275\}\hfill{}\\

\textbf{HALTER} Heb: {\large\H רסן} {[}X{]} Def: For leading an animal. \{Strong's: 7448\}\hfill{}\\

\textbf{HAMMER (Verb)} Heb: {\large\H רקע} r.q.ah Def: To beat a malleable metal with a hammer to make thin sheets. \{Strong's: 7554\}\hfill{}\\

\textbf{HAND} Heb: {\large\H יד} yad Def: The terminal, functional part of the forelimb. Hand with the ability to work, throw and give thanks. Also euphemistically for the arm. \{Strong's: 3027, 3028, 3197\}\hfill{}\\

\textbf{HAND.OVER (Verb)} Heb: {\large\H ירט} y.r.t Def: {[}X{]} \{Strong's: 3399\}\hfill{}\\

\textbf{HAND.SPAN} Heb: {\large\H טפח} te-phahh Def: A linear standard of measure that is equal to the span of the fingers of the hand. \{Strong's: 2947\}\hfill{}\\

\textbf{HANDFUL} Heb: {\large\H קומץ} qo-mets Def: As much of or as many as the hand can grasp. \{Strong's: 7062\}\hfill{}\\

\textbf{HANG (Verb)} Heb: {\large\H תלה} t.l.h Def: To suspend with no support from below. \{Strong's: 8511, 8518\}\hfill{}\\

\textbf{HAPPINESS} Heb: {\large\H אושר} o-sher Def: A state of well-being and contentment. One who is happy is one whose life is lived straightly. \{Strong's: 837\}\hfill{}\\

\textbf{HAPPY} Heb: {\large\H אשר} a-sheyr Def: A feeling of joy or satisfaction. \{Strong's: 835\}\hfill{}\\

\textbf{HAPPY (Verb)} Heb: {\large\H אשר} a.sh.r Def: Enjoying well-being and contentment. One who is happy is one whose life is lived straightly. \{Strong's: 833\}\hfill{}\\

\textbf{HARASS (Verb)} Heb: {\large\H צוך} ts.w.k Def: To press into a tight place, an oppression. \{Strong's: 6693\}\hfill{}\\

\textbf{HARD} Heb: {\large\H קשה} qa-sheh Def: Not easily penetrated; resistant to stress; firm; lacking in responsiveness. \{Strong's: 7186\}\hfill{}\\

\textbf{HARDSHIP} Heb: {\large\H עיצבון} i-tsa-von Def: Privation; suffering; something that causes or entails suffering or privation. \{Strong's: 6093\}\hfill{}\\

\textbf{HARE} Heb: {\large\H ארנבת} {[}X{]} Def: {[}X{]} \{Strong's: 768\}\hfill{}\\

\textbf{HARM} Heb: {\large\H אסון} a-son Def: Physical or mental damage; injury. The pain from the thorn. \{Strong's: 611\}\hfill{}\\

\textbf{HARNESS} Heb: {\large\H שיריון} shir-yon Def: An armor made from tightly wound cords of leather. \{Strong's: 5630, 8302\}\hfill{}\\

\textbf{HARP} Heb: {\large\H כינור} ki-nor Def: A plucked stringed musical instrument; \{Strong's: 3658\}\hfill{}\\

\textbf{HARVEST} Heb: {\large\H קציר} qa-tsir Def: The season for gathering agricultural crops. Time when the plants are severed from their roots to be used for seed or food. \{Strong's: 7105\}\hfill{}\\

\textbf{HASTE} Heb: {\large\H חיפזון} hhi-pha-zon Def: A hurried action. \{Strong's: 2649\}\hfill{}\\

\textbf{HASTE (Verb)} Heb: {\large\H חפז} hh.p.z Def: To hurry in flight. \{Strong's: 2648\}\hfill{}\\

\textbf{HASTILY} Heb: {\large\H עושם} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{HASTY} Heb: {\large\H עוש} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{HATE} Heb: {\large\H סנאה} {[}X{]} Def: {[}X{]} \{Strong's: 8135\}\hfill{}\\

\textbf{HATE (Verb)} Heb: {\large\H סנא} s.n.a Def: Intense hostility and aversion, usually deriving from fear, anger, or sense of injury; extreme dislike or antipathy. \{Strong's: 8130, 8131\}\hfill{}\\

\textbf{HATED} Heb: {\large\H סניא} {[}X{]} \textbf{\textbackslash{}} {\large\H סניאה} {[}X{]} Def: {[}X{]} \{Strong's: 8146\}\hfill{}\\

\textbf{HAVE.COMPASSION (Verb)} Heb: {\large\H רחם} r.hh.m Def: To have a feeling of deep sympathy and sorrow for another who is stricken by misfortune, accompanied by a strong desire to alleviate the suffering. \{Strong's: 7355\}\hfill{}\\

\textbf{HAVE.HORNS (Verb)} Heb: {\large\H קרן} q.r.n Def: One of a pair of bony processes that arise from the head of many animals, sometimes used as a wind instrument. The horn-shaped protrusions of the altar or a musical instrument. \{Strong's: 7160\}\hfill{}\\

\textbf{HAVING.AN.EYE} Heb: {\large\H עינן} ey-nan Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{HAWK} Heb: {\large\H איה} a-yah Def: {[}X{]} \{Strong's: 344\}\hfill{}\\

\textbf{HAZEL} Heb: {\large\H לוז} luz Def: A light brown to strong yellowish brown color; small trees or shrubs bearing nuts enclosed in a leafy involucres. \{Strong's: 3869\}\hfill{}\\

\textbf{HE} Heb: {\large\H הוא} hu Def: The male who is neither speaker nor hearer. \{Strong's: 1931, 1932\}\hfill{}\\

\textbf{HE.GOAT} Heb: {\large\H תיש} ta-yish Def: A male goat. \{Strong's: 8495\}\hfill{}\\

\textbf{HEAD} Heb: {\large\H ראש} rosh Def: The top of the body. A person in authority or role of leader. The top, beginning or first of something. \{Strong's: 7217, 7218, 7389\}\hfill{}\\

\textbf{HEAD.OF.WHEAT} Heb: {\large\H מלילה} {[}X{]} Def: A conglomeration of grain seeds together. \{Strong's: 4425\}\hfill{}\\

\textbf{HEADDRESS} Heb: {\large\H מגביעת} mig-ba-at Def: A bowl shaped covering for the head. A covering for protection. \{Strong's: 4021\}\hfill{}\\

\textbf{HEADREST} Heb: {\large\H מראשה} me-ra-a-shah Def: A support for the head. Place where the head is laid. \{Strong's: 4763\}\hfill{}\\

\textbf{HEAL (Verb)} Heb: {\large\H רפא} r.p.a Def: To restore to health or wholeness. \{Strong's: 7495\}\hfill{}\\

\textbf{HEAP} Heb: {\large\H נד} neyd Def: A large pile dirt or rubbish. \{Strong's: 5067\}\hfill{}\\

\textbf{HEAR (Verb)} Heb: {\large\H שמע} sh.m.ah Def: To perceive or apprehend by the ear; to listen to with attention. To obey. \{Strong's: 8085, 8086\}\hfill{}\\

\textbf{HEARER} Heb: {\large\H שימעון} shi-mon Def: One who listens. The one who acts upon what he has heard. \{Strong's: n/a\}\hfill{}\\

\textbf{HEARING} Heb: {\large\H משמע} {[}X{]} Def: {[}X{]} \{Strong's: 4926\}\hfill{}\\

\textbf{HEART} Heb: {\large\H לב} leyv Def: Literally, the vital organ which pumps blood, but, also seen as the seat of thought; the mind. \{Strong's: 1079, 3820, 3821, 3824, 3825\}\hfill{}\\

\textbf{HEAT (Verb)} Heb: {\large\H יחם} y.hh.m Def: Natural body warmth, as well as the time of estrous when animals mate. Conception from an animal’s mating or through the heat of passion. \{Strong's: 3179\}\hfill{}\\

\textbf{HEAVINESS} Heb: {\large\H כבדות} ke-vey-dut Def: A physical or spiritual weight. A sadness or burden. \{Strong's: 3517\}\hfill{}\\

\textbf{HEAVY} Heb: {\large\H כבד} ka-ved Def: Having great weight. Something that is weighty. May also be grief or sadness in the sense of heaviness. Also, the liver as the heaviest of the organs. \{Strong's: 3515, 3516\}\hfill{}\\

\textbf{HEAVY.BURDEN} Heb: {\large\H טורח} {[}X{]} Def: {[}X{]} \{Strong's: 2960\}\hfill{}\\

\textbf{HEEL} Heb: {\large\H עקב} e-qev Def: What is restrained when taking a step forward. \{Strong's: 6119, 6120\}\hfill{}\\

\textbf{HEIFER} Heb: {\large\H עגלה} eg-lah Def: A young cow, especially one that has not had a calf. \{Strong's: 5697\}\hfill{}\\

\textbf{HEIGHT} Heb: {\large\H קומה} qo-mah Def: The highest part or most advanced point; the condition of being tall or high. In the sense of being raised up. \{Strong's: 6967\}\hfill{}\\

\textbf{HEIR} Heb: {\large\H נין} nin Def: One who inherits or is entitled to inherit property. \{Strong's: 5209\}\hfill{}\\

\textbf{HELP} Heb: {\large\H עזר} e-zer \textbf{\textbackslash{}} {\large\H עזרה} ez-rah Def: Providing assistance or relief to another. One who comes to assist with a trouble or burden. \{Strong's: 5828, 5833\}\hfill{}\\

\textbf{HELP (Verb)} Heb: {\large\H עזר} ah.z.r Def: To give assistance or support to. \{Strong's: 5826\}\hfill{}\\

\textbf{HEM} Heb: {\large\H שול} shul Def: The outer edge of a garment. \{Strong's: 7757\}\hfill{}\\

\textbf{HERB} Heb: {\large\H עשב} ey-sev Def: The grasses and plants of the field used for their medicinal, savory, or aromatic qualities. \{Strong's: 6211, 6212\}\hfill{}\\

\textbf{HERBAGE} Heb: {\large\H חסיל} {[}X{]} Def: A plant used as food for men and animals as grown in the yard. \{Strong's: 2682\}\hfill{}\\

\textbf{HERE} Heb: {\large\H פו} po Def: In or at this place. \{Strong's: 6311\}\hfill{}\\

\textbf{HERITAGE} Heb: {\large\H ירושה} {[}X{]} Def: {[}X{]} \{Strong's: 3425\}\hfill{}\\

\textbf{HEW (Verb)} Heb: {\large\H חצב} hh.ts.b Def: {[}X{]} \{Strong's: 2672\}\hfill{}\\

\textbf{HEWN.ONE} Heb: {\large\H גדעון} gid-on Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{HEWN.STONE} Heb: {\large\H גזית} ga-zit Def: Stones that are sheered or chipped to form flat sides or an object. \{Strong's: 1496\}\hfill{}\\

\textbf{HHOLED} Heb: {\large\H חולד} {[}X{]} Def: An unknown animal that burrows in the ground. \{Strong's: 2467\}\hfill{}\\

\textbf{HHOMET} Heb: {\large\H חומט} {[}X{]} Def: An unknown animal. \{Strong's: 2546\}\hfill{}\\

\textbf{HIDDEN} Heb: {\large\H נחבי} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{HIDE (Verb)} Heb: {\large\H סתר} s.t.r Def: To put out of sight; to conceal from view; to keep secret. Hide or conceal. \{Strong's: 5641, 5642, 8368\}\hfill{}\\

\textbf{HIDING} Heb: {\large\H סתר} {[}X{]} \textbf{\textbackslash{}} {\large\H סיתרה} {[}X{]} Def: A shelter or other place of hiding. \{Strong's: 5643\}\hfill{}\\

\textbf{HIDING.PLACE} Heb: {\large\H חובה} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{HIGH} Heb: {\large\H גבוה} ga-vo-ah Def: Advanced in height such as a wall or hill. \{Strong's: 1364\}\hfill{}\\

\textbf{HIGH.LAND} Heb: {\large\H אררט} {[}X{]} Def: {[}X{]} \{Strong's: 780\}\hfill{}\\

\textbf{HIGH.ONE} Heb: {\large\H סיון} si-on Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{HIGHWAY} Heb: {\large\H מסילה} {[}X{]} Def: A road constructed above the surrounding area. \{Strong's: 4546\}\hfill{}\\

\textbf{HILL} Heb: {\large\H הר} har Def: An elevation of land such as a hill or mountain. \{Strong's: 2022\}\hfill{}\\

\textbf{HILL.COUNTRY} Heb: {\large\H הרן} har Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{HIP} Heb: {\large\H נשה} na-she Def: Each side of the trunk formed by the lateral parts of the pelvis and upper part of the femur (thigh bone) together with the fleshy parts covering them. \{Strong's: 5384\}\hfill{}\\

\textbf{HIPS} Heb: {\large\H כסל} {[}X{]} Def: The seat of confidence. In a foolish or proper manner. \{Strong's: 3689, 5529, 5530\}\hfill{}\\

\textbf{HIRE (Verb)} Heb: {\large\H שכר} sh.k.r Def: Payment for labor or personal services; to engage the personal service of another. \{Strong's: 7936\}\hfill{}\\

\textbf{HIRELING} Heb: {\large\H שכיר} se-khir Def: One who is hired for service and receives compensation. \{Strong's: 7916\}\hfill{}\\

\textbf{HIT (Verb)} Heb: {\large\H נכה} n.k.h Def: To deliver a blow by action; to strike with the hand; to clap, kill or harm. \{Strong's: 5221\}\hfill{}\\

\textbf{HITTING} Heb: {\large\H סבתכא} {[}X{]} Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{HIYN} Heb: {\large\H הין} hin Def: A liquid measure equal to about 5 quarts (6 liters). \{Strong's: 1969\}\hfill{}\\

\textbf{HOARFROST} Heb: {\large\H כפור} ke-phor Def: A covering of small ice crystals, formed from frozen water vapor. \{Strong's: 3713\}\hfill{}\\

\textbf{HOLD.A.FEAST (Verb)} Heb: {\large\H חגג} hh.g.g Def: The act of performing a celebration. \{Strong's: 2287\}\hfill{}\\

\textbf{HOLD.A.GRUDGE (Verb)} Heb: {\large\H סטם} s.t.m Def: Be unwilling to give in or admit to. \{Strong's: 7852\}\hfill{}\\

\textbf{HOLD.BACK (Verb)} Heb: {\large\H אפק} a.p.q Def: To hinder the progress or achievement of; restrain, as the banks of a river hold back the water. \{Strong's: 662\}\hfill{}\\

\textbf{HOLD.UP (Verb)} Heb: {\large\H סעד} s.ah.d Def: To continue in the same condition without failing or losing effectiveness or force. Be a support or aid for strength or rest. \{Strong's: 5582, 5583\}\hfill{}\\

\textbf{HOLDINGS} Heb: {\large\H אחוזה} a-hhu-zah Def: Property that is held or owned. \{Strong's: 272\}\hfill{}\\

\textbf{HOLLOW.OUT (Verb)} Heb: {\large\H קבב} q.b.b Def: To pierce through creating a cavity. \{Strong's: 6895\}\hfill{}\\

\textbf{HONEY} Heb: {\large\H דבש} de-vash Def: A sweet material elaborated out of the nectar of flowers in the honey sac of various bees. Also, dates as a thick, sticky and sweet food. \{Strong's: 1706\}\hfill{}\\

\textbf{HONOR} Heb: {\large\H הדר} {[}X{]} Def: Someone or something that has been enlarged in size, pride or majesty. \{Strong's: 1923, 1925, 1926\}\hfill{}\\

\textbf{HOOD} Heb: {\large\H מסוה} mas-weh Def: A covering of the entire head and face. \{Strong's: 4533\}\hfill{}\\

\textbf{HOOK} Heb: {\large\H קרס} qe-res Def: A straight piece of wood or metal that is bent at one end. \{Strong's: 7165\}\hfill{}\\

\textbf{HOP (Verb)} Heb: {\large\H פסח} p.s.hh Def: To jump from one position to another. Also, to be lame, as one who hops on one leg. \{Strong's: 6452\}\hfill{}\\

\textbf{HOPPING} Heb: {\large\H פסח} pe-sahh Def: The feast celebrating the ``hopping'' (usually called ``Passover'' but more literally means ``hop over''). \{Strong's: n/a\}\hfill{}\\

\textbf{HORDE} Heb: {\large\H ערוב} a-rov Def: A large swarm of flies in the sense of a mixture. Also used for a large group of people. \{Strong's: 6157\}\hfill{}\\

\textbf{HORN} Heb: {\large\H קרן} qe-ren Def: One of a pair of bony processes that arise from the head of many animals and used as a wind instrument. The horns of an animal or a musical instrument in the shape of a horn. \{Strong's: 7161, 7162\}\hfill{}\\

\textbf{HORNET} Heb: {\large\H צירעה} tsir-ah Def: A flying insect with a stinger that is capable of causing serious injury or death to one that is stung. \{Strong's: 6880\}\hfill{}\\

\textbf{HORSE} Heb: {\large\H סוס} sus Def: A domesticated animal used as a beast of burden, a draft animal or for riding. \{Strong's: 5483\}\hfill{}\\

\textbf{HORSEMAN} Heb: {\large\H פרש} pa-rash Def: One that rides a horse. \{Strong's: 6571\}\hfill{}\\

\textbf{HOSTILITY} Heb: {\large\H איבה} ey-vah Def: Conflict, opposition, or resistance; overt acts of warfare. \{Strong's: 342\}\hfill{}\\

\textbf{HOT} Heb: {\large\H חום} hhom Def: Having a relatively high temperature; eager; passionate. \{Strong's: 2525, 2527\}\hfill{}\\

\textbf{HOT.SPRING} Heb: {\large\H ימים} yeymim Def: A spring with water above body temperature. \{Strong's: 3222\}\hfill{}\\

\textbf{HOUSE} Heb: {\large\H בית} beyt Def: The structure or the family, as a household that resides within the house. A housing. Within. \{Strong's: 1004, 1005\}\hfill{}\\

\textbf{HOW} Heb: {\large\H איך} eykh Def: In what way or manner; by what means. \{Strong's: 349\}\hfill{}\\

\textbf{HOW.LONG} Heb: {\large\H מתי} ma-tai Def: An unknown duration of time. \{Strong's: 4970\}\hfill{}\\

\textbf{HOWL (Verb)} Heb: {\large\H יבב} y.b.b Def: {[}X{]} \{Strong's: 2980\}\hfill{}\\

\textbf{HOWLING} Heb: {\large\H ילל} {[}X{]} Def: {[}X{]} \{Strong's: 3214\}\hfill{}\\

\textbf{HUMAN} Heb: {\large\H אדם} a-dam Def: Of, relating to, or characteristic of man. The first man. All of mankind as the descendants of the first man. \{Strong's: 120\}\hfill{}\\

\textbf{HUNCHBACK} Heb: {\large\H גיבן} {[}X{]} Def: As a lump of the back. \{Strong's: 1384\}\hfill{}\\

\textbf{HUNDRED} Heb: {\large\H מאה} mey-ah Def: A specific number but also a large amount without any reference to a specific number. \{Strong's: 3967, 3969\}\hfill{}\\

\textbf{HUNGER} Heb: {\large\H רעב} ra-eyv Def: A craving or urgent need for food. \{Strong's: 7457, 7458\}\hfill{}\\

\textbf{HUNT (Verb)} Heb: {\large\H ציד} ts.y.d Def: To attempt to find something with the intent to capture. Hunt in the sense of laying in ambush. \{Strong's: 6679\}\hfill{}\\

\textbf{HUNTER} Heb: {\large\H ציד} tsa-yad Def: One who searches for something. Lays in ambush. \{Strong's: 6719\}\hfill{}\\

\textbf{HUNTING} Heb: {\large\H צידון} tsa-yid Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{HURL (Verb)} Heb: {\large\H טחה} t.hh.h Def: To throw down with violence. The area which a bow can be shot from a central point. \{Strong's: 2909\}\hfill{}\\

\textbf{HURRY (Verb)} Heb: {\large\H מהר} m.h.r Def: To carry or cause to go with haste. \{Strong's: 4116, 4117\}\hfill{}\\

\textbf{HUT} Heb: {\large\H קובה} {[}X{]} Def: As a cavity. \{Strong's: 6898\}\hfill{}\\

\textbf{HYSSOP} Heb: {\large\H אזוב} ey-zov Def: An aromatic herb whose twigs were used in ceremonial sprinkling. \{Strong's: 231\}\hfill{}\\

\textbf{I} Heb: {\large\H אני} a-ni Def: A person aware of possessing a personal identity in self-reference. \{Strong's: 576, 589, 595\}\hfill{}\\

\textbf{ICE} Heb: {\large\H קרח} qe-rahh Def: Frozen water. Cold ice, frost or crystals. \{Strong's: 7140\}\hfill{}\\

\textbf{IDOL} Heb: {\large\H גלול} {[}X{]} Def: The image of a god made from wood or stone that is revered. \{Strong's: 1544\}\hfill{}\\

\textbf{IF} Heb: {\large\H אים} im Def: Allowing that; on condition that. A desire to bind two ideas together. \{Strong's: 518\}\hfill{}\\

\textbf{IGNITING} Heb: {\large\H בעור} {[}X{]} Def: \{Strong's: n/a\}\hfill{}\\

\textbf{ILL (Verb)} Heb: {\large\H דוה} d.w.h Def: {[}X{]} \{Strong's: 1738\}\hfill{}\\

\textbf{ILLNESS} Heb: {\large\H דוה} {[}X{]} Def: Also a woman's cycle. \{Strong's: 1739\}\hfill{}\\

\textbf{IMAGE} Heb: {\large\H צלם} tse-lem Def: A reproduction or imitation of the form of a person or thing. The form of something as a shadow of the original. \{Strong's: 6754, 6755\}\hfill{}\\

\textbf{IMAGERY} Heb: {\large\H מצקית} {[}X{]} Def: The casting of an image. \{Strong's: 4906\}\hfill{}\\

\textbf{IMAGINATION} Heb: {\large\H שרירות} {[}X{]} Def: A twisting together of thoughts. \{Strong's: 8307\}\hfill{}\\

\textbf{IMAGING} Heb: {\large\H צלמונה} tsal-mo-nah Def: \{Strong's: n/a\}\hfill{}\\

\textbf{IMBIBE (Verb)} Heb: {\large\H סבא} s.b.a Def: To drink strong drink that can cause intoxication. \{Strong's: 5433\}\hfill{}\\

\textbf{IMITATE (Verb)} Heb: {\large\H תעע} t.ah.ah Def: To follow as a model, pattern or example. \{Strong's: 8591\}\hfill{}\\

\textbf{IMMIGRANT} Heb: {\large\H פלשת} pe-le-shet Def: Someone from outside of the homeland. Someone who migrated from another land or country. \{Strong's: n/a\}\hfill{}\\

\textbf{IMPATIENT} Heb: {\large\H לאה} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{IN.FRONT} Heb: {\large\H נוכח} no-khahh Def: Before or opposite to something. \{Strong's: 5227\}\hfill{}\\

\textbf{IN.LAW} Heb: {\large\H חתן} hha-tan Def: One related by marriage. \{Strong's: 2860\}\hfill{}\\

\textbf{IN.LINE} Heb: {\large\H מערכת} {[}X{]} Def: As an arrangement. \{Strong's: 4635\}\hfill{}\\

\textbf{IN.THIS.WAY} Heb: {\large\H כוה} ko Def: To do something in a certain manner; a reference to the previous or following context. \{Strong's: 3541, 3542, 3602\}\hfill{}\\

\textbf{INCENSE.SMOKE} Heb: {\large\H קטורת} qe-to-ret Def: Usually made of several spices and or fruits, etc. To emit a fragrance. Used at the altar as a sweet savor. \{Strong's: 6988, 7004\}\hfill{}\\

\textbf{INCREASE (Verb)} Heb: {\large\H רבה} r.b.h Def: To become progressively greater; to multiply by the production of young; to be abundant of number, strength or authority. \{Strong's: 7235, 7236\}\hfill{}\\

\textbf{INCREASE.IN.NUMBER (Verb)} Heb: {\large\H רבב} r.b.b Def: To become progressively greater; to multiply by the production of young. Multiply. Also, meaning ``to shoot'' from the abundant arrows of the archer. \{Strong's: 7231, 7232\}\hfill{}\\

\textbf{INCREASING} Heb: {\large\H כסד} {[}X{]} Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{INDEED} Heb: {\large\H אומנם} um-nam Def: Without any question. \{Strong's: 552\}\hfill{}\\

\textbf{INFANT} Heb: {\large\H שיליה} {[}X{]} Def: As drawn out of the mother. \{Strong's: 7988\}\hfill{}\\

\textbf{INFECT (Verb)} Heb: {\large\H צרע} ts.r.ah Def: To taint or contaminate with something that affects quality, character, or condition unfavorably. To be infected with leprosy, mildew or mold. \{Strong's: 6879\}\hfill{}\\

\textbf{INFECTION} Heb: {\large\H צרעת} {[}X{]} Def: A contaminated substance, such as a disease, mold or mildew, on the skin, cloth or a building. \{Strong's: 6883\}\hfill{}\\

\textbf{INFIRMITY} Heb: {\large\H חלי} {[}X{]} Def: A piercing pain. \{Strong's: 2483\}\hfill{}\\

\textbf{INFLAME (Verb)} Heb: {\large\H דלק} d.l.q Def: To excite to excessive or uncontrollable action or feeling. \{Strong's: 1814, 1815\}\hfill{}\\

\textbf{INFLAMMATION} Heb: {\large\H דלקת} {[}X{]} Def: {[}X{]} \{Strong's: 1816\}\hfill{}\\

\textbf{INHERIT (Verb)} Heb: {\large\H נחל} n.hh.l Def: A passing down of properties, wealth or blessings to the offspring. \{Strong's: 5157\}\hfill{}\\

\textbf{INHERITANCE} Heb: {\large\H נחלה} na-hha-lah Def: The acquisition of a possession from past generations. \{Strong's: 5159\}\hfill{}\\

\textbf{INNOCENCE} Heb: {\large\H נקיון} na-qi-on Def: Freedom from guilt or sin through being unacquainted with evil. A state of innocence as an infant. \{Strong's: 5356\}\hfill{}\\

\textbf{INNOCENT} Heb: {\large\H נקי} na-qi Def: Free from guilt or sin. A state of innocence as an infant. \{Strong's: 5355\}\hfill{}\\

\textbf{INSCRIBE (Verb)} Heb: {\large\H חקק} hh.q.q Def: To write, engrave or print as a lasting record. A decree or custom. \{Strong's: 2710\}\hfill{}\\

\textbf{INSTALLATION} Heb: {\large\H מלוא} mi-lu Def: Placed in its proper and permanent position. \{Strong's: 4394\}\hfill{}\\

\textbf{INTELLIGENCE} Heb: {\large\H תבון} ta-vun \textbf{\textbackslash{}} {\large\H תבונה} te-vu-nah Def: The ability to learn, reason, plan and build. \{Strong's: 8394\}\hfill{}\\

\textbf{INTERCEDE (Verb)} Heb: {\large\H עתר} ah.t.r Def: To intervene between parties to reconcile differences. Supplicate on the behalf of another. \{Strong's: 6279\}\hfill{}\\

\textbf{INTEREST} Heb: {\large\H תרבית} {[}X{]} Def: From usury. \{Strong's: 8636\}\hfill{}\\

\textbf{INTERPRET (Verb)} Heb: {\large\H פתר} p.t.r Def: To explain or tell the meaning of. \{Strong's: 6590, 6622\}\hfill{}\\

\textbf{INTERPRETATION} Heb: {\large\H פיתרון} pit-ron Def: The act or result of interpreting. \{Strong's: 6623\}\hfill{}\\

\textbf{INTERPRETING} Heb: {\large\H פתור} pe-tor Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{INVADE (Verb)} Heb: {\large\H גוד} g.w.d Def: To enter for conquest or plunder. The slicing through of a band of men. \{Strong's: 1464\}\hfill{}\\

\textbf{INVENTION} Heb: {\large\H מחשבה} ma-hha-sha-vah Def: A product of the imagination. Designing or planning of inventions or plans. \{Strong's: 4284\}\hfill{}\\

\textbf{INVESTIGATE (Verb)} Heb: {\large\H פקר} p.q.r Def: To look or search for something. \{Strong's: 1239, 1240\}\hfill{}\\

\textbf{IRON} Heb: {\large\H ברזל} bar-zel Def: A heavy element frequently used in the making of weapons and tools. The most used of metals. \{Strong's: 1270, 6523\}\hfill{}\\

\textbf{IRRITATE (Verb)} Heb: {\large\H מאר} m.a.r Def: {[}X{]} \{Strong's: 3992\}\hfill{}\\

\textbf{ISLAND} Heb: {\large\H אי} iy Def: A tract of land surrounded by water. Also a country in the sense of isolated. \{Strong's: 336, 339\}\hfill{}\\

\textbf{ISSUE} Heb: {\large\H זוב} {[}X{]} Def: {[}X{]} \{Strong's: 2101\}\hfill{}\\

\textbf{ISSUE (Verb)} Heb: {\large\H זוב} z.w.b Def: To flow out; to go, pass, or flow out; emerge. \{Strong's: 2100\}\hfill{}\\

\textbf{ITCH} Heb: {\large\H גרב} {[}X{]} Def: {[}X{]} \{Strong's: 1618\}\hfill{}\\

\textbf{ITEM} Heb: {\large\H כלי} ke-li Def: A utensil or implement usually for carrying or storing various materials. \{Strong's: 3627\}\hfill{}\\

\textbf{JAR} Heb: {\large\H כד} kad Def: A sudden and unexpected shake; a wide-mouthed container. \{Strong's: 3537\}\hfill{}\\

\textbf{JASPER} Heb: {\large\H ישפה} yash-phey Def: Probably the Jasper which may be red, yellow or brown in color. The Septuagint uses laspis meaning Jasper. Other possible translations are Ruby, Hyacinth and Emerald. \{Strong's: 3471\}\hfill{}\\

\textbf{JAW} Heb: {\large\H לחי} {[}X{]} Def: From the moist cheeks. \{Strong's: 3895\}\hfill{}\\

\textbf{JEWEL} Heb: {\large\H סגולה} se-gu-lah Def: A precious stone. Something of value. \{Strong's: 5459\}\hfill{}\\

\textbf{JOIN (Verb)} Heb: {\large\H לוה} l.w.h Def: To bind together. \{Strong's: 3867\}\hfill{}\\

\textbf{JOINED.TOGETHER (Verb)} Heb: {\large\H שלב} sh.l.b Def: Two becoming one purposely. \{Strong's: 7947\}\hfill{}\\

\textbf{JOINING} Heb: {\large\H לו} law Def: The attachment of objects through binding together. \{Strong's: n/a\}\hfill{}\\

\textbf{JOINT} Heb: {\large\H מחברת} mahh-be-ret Def: The point at which two opposing objects meet. \{Strong's: 4225\}\hfill{}\\

\textbf{JOURNEY} Heb: {\large\H מסע} mas-sah Def: The packing up of camp for the purpose of beginning a journey. \{Strong's: 4550, 4551\}\hfill{}\\

\textbf{JOURNEY (Verb)} Heb: {\large\H נסע} n.s.ah Def: To travel or pass from one place to another; to break camp and begin a journey. \{Strong's: 5265\}\hfill{}\\

\textbf{JUDGE} Heb: {\large\H פליל} pa-lil Def: One who presides over a dispute. \{Strong's: 6414\}\hfill{}\\

\textbf{JUDGMENT} Heb: {\large\H שפט} she-phet Def: Reward for action, good or bad. An aspect of determining the outcome. \{Strong's: 8201\}\hfill{}\\

\textbf{JUDICIAL} Heb: {\large\H שפטן} shaph-tan Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{JUG} Heb: {\large\H קשה} qa-sah Def: A vessel used for storage of water, grain, etc. \{Strong's: 7184\}\hfill{}\\

\textbf{JUICE} Heb: {\large\H משרה} {[}X{]} Def: As loosened from the fruit. \{Strong's: 4952\}\hfill{}\\

\textbf{JUNIPER} Heb: {\large\H רתם} {[}X{]} \textbf{\textbackslash{}} {\large\H רתמה} rit-mah Def: An unknown tree. \{Strong's: 7574\}\hfill{}\\

\textbf{KEEP (Verb)} Heb: {\large\H נטר} n.t.r Def: To hold onto. \{Strong's: 5201, 5202\}\hfill{}\\

\textbf{KEEP.BACK (Verb)} Heb: {\large\H חסך} hh.s.k Def: To hold something back or restrain. \{Strong's: 2820\}\hfill{}\\

\textbf{KEEP.SECRET (Verb)} Heb: {\large\H כחד} k.hh.d Def: To refrain from disclosing information. \{Strong's: 3582\}\hfill{}\\

\textbf{KEEP.SILENT (Verb)} Heb: {\large\H חרש} hh.r.sh Def: To stand still and be silent. \{Strong's: 2790\}\hfill{}\\

\textbf{KEEP.WATCH (Verb)} Heb: {\large\H צפה} ts.p.h Def: To be on the look-out for danger or opportunity. \{Strong's: 6822\}\hfill{}\\

\textbf{KERMES} Heb: {\large\H תולע} to-la Def: The 'coccus ilicis,' a worm used for medicinal purposes as well as for making a crimson dye. \{Strong's: 8438\}\hfill{}\\

\textbf{KERNAL} Heb: {\large\H חרצן} {[}X{]} Def: The seed of a grape as sharp. \{Strong's: 2785\}\hfill{}\\

\textbf{KERUV} Heb: {\large\H כרוב} ke-ruv Def: A supernatural creature, identified in other Semitic cultures as a winged lion, a Griffin. \{Strong's: 3742\}\hfill{}\\

\textbf{KICK (Verb)} Heb: {\large\H בעט} b.ah.t Def: {[}X{]} \{Strong's: 1163\}\hfill{}\\

\textbf{KIDNEY} Heb: {\large\H כליה} kil-yah Def: An organ of the body. The seat of emotion in Hebraic thought. \{Strong's: 3629\}\hfill{}\\

\textbf{KILL (Verb)} Heb: {\large\H הרג} h.r.g Def: To deprive of life; to slaughter. \{Strong's: 2026\}\hfill{}\\

\textbf{KIN} Heb: {\large\H שארה} {[}X{]} Def: A near female relative. \{Strong's: 7608\}\hfill{}\\

\textbf{KIND} Heb: {\large\H מין} min Def: A category of creature that comes from its own kind as a firm rule. \{Strong's: 4327\}\hfill{}\\

\textbf{KIND.ONE} Heb: {\large\H חסיד} {[}X{]} Def: One who shows favor, mercy or compassion to another. \{Strong's: 2623\}\hfill{}\\

\textbf{KINDLE (Verb)} Heb: {\large\H קדח} q.d.hh Def: To kindle a fire. \{Strong's: 6919\}\hfill{}\\

\textbf{KINDLED} Heb: {\large\H תבערה} tav-ey-rah Def: \{Strong's: n/a\}\hfill{}\\

\textbf{KINDNESS} Heb: {\large\H חסד} hhe-sed Def: Of a sympathetic nature; quality or state of being sympathetic. In the sense of bowing the neck to another as a sign of kindness. \{Strong's: 2617\}\hfill{}\\

\textbf{KINDRED} Heb: {\large\H מולדת} mo-le-det Def: A group of related individuals. \{Strong's: 4138\}\hfill{}\\

\textbf{KING} Heb: {\large\H מלך} me-lekh Def: The male ruler of a nation or city state. \{Strong's: 4428, 4430, 4431\}\hfill{}\\

\textbf{KINGDOM} Heb: {\large\H ממלכה} mam-la-khah Def: The area under the control of a king. \{Strong's: 4467\}\hfill{}\\

\textbf{KISS (Verb)} Heb: {\large\H נשק} n.sh.q Def: To touch together as when kissing with the lips or in battle with weapons. \{Strong's: 5401\}\hfill{}\\

\textbf{KNEAD (Verb)} Heb: {\large\H לוש} l.w.sh Def: To work and press dough. Knead dough for bread. \{Strong's: 3888\}\hfill{}\\

\textbf{KNEADING.BOWL} Heb: {\large\H משארת} mish-eret Def: The vessel used for mixing bread dough. \{Strong's: 4863\}\hfill{}\\

\textbf{KNEE} Heb: {\large\H ברך} be-rekh Def: The joint between the femur and tibia of the leg. \{Strong's: 1290, 1291\}\hfill{}\\

\textbf{KNEEL (Verb)} Heb: {\large\H ברך} b.r.k Def: To bend the knee, to kneel in homage or to kneel down to get a drink water. The piel (intensive) form means ``respect,'' in the sense of kneeling before another. \{Strong's: 1288, 1289\}\hfill{}\\

\textbf{KNIFE} Heb: {\large\H מאכלת} ma-a-ke-let Def: A cutting instrument consisting of a sharp blade and handle. What is used for preparing and eating food. \{Strong's: 3979\}\hfill{}\\

\textbf{KNOB} Heb: {\large\H כפתור} kaph-tor Def: An ornamental round lump or protuberance on the surface or at the end of something. \{Strong's: 3730\}\hfill{}\\

\textbf{KNOCK (Verb)} Heb: {\large\H חבט} hh.b.t Def: To knock a tree to remove its fruit, also a threshing. \{Strong's: 2251\}\hfill{}\\

\textbf{KNOLL} Heb: {\large\H גיבעה} giv-ah Def: A small round hill. \{Strong's: 1389\}\hfill{}\\

\textbf{KNOW (Verb)} Heb: {\large\H ידע} y.d.ah Def: To have an intimate and personal understanding; to have an intimate relationship with another person, usually sexual. \{Strong's: 3045, 3046\}\hfill{}\\

\textbf{KNOWER} Heb: {\large\H ידעני} {[}X{]} Def: One with special knowledge. \{Strong's: 3049\}\hfill{}\\

\textbf{LA'A'NAH} Heb: {\large\H לענה} {[}X{]} Def: An unknown bitter plant. \{Strong's: 3939\}\hfill{}\\

\textbf{LABOR} Heb: {\large\H עמל} a-mal Def: To exert one’s power of body or mind, especially with painful or strenuous effort. A labor that causes grief, pain or weariness. A laborer as one who toils. \{Strong's: 5999, 6001\}\hfill{}\\

\textbf{LACE} Heb: {\large\H סרוך} se-rokh Def: A cord or string used to draw the edges of shoes or a garment together, as twisted around the foot for attaching sandals. \{Strong's: 8288\}\hfill{}\\

\textbf{LACKING} Heb: {\large\H מחסור} {[}X{]} Def: {[}X{]} \{Strong's: 4270\}\hfill{}\\

\textbf{LADANUM} Heb: {\large\H לוט} lot Def: An aromatic gum resin obtained from a tree and having a bitter slightly pungent taste. \{Strong's: 3910\}\hfill{}\\

\textbf{LADDER} Heb: {\large\H סולם} su-lam Def: Used to raise up. A structure for climbing up or down. \{Strong's: 5551\}\hfill{}\\

\textbf{LAME} Heb: {\large\H פיסח} {[}X{]} Def: As one who hops one leg. \{Strong's: 6455\}\hfill{}\\

\textbf{LAMENT (Verb)} Heb: {\large\H ספד} s.p.d Def: To mourn aloud; wail. \{Strong's: 5594\}\hfill{}\\

\textbf{LAMENTING} Heb: {\large\H מספד} mis-peyd Def: The act of mourning. \{Strong's: 4553\}\hfill{}\\

\textbf{LAMP} Heb: {\large\H נר} ner Def: A container for an inflammable liquid, as oil, which is burned at a wick as a means of illumination. \{Strong's: 5216\}\hfill{}\\

\textbf{LAMPSTAND} Heb: {\large\H מנורה} me-no-rah Def: A platform, sometimes elevated, for holding a lamp. \{Strong's: 4501\}\hfill{}\\

\textbf{LAND} Heb: {\large\H ארץ} e-rets Def: The solid part of the earth's surface. The whole of the earth or a region. \{Strong's: 772, 776, 778\}\hfill{}\\

\textbf{LAP.AROUND (Verb)} Heb: {\large\H צנף} ts.n.p Def: {[}X{]} \{Strong's: 6801\}\hfill{}\\

\textbf{LAPIS.LAZULI} Heb: {\large\H ספיר} sa-phir Def: Probably the Lapis Lazuli which is similar to the color of the Sapphire. While the Hebrew word is saphiyr, the origin of the word Sapphire, the Sapphire was unknown until the Roman period. \{Strong's: 5601\}\hfill{}\\

\textbf{LAST} Heb: {\large\H אחרון} a-hha-ron \textbf{\textbackslash{}} {\large\H אחרונה} a-hha-ro-nah Def: In, to or toward the back. To be in back of, at the rear or following after something. \{Strong's: 314\}\hfill{}\\

\textbf{LAST.NIGHT} Heb: {\large\H אמש} e-mesh Def: The previous night or a time past. \{Strong's: 570\}\hfill{}\\

\textbf{LATE} Heb: {\large\H אפיל} a-phil Def: The latter part of the day, in the sense of night as being dark. The latter part of a season. At or near the end. \{Strong's: 648\}\hfill{}\\

\textbf{LATE.RAIN} Heb: {\large\H מלקוש} {[}X{]} Def: A late rain that causes a latter growth of crops. \{Strong's: 4456\}\hfill{}\\

\textbf{LAUGH (Verb)} Heb: {\large\H צחק} ts.hh.q Def: To show mirth, joy, or scorn with a smile and chuckle or explosive sound. \{Strong's: 6711\}\hfill{}\\

\textbf{LAUGHTER} Heb: {\large\H צחוק} tse-hhoq Def: The sound of or as of laughing. \{Strong's: 6712\}\hfill{}\\

\textbf{LAW} Heb: {\large\H דת} {[}X{]} Def: A law, decree or edict. \{Strong's: 1881, 1882\}\hfill{}\\

\textbf{LAY.DOWN (Verb)} Heb: {\large\H שכב} sh.k.b Def: To give up; to lie down for copulation, rest or sleep. \{Strong's: 7901\}\hfill{}\\

\textbf{LAY.IN.WAIT (Verb)} Heb: {\large\H צדה} ts.d.h Def: To hide in ambush. \{Strong's: 6658\}\hfill{}\\

\textbf{LAY.WASTE (Verb)} Heb: {\large\H בלק} b.l.q Def: {[}X{]} \{Strong's: 1110\}\hfill{}\\

\textbf{LAYING.PLACE} Heb: {\large\H משכב} mish-kav Def: The location one lays for rest or sleep. \{Strong's: 4903, 4904\}\hfill{}\\

\textbf{LEAD} Heb: {\large\H עופרת} o-phe-ret Def: A very heavy metal that is commonly melted and poured into casts to make statues or other objects. \{Strong's: 5777\}\hfill{}\\

\textbf{LEAD (Verb)} Heb: {\large\H נהל} n.h.l Def: To guide on a way, especially by going in advance. The flock directed to the pasture at the end of the journey. \{Strong's: 5095\}\hfill{}\\

\textbf{LEADER} Heb: {\large\H אציל} a-tsil Def: One who is in charge or in command of others. \{Strong's: 678\}\hfill{}\\

\textbf{LEAF} Heb: {\large\H עלה} a-leh Def: Foliage of a tree or plant. As high in the tree. \{Strong's: 5929\}\hfill{}\\

\textbf{LEAN} Heb: {\large\H רזה} {[}X{]} Def: {[}X{]} \{Strong's: 7330\}\hfill{}\\

\textbf{LEAN (Verb)} Heb: {\large\H שען} sh.ah.n Def: To cast one’s weight to one side for support. Lean on something for rest or support. \{Strong's: 8172\}\hfill{}\\

\textbf{LEAP (Verb)} Heb: {\large\H זנק} z.n.q Def: {[}X{]} \{Strong's: 2187\}\hfill{}\\

\textbf{LEAPING.LOCUST} Heb: {\large\H חרגול} {[}X{]} Def: {[}X{]} \{Strong's: 2728\}\hfill{}\\

\textbf{LEARN (Verb)} Heb: {\large\H למד} l.m.d Def: To acquire knowledge or skill through instruction from one who is experienced. The piel form of the Hebrew verb means “cause to learn,” or “teach.”\} \{Strong's: 3925\}\hfill{}\\

\textbf{LEARNING} Heb: {\large\H לקח} {[}X{]} Def: Teachings and instructions that are received in the sense of being taken. \{Strong's: 3948\}\hfill{}\\

\textbf{LEAVE (Verb)} Heb: {\large\H עזב} ah.z.b Def: To go away from; to neglect. \{Strong's: 5800, 5805\}\hfill{}\\

\textbf{LEAVE.ALONE (Verb)} Heb: {\large\H שבק} sh.b.q Def: {[}X{]} \{Strong's: 7662\}\hfill{}\\

\textbf{LEAVE.BEHIND (Verb)} Heb: {\large\H יתר} y.t.r Def: To set aside; to retain or hold over to a future time or place; to leave a remainder. \{Strong's: 3498\}\hfill{}\\

\textbf{LEAVE.IN.PLACE (Verb)} Heb: {\large\H יצג} y.ts.g Def: To put something in a place. \{Strong's: 3322\}\hfill{}\\

\textbf{LEAVEN} Heb: {\large\H שאור} se-or Def: The element that causes bread to rise, such as salt or yeast. \{Strong's: 7603\}\hfill{}\\

\textbf{LEAVENED.BREAD} Heb: {\large\H חמץ} hha-mets Def: Dough that has had leaven added to make a sour bread. \{Strong's: 2557\}\hfill{}\\

\textbf{LEFT.HAND (Verb)} Heb: {\large\H סמאל} s.m.a Def: To choose the left hand or path. \{Strong's: 8040, 8041, 8042\}\hfill{}\\

\textbf{LEG} Heb: {\large\H כרע} ka-ra Def: The appendage from the ankle to the hip and bends at the knee. \{Strong's: 3767\}\hfill{}\\

\textbf{LENGTH} Heb: {\large\H אורך} o-rekh Def: A measured distance or dimension. \{Strong's: 753\}\hfill{}\\

\textbf{LENTIL} Heb: {\large\H עדש} a-dash Def: A leguminous plant with flattened edible seeds. \{Strong's: 5742\}\hfill{}\\

\textbf{LEOPARD} Heb: {\large\H נמר} {[}X{]} \textbf{\textbackslash{}} {\large\H נמרה} {[}X{]} Def: {[}X{]} \{Strong's: 5245, 5246\}\hfill{}\\

\textbf{LET.ALONE (Verb)} Heb: {\large\H נטש} n.t.sh Def: To be left behind by those who leave. \{Strong's: 5203\}\hfill{}\\

\textbf{LET.LOOSE (Verb)} Heb: {\large\H נתר} n.t.r Def: {[}X{]} \{Strong's: 5425, 5426\}\hfill{}\\

\textbf{LEVEL.VALLEY} Heb: {\large\H ביקעה} biq-a Def: A depression in the earth’s surface between ranges of mountains. Wide level valley as a division between mountains ranges. \{Strong's: 1236, 1237\}\hfill{}\\

\textbf{LICK (Verb)} Heb: {\large\H לחח} l.hh.hh Def: {[}X{]} \{Strong's: 3897, 3952\}\hfill{}\\

\textbf{LID} Heb: {\large\H כפורת} ka-po-ret Def: The cover of a box or other container. \{Strong's: 3727\}\hfill{}\\

\textbf{LIE} Heb: {\large\H כזב} {[}X{]} Def: {[}X{]} \{Strong's: 3577\}\hfill{}\\

\textbf{LIE (Verb)} Heb: {\large\H כזב} k.z.b Def: To give a spoken word to deceive, cause failure or disappoint; Not functioning within its intended capacity \{Strong's: 3576\}\hfill{}\\

\textbf{LIEUTENANT} Heb: {\large\H שליש} sha-lish Def: A leader who is responsible for a group of thirty. \{Strong's: 7991\}\hfill{}\\

\textbf{LIFT (Verb)} Heb: {\large\H רמם} r.m.m Def: {[}X{]} \{Strong's: 7426, 7318\}\hfill{}\\

\textbf{LIFT.HIGH (Verb)} Heb: {\large\H סגב} s.g.b Def: {[}X{]} \{Strong's: 7682\}\hfill{}\\

\textbf{LIFT.UP (Verb)} Heb: {\large\H נסא} n.s.a Def: To lift up a burden or load and carry it; to lift up camp and begin a journey; to forgive in the sense of removing the offense. \{Strong's: 4984, 5375, 5376\}\hfill{}\\

\textbf{LIFTED} Heb: {\large\H רהם} ra-ham Def: Raised up in position or in exaltation. \{Strong's: n/a\}\hfill{}\\

\textbf{LIGHT} Heb: {\large\H אור} or Def: The illumination from the sun, moon, stars, fire, candle or other source. \{Strong's: 216, 217\}\hfill{}\\

\textbf{LIGHT (Verb)} Heb: {\large\H אור} a.w.r Def: To shine with an intense light; be or give off light; to be bright. \{Strong's: 215\}\hfill{}\\

\textbf{LIGHT.BRINGER} Heb: {\large\H אהרון} a-ha-ron Def: One who carries light into the darkness. \{Strong's: n/a\}\hfill{}\\

\textbf{LIGHTWEIGHT} Heb: {\large\H קלקל} {[}X{]} Def: Something that is light in weight or position (worthless). \{Strong's: 7052\}\hfill{}\\

\textbf{LIKENESS} Heb: {\large\H דמות} da-mut Def: Copy; resemblance. The quality or state of being like something or someone else. \{Strong's: 1823\}\hfill{}\\

\textbf{LIME} Heb: {\large\H סיד} {[}X{]} Def: A chalky white powder used for making plaster. \{Strong's: 7875\}\hfill{}\\

\textbf{LIMP (Verb)} Heb: {\large\H צלע} ts.l.ah Def: To walk lamely, especially favoring one leg; to go unsteadily; to proceed with difficulty or slowly. From damage to the ridge of the hip. \{Strong's: 6760\}\hfill{}\\

\textbf{LINEN} Heb: {\large\H שש} sheysh Def: Fabric made of flax and noted for its strength, coolness and luster. A white cloth. Also, marble from its whiteness. \{Strong's: 7893, 8336\}\hfill{}\\

\textbf{LINGER (Verb)} Heb: {\large\H מהה} m.h.h Def: To be slow in parting or in quitting something. \{Strong's: 4102\}\hfill{}\\

\textbf{LINSEY.WOOLSEY} Heb: {\large\H שעטנז} {[}X{]} Def: {[}X{]} \{Strong's: 8162\}\hfill{}\\

\textbf{LINTEL} Heb: {\large\H משקוף} mash-qoph Def: A horizontal architectural member supporting the weight above an opening, as a window or a door. \{Strong's: 4947\}\hfill{}\\

\textbf{LION} Heb: {\large\H אריה} ar-yeyh Def: A large carnivorous chiefly nocturnal cat. A feared animal. \{Strong's: 738, 744\}\hfill{}\\

\textbf{LION.LIKE} Heb: {\large\H ארירך} {[}X{]} Def: {[}X{]} \{Strong's: 746\}\hfill{}\\

\textbf{LIONESS} Heb: {\large\H לביא} la-vi Def: A female lion. \{Strong's: 3833\}\hfill{}\\

\textbf{LIP} Heb: {\large\H שפה} sa-phah Def: The rim or edge of the mouth or other opening. Language, as spoken from the lips. \{Strong's: 8193\}\hfill{}\\

\textbf{LIQUOR} Heb: {\large\H שכר} shey-khar Def: An intoxicating drink. \{Strong's: 7941\}\hfill{}\\

\textbf{LITTLE.ONE} Heb: {\large\H צעיר} tsa-ir Def: Small in size or extent. Something or someone that is smaller, younger or less significant. \{Strong's: 2191, 2192, 6810\}\hfill{}\\

\textbf{LIVE (Verb)} Heb: {\large\H חיה} hh.y.h Def: To be alive and continue alive. Have life within. The revival of life gained from food or other necessity. The piel (intensive) form means ``keep alive.'' \{Strong's: 2418, 2421, 2425\}\hfill{}\\

\textbf{LIVELY} Heb: {\large\H חיה} hhay-eh Def: Having the vigor of life. \{Strong's: 2422\}\hfill{}\\

\textbf{LIVESTOCK} Heb: {\large\H מקנה} miq-neh Def: Animals kept or raised for use or pleasure. What is purchased or possessed. \{Strong's: 4735\}\hfill{}\\

\textbf{LIVING} Heb: {\large\H חי} hhai \textbf{\textbackslash{}} {\large\H חיה} hhai-ah Def: The quality that distinguishes a vital and functional being from a dead body; life. Literally the stomach. Used idiomatically of living creatures, especially in conjunction with land, ground or field. \{Strong's: 2416, 2417\}\hfill{}\\

\textbf{LIZARD} Heb: {\large\H לטאה} {[}X{]} Def: From the camouflaging capability of the lizard to hide. \{Strong's: 3911\}\hfill{}\\

\textbf{LO} Heb: {\large\H הא} hey Def: To draw attention to something important. \{Strong's: 1887, 1888\}\hfill{}\\

\textbf{LOAD} Heb: {\large\H משא} ma-sa Def: Something that is lifted up and carried. The lifting up of the voice in song. \{Strong's: 4853\}\hfill{}\\

\textbf{LOAD (Verb)} Heb: {\large\H עמס} ah.m.s Def: That which is put on a person or pack animal to be carried. \{Strong's: 6006\}\hfill{}\\

\textbf{LOAN} Heb: {\large\H מנשה} {[}X{]} \textbf{\textbackslash{}} {\large\H מנשאה} {[}X{]} Def: {[}X{]} \{Strong's: 4859, 4874\}\hfill{}\\

\textbf{LOATHE (Verb)} Heb: {\large\H קוץ} q.w.ts Def: To dislike greatly and often with disgust. To be sickened as if pierced by a thorn. \{Strong's: 6973\}\hfill{}\\

\textbf{LOBE} Heb: {\large\H יותרת} yo-te-ret Def: The extended point of the liver. \{Strong's: 3508\}\hfill{}\\

\textbf{LOCUST} Heb: {\large\H סלעם} {[}X{]} Def: From its high jumping. \{Strong's: 5556\}\hfill{}\\

\textbf{LOFT} Heb: {\large\H עליה} {[}X{]} Def: A room on top of the house used during hot days of summer. \{Strong's: 5944, 5952\}\hfill{}\\

\textbf{LOG} Heb: {\large\H לג} {[}X{]} Def: A standard of measure. \{Strong's: 3849\}\hfill{}\\

\textbf{LOIN.WRAP} Heb: {\large\H חגורה} hha-go-rah Def: A sash or belt that encircles the waist. \{Strong's: 2290\}\hfill{}\\

\textbf{LOINS} Heb: {\large\H חלץ} hha-lats Def: The pubic region; the generative organs. In the sense of the next generation being drawn out of the loins. \{Strong's: 2504, 2783\}\hfill{}\\

\textbf{LONG.GARMENT} Heb: {\large\H מד} {[}X{]} Def: {[}X{]} \{Strong's: 4055\}\hfill{}\\

\textbf{LONG.HAIR} Heb: {\large\H פרע} {[}X{]} Def: As let loose. \{Strong's: 6545\}\hfill{}\\

\textbf{LONG.WINGED} Heb: {\large\H אבר} {[}X{]} Def: {[}X{]} \{Strong's: 83\}\hfill{}\\

\textbf{LOOK} Heb: {\large\H הינה} hi-ney Def: To ascertain by the use of one's eyes. \{Strong's: 2009\}\hfill{}\\

\textbf{LOOK.DOWN (Verb)} Heb: {\large\H שקף} sh.q.p Def: To look out and down as through a window. \{Strong's: 8259\}\hfill{}\\

\textbf{LOOK.FORTH (Verb)} Heb: {\large\H סכה} s.k.h Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{LOOK.INTO} Heb: {\large\H חז} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{LOOK.UPON (Verb)} Heb: {\large\H שור} sh.w.r Def: {[}X{]} \{Strong's: 7789\}\hfill{}\\

\textbf{LOOK.WITH.RESPECT (Verb)} Heb: {\large\H שעה} sh.ah.h Def: To look upon with high regard. \{Strong's: 8159\}\hfill{}\\

\textbf{LOOP} Heb: {\large\H לולאה} lu-lah Def: A circular object that is open in the middle. \{Strong's: 3924\}\hfill{}\\

\textbf{LOOSE (Verb)} Heb: {\large\H פרע} p.r.ah Def: To uncover, remove or let go. Such as to make naked by removing clothing. To uncover the head. \{Strong's: 6544\}\hfill{}\\

\textbf{LOOSEN (Verb)} Heb: {\large\H זחח} z.hh.hh Def: To make less tight; slacken or relax. To untie or remove. \{Strong's: 2118\}\hfill{}\\

\textbf{LORD} Heb: {\large\H אדון} a-don Def: The ruler as the foundation to the community. \{Strong's: 113\}\hfill{}\\

\textbf{LOST} Heb: {\large\H רשע} re-sha Def: Departed from the correct path or way, either out of ignorance or revolt. \{Strong's: 7562, 7563\}\hfill{}\\

\textbf{LOST.THING} Heb: {\large\H אבדה} a-vey-dah Def: An object that is missing or misplaced. \{Strong's: 9\}\hfill{}\\

\textbf{LOT} Heb: {\large\H גורל} {[}X{]} Def: Colored stones that are thrown and read to determine a course of action or to make a decision. \{Strong's: 1486\}\hfill{}\\

\textbf{LOUD.NOISE} Heb: {\large\H רוע} rey-a Def: A loud, confused, constant noise or sound \{Strong's: 7452\}\hfill{}\\

\textbf{LOVE (Verb)} Heb: {\large\H אהב} a.h.b Def: To provide and protect that which is given as a privilege. An intimacy of action and emotion. Strong affection for another arising from personal ties. \{Strong's: 157\}\hfill{}\\

\textbf{LOW} Heb: {\large\H שפל} {[}X{]} \textbf{\textbackslash{}} {\large\H שפלה} {[}X{]} Def: {[}X{]} \{Strong's: 8215, 8216, 8217\}\hfill{}\\

\textbf{LOW.COUNTRY} Heb: {\large\H דדן} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{LOWER (Verb)} Heb: {\large\H כנע} k.n.ah Def: To be brought down low in humility or submission. \{Strong's: 3665\}\hfill{}\\

\textbf{LOWER.PART} Heb: {\large\H תחתי} tahh-ti Def: The part beneath. A low place. \{Strong's: 8482\}\hfill{}\\

\textbf{LOWERED} Heb: {\large\H כנען} ke-na-an Def: Brought down. \{Strong's: n/a\}\hfill{}\\

\textbf{LOWLAND} Heb: {\large\H שפלה} {[}X{]} Def: A low place. \{Strong's: 8219\}\hfill{}\\

\textbf{LUMINARY} Heb: {\large\H מאור} ma-or Def: That which gives off light. \{Strong's: 3974\}\hfill{}\\

\textbf{LYING.DOWN} Heb: {\large\H שכבה} she-kha-vah Def: A laying with another in copulation. Something spread out. \{Strong's: 7902\}\hfill{}\\

\textbf{LYRE} Heb: {\large\H כרן} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{MADNESS} Heb: {\large\H שיגעון} {[}X{]} Def: {[}X{]} \{Strong's: 7697\}\hfill{}\\

\textbf{MAGGOT} Heb: {\large\H רימה} ri-mah Def: The larvae of flies. \{Strong's: 7415\}\hfill{}\\

\textbf{MAGICIAN} Heb: {\large\H חרטום} hhar-tom Def: One who performs tricks of illusion and sleight of hand. Writes magical circles and lines. \{Strong's: 2748, 2749\}\hfill{}\\

\textbf{MAGNIFICENCE} Heb: {\large\H גודל} {[}X{]} Def: An increase in size power or authority. \{Strong's: 1433\}\hfill{}\\

\textbf{MAGNIFIED} Heb: {\large\H גדל} ga-deyl Def: An increased significance or size. \{Strong's: 1432\}\hfill{}\\

\textbf{MAGNIFY (Verb)} Heb: {\large\H גדל} g.d.l Def: To increase in size or one's position of honor. \{Strong's: 1431\}\hfill{}\\

\textbf{MAID} Heb: {\large\H שיפחה} shiph-hhah Def: An unmarried young woman. \{Strong's: 8198\}\hfill{}\\

\textbf{MAJESTY} Heb: {\large\H גאון} ga-on Def: Elevated to a higher position. Supreme greatness or authority. \{Strong's: 1347\}\hfill{}\\

\textbf{MAKE (Verb)} Heb: {\large\H פעל} p.ah.l Def: To perform a task of physical labor. \{Strong's: 6466, 6468\}\hfill{}\\

\textbf{MAKE.A.PLEDGE (Verb)} Heb: {\large\H עבט} ah.b.t Def: {[}X{]} \{Strong's: 5670\}\hfill{}\\

\textbf{MAKE.A.VOW (Verb)} Heb: {\large\H נדר} n.d.r Def: To promise solemnly; to make an agreement where one promises an action if the other reciprocates with another action. \{Strong's: 5087\}\hfill{}\\

\textbf{MAKE.BALD (Verb)} Heb: {\large\H קרח} q.r.hh Def: To shave the hair of the head to make bald. \{Strong's: 7139\}\hfill{}\\

\textbf{MAKE.BRICKS (Verb)} Heb: {\large\H לבן} l.b.n Def: To shape moist clay or earth into blocks for construction purposes. Can also mean to be ``white.'' \{Strong's: 3835\}\hfill{}\\

\textbf{MAKE.FAT (Verb)} Heb: {\large\H דשן} d.sh.n Def: To make or become large with fat tissue. \{Strong's: 1878\}\hfill{}\\

\textbf{MAKE.HASTE (Verb)} Heb: {\large\H עוש} ah.w.sh Def: {[}X{]} \{Strong's: 2363, 5789\}\hfill{}\\

\textbf{MAKE.RESTITUTION (Verb)} Heb: {\large\H שלם} sh.l.m Def: To restore or make right through action, payment or restoration to a rightful owner. \{Strong's: 7999, 8000\}\hfill{}\\

\textbf{MALE} Heb: {\large\H זכר} za-khar Def: Being the gender who begets offspring. One who acts and speaks for the family. \{Strong's: 1798, 2145\}\hfill{}\\

\textbf{MALE.GOAT} Heb: {\large\H עתוד} a-tud Def: A male member of a flock of goats. \{Strong's: 6259, 6260\}\hfill{}\\

\textbf{MALE.KID} Heb: {\large\H גדי} ge-di Def: A young goat. \{Strong's: 1423\}\hfill{}\\

\textbf{MALE.PROSTITUTE} Heb: {\large\H קדש} {[}X{]} Def: A male prostitute set aside for a special purpose. \{Strong's: 6945\}\hfill{}\\

\textbf{MAN} Heb: {\large\H איש} ish Def: An adult male human. As mortal. Also, used to mean ``each'' in the sense of an individual. \{Strong's: 376, 377\}\hfill{}\\

\textbf{MANDRAKES} Heb: {\large\H דודי} du-dai Def: A plant boiled as an aphrodisiac. \{Strong's: 1736\}\hfill{}\\

\textbf{MANE.OF.A.HORSE} Heb: {\large\H רעמה} {[}X{]} Def: {[}X{]} \{Strong's: 7483\}\hfill{}\\

\textbf{MANY} Heb: {\large\H מאוד} me-od Def: A large but indefinite number. An abundance of things (many, much, great), actions (complete, wholly, strong, quick) or character (very). \{Strong's: 3966\}\hfill{}\\

\textbf{MARCH (Verb)} Heb: {\large\H צעד} ts.ah.d Def: To move along steadily, usually with a rhythmic stride and in step with others. \{Strong's: 6805\}\hfill{}\\

\textbf{MARKER} Heb: {\large\H טוטפה} to-ta-phah Def: A mark or emblem used to identify a purpose. \{Strong's: 2903\}\hfill{}\\

\textbf{MARRY (Verb)} Heb: {\large\H בעל} b.ah.l Def: To join as husband and wife. \{Strong's: 1166\}\hfill{}\\

\textbf{MARSH.GRASS} Heb: {\large\H אחו} a-hhu Def: The tall grasses that line a marsh as a wall. \{Strong's: 260\}\hfill{}\\

\textbf{MARVEL (Verb)} Heb: {\large\H תמה} t.m.h Def: Something that causes wonder or astonishment. To see or perceive a full sight, such as a wonder or miracle. \{Strong's: 8539\}\hfill{}\\

\textbf{MASTER} Heb: {\large\H בעל} ba-al Def: Having chief authority; a workman qualified to teach apprentices. \{Strong's: 1167, 1169\}\hfill{}\\

\textbf{MATERIAL} Heb: {\large\H קינין} qin-yan Def: Something owned, occupied or controlled. The goods and wealth acquired from the idea of acquiring materials for building a nest. \{Strong's: 7075\}\hfill{}\\

\textbf{MATTER} Heb: {\large\H אומל} {[}X{]} Def: A word or utterance spoken about something. \{Strong's: 562\}\hfill{}\\

\textbf{MATTRESS} Heb: {\large\H ערס} {[}X{]} Def: {[}X{]} \{Strong's: 6210\}\hfill{}\\

\textbf{MATURE} Heb: {\large\H תם} tam Def: Having completed natural growth and development. An upright and correct nature. \{Strong's: 8535\}\hfill{}\\

\textbf{MEASURE (Verb)} Heb: {\large\H מדד} m.d.d Def: To determine the length of something by comparing it to a standard of measure. \{Strong's: 4058\}\hfill{}\\

\textbf{MEASURED.AMOUNT} Heb: {\large\H תוכן} to-khen Def: A calculated measurement of weight. \{Strong's: 8506\}\hfill{}\\

\textbf{MEASUREMENT} Heb: {\large\H מדה} mi-dah Def: A size or distance that is determined by comparing to a standard of measure. \{Strong's: 4060, 4061\}\hfill{}\\

\textbf{MEASURING} Heb: {\large\H מודד} {[}X{]} Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{MEAT} Heb: {\large\H מזון} ma-zon Def: Solid food as distinguished from drink; flesh; a meal. \{Strong's: 4202, 4203\}\hfill{}\\

\textbf{MEDDLE (Verb)} Heb: {\large\H גרה} g.r.h Def: To struggle with to gain control over. \{Strong's: 1624\}\hfill{}\\

\textbf{MEDITATE (Verb)} Heb: {\large\H סוח} s.w.hh Def: To engage in contemplation. A sweeping away in thought. \{Strong's: 7742\}\hfill{}\\

\textbf{MEDITATING.ONE} Heb: {\large\H סיחון} si-hhon Def: \{Strong's: n/a\}\hfill{}\\

\textbf{MEET (Verb)} Heb: {\large\H קרה} q.r.h Def: To come into the presence of; to go to meet another; to have a chance encounter. \{Strong's: 7122, 7125, 7136\}\hfill{}\\

\textbf{MEETING} Heb: {\large\H מקרה} miq-rah Def: A planned or accidental coming together. An encounter. \{Strong's: 4744, 4745\}\hfill{}\\

\textbf{MELON} Heb: {\large\H אבטיח} {[}X{]} Def: A fruit that clings to the vine. \{Strong's: 20\}\hfill{}\\

\textbf{MELT.AWAY (Verb)} Heb: {\large\H מסס} m.s.s Def: To become liquefied by warmth or heat. Also, the dissolving of the heart through fear or discouragement. \{Strong's: 4549\}\hfill{}\\

\textbf{MEMORIAL} Heb: {\large\H אזכרה} {[}X{]} Def: A remembering and action based on a past even. \{Strong's: 234\}\hfill{}\\

\textbf{MEMORY} Heb: {\large\H זכר} zey-kher Def: A remembering based on a past event often through an annual festival. \{Strong's: 2143\}\hfill{}\\

\textbf{MEN} Heb: {\large\H זכור} za-khur Def: Male persons. \{Strong's: 2138\}\hfill{}\\

\textbf{MERCHANDISE} Heb: {\large\H ממכר} {[}X{]} \textbf{\textbackslash{}} {\large\H ממכרת} {[}X{]} Def: {[}X{]} \{Strong's: 4465, 4466\}\hfill{}\\

\textbf{MESSENGER} Heb: {\large\H מלאך} mal-akh Def: One who bears a message or runs an errand. Walks for another. \{Strong's: 4397, 4398\}\hfill{}\\

\textbf{METAL.PLATING} Heb: {\large\H צפוי} tsi-phu-i Def: Thin layers of metals used to cover materials to give the look of metal. A hammered out sheet of gold used to overlay something. \{Strong's: 6826\}\hfill{}\\

\textbf{METROPOLIS} Heb: {\large\H קריה} {[}X{]} Def: A large populace of people; a town or village. A place of meeting and gathering. \{Strong's: 7149, 7151\}\hfill{}\\

\textbf{MIDDLEMOST} Heb: {\large\H תיכון} ti-khon Def: The absolute center. \{Strong's: 8484\}\hfill{}\\

\textbf{MIDSECTION} Heb: {\large\H ירך} ya-rey-akh Def: The lower abdomen and back. \{Strong's: 3409\}\hfill{}\\

\textbf{MIDST} Heb: {\large\H תוך} ta-wek Def: The center or middle of the whole. \{Strong's: 8432\}\hfill{}\\

\textbf{MIGHTY.ONE} Heb: {\large\H אל} el Def: One who holds authority over others, such as a judge, chief or god. In the sense of being yoked to one another. \{Strong's: 410\}\hfill{}\\

\textbf{MIGRATION} Heb: {\large\H סלכה} sal-kah Def: A path that winds back on itself. To twist words or actions away from their proper context. \{Strong's: n/a\}\hfill{}\\

\textbf{MILDEW} Heb: {\large\H ירקון} {[}X{]} Def: As a thin green film. \{Strong's: 3420\}\hfill{}\\

\textbf{MILL} Heb: {\large\H טחון} {[}X{]} Def: A hand mill for grinding medicinal herbs into a powder. \{Strong's: 2911\}\hfill{}\\

\textbf{MILLSTONE} Heb: {\large\H רחה} re-hheh Def: A large circular stone that is revolved on top of another stone to grind grain into flour. \{Strong's: 7347\}\hfill{}\\

\textbf{MIMIC (Verb)} Heb: {\large\H לוץ} l.w.ts Def: To imitate another person’s speech as an interpretation or in scorn. \{Strong's: 3887\}\hfill{}\\

\textbf{MINGLED} Heb: {\large\H כילא} {[}X{]} Def: Something produced by the forbidden practice of crossing together different kinds, such as crossbreeding cattle and the mixing of wool and linen. Always written in the double plural form. \{Strong's: 3610\}\hfill{}\\

\textbf{MINISTER (Verb)} Heb: {\large\H שרת} sh.r.t Def: To give aid or service; to be in service to another. \{Strong's: 8334\}\hfill{}\\

\textbf{MINISTRY} Heb: {\large\H שרת} {[}X{]} Def: {[}X{]} \{Strong's: 8335\}\hfill{}\\

\textbf{MIRE} Heb: {\large\H יון} {[}X{]} Def: {[}X{]} \{Strong's: 3121\}\hfill{}\\

\textbf{MISCHIEF} Heb: {\large\H זמה} {[}X{]} Def: An annoying action resulting in grief, harm or evil. \{Strong's: 2154\}\hfill{}\\

\textbf{MISCHIEFOUS} Heb: {\large\H זמזום} zam-zum Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{MISERY} Heb: {\large\H מכאוב} makh-ov Def: An agony of the heart. \{Strong's: 4341\}\hfill{}\\

\textbf{MIST} Heb: {\large\H אד} ad Def: A vapor or fine spray. \{Strong's: 108\}\hfill{}\\

\textbf{MIX (Verb)} Heb: {\large\H בלל} b.l.l Def: To combine in one mass; to mingle together. \{Strong's: 1101\}\hfill{}\\

\textbf{MIXED.MULTITUDE} Heb: {\large\H אספסף} {[}X{]} Def: A gathering of people. \{Strong's: 628\}\hfill{}\\

\textbf{MIXED.UP} Heb: {\large\H בבל} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{MIXTURE} Heb: {\large\H ערב} ey-rev Def: Two or more elements to create one new element. Also the woof in weaving from its mixing of colors. \{Strong's: 6154\}\hfill{}\\

\textbf{MODERATE (Verb)} Heb: {\large\H דין} d.y.n Def: To rule over quarrels or other conflicts. \{Strong's: 1777, 1778\}\hfill{}\\

\textbf{MODERATOR} Heb: {\large\H דן} dan Def: A judge. One who presides over a dispute. \{Strong's: n/a\}\hfill{}\\

\textbf{MOIST} Heb: {\large\H לח} lahh Def: Slightly or moderately wet. \{Strong's: 3892, 3893\}\hfill{}\\

\textbf{MOLD (Verb)} Heb: {\large\H יצר} y.ts.r Def: To give shape to; to press or squeeze, as when pressing clay into a shape to form a vessel. \{Strong's: 3334, 3335\}\hfill{}\\

\textbf{MOLDING} Heb: {\large\H זר} zeyr Def: Material used to encompass an area or to enhance or beautify. Spread or scattered over a large area. \{Strong's: 2213\}\hfill{}\\

\textbf{MOMENT} Heb: {\large\H רגע} re-ga Def: A single point in time. A wink of the eye. \{Strong's: 7281, 7282\}\hfill{}\\

\textbf{MONUMENT} Heb: {\large\H מצבה} ma-tsey-vah Def: A lasting evidence, reminder, or example of someone or something. As standing tall and firm. \{Strong's: 4676\}\hfill{}\\

\textbf{MOON} Heb: {\large\H ירח} ye-rey-ahh Def: The second brightest object in the sky which reflects the sun's light. Also, a month by counting its cycles. \{Strong's: 3391, 3393, 3394\}\hfill{}\\

\textbf{MOREOVER} Heb: {\large\H אף} aph Def: In addition to what has been said. \{Strong's: 637, 638\}\hfill{}\\

\textbf{MORNING} Heb: {\large\H בוקר} bo-qer Def: The time from sunrise to noon. Breaking of daylight. \{Strong's: 1242\}\hfill{}\\

\textbf{MORROW} Heb: {\large\H מחרת} ma-hha-ret Def: The next day. At a time following. \{Strong's: 4283\}\hfill{}\\

\textbf{MORTAL.MAN} Heb: {\large\H מת} mat Def: Subject to death. As mortal. \{Strong's: 4962\}\hfill{}\\

\textbf{MORTAR} Heb: {\large\H חומר} hho-mer Def: A thick and slimy soil used to join bricks or for making bricks. \{Strong's: 2563\}\hfill{}\\

\textbf{MOTHER} Heb: {\large\H אם} eym Def: A female parent. Maternal tenderness or affection. One who fulfills the role of a mother. \{Strong's: 517\}\hfill{}\\

\textbf{MOUND} Heb: {\large\H גל} gal Def: An artificial hill or bank of earth or stones. A pile of rocks or soil. A spring gushing out of the ground. \{Strong's: 1530\}\hfill{}\\

\textbf{MOUNT} Heb: {\large\H הרר} ha-rar Def: To increase in amount or extent; to get up on something above the level of the ground. \{Strong's: 2042\}\hfill{}\\

\textbf{MOUNTAIN.SIDE} Heb: {\large\H צדד} ze-dad Def: To hide in ambush. \{Strong's: n/a\}\hfill{}\\

\textbf{MOURN (Verb)} Heb: {\large\H אבל} a.b.l Def: To feel or express grief or sorrow. \{Strong's: 56\}\hfill{}\\

\textbf{MOURNING} Heb: {\large\H אבל} a-veyl Def: A flowing of tears. Also, a meadow as a weeping ground. \{Strong's: 57, 58, 60\}\hfill{}\\

\textbf{MOUSE} Heb: {\large\H עכבר} {[}X{]} Def: {[}X{]} \{Strong's: 5909\}\hfill{}\\

\textbf{MOUTH} Heb: {\large\H פה} peh Def: The opening through which food enters the body. Any opening. \{Strong's: 6310\}\hfill{}\\

\textbf{MOVE.AWAY (Verb)} Heb: {\large\H מוש} m.w.sh Def: To pass from one place or position to another. \{Strong's: 4185\}\hfill{}\\

\textbf{MOVING} Heb: {\large\H מוש} mush Def: What has passed from one place to another. \{Strong's: n/a\}\hfill{}\\

\textbf{MULTITUDE} Heb: {\large\H המון} ha-mon Def: A great number of people. A loud group. \{Strong's: 1995\}\hfill{}\\

\textbf{MURDER (Verb)} Heb: {\large\H רצח} r.ts.hh Def: A killing committed with malice aforethought, characterized by deliberation or premeditation. \{Strong's: 7523\}\hfill{}\\

\textbf{MURKINESS} Heb: {\large\H עיפה} {[}X{]} Def: {[}X{]} \{Strong's: 5890\}\hfill{}\\

\textbf{MURMUR (Verb)} Heb: {\large\H לון} l.w.n Def: To make a low or indistinct sound, esp. Continuously. To complain in a low tone, usually in private. \{Strong's: 3885\}\hfill{}\\

\textbf{MURMURING} Heb: {\large\H תלונה} te-lu-nah Def: A continuously low or indistinct sound. A complaining in low tones, usually in private. \{Strong's: 8519\}\hfill{}\\

\textbf{MUSIC} Heb: {\large\H זימרת} zim-rat Def: An art of sound in time that expresses ideas and emotions in significant forms through the elements of rhythm, melody, harmony, and color. \{Strong's: 2176\}\hfill{}\\

\textbf{MUSICIAN} Heb: {\large\H זימרן} zim-rah Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{MUSTER (Verb)} Heb: {\large\H צבא} ts.b.a Def: To gather together a group for service, work or war. \{Strong's: 6633\}\hfill{}\\

\textbf{MUTE} Heb: {\large\H אילם} i-leym Def: Inability to speak. A bound up tongue. \{Strong's: 483\}\hfill{}\\

\textbf{MUZZLE (Verb)} Heb: {\large\H חסם} hh.s.m Def: {[}X{]} \{Strong's: 2629\}\hfill{}\\

\textbf{MYRIAD} Heb: {\large\H רבבה} re-va-vah Def: A great abundance in numbers. \{Strong's: 7233\}\hfill{}\\

\textbf{MYRRH} Heb: {\large\H מור} mor Def: A sweet smelling spice. Used as an exchange due to its monetary value. \{Strong's: 4753\}\hfill{}\\

\textbf{NAIL} Heb: {\large\H יתת} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{NAKED} Heb: {\large\H עירום} ey-rom Def: Without clothes in the sense of bare skin. \{Strong's: 5903\}\hfill{}\\

\textbf{NAKEDNESS} Heb: {\large\H ערוה} er-wah Def: The state of being without clothing. Idiomatic for sexual relations. \{Strong's: 6172, 6173\}\hfill{}\\

\textbf{NARROW} Heb: {\large\H צר} tsar Def: Of slender width. A narrow, tight place or situation, a difficulty. An enemy or adversary as one who closes in with pressure. \{Strong's: 6862\}\hfill{}\\

\textbf{NARROW.WAY} Heb: {\large\H משעול} {[}X{]} Def: A hollow in the land. \{Strong's: 4934\}\hfill{}\\

\textbf{NATAPH} Heb: {\large\H נטף} na-taph Def: An unknown precious stone. \{Strong's: 5198\}\hfill{}\\

\textbf{NATION} Heb: {\large\H גוי} goy Def: A community of people of one or more nationalities and having a more or less defined territory and government. The people as the back, or body of the nation. \{Strong's: 1471\}\hfill{}\\

\textbf{NATIVE} Heb: {\large\H אזרח} ez-rahh Def: Born and raised in the Land. \{Strong's: 249\}\hfill{}\\

\textbf{NATIVITY} Heb: {\large\H לוד} lud Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{NEAR} Heb: {\large\H קרוב} qa-rov Def: Close to; at or within a short distance from. Also, a kin, as a near relative. \{Strong's: 7138\}\hfill{}\\

\textbf{NECK} Heb: {\large\H עורף} o-reph Def: The part of a person that connects the head with the body. \{Strong's: 6203\}\hfill{}\\

\textbf{NECK.BAND} Heb: {\large\H ענק} {[}X{]} Def: An ornamental chain, band or cord worn around the neck. \{Strong's: 6060\}\hfill{}\\

\textbf{NECKLACE} Heb: {\large\H רביד} ra-vid Def: A series of links worn as an ornament or insignia in the sense of being spread over the neck. \{Strong's: 7242\}\hfill{}\\

\textbf{NEEDY} Heb: {\large\H אביון} ev-yon Def: In a condition of need or want. \{Strong's: 34\}\hfill{}\\

\textbf{NEIGHBOR} Heb: {\large\H עמית} {[}X{]} Def: {[}X{]} \{Strong's: 5997\}\hfill{}\\

\textbf{NESHER} Heb: {\large\H נשר} ne-sher Def: An unknown bird, but probably a hawk or eagle. \{Strong's: 5403, 5404\}\hfill{}\\

\textbf{NEST} Heb: {\large\H קן} qeyn Def: A bed or receptacle prepared by a bird for its eggs and young. The stall of an animal as a nest. \{Strong's: 7064\}\hfill{}\\

\textbf{NESTING} Heb: {\large\H קינן} qin-yan Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{NET} Heb: {\large\H סבך} se-vakh Def: An open-meshed fabric twisted, knotted, or woven at regular intervals. Also, a thicket as an interwoven network of thorns. \{Strong's: 5442, 7638\}\hfill{}\\

\textbf{NETTING} Heb: {\large\H רשת} re-shet Def: A sheet of meshed fabric, cord or metal. \{Strong's: 7568\}\hfill{}\\

\textbf{NEVERTHELESS} Heb: {\large\H אבל} a-val Def: In spite of that. A flowing of certainty. \{Strong's: 61\}\hfill{}\\

\textbf{NEW} Heb: {\large\H חדש} hha-dash Def: Something that is new, renewed, restored or repaired. \{Strong's: 2319, 2323\}\hfill{}\\

\textbf{NEW.MOON} Heb: {\large\H חודש} hho-desh Def: The moon phase when the thin crescent first appears and is perceived as the renewal of the moon. The first day of the month. Also, a month as the interval between crescents. \{Strong's: 2320\}\hfill{}\\

\textbf{NIGHT} Heb: {\large\H ליל} la-yil Def: The time from dusk to dawn. The hours associated with darkness and sleep. \{Strong's: 3915\}\hfill{}\\

\textbf{NIGHT.WATCH} Heb: {\large\H אשמורה} ash-mu-rah Def: An increment of time during the night when guards watch the area. \{Strong's: 821\}\hfill{}\\

\textbf{NINE} Heb: {\large\H תשע} ti-sha \textbf{\textbackslash{}} {\large\H תשע} tey-sha Def: A cardinal number. The total number of hours in an ancient day or night. \{Strong's: 8672, 8673\}\hfill{}\\

\textbf{NINTH} Heb: {\large\H תשיעי} {[}X{]} Def: {[}X{]} \{Strong's: 8671\}\hfill{}\\

\textbf{NOBILITY} Heb: {\large\H חירה} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{NOBLE} Heb: {\large\H סר} sar Def: Possessing outstanding qualities or properties. Of high birth or exalted rank. One who has authority. May also mean ``heavy'' from the weight of responsibility on one in authority. \{Strong's: 5620, 8269\}\hfill{}\\

\textbf{NOBLEWOMAN} Heb: {\large\H סרה} {[}X{]} Def: A female of authority. \{Strong's: 8282\}\hfill{}\\

\textbf{NOD (Verb)} Heb: {\large\H נוד} n.w.d Def: A quick downward motion of the head. To shake or wag out of pity, sorrow or wandering. \{Strong's: 5110, 5111\}\hfill{}\\

\textbf{NODDING} Heb: {\large\H נוד} nod Def: In the sense of nodding ones head when wandering about. \{Strong's: 5112\}\hfill{}\\

\textbf{NOMAD} Heb: {\large\H צי} {[}X{]} Def: Also a ship as a nomad of the sea. \{Strong's: 6716\}\hfill{}\\

\textbf{NONE} Heb: {\large\H בל} {[}X{]} Def: {[}X{]} \{Strong's: 1077\}\hfill{}\\

\textbf{NORTH} Heb: {\large\H צפון} tsa-phon Def: From the North Star which is watched for direction. \{Strong's: 6828\}\hfill{}\\

\textbf{NOSE} Heb: {\large\H אף} aph Def: The organ bearing the nostrils on the anterior of the face. The nostrils when used in the plural form. Also meaning anger from the flaring of the nostrils and the redness of the nose when angry. \{Strong's: 639\}\hfill{}\\

\textbf{NOSE.RING} Heb: {\large\H חח} hhahh Def: A round piece of jewelry, usually of a metal, that is pierced through the nose or lip. \{Strong's: 2397\}\hfill{}\\

\textbf{NOT} Heb: {\large\H לוא} lo Def: A function word to stand for the negative. As being without. \{Strong's: 3808\}\hfill{}\\

\textbf{NOURISHMENT} Heb: {\large\H מאכל} ma-a-kal Def: Food; nutriment. For giving sustenance and making one whole. \{Strong's: 3978\}\hfill{}\\

\textbf{NOW} Heb: {\large\H עתה} a-tah Def: At the present time or moment. \{Strong's: 6258\}\hfill{}\\

\textbf{NUDE} Heb: {\large\H ערום} a-rom Def: Without clothes in the sense of bare skin. \{Strong's: 6174\}\hfill{}\\

\textbf{NUMBER} Heb: {\large\H מספר} mis-phar Def: A sum of units. Counting as a recording. \{Strong's: 4557\}\hfill{}\\

\textbf{NUMEROUS} Heb: {\large\H עצום} a-tsum Def: Involving more than one. \{Strong's: 6099\}\hfill{}\\

\textbf{OAK} Heb: {\large\H אללה} eyl-lah Def: The tough durable wood of the oak tree. Strongest of the woods. \{Strong's: 424, 427\}\hfill{}\\

\textbf{OAK.TREE} Heb: {\large\H אילן} {[}X{]} Def: {[}X{]} \{Strong's: 363\}\hfill{}\\

\textbf{OASIS} Heb: {\large\H מנוח} ma-no-ahh \textbf{\textbackslash{}} {\large\H מנוחה} me-nu-hhah Def: A location where there is freedom from activity or labor; a place for resting or lodging. \{Strong's: 4494, 4496\}\hfill{}\\

\textbf{OATH} Heb: {\large\H אלה} a-lah Def: Something corroborated by a vow. A binding agreement, including the curse for violating the oath. \{Strong's: 423\}\hfill{}\\

\textbf{OBEDIENCE} Heb: {\large\H יקהה} ye-qa-hah Def: Submission to the will of another. In the sense of being restrained. \{Strong's: 3349\}\hfill{}\\

\textbf{OBESE} Heb: {\large\H דשן} {[}X{]} Def: {[}X{]} \{Strong's: 1879, 1880\}\hfill{}\\

\textbf{OFFENSE} Heb: {\large\H פשע} pe-sha Def: The exceeding of due bounds or limits. \{Strong's: 6588\}\hfill{}\\

\textbf{OFFER.WILLINGLY (Verb)} Heb: {\large\H נדב} n.d.b Def: To give from a willing heart. \{Strong's: 5068, 5069\}\hfill{}\\

\textbf{OFFERED.WILLINGLY} Heb: {\large\H נדב} na-dav Def: Given of one's free will without recompense. \{Strong's: n/a\}\hfill{}\\

\textbf{OFFERING} Heb: {\large\H תרומה} te-ru-mah Def: A donation presented to another. \{Strong's: 8641\}\hfill{}\\

\textbf{OFFSHOOT} Heb: {\large\H עקר} ey-qer Def: {[}X{]} \{Strong's: 6133\}\hfill{}\\

\textbf{OH} Heb: {\large\H אוי} {[}X{]} Def: A passionate cry of desire. \{Strong's: 188\}\hfill{}\\

\textbf{OIL} Heb: {\large\H שמן} she-men Def: A semi-liquid, often oily and thick. Usually olive oil and used as a medicinal ointment. Also, meaning fat or rich. \{Strong's: 8081, 8082\}\hfill{}\\

\textbf{OINTMENT} Heb: {\large\H משחה} mash-hhah Def: An oil or other liquid that is smeared on an animal or person for healing or dedication. \{Strong's: 4888\}\hfill{}\\

\textbf{OINTMENT.MIXTURE} Heb: {\large\H מרקחת} mir-qa-hhat Def: A mixture of spices for an ointment or perfume. \{Strong's: 4842\}\hfill{}\\

\textbf{OLD.AGE} Heb: {\large\H זיקנה} ziq-nah Def: One up in years. \{Strong's: 2209\}\hfill{}\\

\textbf{OLIVE} Heb: {\large\H זית} za-yit Def: The fruit or the tree. The fruit of the olive is used for food and as a source of oil. \{Strong's: 2132\}\hfill{}\\

\textbf{OLIVINE} Heb: {\large\H פיטדה} pit-dah Def: Probably the Olivine, a green gemstone. The Septuagint uses the word topazios, but the Topaz was unknown at the time of the Exodus. Another possible meaning of this word is Chrysolite. \{Strong's: 6357\}\hfill{}\\

\textbf{OMER} Heb: {\large\H עומר} o-mer Def: A dry measure equal to one tenth of an ephah (about two liters). \{Strong's: 6016\}\hfill{}\\

\textbf{ON.ACCOUNT.OF} Heb: {\large\H גלל} ge-lal Def: A telling of what occurred previously. Thus used in Hebrew as a rolling back around. \{Strong's: 1558\}\hfill{}\\

\textbf{ON.FOOT} Heb: {\large\H רגלי} rag-li Def: A soldier, messenger or traveler who moves on foot. \{Strong's: 7273\}\hfill{}\\

\textbf{ONE} Heb: {\large\H עשתי} ash-tey Def: Existing, acting, or considered as a single unit, entity, or individual. \{Strong's: 6249\}\hfill{}\\

\textbf{ONE.HALF} Heb: {\large\H מחצית} ma-hha-tsit Def: A portion that is equal to the remainder. \{Strong's: 4276\}\hfill{}\\

\textbf{ONE.TENTH} Heb: {\large\H עשרון} i-sa-ron Def: An equal part of something divided into ten parts. \{Strong's: 6241\}\hfill{}\\

\textbf{ONION} Heb: {\large\H בצל} {[}X{]} Def: {[}X{]} \{Strong's: 1211\}\hfill{}\\

\textbf{ONLY} Heb: {\large\H רק} raq Def: A single instance or thing and nothing more or different. \{Strong's: 7535\}\hfill{}\\

\textbf{ONYCHA} Heb: {\large\H שחלת} she-hhey-let Def: An unknown precious stone. \{Strong's: 7827\}\hfill{}\\

\textbf{ONYX} Heb: {\large\H שוהם} sho-ham Def: Probably the Onyx, a form of quartz that may be of any color. The Septuagint uses beryllios (Beryl). Another possible translation is the Malachite. \{Strong's: 7718\}\hfill{}\\

\textbf{OPAL} Heb: {\large\H לשם} le-shem Def: Possibly the Opal, which may be found in a wide variety of colors. Other possible translates are Amber, Jacinth, Agate or Amethyst. \{Strong's: 3958\}\hfill{}\\

\textbf{OPEN (Verb)} Heb: {\large\H פתח} p.t.hh Def: To open up as opening a gate or door; to have no confining barrier. The piel (intensive) form means ``engrave.'' \{Strong's: 6603, 6605, 6606\}\hfill{}\\

\textbf{OPEN.SPACE} Heb: {\large\H מגרש} {[}X{]} \textbf{\textbackslash{}} {\large\H מגרשה} {[}X{]} Def: A place for grazing livestock, usually on the outskirts of a village or city. \{Strong's: 4054\}\hfill{}\\

\textbf{OPEN.UP (Verb)} Heb: {\large\H פקח} p.q.hh Def: To make available or accessible. Open the eyes or ears to see or hear. \{Strong's: 6491\}\hfill{}\\

\textbf{OPENED.WIDE} Heb: {\large\H פעור} pe-or Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{OPENING} Heb: {\large\H פתח} pe-tahh Def: Something that is open, as an entrance or opening of a tent, house or city. \{Strong's: 6607, 6608\}\hfill{}\\

\textbf{OPINION} Heb: {\large\H דע} {[}X{]} Def: To possess an intimate knowledge. \{Strong's: 1843\}\hfill{}\\

\textbf{OPPONENT} Heb: {\large\H סטן} {[}X{]} Def: One who is on the opposing side of an action or thought; an adversary. \{Strong's: 7854\}\hfill{}\\

\textbf{OPPOSITE} Heb: {\large\H נגד} ne-ged Def: Something in front of; on the other side; in the presence of. \{Strong's: 5048, 5049\}\hfill{}\\

\textbf{OPPOSITION} Heb: {\large\H סיטנה} {[}X{]} Def: {[}X{]} \{Strong's: 7855\}\hfill{}\\

\textbf{OPPRESS (Verb)} Heb: {\large\H עשק} ah.sh.q Def: To press into or on another through for force or deceit. \{Strong's: 6231\}\hfill{}\\

\textbf{OPPRESSION} Heb: {\large\H עושק} {[}X{]} Def: {[}X{]} \{Strong's: 6233\}\hfill{}\\

\textbf{OR} Heb: {\large\H או} o Def: An alternative or optional desire. \{Strong's: 176\}\hfill{}\\

\textbf{ORDINARY} Heb: {\large\H חל} {[}X{]} Def: A place, person or thing that is not set apart for a specific function. \{Strong's: 2455\}\hfill{}\\

\textbf{ORNAMENT} Heb: {\large\H מגדנה} mig-da-nah Def: Something that lends grace and beauty. Precious ornaments probably with gems. \{Strong's: 4030\}\hfill{}\\

\textbf{ORNAMENTAL.RING} Heb: {\large\H נזם} ne-zem Def: A circular band worn as an ornament. \{Strong's: 5141\}\hfill{}\\

\textbf{ORPHAN} Heb: {\large\H יתום} ya-tom Def: Having no mother or father. \{Strong's: 3490\}\hfill{}\\

\textbf{OTHER} Heb: {\large\H אחר} a-hhar Def: One that remains or follows after another. \{Strong's: 312, 317\}\hfill{}\\

\textbf{OTHER.SIDE} Heb: {\large\H עבר} ey-ver Def: As being across from this side. \{Strong's: 5676\}\hfill{}\\

\textbf{OTHERWISE} Heb: {\large\H פן} peyn Def: In a different manner or way. \{Strong's: 6435\}\hfill{}\\

\textbf{OUT.OF.SIGHT} Heb: {\large\H עלמון} al-mon Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{OUTCRY} Heb: {\large\H שועה} shaw-ah Def: An expression of need, or help or injustice. A loud wail from distress. \{Strong's: 7775\}\hfill{}\\

\textbf{OUTER} Heb: {\large\H קיצון} qi-tson Def: The furthest from the center. The end. \{Strong's: 7020\}\hfill{}\\

\textbf{OUTER.COVERING} Heb: {\large\H כסוי} {[}X{]} Def: {[}X{]} \{Strong's: 3681\}\hfill{}\\

\textbf{OUTER.GARMENT} Heb: {\large\H שלמה} sal-mah Def: Garments worn over top of other garments. \{Strong's: 8008\}\hfill{}\\

\textbf{OUTER.RIM} Heb: {\large\H כרכוב} kar-kov Def: The out edge of something. \{Strong's: 3749\}\hfill{}\\

\textbf{OUTSIDE} Heb: {\large\H חוץ} hhuts Def: A place or region beyond an enclosure or barrier. \{Strong's: 2351\}\hfill{}\\

\textbf{OVEN} Heb: {\large\H תנור} ta-nur Def: A chamber used for baking, heating or drying. As a lamp for cooking. \{Strong's: 8574\}\hfill{}\\

\textbf{OVERCOME (Verb)} Heb: {\large\H גבר} g.b.r Def: To get the better of. Be successful in strength or authority. \{Strong's: 1396\}\hfill{}\\

\textbf{OVERHANG} Heb: {\large\H סרח} se-rahh Def: What is left over. A remnant. Residue or overhanging. \{Strong's: 5629\}\hfill{}\\

\textbf{OVERHANG (Verb)} Heb: {\large\H סרח} s.r.hh Def: To proceed beyond any given or supposed limit or measure. To extend beyond proper bounds. To be superfluous. \{Strong's: 5628\}\hfill{}\\

\textbf{OVERLAY (Verb)} Heb: {\large\H צפה} ts.p.h Def: To cover with a different material, usually with gold. \{Strong's: 6823\}\hfill{}\\

\textbf{OVERLOOK (Verb)} Heb: {\large\H נשה} n.sh.h Def: To unintentionaly look past, forget. \{Strong's: 5382\}\hfill{}\\

\textbf{OVERSEER} Heb: {\large\H פקיד} pa-qid Def: One who carefully watches over; a superintendent. \{Strong's: 6496\}\hfill{}\\

\textbf{OVERSIGHT} Heb: {\large\H משגה} mish-geh Def: Watchful and responsible care. \{Strong's: 4870\}\hfill{}\\

\textbf{OVERTAKE (Verb)} Heb: {\large\H נסג} n.s.g Def: To catch up with; to remove in the sense of taking over. \{Strong's: 5253, 5381\}\hfill{}\\

\textbf{OVERTHROWING} Heb: {\large\H מהפכה} {[}X{]} Def: {[}X{]} \{Strong's: 4114\}\hfill{}\\

\textbf{OVERTHROWN} Heb: {\large\H ריסה} ri-sah Def: To ruin or break into pieces by throwing or pulling down. Meaning Dubious. \{Strong's: n/a\}\hfill{}\\

\textbf{OVERTOP (Verb)} Heb: {\large\H הגג} h.g.g Def: The covering of a dwelling place. \{Strong's: n/a\}\hfill{}\\

\textbf{OVERTURN (Verb)} Heb: {\large\H הפך} h.p.k Def: To turn something over or upside down, as if pouring out its contents. \{Strong's: 2015\}\hfill{}\\

\textbf{OVERTURNING} Heb: {\large\H הפכה} ha-phey-khah Def: The act of turning something over. \{Strong's: 2018\}\hfill{}\\

\textbf{OWNER} Heb: {\large\H גביר} ge-vir Def: Possessor of an article or property. \{Strong's: 1376\}\hfill{}\\

\textbf{OX} Heb: {\large\H שור} shor Def: A domestic bovine animal used for pulling heavy loads. \{Strong's: 7794, 8450\}\hfill{}\\

\textbf{PACK (Verb)} Heb: {\large\H טען} t.ah.n Def: A bundle arranged for carrying. \{Strong's: 2943\}\hfill{}\\

\textbf{PALACE} Heb: {\large\H ארם} {[}X{]} Def: As built in high places. \{Strong's: n/a\}\hfill{}\\

\textbf{PALISADE} Heb: {\large\H עופל} {[}X{]} Def: {[}X{]} \{Strong's: 6076\}\hfill{}\\

\textbf{PALM} Heb: {\large\H כף} kaph Def: A tropical tree with fan-shaped leaves. Part of the hand or foot between the base of the digits and the wrist or ankle. A palm-shaped object. \{Strong's: 3709, 3710\}\hfill{}\\

\textbf{PALM.GROVE} Heb: {\large\H דיקלה} da-phaq Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{PAN} Heb: {\large\H מחבת} {[}X{]} Def: {[}X{]} \{Strong's: 4227\}\hfill{}\\

\textbf{PARAPET} Heb: {\large\H מעקה} {[}X{]} Def: A place of pressing as one leans on it. A wall that is placed around the roof as this place was occupied because of its coolness in the summer. \{Strong's: 4624\}\hfill{}\\

\textbf{PARCEL} Heb: {\large\H חלקה} hhal-qah Def: A section or portion of land that has been purchased or aquired. \{Strong's: 2513\}\hfill{}\\

\textbf{PARCHED} Heb: {\large\H נגב} ne-gev Def: A dry and arid region, a desert. \{Strong's: n/a\}\hfill{}\\

\textbf{PARCHING.HEAT} Heb: {\large\H חורב} hho-rev Def: To shrivel or toast with intense heat. \{Strong's: 2721\}\hfill{}\\

\textbf{PART (Verb)} Heb: {\large\H פצה} p.ts.h Def: To separate. Part the lips to open the mouth. \{Strong's: 6475\}\hfill{}\\

\textbf{PARTNER} Heb: {\large\H מרע} mey-rey-a Def: One that shares. A close companion. \{Strong's: 4828\}\hfill{}\\

\textbf{PARTRIDGE} Heb: {\large\H חגלה} hhag-lah Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{PASS.OVER (Verb)} Heb: {\large\H חלף} hh.l.p Def: To pass through, by or over something. Also, to change in the sense of going to another one, side or thought. The piel (intensive) form means ``change.'' \{Strong's: 2498, 2499\}\hfill{}\\

\textbf{PAST.TIME} Heb: {\large\H קדמה} {[}X{]} Def: A time that is before. \{Strong's: 6927, 6928\}\hfill{}\\

\textbf{PASTE (Verb)} Heb: {\large\H חמר} hh.m.r Def: To smear a paste such as mortar on bricks or tar on a boat. \{Strong's: 2560\}\hfill{}\\

\textbf{PASTURE} Heb: {\large\H מקהל} {[}X{]} \textbf{\textbackslash{}} {\large\H מקהלה} {[}X{]} Def: The place where the flock gathers. \{Strong's: 4721\}\hfill{}\\

\textbf{PATH} Heb: {\large\H אורח} o-rahh Def: The road or route one travels. \{Strong's: 734\}\hfill{}\\

\textbf{PATTERN} Heb: {\large\H תבנית} tav-nit Def: A model or instructions detailing a construction. \{Strong's: 8403\}\hfill{}\\

\textbf{PAYMENT} Heb: {\large\H מסכורת} mas-ko-ret Def: Something that is paid. \{Strong's: 4909\}\hfill{}\\

\textbf{PEASANT} Heb: {\large\H פרז} pa-raz Def: One of lower rank, or value, usually dwelling in a town without walls. \{Strong's: 6518\}\hfill{}\\

\textbf{PEDESTAL} Heb: {\large\H מכונה} me-kho-nah Def: A base that is firm and functions as a supports. \{Strong's: 4350\}\hfill{}\\

\textbf{PEEL (Verb)} Heb: {\large\H פצל} p.ts.l Def: The skin or rind of a fruit; to strip off an outer layer. \{Strong's: 6478\}\hfill{}\\

\textbf{PEEL.OFF (Verb)} Heb: {\large\H פשט} p.sh.t Def: To strip off an outer layer; to spread apart; to invade in the sense of spreading out for an attack; to strip off clothing in the sense of spreading the garment for removal. \{Strong's: 6584\}\hfill{}\\

\textbf{PEG} Heb: {\large\H וו} waw Def: A peg, nail or hook as used for attaching one thing to another. \{Strong's: 2053\}\hfill{}\\

\textbf{PEOPLE} Heb: {\large\H עם} am Def: A large group of men or women. \{Strong's: 5971, 5972\}\hfill{}\\

\textbf{PERCEIVE (Verb)} Heb: {\large\H חזה} hh.z.h Def: To be able to understand on a higher level; to see something that is not physically present. \{Strong's: 1957, 2370, 2372\}\hfill{}\\

\textbf{PERES} Heb: {\large\H פרס} {[}X{]} Def: An unknown bird of prey. \{Strong's: 6538\}\hfill{}\\

\textbf{PERFORATE (Verb)} Heb: {\large\H חרם} hh.r.m Def: To fill with holes. To make holes. \{Strong's: 2763\}\hfill{}\\

\textbf{PERFORATED} Heb: {\large\H חרם} {[}X{]} \textbf{\textbackslash{}} {\large\H חרמה} {[}X{]} Def: Something filled with holes or is perforated. Also something accursed in the sense of being filled with holes. \{Strong's: 2764\}\hfill{}\\

\textbf{PERFORATED.ONE} Heb: {\large\H חרמון} hher-mon Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{PERFORM (Verb)} Heb: {\large\H פלא} p.l.a Def: To do a wondrous action that shows ones might. \{Strong's: 6381\}\hfill{}\\

\textbf{PERFORMANCE} Heb: {\large\H פלא} pe-le Def: A wondrous action. \{Strong's: 6382\}\hfill{}\\

\textbf{PERFORMING} Heb: {\large\H פלוא} pa-lu Def: The act of doing, displaying, or creating. \{Strong's: n/a\}\hfill{}\\

\textbf{PERISH} Heb: {\large\H אובד} {[}X{]} Def: {[}X{]} \{Strong's: 8\}\hfill{}\\

\textbf{PERISH (Verb)} Heb: {\large\H אבד} a.b.d Def: To be deserted or abandoned; separated from the whole, life or functionality. \{Strong's: 6, 7\}\hfill{}\\

\textbf{PERMANENT} Heb: {\large\H צמיתות} {[}X{]} Def: Something that is continual. \{Strong's: 6783\}\hfill{}\\

\textbf{PERSECUTION} Heb: {\large\H צרה} tsa-rah Def: To agitate mentally or spiritually; worry; disturb. \{Strong's: 6869\}\hfill{}\\

\textbf{PERSON} Heb: {\large\H אנוש} {[}X{]} Def: An individual, a man. \{Strong's: 582\}\hfill{}\\

\textbf{PERSUADE (Verb)} Heb: {\large\H סות} Def: {[}X{]} \{Strong's: 5496\}\hfill{}\\

\textbf{PESTILENCE} Heb: {\large\H מגפה} ma-gey-phah Def: A plague or other disaster that smites people or beasts. \{Strong's: 4046\}\hfill{}\\

\textbf{PETEN} Heb: {\large\H פתן} {[}X{]} Def: An unknown serpent, from its open mouth. \{Strong's: 6620\}\hfill{}\\

\textbf{PICK.OUT (Verb)} Heb: {\large\H נקר} n.q.r Def: {[}X{]} \{Strong's: 5365\}\hfill{}\\

\textbf{PICK.UP (Verb)} Heb: {\large\H לקט} l.q.t Def: To take hold of and lift up; to gather together. \{Strong's: 3950\}\hfill{}\\

\textbf{PIECE} Heb: {\large\H נתח} ney-tahh Def: A part of the original. What has been cut from the whole. \{Strong's: 5409\}\hfill{}\\

\textbf{PIERCE (Verb)} Heb: {\large\H דקר} d.q.r Def: To pierce through with a sword or other sharp object. \{Strong's: 1856\}\hfill{}\\

\textbf{PIERCE.THROUGH (Verb)} Heb: {\large\H נקב} n.q.b Def: To make a hole by puncturing or penetrating; to curse in the sense of piercing through. \{Strong's: 5344\}\hfill{}\\

\textbf{PIERCED.BREAD} Heb: {\large\H חלה} hha-lah Def: Bread that has many holes, as perforated. \{Strong's: 2471\}\hfill{}\\

\textbf{PIERCING} Heb: {\large\H שנינה} {[}X{]} Def: {[}X{]} \{Strong's: 8148\}\hfill{}\\

\textbf{PILE (Verb)} Heb: {\large\H ערם} ah.r.m Def: To mound up in a heap. \{Strong's: 6192\}\hfill{}\\

\textbf{PILE.OF.RUINS} Heb: {\large\H עי} {[}X{]} Def: {[}X{]} \{Strong's: 5856\}\hfill{}\\

\textbf{PILE.UP (Verb)} Heb: {\large\H צבר} ts.b.r Def: To heap something up in a mound. \{Strong's: 6651\}\hfill{}\\

\textbf{PILGRIMAGE} Heb: {\large\H מגור} ma-gur Def: A journey of a pilgrim; the course of life on earth. One who travels in a strange land. The pilgrimage or the dwelling place of a stranger. \{Strong's: 4033\}\hfill{}\\

\textbf{PILLAR} Heb: {\large\H עמוד} a-mud Def: A standing upright post or column. \{Strong's: 5982\}\hfill{}\\

\textbf{PILLAR.BASE} Heb: {\large\H רפיד} re-phid \textbf{\textbackslash{}} {\large\H רפידה} {[}X{]} Def: The lowest or deepest part of anything. \{Strong's: 7507\}\hfill{}\\

\textbf{PISTACHIO} Heb: {\large\H בוטן} bo-ten Def: A greenish-yellow nut from a small tree of the same name. From its belly shape. \{Strong's: 992\}\hfill{}\\

\textbf{PIT} Heb: {\large\H פחת} {[}X{]} \textbf{\textbackslash{}} {\large\H פחתת} {[}X{]} Def: A hole in the skin from disease. \{Strong's: 6354, 6356\}\hfill{}\\

\textbf{PIT.DIGGER} Heb: {\large\H שוחם} shu-hham Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{PITCH} Heb: {\large\H זפת} ze-phet Def: A sticky substance used to seal wood from water leakage. \{Strong's: 2203\}\hfill{}\\

\textbf{PITCH.TENT (Verb)} Heb: {\large\H אהל} a.h.l Def: To set up camp. By extension, can also mean a distant shining, such as the moon. \{Strong's: 166, 167\}\hfill{}\\

\textbf{PITIED} Heb: {\large\H חמול} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{PITIFUL} Heb: {\large\H חמלה} hhem-lah Def: Having or showing sympathetic consciousness of others’ distress with a desire to alleviate it. \{Strong's: 2551\}\hfill{}\\

\textbf{PLACE (Verb)} Heb: {\large\H סים} s.y.m Def: To put or set in a particular place, position, situation, or relation. \{Strong's: 3455, 7760, 7761\}\hfill{}\\

\textbf{PLACE.OF.LODGING} Heb: {\large\H מלון} ma-lon Def: An establishment for lodging and entertaining travelers. A place for spending the night. \{Strong's: 4411\}\hfill{}\\

\textbf{PLACE.TO.BURN} Heb: {\large\H מקטר} miq-tar Def: A specific location used for burning incense. \{Strong's: 4729\}\hfill{}\\

\textbf{PLAGUE} Heb: {\large\H נגע} ne-ga Def: An epidemic disease causing high mortality. An epidemic or other sore or illness as a touch from God. \{Strong's: 5061\}\hfill{}\\

\textbf{PLAIN} Heb: {\large\H מישור} {[}X{]} Def: A level, or straight, place. \{Strong's: 4334\}\hfill{}\\

\textbf{PLAIT} Heb: {\large\H משבצה} mish-be-tsah Def: A woven or checkered work. \{Strong's: 4865\}\hfill{}\\

\textbf{PLANT (Verb)} Heb: {\large\H נטע} n.t.ah Def: To put or set into the ground for growth; to establish plants in the sense of setting into place in the soil. \{Strong's: 5193\}\hfill{}\\

\textbf{PLANTATION} Heb: {\large\H כרמל} {[}X{]} Def: A field that produces an abundance of fruit. \{Strong's: 3759\}\hfill{}\\

\textbf{PLASTER (Verb)} Heb: {\large\H טוח} t.w.hh Def: To spread plaster out on a surface. \{Strong's: 2902\}\hfill{}\\

\textbf{PLATFORM} Heb: {\large\H במה} {[}X{]} Def: A place higher than the surrounding area. Often used in reference to sacred, or exalted, places. \{Strong's: 1116\}\hfill{}\\

\textbf{PLATTER} Heb: {\large\H קערה} qe-a-rah Def: A large plate, serving dish. \{Strong's: 7086\}\hfill{}\\

\textbf{PLEA} Heb: {\large\H דין} {[}X{]} Def: {[}X{]} \{Strong's: 1779, 1780, 1781, 1782\}\hfill{}\\

\textbf{PLEAD (Verb)} Heb: {\large\H פלל} p.l.l Def: To entreat or appeal earnestly; to fall to the ground to plead a cause to one in authority; prevent a judgment. \{Strong's: 6419\}\hfill{}\\

\textbf{PLEASANT} Heb: {\large\H חמדה} hhem-dah Def: Having qualities that tend to give pleasure. An object of desire. \{Strong's: 2532\}\hfill{}\\

\textbf{PLEASANTNESS} Heb: {\large\H נעמן} {[}X{]} Def: {[}X{]} \{Strong's: 5282\}\hfill{}\\

\textbf{PLEASE} Heb: {\large\H נא} na Def: A pleading or request for action from another. \{Strong's: 577, 4994\}\hfill{}\\

\textbf{PLEASURE} Heb: {\large\H עדן} e-den Def: A state of gratification. \{Strong's: 5730\}\hfill{}\\

\textbf{PLEDGE} Heb: {\large\H עבוט} {[}X{]} Def: What is given as security for a loan. \{Strong's: 5667\}\hfill{}\\

\textbf{PLENTY} Heb: {\large\H סבע} sa-va Def: A full or more than adequate supply. What is full, satisfied or abundant. \{Strong's: 7647, 7649\}\hfill{}\\

\textbf{PLOT (Verb)} Heb: {\large\H זמם} z.m.m Def: To devise a plan of action, usually with evil intent. \{Strong's: 2161\}\hfill{}\\

\textbf{PLOWING} Heb: {\large\H חריש} hha-rish Def: Breaking up the ground in order to plant a crop. The time of plowing. \{Strong's: 2758\}\hfill{}\\

\textbf{PLOWSHARE} Heb: {\large\H את} yet Def: The cutting point of a plow. \{Strong's: 855\}\hfill{}\\

\textbf{PLUCK (Verb)} Heb: {\large\H זמר} z.m.r Def: To make music by plucking an instrument. To pick fruit. \{Strong's: 2167, 2168\}\hfill{}\\

\textbf{PLUCK.AWAY (Verb)} Heb: {\large\H גזל} g.z.l Def: To take off something or someone by force through picking off, robbing or plundering. \{Strong's: 1497\}\hfill{}\\

\textbf{PLUCK.OUT (Verb)} Heb: {\large\H משה} m.sh.h Def: To draw or pull out. \{Strong's: 4871\}\hfill{}\\

\textbf{PLUCK.UP (Verb)} Heb: {\large\H עקר} ah.q.r Def: To pull or dig out the roots. \{Strong's: 6131, 6132\}\hfill{}\\

\textbf{PLUCKED} Heb: {\large\H גזלה} {[}X{]} Def: {[}X{]} \{Strong's: 1500\}\hfill{}\\

\textbf{PLUCKED.OUT} Heb: {\large\H מושה} mo-sheh Def: What is drawn or pulled out. \{Strong's: n/a\}\hfill{}\\

\textbf{PLUCKING} Heb: {\large\H גזל} {[}X{]} Def: {[}X{]} \{Strong's: 1498, 1499\}\hfill{}\\

\textbf{PLUMAGE} Heb: {\large\H חסידה} {[}X{]} Def: From its long and bowed neck. The soft feathers of the storks neck. \{Strong's: 2624\}\hfill{}\\

\textbf{PLUNDER (Verb)} Heb: {\large\H בזז} b.z.z Def: To commit robbery or looting. \{Strong's: 962\}\hfill{}\\

\textbf{POINT} Heb: {\large\H צפורן} {[}X{]} Def: The sharp pointed talon of a bird. Also a fingernail or the sharp point of a flint. \{Strong's: 6856\}\hfill{}\\

\textbf{POINT (Verb)} Heb: {\large\H תאה} t.a.h Def: To identify a mark. \{Strong's: 8376\}\hfill{}\\

\textbf{POISONOUS} Heb: {\large\H מרירי} {[}X{]} Def: {[}X{]} \{Strong's: 4815\}\hfill{}\\

\textbf{POLE} Heb: {\large\H מוטה} {[}X{]} Def: The bent bar of the yoke that goes around the neck, also a branch that is used as pole. \{Strong's: 4133\}\hfill{}\\

\textbf{POMEGRANATE} Heb: {\large\H רמון} ri-mon Def: A sweet deep red fruit prolific with seeds. A symbol of compassion and love. \{Strong's: 7416\}\hfill{}\\

\textbf{POOL} Heb: {\large\H אגם} a-gam Def: A collection of water, either natural or manmade. Once (Jeremiah 51:32) used for the reeds which line the pond. \{Strong's: 98, 99\}\hfill{}\\

\textbf{POPLAR} Heb: {\large\H ליבנה} liv-nah Def: A tree with white bark. \{Strong's: 3839\}\hfill{}\\

\textbf{PORTION} Heb: {\large\H חלק} hhey-leq Def: An individual’s part or share of something. The portions dispersed out. \{Strong's: 2506\}\hfill{}\\

\textbf{POSSESS (Verb)} Heb: {\large\H ירש} y.r.sh Def: To come into possession of or receive especially as a right or divine portion; o receive from an ancestor at his death; to take possession, either by seizing or through inheritance. \{Strong's: 3423\}\hfill{}\\

\textbf{POSSESSION} Heb: {\large\H מורש} {[}X{]} \textbf{\textbackslash{}} {\large\H מורשה} mo-ra-shah Def: Something that is personally owned. \{Strong's: 4180, 4181\}\hfill{}\\

\textbf{POSSIBLY} Heb: {\large\H אולי} u-li Def: Being within the limits of ability, capacity, or realization. A possible outcome. To desire what you are without in the sense of joining. \{Strong's: 194\}\hfill{}\\

\textbf{POST} Heb: {\large\H נציב} ne-tsiv Def: The place at which a soldier is stationed. As standing tall and firm. A garrison. \{Strong's: 5333\}\hfill{}\\

\textbf{POSTERITY} Heb: {\large\H נכד} ne-khed Def: The offspring of a progenitor to the furthest generation. Continuation through the next generation. \{Strong's: 5220\}\hfill{}\\

\textbf{POT} Heb: {\large\H סיר} sir Def: A vessel used for cooking or storing. \{Strong's: 5518\}\hfill{}\\

\textbf{POTSHERD} Heb: {\large\H חרס} {[}X{]} Def: Used for making pottery. Skin irritations are treated by applying clay to the irritation and left to dry. Clay left in the sun dries. \{Strong's: 2775, 2789\}\hfill{}\\

\textbf{POUCH} Heb: {\large\H צרור} tse-ror Def: A group of things fastened together for convenient handling. Something that is bound up tightly. \{Strong's: 6872\}\hfill{}\\

\textbf{POUR (Verb)} Heb: {\large\H נסך} n.s.k Def: To cause to flow in a stream; to give full expression to. \{Strong's: 5258, 5259, 5260\}\hfill{}\\

\textbf{POUR.DOWN (Verb)} Heb: {\large\H יצק} y.ts.q Def: To send a liquid from a container into another container or onto a person or object; to pour molten metal into a cast. \{Strong's: 3251, 3332\}\hfill{}\\

\textbf{POUR.OUT (Verb)} Heb: {\large\H שפך} sh.p.k Def: To let flow a liquid, often the blood of an animal in sacrifice or a man. \{Strong's: 8210\}\hfill{}\\

\textbf{POURED.OUT} Heb: {\large\H נסיך} {[}X{]} Def: A liquid poured out as an offering. \{Strong's: 5257\}\hfill{}\\

\textbf{POURING} Heb: {\large\H נסך} ne-sak Def: A liquid poured out as an offering or the pouring of a molten metal to form images. \{Strong's: 5261, 5262\}\hfill{}\\

\textbf{POVERTY} Heb: {\large\H מסכנות} {[}X{]} Def: Those who rely on benefits from others. \{Strong's: 4544\}\hfill{}\\

\textbf{POWDER} Heb: {\large\H עפר} a-phar Def: Matter in a fine particulate state. An abundant amount of powdery substance as dust or ash. \{Strong's: 6083\}\hfill{}\\

\textbf{POWDERY} Heb: {\large\H עפרון} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{POWER} Heb: {\large\H אלוה} e-lo-ah Def: Possession of control, authority, or influence over others; physical might. The power or might of one who rules or teaches. One who yokes with another. Often applies to rulers or a god. Often used in the plural form literally meaning ``mighty ones,'' but often used in a singular sense to mean ``The Mighty One.'' \{Strong's: 430, 433\}\hfill{}\\

\textbf{PRECIOUS} Heb: {\large\H מגד} {[}X{]} Def: What is choice, precious or excellent. \{Strong's: 4022\}\hfill{}\\

\textbf{PRECIOUS.METAL} Heb: {\large\H בצר} {[}X{]} Def: What is stored away and protected. \{Strong's: 1220, 1222\}\hfill{}\\

\textbf{PRECIPITATE (Verb)} Heb: {\large\H מטר} m.t.r Def: To rain or snow. \{Strong's: 4305\}\hfill{}\\

\textbf{PRECIPITATION} Heb: {\large\H מטר} ma-tar Def: A rain, snow or exceptionally heavy dew. \{Strong's: 4306\}\hfill{}\\

\textbf{PREDICT (Verb)} Heb: {\large\H נחש} n.hh.sh Def: {[}X{]} \{Strong's: 5172\}\hfill{}\\

\textbf{PREGNANCY} Heb: {\large\H הרון} hey-ron Def: The quality of containing unborn young within the body. From the mound of the belly. \{Strong's: 2032\}\hfill{}\\

\textbf{PREGNANT} Heb: {\large\H הרה} ha-reh Def: Containing unborn young within the body. \{Strong's: 2030\}\hfill{}\\

\textbf{PREPARE (Verb)} Heb: {\large\H כון} k.w.n Def: To put in proper condition or readiness. The piel (intensive) form means ``establish.'' \{Strong's: 3559\}\hfill{}\\

\textbf{PREPARED} Heb: {\large\H עתיד} {[}X{]} Def: {[}X{]} \{Strong's: 6263, 6264\}\hfill{}\\

\textbf{PRESENT} Heb: {\large\H ברכה} be-ra-khah Def: A gift given to another in respect as if on bended knee. Also, a pool of water as a place where one kneels down to drink from. \{Strong's: 1293, 1295\}\hfill{}\\

\textbf{PRESERVE (Verb)} Heb: {\large\H נצר} n.ts.r Def: To watch over or guard for protection. \{Strong's: 5341\}\hfill{}\\

\textbf{PRESS (Verb)} Heb: {\large\H סחט} s.hh.t Def: Pressure or pushing action. \{Strong's: 7818\}\hfill{}\\

\textbf{PRESS.FIRMLY (Verb)} Heb: {\large\H מעך} m.ah.k Def: {[}X{]} \{Strong's: 4600\}\hfill{}\\

\textbf{PRESS.HARD (Verb)} Heb: {\large\H פצר} p.ts.r Def: To push or urge another into an action. \{Strong's: 6484\}\hfill{}\\

\textbf{PRESS.IN (Verb)} Heb: {\large\H צרר} ts.r.r Def: To confine or restrict in a tight place. \{Strong's: 6887\}\hfill{}\\

\textbf{PRESS.OUT.OIL (Verb)} Heb: {\large\H צהר} ts.h.r Def: Extracting the fluids from the olive. \{Strong's: 6671\}\hfill{}\\

\textbf{PRESSED.PIECES} Heb: {\large\H מדוכה} {[}X{]} Def: {[}X{]} \{Strong's: 4085\}\hfill{}\\

\textbf{PRESUME (Verb)} Heb: {\large\H עפל} ah.p.l Def: {[}X{]} \{Strong's: 6075\}\hfill{}\\

\textbf{PREY} Heb: {\large\H טרף} te-reph Def: An animal taken as food by a predator. The meat that is torn by the predator. \{Strong's: 2964, 2965\}\hfill{}\\

\textbf{PRICE} Heb: {\large\H מכיר} {[}X{]} Def: {[}X{]} \{Strong's: 4242\}\hfill{}\\

\textbf{PRICKLY.THORN} Heb: {\large\H סנין} {[}X{]} Def: A sharp thorn that causes pain. \{Strong's: 6796\}\hfill{}\\

\textbf{PRIDE} Heb: {\large\H גאוה} {[}X{]} Def: A lifting up in a positive or negative sense. \{Strong's: 1346\}\hfill{}\\

\textbf{PRINCESS} Heb: {\large\H סרי} {[}X{]} Def: A female of authority. \{Strong's: n/a\}\hfill{}\\

\textbf{PRISON} Heb: {\large\H סוהר} so-har Def: A place of confinement. \{Strong's: 5470\}\hfill{}\\

\textbf{PRISONER} Heb: {\large\H אסיר} a-sir Def: One who is bound or confined. \{Strong's: 615, 616\}\hfill{}\\

\textbf{PRODUCE} Heb: {\large\H פרי} pe-ri Def: Agricultural products, especially fresh fruits and vegetables. The harvested product of a crop. \{Strong's: 6529\}\hfill{}\\

\textbf{PRODUCT} Heb: {\large\H יבול} {[}X{]} Def: The growth of fruits and crops from flooding waters. \{Strong's: 2981\}\hfill{}\\

\textbf{PRODUCTION} Heb: {\large\H תבואה} te-vu-ah Def: Total output of a commodity or an industry. An increase of produce, usually of fruit. \{Strong's: 8393\}\hfill{}\\

\textbf{PROFIT} Heb: {\large\H בצע} be-tsa Def: A valuable return; to derive benefit. The taking of money or something of value through force in the sense of cutting. \{Strong's: 1215\}\hfill{}\\

\textbf{PROJECTILE} Heb: {\large\H שלח} {[}X{]} Def: A weapon that is sent by the hand. Also a plant shoot as sent out of the ground. \{Strong's: 7973\}\hfill{}\\

\textbf{PROLONG (Verb)} Heb: {\large\H ארך} a.r.k Def: To lengthen or delay. \{Strong's: 748, 749\}\hfill{}\\

\textbf{PROPERTY} Heb: {\large\H ירשה} {[}X{]} Def: {[}X{]} \{Strong's: 3424\}\hfill{}\\

\textbf{PROPHESY (Verb)} Heb: {\large\H נבא} n.b.a Def: To utter the words or instructions of Elohiym received through a vision or dream. \{Strong's: 5012, 5013\}\hfill{}\\

\textbf{PROPHET} Heb: {\large\H נביא} na-vi Def: One who utters the words or instructions of Elohiym that are received through a vision or dream. \{Strong's: 5029, 5030\}\hfill{}\\

\textbf{PROPHETESS} Heb: {\large\H נביאה} na-vi-ah Def: One gifted with more than ordinary spiritual and moral insight. Who brings forth the inner fruit. \{Strong's: 5031\}\hfill{}\\

\textbf{PROPORTION} Heb: {\large\H מסה} {[}X{]} Def: An offering. \{Strong's: 4530\}\hfill{}\\

\textbf{PROSPER (Verb)} Heb: {\large\H צלח} ts.l.hh Def: To succeed; to move forward in distance, position or in thriving. \{Strong's: 6743, 6744\}\hfill{}\\

\textbf{PROSTITUTION} Heb: {\large\H זנון} za-nun Def: As paid with food. \{Strong's: 2183\}\hfill{}\\

\textbf{PROTECTION} Heb: {\large\H סיתר} si-tar Def: Shielded from harm or destruction, in the sense of being hidden. \{Strong's: n/a\}\hfill{}\\

\textbf{PROTECTIVE} Heb: {\large\H חנון} hha-nun Def: One who provides rescue or help to another. \{Strong's: 2587\}\hfill{}\\

\textbf{PROUD} Heb: {\large\H זדון} {[}X{]} Def: {[}X{]} \{Strong's: 2087\}\hfill{}\\

\textbf{PROUD.BEHOLDER} Heb: {\large\H גשור} ge-shur Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{PROVENDER} Heb: {\large\H מספוא} mis-po Def: Dry food for domestic animals. A gathering of food. \{Strong's: 4554\}\hfill{}\\

\textbf{PROVIDE (Verb)} Heb: {\large\H יהב} y.h.b Def: To give what is due; to grant or allow permission. \{Strong's: 3051, 3052\}\hfill{}\\

\textbf{PROVIDE.FOOD (Verb)} Heb: {\large\H לעט} l.ah.t Def: Supply nourishment. \{Strong's: 3938\}\hfill{}\\

\textbf{PROVIDE.PROTECTION (Verb)} Heb: {\large\H חנן} hh.n.n Def: To rescue or give help to another, to treat as valuable. The hitpael (reflexive) form means ``beseech.'' \{Strong's: 2589, 2603, 2604\}\hfill{}\\

\textbf{PROVISIONS} Heb: {\large\H צידה} tsi-dah Def: A stock of needed materials. The produce of the hunt. Also, used for ``food'' in general. \{Strong's: 6720\}\hfill{}\\

\textbf{PULL.OUT (Verb)} Heb: {\large\H שלף} sh.l.p Def: To pull out, up or off. \{Strong's: 8025\}\hfill{}\\

\textbf{PULLED.OUT} Heb: {\large\H שלף} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{PULVERIZE (Verb)} Heb: {\large\H שחק} sh.hh.q Def: To continually beat something to make it small or turn to powder. \{Strong's: 7833\}\hfill{}\\

\textbf{PUNISHMENT} Heb: {\large\H פיקרת} pi-qo-ret Def: {[}X{]} \{Strong's: 1244\}\hfill{}\\

\textbf{PURCHASE (Verb)} Heb: {\large\H קנה} q.n.h Def: To acquire ownership or occupation through an exchange. \{Strong's: 7066, 7069\}\hfill{}\\

\textbf{PURCHASED} Heb: {\large\H קנת} qe-nat Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{PURE} Heb: {\large\H טהור} ta-hor \textbf{\textbackslash{}} {\large\H טהורה} ta-ho-rah Def: Unmixed with any other matter. A man, animal or object that is free of impurities or is not mixed. \{Strong's: 2889, 2890\}\hfill{}\\

\textbf{PURE.GOLD} Heb: {\large\H פז} {[}X{]} Def: {[}X{]} \{Strong's: 6337\}\hfill{}\\

\textbf{PURPLE} Heb: {\large\H ארגמן} ar-ga-man Def: A reddish-blue color used to dye yarn and used in weaving. \{Strong's: 713\}\hfill{}\\

\textbf{PURSUE (Verb)} Heb: {\large\H רדף} r.d.p Def: To follow in order to overtake, capture, kill, or defeat; to pursue in chase or persecution. \{Strong's: 7291\}\hfill{}\\

\textbf{PUSH (Verb)} Heb: {\large\H נגש} n.g.sh Def: To drive oxen or men. \{Strong's: 5065\}\hfill{}\\

\textbf{PUSTULE} Heb: {\large\H אבעבועה} a-va-bu-ah Def: A swelling irritation that festers on the skin. An inflammatory pustule as an eruption. \{Strong's: 76\}\hfill{}\\

\textbf{QA'AT} Heb: {\large\H קאת} {[}X{]} Def: An unknown bird that vomits up its food for its chicks. \{Strong's: 6893\}\hfill{}\\

\textbf{QESHIYTAH} Heb: {\large\H קשיטה} qe-shiy-tah Def: A unit of value, money. \{Strong's: 7192\}\hfill{}\\

\textbf{QUAIL} Heb: {\large\H שלו} se-law Def: A small bird used as a food. \{Strong's: 7958\}\hfill{}\\

\textbf{QUANTITY} Heb: {\large\H מסורה} {[}X{]} Def: A large amount. \{Strong's: 4884\}\hfill{}\\

\textbf{QUARREL} Heb: {\large\H מדין} mid-yan Def: A rather loud verbal disagreement. \{Strong's: 4079\}\hfill{}\\

\textbf{QUARTER} Heb: {\large\H רבע} re-va Def: One portion from the whole that has been divided into four equal parts. One side of a four sided square. A fourth. \{Strong's: 7252, 7253\}\hfill{}\\

\textbf{QUARTZ} Heb: {\large\H חלמיש} {[}X{]} Def: An unknown stone. \{Strong's: 2496\}\hfill{}\\

\textbf{QUEEN} Heb: {\large\H מלכה} {[}X{]} Def: A female ruler of a region. \{Strong's: 4433, 4436\}\hfill{}\\

\textbf{QUENCH (Verb)} Heb: {\large\H כבה} k.b.h Def: {[}X{]} \{Strong's: 3518\}\hfill{}\\

\textbf{QUICKLY} Heb: {\large\H מהר} ma-heyr \textbf{\textbackslash{}} {\large\H מהרה} me-hey-rah Def: To act on a matter as soon as possible. \{Strong's: 4118, 4120\}\hfill{}\\

\textbf{QUIETNESS} Heb: {\large\H נחת} na-hhat Def: Without noise, without making a sound. \{Strong's: 5183\}\hfill{}\\

\textbf{QUIVER} Heb: {\large\H תלי} te-li Def: A case for holding or carrying arrows. As hung over the shoulder. \{Strong's: 8522\}\hfill{}\\

\textbf{RA'AH} Heb: {\large\H ראה} {[}X{]} Def: An unknown bird of prey with a keen sense of sight. \{Strong's: 7201\}\hfill{}\\

\textbf{RAFTER} Heb: {\large\H קורה} qo-rah Def: The beams which the roof of the house sits on. \{Strong's: 6982\}\hfill{}\\

\textbf{RAHHAM} Heb: {\large\H רחם} ra-hham \textbf{\textbackslash{}} {\large\H רחם} ra-hha-mah Def: An unknown species of bird. \{Strong's: 7360\}\hfill{}\\

\textbf{RAIMENT} Heb: {\large\H כסות} ke-sut Def: Clothing; garments. \{Strong's: 3682\}\hfill{}\\

\textbf{RAIN.SHOWER} Heb: {\large\H גשם} ge-shem Def: The rain of the skies. \{Strong's: 1653, 1655, 1730\}\hfill{}\\

\textbf{RAINDROP} Heb: {\large\H סעיר} {[}X{]} Def: As the hair from heaven. \{Strong's: 8164\}\hfill{}\\

\textbf{RAISE.UP (Verb)} Heb: {\large\H רום} r.w.m Def: To lift something up. \{Strong's: 7311, 7313\}\hfill{}\\

\textbf{RAISED} Heb: {\large\H רם} ram Def: Lifted up in position or in exaltation. \{Strong's: n/a\}\hfill{}\\

\textbf{RAM} Heb: {\large\H שה} seh Def: A member of a flock of sheep or goats. \{Strong's: 2089, 7716\}\hfill{}\\

\textbf{RAM.HORN} Heb: {\large\H שופר} sho-phar Def: The horn of ram made into a trumpet that emits a bright and beautiful sound. \{Strong's: 7782\}\hfill{}\\

\textbf{RAMPART} Heb: {\large\H חומה} hho-mah Def: A fortified enclosure. \{Strong's: 2346\}\hfill{}\\

\textbf{RANK} Heb: {\large\H מערכה} ma-a-ra-khah Def: A row, line, or series of things or persons. \{Strong's: 4634\}\hfill{}\\

\textbf{RANSOM} Heb: {\large\H פדות} pe-dut Def: The act of requiring, or paying, a price for something that was stolen or wrongfully taken. \{Strong's: 6304\}\hfill{}\\

\textbf{RANSOM (Verb)} Heb: {\large\H פדה} p.d.h Def: To Pay the price stipulated, to retrieve what has been stolen or wrongfully taken. \{Strong's: 6299\}\hfill{}\\

\textbf{RANSOM.PRICE} Heb: {\large\H פדיון} pid-yon Def: A stipulated amount given to retrieve what has been stolen or wrongfully taken. \{Strong's: 6306\}\hfill{}\\

\textbf{RANSOMED} Heb: {\large\H פדה} pe-dah Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{RAPID} Heb: {\large\H חידקל} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{RASH} Heb: {\large\H בהק} {[}X{]} Def: {[}X{]} \{Strong's: 933\}\hfill{}\\

\textbf{RATTLE} Heb: {\large\H נע} ney-a Def: A noun of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{RAVE (Verb)} Heb: {\large\H שגע} sh.g.ah Def: {[}X{]} \{Strong's: 7696\}\hfill{}\\

\textbf{RAVEN} Heb: {\large\H עורב} o-reyv Def: A glossy black bird. As black in color. \{Strong's: 6158\}\hfill{}\\

\textbf{RAVINE} Heb: {\large\H אשדה} {[}X{]} Def: {[}X{]} \{Strong's: 794\}\hfill{}\\

\textbf{RAW} Heb: {\large\H נא} na Def: Uncooked meat. Meat that is not fit for consumption. \{Strong's: 4995\}\hfill{}\\

\textbf{RAZOR} Heb: {\large\H תער} ta-ar Def: For shaving hair and making the face naked. For holding a blade. \{Strong's: 8593\}\hfill{}\\

\textbf{REACH (Verb)} Heb: {\large\H פגע} p.g.ah Def: To touch or grasp; to get up to or as far as; to come together in meeting by chance; to give or place in the sense of a meeting. \{Strong's: 6293\}\hfill{}\\

\textbf{READING} Heb: {\large\H מקרא} {[}X{]} Def: {[}X{]} \{Strong's: 4744\}\hfill{}\\

\textbf{REASON} Heb: {\large\H חשבון} {[}X{]} Def: A designed device. \{Strong's: 2808\}\hfill{}\\

\textbf{REBEL (Verb)} Heb: {\large\H מרד} m.r.d Def: To oppose or disobey one in authority or control. \{Strong's: 4775\}\hfill{}\\

\textbf{REBELLING} Heb: {\large\H נמרוד} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{REBELLION} Heb: {\large\H מרד} {[}X{]} Def: {[}X{]} \{Strong's: 4776, 4777, 4779\}\hfill{}\\

\textbf{REBELLIOUS} Heb: {\large\H מרי} {[}X{]} Def: {[}X{]} \{Strong's: 4805\}\hfill{}\\

\textbf{REBUKE} Heb: {\large\H מגערת} {[}X{]} Def: {[}X{]} \{Strong's: 4045\}\hfill{}\\

\textbf{REBUKE (Verb)} Heb: {\large\H גער} g.ah.r Def: A communication directed toward a disorderly person to effect a return to their rightful place of order. \{Strong's: 1605\}\hfill{}\\

\textbf{RECEIVE (Verb)} Heb: {\large\H קבל} q.b.l Def: To take or accept what has been given. \{Strong's: 6901, 6902\}\hfill{}\\

\textbf{RECKLESS} Heb: {\large\H פחז} pa-hhaz Def: Marked by lack of proper caution. \{Strong's: 6349\}\hfill{}\\

\textbf{RECKON (Verb)} Heb: {\large\H מנה} m.n.h Def: To appoint, assign, count or number a set of things or people. \{Strong's: 4483, 4487\}\hfill{}\\

\textbf{RECOGNIZE (Verb)} Heb: {\large\H נכר} n.k.r Def: To acknowledge or take notice of in some definite way. \{Strong's: 5234\}\hfill{}\\

\textbf{RECOMPENSE} Heb: {\large\H שילם} {[}X{]} Def: In the sense of making complete. \{Strong's: 8005\}\hfill{}\\

\textbf{RECORD} Heb: {\large\H סהד} {[}X{]} Def: {[}X{]} \{Strong's: 7717\}\hfill{}\\

\textbf{RED} Heb: {\large\H אדום} a-dom \textbf{\textbackslash{}} {\large\H אדומה} a-du-mah Def: Of the color red. Ruddy; florid. \{Strong's: 122\}\hfill{}\\

\textbf{REDDISH} Heb: {\large\H אדמדם} {[}X{]} \textbf{\textbackslash{}} {\large\H אדמדמת} a-dam-da-met Def: {[}X{]} \{Strong's: 125\}\hfill{}\\

\textbf{REDDISH.GRAY} Heb: {\large\H צוחר} tso-hhar Def: A dark grayish ruddy color. \{Strong's: n/a\}\hfill{}\\

\textbf{REDEEM (Verb)} Heb: {\large\H גאל} g.a.l Def: To buy back. Restore one to his original position or avenge his death. In the participle form this verb means ``avenger,'' as it is the role of the nearest relative to buy back one in slavery or avenge his murder. \{Strong's: 1350\}\hfill{}\\

\textbf{REDEEMED} Heb: {\large\H פדוי} {[}X{]} Def: {[}X{]} \{Strong's: 6302\}\hfill{}\\

\textbf{REDEMPTION} Heb: {\large\H גאולה} {[}X{]} Def: {[}X{]} \{Strong's: 1353\}\hfill{}\\

\textbf{REDUCED.TO.ASHES} Heb: {\large\H אופיר} a-phar Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{REED.PIPE} Heb: {\large\H עוגב} u-gav Def: A wind instrument made of reeds. \{Strong's: 5748\}\hfill{}\\

\textbf{REED-BASKET} Heb: {\large\H טנא} {[}X{]} Def: {[}X{]} \{Strong's: 2935\}\hfill{}\\

\textbf{REEDS} Heb: {\large\H סוף} suph Def: The plants that grow at the edge, or lip, of a river or pond. This word can also mean the edge or conclusion of something. \{Strong's: 5488, 5490, 5491\}\hfill{}\\

\textbf{REFINE (Verb)} Heb: {\large\H פזז} p.z.z Def: To reduce to a pure state. \{Strong's: 6338, 6339\}\hfill{}\\

\textbf{REFINED} Heb: {\large\H זך} zak Def: An oil or other substance that is free of impurities. Also, a person without impurities. \{Strong's: 2134\}\hfill{}\\

\textbf{REFLECTION} Heb: {\large\H מראה} mar-ah Def: The return of light or sound waves from a surface; production of an image as by a mirror. \{Strong's: 4759\}\hfill{}\\

\textbf{REFUGE} Heb: {\large\H מקלט} {[}X{]} Def: A place one may run to for safety from an avenger. \{Strong's: 4733\}\hfill{}\\

\textbf{REFUGE (Verb)} Heb: {\large\H חסה} hh.s.h Def: To take shelter or place ones trust in someone or something of support. \{Strong's: 2620\}\hfill{}\\

\textbf{REFUSE (Verb)} Heb: {\large\H מאן} m.a.n Def: To express one's self as being unwilling to accept. \{Strong's: 3985\}\hfill{}\\

\textbf{REFUSING} Heb: {\large\H מאן} ma-eyn Def: Rejection of a proposal, denial. \{Strong's: 3986, 3987\}\hfill{}\\

\textbf{REGION} Heb: {\large\H חבל} {[}X{]} Def: An area surrounded by a specific border. \{Strong's: 2256, 2257\}\hfill{}\\

\textbf{REGISTER (Verb)} Heb: {\large\H פקד} p.q.d Def: \{Strong's: 6485, 6486\}\hfill{}\\

\textbf{REGULATE (Verb)} Heb: {\large\H משל} m.sh.l Def: To govern or correct according to rule; to bring order, method, or uniformity to; to compare one thing to another in the sense of a rule of measurement, often as a proverb or parable. \{Strong's: 4910, 4911\}\hfill{}\\

\textbf{REGULATION} Heb: {\large\H ממשלה} mem-sha-lah Def: An authoritative rule dealing with details or procedure. The power and authority of one to regulate and control over another. \{Strong's: 4475\}\hfill{}\\

\textbf{REIGN (Verb)} Heb: {\large\H מלך} m.l.k Def: To rule over a kingdom as king or queen. \{Strong's: 4427\}\hfill{}\\

\textbf{REJECT (Verb)} Heb: {\large\H מאס} m.a.s Def: To refuse an action or thought that is not wanted or is despised. \{Strong's: 3988\}\hfill{}\\

\textbf{REJOICE (Verb)} Heb: {\large\H שמח} sh.m.hh Def: To be happy, glad. \{Strong's: 8055\}\hfill{}\\

\textbf{REJOICING} Heb: {\large\H סמח} {[}X{]} \textbf{\textbackslash{}} {\large\H סמחה} {[}X{]} Def: A state of felicity or happiness. \{Strong's: 8056, 8057\}\hfill{}\\

\textbf{RELEASE} Heb: {\large\H שמטה} {[}X{]} Def: As shaken off. \{Strong's: 8059\}\hfill{}\\

\textbf{RELEASE (Verb)} Heb: {\large\H שמט} sh.m.t Def: To let go by dropping or shaking loose. \{Strong's: 8058\}\hfill{}\\

\textbf{RELIEF} Heb: {\large\H ישועה} ye-shu-ah Def: A deliverance or freedom from a trouble, burden or danger. \{Strong's: 3444\}\hfill{}\\

\textbf{REMAIN (Verb)} Heb: {\large\H שאר} sh.a.r Def: To continue unchanged; to stay behind. \{Strong's: 7604\}\hfill{}\\

\textbf{REMAINDER} Heb: {\large\H יתר} ye-ter Def: A remaining group, part or trace. \{Strong's: 3499\}\hfill{}\\

\textbf{REMAINS} Heb: {\large\H שאר} she-ar Def: What is left behind, a residue. A relative as a remnant. Flesh as what remains after death. \{Strong's: 7605, 7606, 7607\}\hfill{}\\

\textbf{REMEMBER (Verb)} Heb: {\large\H זכר} z.k.r Def: To recall an event or action in memorial or reflection. To speak on behalf of another.To reenact a past event as a memorial. The hiphil (causative) form means ``mention.'' \{Strong's: 2142\}\hfill{}\\

\textbf{REMEMBRANCE} Heb: {\large\H זיכרון} zikh-ron Def: A recalling of a past event. Also, an action based on a past event. \{Strong's: 1799, 2146\}\hfill{}\\

\textbf{REMNANT} Heb: {\large\H שארית} she-ey-rit Def: A usually small part, member, or trace remaining. \{Strong's: 7611\}\hfill{}\\

\textbf{REMOVAL} Heb: {\large\H נידה} {[}X{]} Def: Something that is taken away or thrown out. A menstruating woman that is removed from the camp. \{Strong's: 5079, 5206\}\hfill{}\\

\textbf{REMOVE.THE.COVER (Verb)} Heb: {\large\H גלה} g.l.h Def: To reveal something by exposing it. Usually to be exposed from the removal of clothing. \{Strong's: 1540, 1541\}\hfill{}\\

\textbf{REMOVED} Heb: {\large\H צוען} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{REPEL (Verb)} Heb: {\large\H הדף} h.d.p Def: {[}X{]} \{Strong's: 1920\}\hfill{}\\

\textbf{REPLACEMENT} Heb: {\large\H חליפה} hha-li-phah Def: That which takes the place of , especially as a substitute or successor. In the sense of passing through one thing to another. \{Strong's: 2487\}\hfill{}\\

\textbf{REPORT} Heb: {\large\H שמע} shey-ma Def: An account or statement of an event or happening. What is heard. \{Strong's: 8088\}\hfill{}\\

\textbf{REPOSE (Verb)} Heb: {\large\H רגע} r.g.ah Def: To stir as in stirring the waters or to stir from sleep. In the sense of stirring the eyes. \{Strong's: 7280\}\hfill{}\\

\textbf{REPRODUCE (Verb)} Heb: {\large\H פרה} p.r.h Def: To produce new individuals of the same kind; to be abundant in fruit. \{Strong's: 6509\}\hfill{}\\

\textbf{REQUEST} Heb: {\large\H שאלה} {[}X{]} Def: A seeking for what is not known. \{Strong's: 7595, 7596\}\hfill{}\\

\textbf{RESCUE (Verb)} Heb: {\large\H ישע} y.sh.ah Def: To free or deliver from a trouble, burden or danger. \{Strong's: 3467\}\hfill{}\\

\textbf{RESEMBLANCE} Heb: {\large\H תמונה} te-mu-nah Def: To be of like kind. Having attributes that are similar in shape, size or value. \{Strong's: 8544\}\hfill{}\\

\textbf{RESEMBLE (Verb)} Heb: {\large\H דמה} d.m.h Def: To be like, similar or compared to something else. To become silent as one dead. \{Strong's: 1819, 1820, 1821\}\hfill{}\\

\textbf{RESERVER} Heb: {\large\H יתרן} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{RESIDE (Verb)} Heb: {\large\H זבל} z.b.l Def: To dwell permanently or continuously. \{Strong's: 2082\}\hfill{}\\

\textbf{RESIDENT} Heb: {\large\H זבולון} ze-vu-lan Def: One who abides or dwells in a place or area. \{Strong's: n/a\}\hfill{}\\

\textbf{RESPITE} Heb: {\large\H רוחה} re-wa-hhah Def: A relief from labor, punishment or trouble. \{Strong's: 7309\}\hfill{}\\

\textbf{REST} Heb: {\large\H נוח} no-ahh Def: {[}X{]} \{Strong's: 5118\}\hfill{}\\

\textbf{REST (Verb)} Heb: {\large\H נוח} n.w.hh Def: Freedom from activity or labor. To rest from trouble or labor. \{Strong's: 5117\}\hfill{}\\

\textbf{REST.DAY} Heb: {\large\H שבתון} sha-ba-ton Def: A day when work and normal activities are halted. \{Strong's: 7677\}\hfill{}\\

\textbf{RESTRAIN (Verb)} Heb: {\large\H עקב} ah.q.b Def: To prevent from doing. Hold back, in the sense of grabbing the heel. \{Strong's: 6117\}\hfill{}\\

\textbf{RESTRICT (Verb)} Heb: {\large\H כלא} k.l.a Def: To confine within bounds. Hold back or prevent someone or something. \{Strong's: 3607\}\hfill{}\\

\textbf{REVIVING} Heb: {\large\H מחיה} mihh-yah Def: Restoring to consciousness or life. \{Strong's: 4241\}\hfill{}\\

\textbf{RHINOCEROS} Heb: {\large\H ראם} {[}X{]} Def: A large land animal where some species have one horn (Latin: unicornis) and others have two (Latin: bicornis). \{Strong's: 7214\}\hfill{}\\

\textbf{RIB} Heb: {\large\H צלה} tsey-la Def: Any of the paired bony or cartilaginous bones that stiffen the walls of the thorax and protect the organs beneath. A ridge of a hill from its similar shape to a rib. Also, the side. \{Strong's: 5967, 6763\}\hfill{}\\

\textbf{RICH} Heb: {\large\H עשיר} a-shir Def: Having wealth or great possessions; abundantly supplied with resources, means, or funds. \{Strong's: 6223\}\hfill{}\\

\textbf{RICHES} Heb: {\large\H עושר} o-ser Def: Wealth. The possessions that make one wealthy. \{Strong's: 6239\}\hfill{}\\

\textbf{RIDDLE} Heb: {\large\H חידה} {[}X{]} Def: {[}X{]} \{Strong's: 2420\}\hfill{}\\

\textbf{RIDE (Verb)} Heb: {\large\H רכב} r.k.b Def: To sit and travel in any conveyance; to sit astride an animal, wagon or chariot. \{Strong's: 7392\}\hfill{}\\

\textbf{RIGHT} Heb: {\large\H ימני} ye-ma-ni Def: A direction as in to the right. \{Strong's: 3233\}\hfill{}\\

\textbf{RIGHT.HAND} Heb: {\large\H ימין} ya-min Def: The hand on the right side of a person. Also, a direction as in ``to the right.'' \{Strong's: 3225\}\hfill{}\\

\textbf{RIM} Heb: {\large\H מסגרת} mis-ge-ret Def: The edge of a region, hole, etc. , in the sense of enclosing. \{Strong's: 4526\}\hfill{}\\

\textbf{RING} Heb: {\large\H טבעת} ta-ba-at Def: A circular band of metal or other durable material. Also the signet ring containing the mark of the owner that is sunk into a lump of clay as a seal. \{Strong's: 2885\}\hfill{}\\

\textbf{RIP (Verb)} Heb: {\large\H פרם} p.r.m Def: {[}X{]} \{Strong's: 6533\}\hfill{}\\

\textbf{RIPE.FRUIT} Heb: {\large\H מלאה} me-ley-ah Def: Fruit that has come to full maturity and fit for eating. \{Strong's: 4395\}\hfill{}\\

\textbf{RIPEN (Verb)} Heb: {\large\H חנט} hh.n.t Def: To bring to completeness or perfection. Give off the fragrance of the fruit as it ripens. To add spices to a body for embalming. \{Strong's: 2590\}\hfill{}\\

\textbf{RISE (Verb)} Heb: {\large\H קום} q.w.m Def: To assume an upright position; to raise or rise up; to continue or establish. \{Strong's: 6965, 6966\}\hfill{}\\

\textbf{RISE.ABOVE (Verb)} Heb: {\large\H יעל} y.ah.l Def: {[}X{]} \{Strong's: 3276\}\hfill{}\\

\textbf{RISE.UP (Verb)} Heb: {\large\H גאה} g.a.h Def: To lift or grow up high. \{Strong's: 1342\}\hfill{}\\

\textbf{RISING} Heb: {\large\H עולה} o-lah Def: A rising of smoke from a burnt offering. Captivity in the sense of placing a yoke on the captives. \{Strong's: 1473, 5930\}\hfill{}\\

\textbf{RISING.SUN} Heb: {\large\H זרח} {[}X{]} Def: The early morning rising of the sun. \{Strong's: 2225\}\hfill{}\\

\textbf{RIVER} Heb: {\large\H נהר} na-har Def: A natural stream of water of considerable volume. The life-giving water that washes over the soil. \{Strong's: 5103, 5104\}\hfill{}\\

\textbf{ROAD} Heb: {\large\H דרך} de-rek Def: A route or path for traveled or walked. The path or manner of life. \{Strong's: 1870\}\hfill{}\\

\textbf{ROAM (Verb)} Heb: {\large\H רוד} r.w.d Def: To wander around restlessly. \{Strong's: 7300\}\hfill{}\\

\textbf{ROAMING} Heb: {\large\H ארוד} ra-dah Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{ROAR (Verb)} Heb: {\large\H הום} h.w.m Def: To make a loud noise. \{Strong's: 1949\}\hfill{}\\

\textbf{ROARING} Heb: {\large\H הם} ha-mon Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{ROAST} Heb: {\large\H צלי} tsa-li Def: A meat that is cooked over a fire. \{Strong's: 6748\}\hfill{}\\

\textbf{ROBE} Heb: {\large\H אדר} {[}X{]} \textbf{\textbackslash{}} {\large\H אדרת} a-de-ret Def: A long flowing outer garment. Wide garment. \{Strong's: 155\}\hfill{}\\

\textbf{ROCK.WALL} Heb: {\large\H שור} shur Def: A wall made of rocks or stones for protection. \{Strong's: 7790, 7791, 7792\}\hfill{}\\

\textbf{ROD} Heb: {\large\H מקל} ma-qeyl \textbf{\textbackslash{}} {\large\H מקלה} maq-lah Def: A long and slender bar of wood. A staff for walking. \{Strong's: 4731\}\hfill{}\\

\textbf{ROLL (Verb)} Heb: {\large\H גלל} g.l.l Def: A written document that may be wrapped round on itself. \{Strong's: 1556, 5953\}\hfill{}\\

\textbf{ROLLING.THING} Heb: {\large\H גלגל} {[}X{]} Def: The wheel of a cart or a whirlwind. \{Strong's: 1534, 1535, 1536\}\hfill{}\\

\textbf{ROOF} Heb: {\large\H גג} gag Def: The covering of a dwelling place. \{Strong's: 1406\}\hfill{}\\

\textbf{ROOF.COVERING} Heb: {\large\H מכסה} mikh-seh Def: Material used for a top or covering of a building. What covers something. \{Strong's: 4372\}\hfill{}\\

\textbf{ROOFING} Heb: {\large\H מגוג} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{ROOT} Heb: {\large\H שורש} {[}X{]} Def: The underground part of a plant. The source or origin of a thing. \{Strong's: 8328, 8330\}\hfill{}\\

\textbf{ROOT.OUT (Verb)} Heb: {\large\H נתש} n.t.sh Def: {[}X{]} \{Strong's: 5428\}\hfill{}\\

\textbf{ROT (Verb)} Heb: {\large\H מקק} m.q.q Def: {[}X{]} \{Strong's: 4743\}\hfill{}\\

\textbf{ROUND.ABOUT} Heb: {\large\H בעד} ba-ad Def: A circuitous way or route. \{Strong's: 1157\}\hfill{}\\

\textbf{ROUND.EARRING} Heb: {\large\H עגיל} {[}X{]} Def: As round. \{Strong's: 5694\}\hfill{}\\

\textbf{ROUND.STONE} Heb: {\large\H עיבל} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{ROUND.UP (Verb)} Heb: {\large\H קהל} q.h.l Def: To gather together a flock, herd or group of people. \{Strong's: 6950, 7035\}\hfill{}\\

\textbf{ROUNDED} Heb: {\large\H עובל} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{ROUNDNESS} Heb: {\large\H כיכר} ki-kar Def: 1. Cylindrical; something as a circle, globe or ring that is round. A round thing or place. A round loaf of bread. An expanse as a round piece of land. 2. Kikar: A dry standard of measure. Usually rendered as ``talent'' in most translations, however the word talent is a transliteration of the Greek word talanton (a Greek coin) used in the Greek Septuagint for the Hebrew word ``kikar.'' \{Strong's: 3603\}\hfill{}\\

\textbf{ROW} Heb: {\large\H טור} tur Def: Set or placed in a line. A mountain range as a row. \{Strong's: 2905, 2906\}\hfill{}\\

\textbf{ROW (Verb)} Heb: {\large\H טור} t.w.r Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{ROW.OF.TENTS} Heb: {\large\H טירה} ti-rah Def: A settlement usually larger than a hamlet and smaller than a town. \{Strong's: 2918\}\hfill{}\\

\textbf{RUB (Verb)} Heb: {\large\H מרט} m.r.t Def: To polish a sword by rubbing it. Also the plucking of hair by rubbing it with a sharp object. \{Strong's: 4803, 4804\}\hfill{}\\

\textbf{RUDDY} Heb: {\large\H אדמוני} ad-mo-niy Def: Having a healthy reddish color. \{Strong's: 132\}\hfill{}\\

\textbf{RUIN} Heb: {\large\H תל} {[}X{]} Def: A city that is covered over and made into a mound. \{Strong's: 8510\}\hfill{}\\

\textbf{RUINED.HEAP} Heb: {\large\H עי} ey Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{RULE (Verb)} Heb: {\large\H רדה} r.d.h Def: To exert control, direction, or influence over, especially by curbing or restraining; to spread out through a land through authority or by walking among the subjects. \{Strong's: 7287\}\hfill{}\\

\textbf{RUN (Verb)} Heb: {\large\H רוץ} r.w.ts Def: To go faster than a walk. \{Strong's: 7323\}\hfill{}\\

\textbf{SACK} Heb: {\large\H סק} saq Def: A bag of cloth or skins for carrying foods or objects. \{Strong's: 8242\}\hfill{}\\

\textbf{SACRIFICE} Heb: {\large\H זבח} ze-vahh Def: An animal killed for an offering. \{Strong's: 1685, 2077\}\hfill{}\\

\textbf{SACRIFICE (Verb)} Heb: {\large\H זבח} z.b.hh Def: An act of offering to deity something precious; to kill an animal for an offering. \{Strong's: 1684, 2076\}\hfill{}\\

\textbf{SACRIFICIAL.BOWL} Heb: {\large\H מנקית} me-na-qit Def: A vessel used to hold the required sacrifice. From the shape of a bowl that holds liquids like a breast that holds milk. \{Strong's: 4518\}\hfill{}\\

\textbf{SADDLE} Heb: {\large\H מרכב} {[}X{]} Def: {[}X{]} \{Strong's: 4817\}\hfill{}\\

\textbf{SADDLE (Verb)} Heb: {\large\H חבש} hh.b.sh Def: A shaped mounted support on which an object can travel; to bind up with a saddle. \{Strong's: 2280\}\hfill{}\\

\textbf{SADDLEBAG} Heb: {\large\H משפת} mish-pat Def: One of a pair of covered pouches laid behind the saddle. For carrying items. \{Strong's: 4942\}\hfill{}\\

\textbf{SAFEGUARD (Verb)} Heb: {\large\H שמר} sh.m.r Def: The act or the duty of protecting or defending; to watch over or guard in the sense of preserving or protecting. To keep watch. \{Strong's: 8104, 8109\}\hfill{}\\

\textbf{SAFEGUARDING} Heb: {\large\H שימור} shi-mur Def: To keep safe. To protect. \{Strong's: 8107\}\hfill{}\\

\textbf{SAFELY} Heb: {\large\H בטח} be-tahh Def: A state or place of safety. \{Strong's: 983\}\hfill{}\\

\textbf{SALT} Heb: {\large\H מלח} me-lahh Def: An ingredient that adds flavor to food and used in preserving foods. \{Strong's: 4416, 4417, 4419\}\hfill{}\\

\textbf{SANCTUARY} Heb: {\large\H מקדש} miq-dash Def: A place set apart for a special purpose. \{Strong's: 4720\}\hfill{}\\

\textbf{SAND} Heb: {\large\H חול} hhul Def: Loose granular material from the disintegration of rocks and consisting of particles not as fine as silt and used in mortar. Sand is used as an abrasive ingredient for drilling by placing it in the hole being drilled. \{Strong's: 2344\}\hfill{}\\

\textbf{SANDAL} Heb: {\large\H נעל} na-al \textbf{\textbackslash{}} {\large\H נעלה} na-a-lah Def: A shoe consisting of a sole strapped to the foot. \{Strong's: 5275\}\hfill{}\\

\textbf{SASH} Heb: {\large\H אבנט} av-neyt Def: A waistband worn around the waist. \{Strong's: 73\}\hfill{}\\

\textbf{SATISFACTION} Heb: {\large\H שבע} so-va Def: The state of being content. \{Strong's: 7648\}\hfill{}\\

\textbf{SAY (Verb)} Heb: {\large\H אמר} a.m.r Def: To speak chains of words that form sentences. \{Strong's: 559, 560\}\hfill{}\\

\textbf{SAYER} Heb: {\large\H אמול} e-mor Def: One who speaks words. Possibly a prophet or psalmist. \{Strong's: n/a\}\hfill{}\\

\textbf{SCAB} Heb: {\large\H ספחת} {[}X{]} Def: A sore that spreads. \{Strong's: 4556, 5597\}\hfill{}\\

\textbf{SCALES} Heb: {\large\H כסכסת} {[}X{]} Def: The covering of a fish. Also the scales of leather armor. \{Strong's: 7193\}\hfill{}\\

\textbf{SCARLET} Heb: {\large\H שני} sha-ni Def: Any of various bright reds. \{Strong's: 8144\}\hfill{}\\

\textbf{SCATTER (Verb)} Heb: {\large\H נפץ} n.p.ts Def: To fling away heedlessly. To separate and go in various directions. \{Strong's: 5310\}\hfill{}\\

\textbf{SCATTER.ABROAD (Verb)} Heb: {\large\H פוץ} p.w.ts Def: To sow, cast or fling widely. \{Strong's: 6327\}\hfill{}\\

\textbf{SCATTERED} Heb: {\large\H פישון} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{SCORCHING} Heb: {\large\H סדום} sa-gan Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{SCORPION} Heb: {\large\H עקרב} {[}X{]} Def: {[}X{]} \{Strong's: 6137\}\hfill{}\\

\textbf{SCOUR (Verb)} Heb: {\large\H מרק} m.r.q Def: To briskly rub something. \{Strong's: 4838\}\hfill{}\\

\textbf{SCRAPE.OFF (Verb)} Heb: {\large\H קצה} q.ts.h Def: To cut something out or make short. \{Strong's: 7096\}\hfill{}\\

\textbf{SCRAPED.BARE} Heb: {\large\H שפם} she-pham Def: {[}NOTE: Dictionary entry needs attention{]} \{Strong's: n/a\}\hfill{}\\

\textbf{SCRATCH (Verb)} Heb: {\large\H חרש} hh.r.sh Def: To plow in the sense of scratching a line in the soil; to engrave on wood or stone by scratching. This word can also mean ``to hold in peace'' or be silent. \{Strong's: 2790\}\hfill{}\\

\textbf{SCRAWNY} Heb: {\large\H דק} daq \textbf{\textbackslash{}} {\large\H דקה} da-qah Def: Wasted away physically. \{Strong's: 1851\}\hfill{}\\

\textbf{SCREAMING} Heb: {\large\H פעו} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{SCROLL} Heb: {\large\H ספר} se-pher \textbf{\textbackslash{}} {\large\H סיפרה} siph-rah Def: A document or record written on a sheet of papyrus, leather or parchment and rolled up for storage. \{Strong's: 5609, 5612, 5613\}\hfill{}\\

\textbf{SCULPT (Verb)} Heb: {\large\H פסל} p.s.l Def: To carve or chisel out a figure from wood or stone. \{Strong's: 6458\}\hfill{}\\

\textbf{SCULPTURE} Heb: {\large\H פסל} pe-sel Def: A figurine that is formed and shaped from stone, wood or clay. \{Strong's: 6456, 6459\}\hfill{}\\

\textbf{SEA} Heb: {\large\H ים} yam Def: A large body of water. Also, the direction of the great sea (the Mediterranean), the west. \{Strong's: 3220, 3221\}\hfill{}\\

\textbf{SE'AH} Heb: {\large\H סאה} se-ah Def: A dry standard of measure equal to 1/3 ephah. \{Strong's: 5429\}\hfill{}\\

\textbf{SEAL} Heb: {\large\H חותם} hho-tam Def: A seal used officially to give personal authority to a document. A signature ring or cylinder with the owner's seal that is pressed into clay to show ownership. \{Strong's: 2368\}\hfill{}\\

\textbf{SEAL (Verb)} Heb: {\large\H חתם} hh.t.m Def: To close tightly, often marked with the emblem of the owner that must be broken before opening. \{Strong's: 2856, 2857\}\hfill{}\\

\textbf{SEARCH (Verb)} Heb: {\large\H חפס} hh.p.s Def: To look thoroughly in an effort to find or discover something. \{Strong's: 2664\}\hfill{}\\

\textbf{SEARCH.OUT (Verb)} Heb: {\large\H בקש} b.q.sh Def: To intently look for someone or something until the object of the search is found. \{Strong's: 1245\}\hfill{}\\

\textbf{SEARCHING} Heb: {\large\H מחתרת} mahh-te-ret Def: A digging up to uncover something hidden. \{Strong's: 4290\}\hfill{}\\

\textbf{SEARING} Heb: {\large\H צרבת} {[}X{]} Def: {[}X{]} \{Strong's: 6867\}\hfill{}\\

\textbf{SEASON (Verb)} Heb: {\large\H מלח} m.l.hh Def: To season with salt to enhance the flavor. \{Strong's: 4414, 4415\}\hfill{}\\

\textbf{SEAT} Heb: {\large\H כיסא} ki-sey Def: A special chair of one in eminence. Usually a throne or seat of authority. \{Strong's: 3678, 3764\}\hfill{}\\

\textbf{SECOND} Heb: {\large\H שני} shey-ni Def: An ordinal number. \{Strong's: 8145\}\hfill{}\\

\textbf{SECRET} Heb: {\large\H לט} lat Def: That which is unknown or hidden. \{Strong's: 3909\}\hfill{}\\

\textbf{SECURE (Verb)} Heb: {\large\H אמן} a.m.n Def: Solidly fixed in place; to stand firm in the sense of a support. Not subject to change or revision. The hiphil (causative) form means ``support.'' \{Strong's: 539, 540\}\hfill{}\\

\textbf{SECURITY.DEPOSIT} Heb: {\large\H תסומה} te-su-mah Def: \{Strong's: 8667\}\hfill{}\\

\textbf{SEE (Verb)} Heb: {\large\H ראה} r.a.h Def: To take notice; to perceive something or someone; to see visions. The niphal (passive) form means ``appear'' and the hiphil (causative) form means ``show.'' \{Strong's: 7200, 7202, 7207, 7212\}\hfill{}\\

\textbf{SEED} Heb: {\large\H זרע} ze-ra Def: The grains or ripened ovules of plants used for sowing. Scattered in the field to produce a crop. The singular word can be used for one or more. Also, the descendants of an individual, either male or female. \{Strong's: 2233, 2234\}\hfill{}\\

\textbf{SEED.OF.GRAIN} Heb: {\large\H גרא} {[}X{]} Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{SEEING} Heb: {\large\H פקח} pi-qey-ahh Def: One who is able to see with the eyes. \{Strong's: 6493\}\hfill{}\\

\textbf{SEEING.AS} Heb: {\large\H יען} ya-an Def: In the degree that. Sense of paying attention. \{Strong's: 3282\}\hfill{}\\

\textbf{SEEK (Verb)} Heb: {\large\H דרש} d.r.sh Def: To look for or search for something or for answers. The niphal (passive) form means ``require.'' \{Strong's: 1875\}\hfill{}\\

\textbf{SEIZE (Verb)} Heb: {\large\H חזק} hh.z.q Def: To possess or take by force; grab hold tightly; to refrain or support by grabbing hold. \{Strong's: 2388\}\hfill{}\\

\textbf{SEIZE.HOLD (Verb)} Heb: {\large\H תפס} t.p.s Def: To take hold of something by force. \{Strong's: 8610\}\hfill{}\\

\textbf{SELECTED} Heb: {\large\H קריא} {[}X{]} Def: Individuals called out for a special purpose. \{Strong's: 7148\}\hfill{}\\

\textbf{SELF.WILL} Heb: {\large\H רצון} ra-tson Def: Used to express determination, insistence, persistence, or willfulness. One's desire. \{Strong's: 7522\}\hfill{}\\

\textbf{SELL (Verb)} Heb: {\large\H מכר} m.k.r Def: To give up property to another for money or another valuable compensation. \{Strong's: 4376\}\hfill{}\\

\textbf{SEND (Verb)} Heb: {\large\H שלח} sh.l.hh Def: To cause to go; to direct, order, or request to go. \{Strong's: 7971, 7972\}\hfill{}\\

\textbf{SEND.OFF} Heb: {\large\H שילוח} shi-lu-ahh Def: To send away a person or gift. \{Strong's: 7964\}\hfill{}\\

\textbf{SENDING} Heb: {\large\H משלח} {[}X{]} \textbf{\textbackslash{}} {\large\H משלחת} {[}X{]} Def: {[}X{]} \{Strong's: 4916, 4917\}\hfill{}\\

\textbf{SEPARATE (Verb)} Heb: {\large\H בדל} b.d.l Def: To set or keep apart. \{Strong's: 914\}\hfill{}\\

\textbf{SERAPH} Heb: {\large\H סרף} {[}X{]} Def: A supernatural creature, possibly a winged serpent or a dragon. \{Strong's: 8314\}\hfill{}\\

\textbf{SERPENT} Heb: {\large\H נחש} na-hhash Def: A poisonous snake that hisses, creeps and bites. \{Strong's: 5175\}\hfill{}\\

\textbf{SERVANT} Heb: {\large\H עבד} e-ved Def: One who provides a service to another, as a slave, bondservant or hired hand. \{Strong's: 5649, 5650, 5652, 5657\}\hfill{}\\

\textbf{SERVE (Verb)} Heb: {\large\H עבד} ah.b.d Def: To provide a service to another, as a servant or slave or to work at a profession. \{Strong's: 5647, 5648\}\hfill{}\\

\textbf{SERVICE} Heb: {\large\H עבודה} a-vo-dah Def: Labor provided by a servant or slave. \{Strong's: 5656\}\hfill{}\\

\textbf{SET.APART (Verb)} Heb: {\large\H קדש} q.d.sh Def: To move or place someone or something separate from the whole for a special purpose. \{Strong's: 6942\}\hfill{}\\

\textbf{SET.ASIDE (Verb)} Heb: {\large\H אצל} a.ts.l Def: To reserve or put aside something in the sense of keeping in the shadow. \{Strong's: 680\}\hfill{}\\

\textbf{SET.DOWN (Verb)} Heb: {\large\H שית} sh.y.t Def: To cause to sit down; to lay down. \{Strong's: 7896\}\hfill{}\\

\textbf{SETTING} Heb: {\large\H מלואה} mi-lu-ah Def: A recess for filling with a stone or other ornament. \{Strong's: 4396\}\hfill{}\\

\textbf{SETTLE (Verb)} Heb: {\large\H ישב} y.sh.b Def: To stay in a dwelling place for the night or for long periods of time; to sit down. \{Strong's: 3427, 3488\}\hfill{}\\

\textbf{SETTLER} Heb: {\large\H תושב} to-shav Def: One who stays temporarily. Travels from place to place. \{Strong's: 8453\}\hfill{}\\

\textbf{SETTLING} Heb: {\large\H מושב} mo-shav Def: The place of sitting, resting or dwelling, usually temporarily. \{Strong's: 4186\}\hfill{}\\

\textbf{SEVEN} Heb: {\large\H שבעה} shiv-ah \textbf{\textbackslash{}} {\large\H שבע} she-va Def: A cardinal number. \{Strong's: 7651, 7657, 7655\}\hfill{}\\

\textbf{SEVENFOLD} Heb: {\large\H שיבעה} {[}X{]} Def: {[}X{]} \{Strong's: 7655\}\hfill{}\\

\textbf{SEVENTH} Heb: {\large\H שביעי} she-vi-i Def: An ordinal number. \{Strong's: 7637\}\hfill{}\\

\textbf{SEVENTH.TIME} Heb: {\large\H שיבעת} {[}X{]} Def: A sequence of events ending with the seventh. \{Strong's: 7659\}\hfill{}\\

\textbf{SEVER (Verb)} Heb: {\large\H קצר} q.ts.r Def: To cut short or small; to harvest in the sense of severing the crop from its stalk; to be impatient in the sense of patience being severed. \{Strong's: 7114\}\hfill{}\\

\textbf{SEW.TOGETHER (Verb)} Heb: {\large\H תפר} t.p.r Def: To join two pieces of cloth with stitches of thread. \{Strong's: 8609\}\hfill{}\\

\textbf{SHA'AR} Heb: {\large\H שער} sha-ar Def: A standard of measure. \{Strong's: 8180\}\hfill{}\\

\textbf{SHADOW} Heb: {\large\H צל} tseyl Def: The dark figure cast on a surface by a body intercepting the rays from a light source. \{Strong's: 6738\}\hfill{}\\

\textbf{SHAHHAPH} Heb: {\large\H שחף} {[}X{]} Def: An unknown bird. \{Strong's: 7828\}\hfill{}\\

\textbf{SHAKE (Verb)} Heb: {\large\H רגז} r.g.z Def: To tremble in fear or anger. \{Strong's: 7264, 7265\}\hfill{}\\

\textbf{SHAKE.IN.AWE (Verb)} Heb: {\large\H פחד} p.hh.d Def: To physically or mentally tremble in amazement or fear. \{Strong's: 6342\}\hfill{}\\

\textbf{SHAKE.OFF (Verb)} Heb: {\large\H נער} n.ah.r Def: To violently shake back and forth to throw something off. To overthrow. \{Strong's: 5286, 5287\}\hfill{}\\

\textbf{SHAKING} Heb: {\large\H רגז} {[}X{]} Def: A shaking anger. \{Strong's: 7266, 7268\}\hfill{}\\

\textbf{SHAKING.IN.FEAR} Heb: {\large\H רעד} ra-ad \textbf{\textbackslash{}} {\large\H רעדה} re-a-dah Def: Being physically effected by shivering or shaking from a dreadful event. \{Strong's: 7461\}\hfill{}\\

\textbf{SHAME} Heb: {\large\H בשן} {[}X{]} \textbf{\textbackslash{}} {\large\H בשנה} {[}X{]} Def: In the sense of being whithered and dried up. \{Strong's: 1317\}\hfill{}\\

\textbf{SHAME (Verb)} Heb: {\large\H כלם} k.l.m Def: To feel pain through something dishonorable, improper or ridiculous. \{Strong's: 3637\}\hfill{}\\

\textbf{SHAPE} Heb: {\large\H תואר} to-ar Def: The outline of an individual. \{Strong's: 8389\}\hfill{}\\

\textbf{SHAPHAN} Heb: {\large\H שפן} {[}X{]} Def: An unknown animal. \{Strong's: 8227\}\hfill{}\\

\textbf{SHARE} Heb: {\large\H מן} mahn \textbf{\textbackslash{}} {\large\H מנה} ma-nah Def: A portion that is provided to a group or person to meet their needs. \{Strong's: 4490\}\hfill{}\\

\textbf{SHARP.SIGHTED} Heb: {\large\H עקן} a-qod Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{SHARP.STONE} Heb: {\large\H צור} tsor Def: A piece of stone from obsidian, flint or chert that forms a narrow and sharp edge when flaked off. \{Strong's: 6864\}\hfill{}\\

\textbf{SHARP.THORN} Heb: {\large\H צן} tseyn Def: A pointed, piercing object. \{Strong's: 6791\}\hfill{}\\

\textbf{SHARPEN (Verb)} Heb: {\large\H לטש} l.t.sh Def: To hone in the sense of narrowing the blade edge by using a whetstone or hammer. To narrow the eyes in the sense of looking sharply, as in squinting. \{Strong's: 3913\}\hfill{}\\

\textbf{SHARPENED} Heb: {\large\H לטוש} la-tash Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{SHATTER (Verb)} Heb: {\large\H חשל} hh.sh.l Def: {[}X{]} \{Strong's: 2826, 2827\}\hfill{}\\

\textbf{SHAVE (Verb)} Heb: {\large\H גלח} g.l.hh Def: To cut off the hair from the face or another part of the body. \{Strong's: 1548\}\hfill{}\\

\textbf{SHE} Heb: {\large\H היא} hi Def: The female who is neither the speaker nor the one addressed. \{Strong's: 1931, 1932\}\hfill{}\\

\textbf{SHE.DONKEY} Heb: {\large\H אתון} a-ton Def: A female ass. \{Strong's: 860\}\hfill{}\\

\textbf{SHE.GOAT} Heb: {\large\H עז} eyz Def: A female goat. \{Strong's: 5795, 5796\}\hfill{}\\

\textbf{SHEAF} Heb: {\large\H עומר} {[}X{]} Def: As bound. \{Strong's: 6016\}\hfill{}\\

\textbf{SHEAR (Verb)} Heb: {\large\H גזז} g.z.z Def: To cut or clip wool or hair from something. \{Strong's: 1494\}\hfill{}\\

\textbf{SHEAVE} Heb: {\large\H שיבול} shi-bol \textbf{\textbackslash{}} {\large\H שיבולת} {[}X{]} Def: Grains grown in fields watered by the flooding of the river. To gather and bind into a sheaf. Also, meaning a flood that gives water to the soil for growing crops. \{Strong's: 5451, 7641\}\hfill{}\\

\textbf{SHEEP} Heb: {\large\H כשב} ke-sev \textbf{\textbackslash{}} {\large\H כסבה} kis-vah Def: A mammal related to the goat and domesticated for its milk, flesh and wool. \{Strong's: 3532, 3535, 3775\}\hfill{}\\

\textbf{SHEEP.PEN} Heb: {\large\H בוצרה} {[}X{]} Def: A walled place of protection. \{Strong's: n/a\}\hfill{}\\

\textbf{SHEET} Heb: {\large\H רקיע} ra-qi-a Def: A broad piece of cloth or metal. As hammered out flat. \{Strong's: 7549\}\hfill{}\\

\textbf{SHELAK} Heb: {\large\H שלך} {[}X{]} Def: An unknown bird. \{Strong's: 7994\}\hfill{}\\

\textbf{SHEPHERD.STAFF} Heb: {\large\H לם} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{SHEQEL} Heb: {\large\H שקל} she-qel Def: A chief Hebrew weight standard of measurement. \{Strong's: 8255, 8625\}\hfill{}\\

\textbf{SHIELD} Heb: {\large\H מגן} {[}X{]} Def: A broad piece of defensive armor carried on the arm. A protective structure. Wall of protection. \{Strong's: 4043\}\hfill{}\\

\textbf{SHINE} Heb: {\large\H מהלל} {[}X{]} Def: {[}X{]} \{Strong's: 4110\}\hfill{}\\

\textbf{SHINE (Verb)} Heb: {\large\H הלל} h.l.l Def: To emit rays of light. Shine brightly. To shine or cause another to shine through one’s actions or words. The piel (intensive) form means ``commend.'' \{Strong's: 1984\}\hfill{}\\

\textbf{SHINING} Heb: {\large\H הילול} {[}X{]} Def: {[}X{]} \{Strong's: 1974\}\hfill{}\\

\textbf{SHIP} Heb: {\large\H אניה} a-ni-yah Def: A large sea-going vessel. As searching through the sea for a distant shore. \{Strong's: 591\}\hfill{}\\

\textbf{SHORE} Heb: {\large\H חוף} hhoph Def: The land bordering a body of water. A place covered. \{Strong's: 2348\}\hfill{}\\

\textbf{SHORT} Heb: {\large\H כיברה} kiv-rah Def: Having little length. A brief distance. \{Strong's: 3530\}\hfill{}\\

\textbf{SHORTNESS} Heb: {\large\H קוצר} qo-tser Def: Short in patience. \{Strong's: 7115\}\hfill{}\\

\textbf{SHOULDER} Heb: {\large\H שכם} she-khem Def: Capacity for bearing a task or blame. The shoulders as the place where loads are placed. \{Strong's: 7926\}\hfill{}\\

\textbf{SHOULDER.PIECE} Heb: {\large\H כתף} ka-teyph Def: The part of an object that acts like a shoulder. \{Strong's: 3802\}\hfill{}\\

\textbf{SHOUT} Heb: {\large\H תרועה} {[}X{]} Def: A great shout of alarm of war or for rejoicing. \{Strong's: 8643\}\hfill{}\\

\textbf{SHOUT (Verb)} Heb: {\large\H רוע} r.w.ah Def: To shout an alarm of war or for great rejoicing. \{Strong's: 7321\}\hfill{}\\

\textbf{SHOUT.ALOUD (Verb)} Heb: {\large\H רנן} r.n.n Def: To cry out loudly in triumph or joy. \{Strong's: 7442, 7444\}\hfill{}\\

\textbf{SHOUTING} Heb: {\large\H אוהד} o-had Def: Raising of the voice to show authority, anger or gladness. \{Strong's: n/a\}\hfill{}\\

\textbf{SHOUTING.OUT} Heb: {\large\H שוע} {[}X{]} Def: {[}X{]} \{Strong's: 7769, 7771, 7773\}\hfill{}\\

\textbf{SHOVEL} Heb: {\large\H יע} ya Def: A flat tray attached to a handle for scooping up hot coals. \{Strong's: 3257\}\hfill{}\\

\textbf{SHOW.PITY (Verb)} Heb: {\large\H חמל} hh.m.l Def: To have compassion; to sympathize. \{Strong's: 2550\}\hfill{}\\

\textbf{SHOWERS} Heb: {\large\H רביב} {[}X{]} Def: {[}X{]} \{Strong's: 7241\}\hfill{}\\

\textbf{SHRINK.BACK (Verb)} Heb: {\large\H זחל} z.hh.l Def: To shrink in fear or timidness. \{Strong's: 1763, 2119\}\hfill{}\\

\textbf{SHRUB} Heb: {\large\H סיך} si-ahh Def: A low-growing, usually severally stemmed bush or woody plant, as used for making booths. \{Strong's: 7880\}\hfill{}\\

\textbf{SHUT (Verb)} Heb: {\large\H סגר} s.g.r Def: To close or block an opening. \{Strong's: 5462, 5463, 5534\}\hfill{}\\

\textbf{SHUT.UP (Verb)} Heb: {\large\H סתם} s.t.m Def: To stop by halting or closing. \{Strong's: 5640\}\hfill{}\\

\textbf{SICK} Heb: {\large\H תחלוא} {[}X{]} Def: {[}X{]} \{Strong's: 8463\}\hfill{}\\

\textbf{SICKENED} Heb: {\large\H מחלת} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{SICKLE} Heb: {\large\H חרמש} {[}X{]} Def: {[}X{]} \{Strong's: 2770\}\hfill{}\\

\textbf{SICKNESS} Heb: {\large\H מחלה} ma-hha-leh \textbf{\textbackslash{}} {\large\H מחלה} ma-hha-lah Def: A physical or emotional illness. Weakened. \{Strong's: 4245\}\hfill{}\\

\textbf{SIDE} Heb: {\large\H צד} tsad Def: An area next to something. \{Strong's: 6654, 6655\}\hfill{}\\

\textbf{SIGH (Verb)} Heb: {\large\H אנח} a.n.hh Def: Exhaling of breath as in relief. To breath out as a desire for rest. \{Strong's: 584\}\hfill{}\\

\textbf{SIGHTLESSNESS} Heb: {\large\H סגור} sa-gur Def: Sightless; unquestioning, as having no regard to rational discrimination, guidance or restriction. As a shutting of the eyes. \{Strong's: 5575\}\hfill{}\\

\textbf{SIGN} Heb: {\large\H אות} ot Def: The motion, gesture, or mark representing an agreement between two parties. A wondrous or miraculous sign. \{Strong's: 226, 852\}\hfill{}\\

\textbf{SILENCE (Verb)} Heb: {\large\H הסה} h.s.h Def: To keep silent by holding the tongue, silent and still. \{Strong's: 2013\}\hfill{}\\

\textbf{SILENCED} Heb: {\large\H דומה} {[}X{]} Def: {[}X{]} \{Strong's: 1745, 1822\}\hfill{}\\

\textbf{SILENT} Heb: {\large\H חרש} hhey-reysh Def: A state of speechlessness or extreme quiet. \{Strong's: 2795\}\hfill{}\\

\textbf{SILVER} Heb: {\large\H כסף} ke-seph Def: A soft metal capable of a high degree of polish used for coinage, implements and ornaments. A desired and precious metal. \{Strong's: 3701, 3702\}\hfill{}\\

\textbf{SIMMER (Verb)} Heb: {\large\H זוד} z.w.d Def: To cook a soup over a fire. To be heated with pride or anger. \{Strong's: 2102, 2103\}\hfill{}\\

\textbf{SINCE} Heb: {\large\H עקב} ey-qev Def: From a time in the past until now, in the sense of being on the heel of something else. \{Strong's: 6118\}\hfill{}\\

\textbf{SINEW} Heb: {\large\H גיד} gid Def: A tendon. \{Strong's: 1517\}\hfill{}\\

\textbf{SING (Verb)} Heb: {\large\H שיר} sh.y.r Def: To express one's voice in a melody or to music. \{Strong's: 7891\}\hfill{}\\

\textbf{SINGE.SCAR} Heb: {\large\H מכוה} {[}X{]} Def: {[}X{]} \{Strong's: 4348\}\hfill{}\\

\textbf{SINGEING} Heb: {\large\H כויה} ke-wi-yah Def: A burning of the skin or hair. \{Strong's: 3555\}\hfill{}\\

\textbf{SINGER} Heb: {\large\H זמר} {[}X{]} Def: As plucked on musical instruments. \{Strong's: 2170, 2171\}\hfill{}\\

\textbf{SINK (Verb)} Heb: {\large\H שקע} sh.q.ah Def: To sink down. \{Strong's: 8257\}\hfill{}\\

\textbf{SINK.DOWN (Verb)} Heb: {\large\H רפה} r.p.h Def: To drop down; to be slack or idle due to weakness, illness or laziness. The niphal (passive) form means ``lazy.'' \{Strong's: 7503\}\hfill{}\\

\textbf{SINKING} Heb: {\large\H שוח} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{SISTER} Heb: {\large\H אחות} a-hhot Def: A female who has the same parents as another or shares one parent with another. \{Strong's: 269\}\hfill{}\\

\textbf{SISTER.IN.LAW} Heb: {\large\H יבמת} {[}X{]} Def: {[}X{]} \{Strong's: 2994\}\hfill{}\\

\textbf{SIT.DOWN (Verb)} Heb: {\large\H תכה} t.k.h Def: Meaning dubious. \{Strong's: 8497\}\hfill{}\\

\textbf{SITE} Heb: {\large\H אתר} {[}X{]} Def: {[}X{]} \{Strong's: 870, 871\}\hfill{}\\

\textbf{SIX} Heb: {\large\H ששה} shi-shah \textbf{\textbackslash{}} {\large\H שש} sheysh Def: A cardinal number. \{Strong's: 8337, 8346, 8353, 8361\}\hfill{}\\

\textbf{SIXTH} Heb: {\large\H שישי} shi-shi Def: An ordinal number. \{Strong's: 8345\}\hfill{}\\

\textbf{SKILL} Heb: {\large\H חכמה} hhakh-mah Def: The ability to decide or discern between good and bad, right and wrong. \{Strong's: 2451, 2452\}\hfill{}\\

\textbf{SKILLED.ONE} Heb: {\large\H חכם} hha-kham Def: A person characterized by a deep understanding of a craft. \{Strong's: 2450\}\hfill{}\\

\textbf{SKILLET} Heb: {\large\H פרור} {[}X{]} Def: A flat surface for preparing foods. \{Strong's: 6517\}\hfill{}\\

\textbf{SKIN} Heb: {\large\H עור} or Def: The integument covering men or animals, as well as leather made from animal skins. The husk of a seed. \{Strong's: 5784, 5785\}\hfill{}\\

\textbf{SKIN.BAG} Heb: {\large\H חמת} hhey-met Def: Used for holding cheese, water or any other liquid. \{Strong's: 2573\}\hfill{}\\

\textbf{SKIN.SORE} Heb: {\large\H ילפת} {[}X{]} Def: {[}X{]} \{Strong's: 3217\}\hfill{}\\

\textbf{SKIP (Verb)} Heb: {\large\H סוס} s.w.s Def: To move with quick steps in joy. \{Strong's: 7797\}\hfill{}\\

\textbf{SKULL} Heb: {\large\H גולגולת} gul-go-let Def: The bones of the head. The roundness of the head or skull. Also a census by the counting of heads. \{Strong's: 1538\}\hfill{}\\

\textbf{SKY} Heb: {\large\H שמה} sha-mah Def: The upper atmosphere that constitutes an apparent great vault or arch over the earth. Place of the winds. \{Strong's: 8064, 8065\}\hfill{}\\

\textbf{SLAB} Heb: {\large\H לוח} lu-ahh Def: A wood or stone tablet or plank. Often used for writing. \{Strong's: 3871\}\hfill{}\\

\textbf{SLANDER} Heb: {\large\H דיבה} di-bah Def: Speaking evil of another (usually done quietly). \{Strong's: 1681\}\hfill{}\\

\textbf{SLAUGHTERING} Heb: {\large\H טבח} te-vahh Def: The act of slaughtering, the meat of the slaughter or one who slaughters. Also an executioner as one who slaughters. \{Strong's: 2874, 2876, 2877\}\hfill{}\\

\textbf{SLAY (Verb)} Heb: {\large\H שחט} sh.hh.t Def: To strike, beat or kill. \{Strong's: 7819, 7820\}\hfill{}\\

\textbf{SLEEP (Verb)} Heb: {\large\H ישן} y.sh.n Def: To rest in a state of suspended consciousness. \{Strong's: 3462\}\hfill{}\\

\textbf{SLEEPING} Heb: {\large\H ישן} {[}X{]} Def: {[}X{]} \{Strong's: 3463, 3465\}\hfill{}\\

\textbf{SLICE (Verb)} Heb: {\large\H סרט} s.r.t Def: {[}X{]} \{Strong's: 8295\}\hfill{}\\

\textbf{SLICE.OFF (Verb)} Heb: {\large\H קצץ} q.ts.ts Def: To make an end of something by cutting it off. \{Strong's: 7082, 7112, 7113\}\hfill{}\\

\textbf{SLICING} Heb: {\large\H סרט} {[}X{]} \textbf{\textbackslash{}} {\large\H סרטת} {[}X{]} Def: {[}X{]} \{Strong's: 8296\}\hfill{}\\

\textbf{SLICK} Heb: {\large\H חלק} hhey-leq Def: The portions dispersed out. \{Strong's: 2509\}\hfill{}\\

\textbf{SLING} Heb: {\large\H קלע} qe-la Def: A weapon made of a pouch that is attached to two long cords and used for throwing stones. Also something that hangs like a sling. \{Strong's: 7050, 7051\}\hfill{}\\

\textbf{SLIP.AWAY (Verb)} Heb: {\large\H מלט} m.l.t Def: To get away through deliverance or escape. \{Strong's: 4422\}\hfill{}\\

\textbf{SLOW} Heb: {\large\H ארך} a-reykh Def: Capable of calmly awaiting an outcome or result. \{Strong's: 750\}\hfill{}\\

\textbf{SMACK (Verb)} Heb: {\large\H צור} ts.w.r Def: To strike or push as an attack. \{Strong's: 2115, 6696\}\hfill{}\\

\textbf{SMACKED} Heb: {\large\H מצור} {[}X{]} Def: A pressing into a city for conquering it. \{Strong's: 4205, 4692\}\hfill{}\\

\textbf{SMALL} Heb: {\large\H קטן} qa-tan Def: Someone or something that is not very large in size, importance, age or significance. \{Strong's: 6996\}\hfill{}\\

\textbf{SMALL.AMOUNT} Heb: {\large\H מעט} me-at Def: Something that is few or small in size or amount. \{Strong's: 4592\}\hfill{}\\

\textbf{SMASH (Verb)} Heb: {\large\H כתת} k.t.t Def: {[}X{]} \{Strong's: 3807\}\hfill{}\\

\textbf{SMASHED} Heb: {\large\H כתית} ka-tit Def: The pressing of the olive to extract the oil. \{Strong's: 3795\}\hfill{}\\

\textbf{SMEAR (Verb)} Heb: {\large\H משח} m.sh.hh Def: To overspread with oil for medical treatment or as a sign of authority. \{Strong's: 4886\}\hfill{}\\

\textbf{SMEARED} Heb: {\large\H משיח} {[}X{]} Def: Someone or something that has been smeared or annointed with an oil as a medication or a sign of taking an office. An anointed one; a messiah. \{Strong's: 4899\}\hfill{}\\

\textbf{SMELL (Verb)} Heb: {\large\H רוח} r.w.hh Def: The odor or scent of a thing. As carried on the wind. To be ``refreshed'', as when taking in a deep breath. \{Strong's: 7304, 7306\}\hfill{}\\

\textbf{SMITE (Verb)} Heb: {\large\H נגף} n.g.p Def: To deliver a hit with the intent to harm; to bring a plague in the sense of a striking. \{Strong's: 5062\}\hfill{}\\

\textbf{SMOKE} Heb: {\large\H עשן} a-sheyn Def: The gaseous products of combustion. \{Strong's: 6226, 6227\}\hfill{}\\

\textbf{SMOKE (Verb)} Heb: {\large\H עשן} ah.sh.n Def: To emit a gaseous cloud when burning. \{Strong's: 6225\}\hfill{}\\

\textbf{SMOKING} Heb: {\large\H קיטור} qi-tor Def: To burn sluggishly without flame. The smoke of the burning incense or fat. \{Strong's: 7008\}\hfill{}\\

\textbf{SMOLDER (Verb)} Heb: {\large\H יקד} y.q.d Def: {[}X{]} \{Strong's: 3344, 3345\}\hfill{}\\

\textbf{SMOOTH} Heb: {\large\H חלקה} hhal-qah Def: Having an even, continuous surface. This word can also mean ``flattery'' in the sense of being slippery. \{Strong's: 2513, 2514\}\hfill{}\\

\textbf{SMOULDERING} Heb: {\large\H מוקד} mo-qeyd \textbf{\textbackslash{}} {\large\H מוקדה} mo-qey-dah Def: {[}X{]} \{Strong's: 4168, 4169\}\hfill{}\\

\textbf{SNAKE} Heb: {\large\H מוף} {[}X{]} Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{SNAP (Verb)} Heb: {\large\H קצף} q.ts.p Def: To make a sudden closing; to break suddenly with a sharp sound; to splinter a piece of wood; to lash out in anger as a splintering. \{Strong's: 7107, 7108\}\hfill{}\\

\textbf{SNARE} Heb: {\large\H מוקש} mo-qeysh Def: A trap laid with bait to capture an animal or person. An entrapment. \{Strong's: 4170\}\hfill{}\\

\textbf{SNARE (Verb)} Heb: {\large\H יקש} y.q.sh Def: {[}X{]} \{Strong's: 3369\}\hfill{}\\

\textbf{SNARER} Heb: {\large\H יקשן} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{SNIP.OFF(V) (Verb)} Heb: {\large\H מול} m.w.l Def: To cut off the front part (Often used in the context of circumcision). \{Strong's: 4135\}\hfill{}\\

\textbf{SNOOZE} Heb: {\large\H שנאה} she-nah Def: To take a nap. \{Strong's: 8139, 8142\}\hfill{}\\

\textbf{SNORT (Verb)} Heb: {\large\H אנף} a.n.p Def: A heavy breathing out of anger. \{Strong's: 599\}\hfill{}\\

\textbf{SNORTING} Heb: {\large\H נחור} na-hhor Def: A forcing of the breath violently through the nostrils with a loud, harsh sound. \{Strong's: n/a\}\hfill{}\\

\textbf{SNOW} Heb: {\large\H שלג} she-leg Def: A precipitation of water in the form of ice crystals. \{Strong's: 7950, 8517\}\hfill{}\\

\textbf{SNOW.MOUNTAIN} Heb: {\large\H סניר} se-nir Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{SO} Heb: {\large\H כן} keyn Def: In a manner or way indicated or suggested. What comes before or after another event. \{Strong's: 3651, 3652\}\hfill{}\\

\textbf{SO.BE.IT} Heb: {\large\H אמן} {[}X{]} Def: An affirmation of firmness and support. \{Strong's: 543\}\hfill{}\\

\textbf{SOFT} Heb: {\large\H ענוג} {[}X{]} \textbf{\textbackslash{}} {\large\H ענוגה} {[}X{]} Def: {[}X{]} \{Strong's: 6028\}\hfill{}\\

\textbf{SOFT (Verb)} Heb: {\large\H ענג} ah.n.g Def: To be delicate and pleasurable. \{Strong's: 6026\}\hfill{}\\

\textbf{SOFTLY} Heb: {\large\H אט} at Def: Free from harshness, sternness, or violence. To act softly. A charmer. \{Strong's: 328\}\hfill{}\\

\textbf{SOJOURN (Verb)} Heb: {\large\H גור} g.w.r Def: To stay as a temporary resident. Travel in a strange land. Also, the extended meaning of ``to be afraid'' of a stranger. \{Strong's: 1481\}\hfill{}\\

\textbf{SOLITARY} Heb: {\large\H יחיד} ya-hhid Def: Separated from the whole of the unit (see Psalm 68:7 {[}6{]}). \{Strong's: 3173\}\hfill{}\\

\textbf{SON} Heb: {\large\H בן} ben Def: A male offspring. This can be the son or a later male descendant of the father. One who continues the family line. \{Strong's: 1121, 1123, 1247, 1248\}\hfill{}\\

\textbf{SONG} Heb: {\large\H שיר} shir \textbf{\textbackslash{}} {\large\H שירה} shi-rah Def: The act or art of singing. \{Strong's: 7892\}\hfill{}\\

\textbf{SOOT} Heb: {\large\H פיח} pi-ahh Def: Residue left after burning. \{Strong's: 6368\}\hfill{}\\

\textbf{SORCERY (Verb)} Heb: {\large\H כשף} k.sh.p Def: To perform supernatural magic. \{Strong's: 3784\}\hfill{}\\

\textbf{SORROW} Heb: {\large\H יגון} ya-gon Def: Deep distress and regret. \{Strong's: 3015\}\hfill{}\\

\textbf{SORROW (Verb)} Heb: {\large\H דוב} d.w.b Def: One who moves slowly. \{Strong's: 1727\}\hfill{}\\

\textbf{SOUTH} Heb: {\large\H דרום} {[}X{]} Def: {[}X{]} \{Strong's: 1864\}\hfill{}\\

\textbf{SOUTHERN.REGION} Heb: {\large\H קתרוס} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{SOW (Verb)} Heb: {\large\H זרע} z.r.ah Def: To spread seeds on the ground; to plant a crop. \{Strong's: 2232\}\hfill{}\\

\textbf{SOWN} Heb: {\large\H זרוע} {[}X{]} Def: {[}X{]} \{Strong's: 2221\}\hfill{}\\

\textbf{SPARE (Verb)} Heb: {\large\H חוס} hh.w.s Def: To forbear to destroy, punish, or harm; give asylum. Give refuge to another. \{Strong's: 2347\}\hfill{}\\

\textbf{SPARK} Heb: {\large\H רשף} {[}X{]} Def: The spark of a fire or thunderbolt. Also an arrow as a flashing thunderbolt. \{Strong's: 7565\}\hfill{}\\

\textbf{SPATTER (Verb)} Heb: {\large\H נזה} n.z.h Def: To ceremonially sprinkle water or oil on something that is being dedicated. \{Strong's: 5137\}\hfill{}\\

\textbf{SPEAK (Verb)} Heb: {\large\H דבר} d.b.r Def: A careful arrangement of words or commands said orally. \{Strong's: 1696\}\hfill{}\\

\textbf{SPEAR} Heb: {\large\H רמח} {[}X{]} Def: {[}X{]} \{Strong's: 7420\}\hfill{}\\

\textbf{SPEARHEAD} Heb: {\large\H קין} {[}X{]} Def: Like the bill of bird used to defend the nest. \{Strong's: 7013\}\hfill{}\\

\textbf{SPECIAL} Heb: {\large\H קודש} qo-desh Def: A person, item, time or place that has the quality of being unique; Separated from the rest for a special purpose. \{Strong's: 6944\}\hfill{}\\

\textbf{SPECKLED} Heb: {\large\H נקוד} na-qod Def: The spots marking sheep and goats. \{Strong's: 5348\}\hfill{}\\

\textbf{SPEECH} Heb: {\large\H אמלה} am-lah Def: The chain of words when speaking. \{Strong's: 565\}\hfill{}\\

\textbf{SPELT} Heb: {\large\H כוסמת} ku-se-met Def: A wheat like grain with what looks like trimmed hair. \{Strong's: 3698\}\hfill{}\\

\textbf{SPICE} Heb: {\large\H נכואת} ne-khot Def: Various aromatic vegetable products used to season or flavor foods. \{Strong's: 5219\}\hfill{}\\

\textbf{SPICE.MIXTURE} Heb: {\large\H רוקח} ro-qahh Def: A mixture of spices for an ointment or perfume. \{Strong's: 7545\}\hfill{}\\

\textbf{SPICE.PLACE} Heb: {\large\H מבסם} {[}X{]} Def: A sweet smelling spice. \{Strong's: n/a\}\hfill{}\\

\textbf{SPIN (Verb)} Heb: {\large\H טוה} t.w.h Def: To revolve in a circle without moving forward. \{Strong's: 2901\}\hfill{}\\

\textbf{SPINE} Heb: {\large\H עצה} {[}X{]} Def: The tree of the body which provides its uprightness. \{Strong's: 6096\}\hfill{}\\

\textbf{SPIT (Verb)} Heb: {\large\H ירק} y.r.q Def: {[}X{]} \{Strong's: 3417\}\hfill{}\\

\textbf{SPIT.UPON (Verb)} Heb: {\large\H ארר} a.r.r Def: To eject saliva, usually on another in spite or disrespect. \{Strong's: 779\}\hfill{}\\

\textbf{SPITTING} Heb: {\large\H מאררה} {[}X{]} Def: {[}X{]} \{Strong's: 3994\}\hfill{}\\

\textbf{SPLASHED} Heb: {\large\H צבעון} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{SPLENDID} Heb: {\large\H פועה} pu-ah Def: Someone or something that is exceptional. A wonder. \{Strong's: n/a\}\hfill{}\\

\textbf{SPLENDOR} Heb: {\large\H הוד} {[}X{]} Def: A prominent beauty or work as shouting out. \{Strong's: 1935\}\hfill{}\\

\textbf{SPLINTER} Heb: {\large\H קצף} {[}X{]} Def: The sharp flying objects from a snapped piece of wood. Also wrath as flying splinters. \{Strong's: 7109, 7110\}\hfill{}\\

\textbf{SPLIT (Verb)} Heb: {\large\H פלג} p.l.g Def: To divide lengthwise. \{Strong's: 6385, 6386\}\hfill{}\\

\textbf{SPLIT.HOOF} Heb: {\large\H פרסה} par-sah Def: The hard covering of a clean animals foot that is divided into two parts. \{Strong's: 6541\}\hfill{}\\

\textbf{SPLITTING} Heb: {\large\H שסע} {[}X{]} Def: {[}X{]} \{Strong's: 8157\}\hfill{}\\

\textbf{SPOIL} Heb: {\large\H שלל} sha-lal Def: Plunder taken from an enemy in war or robbery. To impair the quality or effect of. \{Strong's: 7998\}\hfill{}\\

\textbf{SPOILS} Heb: {\large\H בז} {[}X{]} Def: Something that is seized by violence and robbery; prey; booty. \{Strong's: 897, 957\}\hfill{}\\

\textbf{SPOKEN} Heb: {\large\H ריפת} {[}X{]} Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{SPOT} Heb: {\large\H שקערורה} {[}X{]} Def: {[}X{]} \{Strong's: 8258\}\hfill{}\\

\textbf{SPOT (Verb)} Heb: {\large\H טלא} t.l.a Def: A small area visibly different from the surrounding area. To be covered with spots. \{Strong's: 2921\}\hfill{}\\

\textbf{SPOTTED} Heb: {\large\H ברוד} ba-rod Def: An animal with white spots which appear as hailstones. \{Strong's: 1261\}\hfill{}\\

\textbf{SPREAD (Verb)} Heb: {\large\H שטח} sh.t.hh Def: {[}X{]} \{Strong's: 7849\}\hfill{}\\

\textbf{SPREAD.ACROSS (Verb)} Heb: {\large\H פשה} p.sh.h Def: To spread out excessively. \{Strong's: 6581\}\hfill{}\\

\textbf{SPREAD.OUT (Verb)} Heb: {\large\H פרש} p.r.sh Def: To expand beyond a starting point; to be easily and plainly understood in the sense of being spread out to see. \{Strong's: 6566, 6567, 6568\}\hfill{}\\

\textbf{SPREAD.WIDE (Verb)} Heb: {\large\H פתה} p.t.h Def: To lay out in a large area. The piel (intensive) form means ``persuade.'' \{Strong's: 6601\}\hfill{}\\

\textbf{SPRING} Heb: {\large\H מעין} ma-yan Def: A source of water issuing from the ground. As the eye of the ground. \{Strong's: 4599\}\hfill{}\\

\textbf{SPRING.UP (Verb)} Heb: {\large\H צמח} ts.m.hh Def: To grow up as a plant. \{Strong's: 6779\}\hfill{}\\

\textbf{SPRINKLE (Verb)} Heb: {\large\H זרק} z.r.q Def: To drip a liquid, usually water or blood. \{Strong's: 2236\}\hfill{}\\

\textbf{SPRINKLED} Heb: {\large\H כנז} {[}X{]} Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{SPRINKLING.BASIN} Heb: {\large\H מזרק} miz-raq Def: A container of liquid that is used to drip the liquid. \{Strong's: 4219\}\hfill{}\\

\textbf{SPROUT (Verb)} Heb: {\large\H דשא} d.sh.a Def: To send up or out new growth, as of a plant. Sprout green sprouts. \{Strong's: 1876\}\hfill{}\\

\textbf{SPROUT.UP} Heb: {\large\H נפג} ne-pheg Def: A word of unknown meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{SQUEEZE (Verb)} Heb: {\large\H לחץ} l.hh.ts Def: To exert pressure either physically or emotionally. \{Strong's: 3905\}\hfill{}\\

\textbf{SQUEEZING} Heb: {\large\H לחץ} la-hhats Def: Pressure being exerted, either physically or emotionally. \{Strong's: 3906\}\hfill{}\\

\textbf{STACK} Heb: {\large\H גדיש} ga-dish Def: A pile of grain or dirt. \{Strong's: 1430\}\hfill{}\\

\textbf{STAFF} Heb: {\large\H שבט} she-vet Def: A walking stick made from the branch of a tree. Also, a tribe as a branch of the family. \{Strong's: 7625, 7626\}\hfill{}\\

\textbf{STAGGER (Verb)} Heb: {\large\H נוע} n.w.ah Def: To reel from side to side; to wag or shake back and forth or up and down; to wander as staggering about. \{Strong's: 5128\}\hfill{}\\

\textbf{STAGGERING} Heb: {\large\H נועה} no-ah Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{STAIR.STEP} Heb: {\large\H מעלה} ma-a-lah Def: A straight or stepped incline for ascending and descending. \{Strong's: 4609\}\hfill{}\\

\textbf{STALK} Heb: {\large\H קנה} qa-neh Def: The main stem and support of a plant. \{Strong's: 7070\}\hfill{}\\

\textbf{STALKER} Heb: {\large\H קנז} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{STAMPED.DOWN} Heb: {\large\H יהץ} ya-hats Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{STAND} Heb: {\large\H תקומה} {[}X{]} Def: {[}X{]} \{Strong's: 8617\}\hfill{}\\

\textbf{STAND (Verb)} Heb: {\large\H עמד} ah.m.d Def: To rise, raise or set in a place. \{Strong's: 5975, 5976\}\hfill{}\\

\textbf{STAND.UP (Verb)} Heb: {\large\H נצב} n.ts.b Def: To be vertical in position; to stand tall and erect; to set in place. \{Strong's: 5324\}\hfill{}\\

\textbf{STANDARD} Heb: {\large\H נס} neys Def: A flag that hangs from a pole with the insignia of a tribe or army. Also, a sail. \{Strong's: 5251\}\hfill{}\\

\textbf{STAR} Heb: {\large\H כוכב} ko-khav Def: A natural luminous body visible in the night sky. \{Strong's: 3556\}\hfill{}\\

\textbf{STARE (Verb)} Heb: {\large\H נבט} n.b.t Def: To carefully look; to make a close inspection. \{Strong's: 5027\}\hfill{}\\

\textbf{STATEMENT} Heb: {\large\H אמל} a-mal Def: A single declaration or remark. \{Strong's: 561\}\hfill{}\\

\textbf{STATION (Verb)} Heb: {\large\H יצב} y.ts.b Def: To stand firm and in place. \{Strong's: 3320, 3321\}\hfill{}\\

\textbf{STATIONED} Heb: {\large\H תרח} {[}X{]} Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{STAVE} Heb: {\large\H משענה} mish-ey-nah Def: A staff made from a sapling or branch. A support for walking. \{Strong's: 4938\}\hfill{}\\

\textbf{STAY (Verb)} Heb: {\large\H יחר} y.hh.r Def: To remain behind; to wait in anticipation. \{Strong's: 3176, 3186\}\hfill{}\\

\textbf{STAY.THE.NIGHT (Verb)} Heb: {\large\H לון} l.w.n Def: To remain or stay through the night. \{Strong's: 3885\}\hfill{}\\

\textbf{STEADFAST} Heb: {\large\H צדק} {[}X{]} Def: The following of the established path or course of action. \{Strong's: 6664\}\hfill{}\\

\textbf{STEADFAST.ONE} Heb: {\large\H צדיק} tsa-diq Def: One that makes or sets right. Conforming to fact, standard or truth. \{Strong's: 6662\}\hfill{}\\

\textbf{STEADFASTNESS} Heb: {\large\H צדקה} tse-de-qah Def: Conformity to fact, standard or truth. \{Strong's: 6666\}\hfill{}\\

\textbf{STEAL (Verb)} Heb: {\large\H גנב} g.n.b Def: To wrongfully take the property of another; rob. \{Strong's: 1589\}\hfill{}\\

\textbf{STEEP.VALLEY} Heb: {\large\H גיא} gai Def: An elongated depression between uplands, hills, or mountains. \{Strong's: 1516\}\hfill{}\\

\textbf{STEP} Heb: {\large\H מדרך} {[}X{]} Def: The distance between the feet of a step. \{Strong's: 4096\}\hfill{}\\

\textbf{STEP.UPON (Verb)} Heb: {\large\H דרך} d.r.k Def: To take a step. A journey as a treading. The stringing of a bow is a treading as the foot is stepped over the bow and using the leg to bend it. \{Strong's: 1869\}\hfill{}\\

\textbf{STERILE} Heb: {\large\H עקר} a-qar Def: Failing to produce or incapable of producing offspring, fruit or spores. Being without children in the sense of being plucked of fruit. \{Strong's: 6135\}\hfill{}\\

\textbf{STEW} Heb: {\large\H נזיד} na-zid Def: Fish or meat cooked with vegetables. To become agitated or worried. \{Strong's: 5138\}\hfill{}\\

\textbf{STICK} Heb: {\large\H בד} bad Def: A branch or staff as separated from the tree. Linen cloth, from its stiff and divided fibers. Often used in the idiom ``to his/her own stick'' meaning alone or self. \{Strong's: 905, 906\}\hfill{}\\

\textbf{STICKERBUSH} Heb: {\large\H סך} {[}X{]} Def: {[}X{]} \{Strong's: 5519, 7899, 7900\}\hfill{}\\

\textbf{STINK (Verb)} Heb: {\large\H באש} b.a.sh Def: To emit a bad odor or be loathsome. \{Strong's: 887, 888\}\hfill{}\\

\textbf{STIR (Verb)} Heb: {\large\H בהל} b.h.l Def: To disturb the quiet of; agitate. \{Strong's: 926, 927\}\hfill{}\\

\textbf{STIR.UP (Verb)} Heb: {\large\H עור} ah.w.r Def: To shake to awaken. \{Strong's: 5782, 5783\}\hfill{}\\

\textbf{STOMACH} Heb: {\large\H קבה} {[}X{]} Def: As a cavity. \{Strong's: 6896\}\hfill{}\\

\textbf{STONE} Heb: {\large\H אבן} e-ven Def: A piece of rock, often in the context of building material. \{Strong's: 68, 69\}\hfill{}\\

\textbf{STONE (Verb)} Heb: {\large\H סקל} s.q.l Def: To gather stones for stoning. The act of throwing rocks with the intention of killing. To remove stones from a road or field. \{Strong's: 5619\}\hfill{}\\

\textbf{STONE.STOOL} Heb: {\large\H אובן} o-ven Def: A platform made of stone and used by a potter or a midwife. \{Strong's: 70\}\hfill{}\\

\textbf{STOOL} Heb: {\large\H כס} keys Def: A seat or throne. \{Strong's: 3676\}\hfill{}\\

\textbf{STOOP (Verb)} Heb: {\large\H כרע} k.r.ah Def: To bend the body forward and downward while bending the knees; to stoop or crouch down by bending or getting on the knees. \{Strong's: 3766\}\hfill{}\\

\textbf{STOP (Verb)} Heb: {\large\H עצר} ah.ts.r Def: To cause to cease; to stop from occurring in the sense of halting, shutting or restraining. \{Strong's: 6113\}\hfill{}\\

\textbf{STORE (Verb)} Heb: {\large\H כמס} k.m.s Def: {[}X{]} \{Strong's: 3647\}\hfill{}\\

\textbf{STORE.UP (Verb)} Heb: {\large\H אצר} a.ts.r Def: To store up something in a safe place as if bound up. \{Strong's: 686\}\hfill{}\\

\textbf{STOREHOUSE} Heb: {\large\H מסכנה} mis-ke-nah Def: Places for storing foods or other items for future benefit. \{Strong's: 4543\}\hfill{}\\

\textbf{STORM (Verb)} Heb: {\large\H סער} s.ah.r Def: To be afraid as from a storm. \{Strong's: 5590, 8175\}\hfill{}\\

\textbf{STRAIGHT} Heb: {\large\H ישר} ya-shar Def: Without a bend, angle, or curve. A straight line, path or thought. The cord of the bow as stretched taught. \{Strong's: 3477\}\hfill{}\\

\textbf{STRAIGHT.ONE} Heb: {\large\H ישורון} ye-shu-run Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{STRAIGHT.TRUMPET} Heb: {\large\H חצוצרה} {[}X{]} Def: A loud wind instrument. \{Strong's: 2689\}\hfill{}\\

\textbf{STRAIGHTNESS} Heb: {\large\H יושר} {[}X{]} Def: {[}X{]} \{Strong's: 3476\}\hfill{}\\

\textbf{STRAIT} Heb: {\large\H מצר} mey-tsar Def: A narrow tight place or situation. \{Strong's: 4712\}\hfill{}\\

\textbf{STRANGER} Heb: {\large\H גר} ger Def: A foreigner that permanently or temporarily resides with a native. A person or thing unknown or with whom one is unacquainted. \{Strong's: 1616\}\hfill{}\\

\textbf{STRAP} Heb: {\large\H מוסר} mu-sar \textbf{\textbackslash{}} {\large\H מוסרה} mo-sey-rah Def: Knowledge, information or example imparted to provide guidance, correction and discipline. \{Strong's: 4561, 4147, 4148\}\hfill{}\\

\textbf{STRAW} Heb: {\large\H תבן} te-ven Def: Stalks of grain after threshing; dry, stalky plant residue. When more permanent structures were built, they were constructed of stones and bricks made of clay and straw; replacing the tent panels as the main component of construction for dwellings. \{Strong's: 8401\}\hfill{}\\

\textbf{STREAM} Heb: {\large\H יאור} ye-or Def: A body of running water; any body of flowing water. \{Strong's: 2975\}\hfill{}\\

\textbf{STREET} Heb: {\large\H רחוב} re-hhov Def: A thoroughfare, especially in a city, town or village. \{Strong's: 7339\}\hfill{}\\

\textbf{STRENGTH} Heb: {\large\H כוח} ko-ahh Def: The quality or state of being strong. \{Strong's: 3581\}\hfill{}\\

\textbf{STRESS} Heb: {\large\H מצוך} {[}X{]} Def: Something that causes oppression. \{Strong's: 4689\}\hfill{}\\

\textbf{STRETCH.OUT (Verb)} Heb: {\large\H רבץ} r.b.ts Def: To lie or stretch out as to rest; to crouch down to hide for an ambush. \{Strong's: 7257\}\hfill{}\\

\textbf{STRIFE} Heb: {\large\H עסק} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{STRIKE.THROUGH (Verb)} Heb: {\large\H מחץ} m.hh.ts Def: {[}X{]} \{Strong's: 4272\}\hfill{}\\

\textbf{STRIKING} Heb: {\large\H נגף} ne-geph Def: The act of being hit. A plague as hitting the people. \{Strong's: 5063\}\hfill{}\\

\textbf{STRING} Heb: {\large\H מישר} mey-shar Def: A cord or rope, as straight. Also a straight line, path or thought. \{Strong's: 4339, 4340\}\hfill{}\\

\textbf{STRIP} Heb: {\large\H פצלה} pe-tsa-lah Def: To remove clothing, covering, or surface matter from. As peeled. \{Strong's: 6479\}\hfill{}\\

\textbf{STRIPED} Heb: {\large\H עקוד} a-qod Def: Having stripes or streaks. As appearing to be whipped with a cord. \{Strong's: 6124\}\hfill{}\\

\textbf{STRIPED.BRUISE} Heb: {\large\H חבורה} hha-bu-rah Def: Marks made by ropes binding the wrist or lashes with a rope. \{Strong's: 2250\}\hfill{}\\

\textbf{STRIVE (Verb)} Heb: {\large\H עסק} ah.s.q Def: A ground of dispute or complaint. A clash between sides. \{Strong's: 6229\}\hfill{}\\

\textbf{STRONG} Heb: {\large\H עז} az Def: Having or marked by great physical strength. \{Strong's: 5794\}\hfill{}\\

\textbf{STRONG.ONE} Heb: {\large\H עזן} a-zan Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{STRUGGLE (Verb)} Heb: {\large\H נצה} n.ts.h Def: The act of trying to achieve the goal, but with hindrances. \{Strong's: 5327\}\hfill{}\\

\textbf{STUBBLE} Heb: {\large\H קש} qash Def: What is left after the stalk has been removed. \{Strong's: 7179\}\hfill{}\\

\textbf{STUBBORNNESS} Heb: {\large\H קשי} {[}X{]} Def: As stiff. \{Strong's: 7190\}\hfill{}\\

\textbf{STUMBLING.BLOCK} Heb: {\large\H מכשול} {[}X{]} Def: Used to cause someone to stumble or topple down. \{Strong's: 4383\}\hfill{}\\

\textbf{SUBDUE (Verb)} Heb: {\large\H כבש} k.b.sh Def: To conquer and bring into subjection; bring under control. Place the foot on the land in the sense of subduing it. Also, to place one’s foot into another nation in the sense of subduing it. \{Strong's: 3533\}\hfill{}\\

\textbf{SUBDUER} Heb: {\large\H כמוש} {[}X{]} Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{SUBMERGE (Verb)} Heb: {\large\H טמן} t.m.n Def: To hide by burying or to cover. \{Strong's: 2934\}\hfill{}\\

\textbf{SUBMERSION} Heb: {\large\H עמורה} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{SUBSIDE (Verb)} Heb: {\large\H שכך} sh.k.k Def: Become quiet or less. To calm down or set down. \{Strong's: 7918\}\hfill{}\\

\textbf{SUBSTANCE} Heb: {\large\H יקום} ye-qum Def: A fundamental or characteristic part or quality. Any standing thing or person. \{Strong's: 3351\}\hfill{}\\

\textbf{SUBTLE} Heb: {\large\H ערום} a-rum Def: Difficult to understand or distinguish. In craftiness or prudence. \{Strong's: 6175\}\hfill{}\\

\textbf{SUBTLETY} Heb: {\large\H ערמה} ar-mah Def: Performance that calls no attention to its self. To act in craftiness or prudence. \{Strong's: 6193, 6195\}\hfill{}\\

\textbf{SUCKED.OUT} Heb: {\large\H מזה} {[}X{]} Def: {[}X{]} \{Strong's: 4198\}\hfill{}\\

\textbf{SUCKLE (Verb)} Heb: {\large\H ינק} y.n.q Def: To give milk to from the breast or udder. The hiphil (causative) form means ``nurse (verb).'' \{Strong's: 3243\}\hfill{}\\

\textbf{SUDDENLY} Heb: {\large\H פיתעום} {[}X{]} Def: As a wink of time. \{Strong's: 6597\}\hfill{}\\

\textbf{SUET} Heb: {\large\H פדר} {[}X{]} Def: {[}X{]} \{Strong's: 6309\}\hfill{}\\

\textbf{SUFFICIENT} Heb: {\large\H די} dai Def: An amount that is not lacking. What is enough. \{Strong's: 1767\}\hfill{}\\

\textbf{SUFFICIENT (Verb)} Heb: {\large\H הון} h.w.n Def: {[}X{]} \{Strong's: 1951\}\hfill{}\\

\textbf{SUM} Heb: {\large\H מתכונת} mat-ko-net Def: The total amount. An amount weighed out. \{Strong's: 4971\}\hfill{}\\

\textbf{SUMMER} Heb: {\large\H קיץ} qits Def: The season between spring and autumn. \{Strong's: 7007, 7019\}\hfill{}\\

\textbf{SUMMIT} Heb: {\large\H ראשית} rey-shit Def: The head, top or beginning of a place, such as a river or mountain, or a time, such as an event. The point at which something starts; origin, source. \{Strong's: 7225\}\hfill{}\\

\textbf{SUN} Heb: {\large\H שמש} she-mesh Def: The luminous body around which the earth revolves and from which it receives heat and light. \{Strong's: 8121, 8122\}\hfill{}\\

\textbf{SUN.IDOL} Heb: {\large\H חמן} {[}X{]} Def: An object of worship representing the sun god. \{Strong's: 2553\}\hfill{}\\

\textbf{SUNKEN} Heb: {\large\H עמוק} {[}X{]} Def: {[}X{]} \{Strong's: 6013\}\hfill{}\\

\textbf{SUNRISE} Heb: {\large\H מזרח} miz-rah Def: When the first light of the sun comes over the horizon. An eastward direction as the place of the rising sun. \{Strong's: 4217\}\hfill{}\\

\textbf{SUPPLY.HOUSE} Heb: {\large\H אוצר} {[}X{]} Def: A place where grain or other items of subsistence are held and protected. \{Strong's: 214\}\hfill{}\\

\textbf{SUPPORT (Verb)} Heb: {\large\H סמך} s.m.k Def: To uphold or defend; to hold up or serve as a foundation or prop for. \{Strong's: 5564\}\hfill{}\\

\textbf{SUPPRESS (Verb)} Heb: {\large\H ינה} y.n.h Def: To cause to be brought low by force, hindered. \{Strong's: 3238\}\hfill{}\\

\textbf{SURE} Heb: {\large\H אמנה} am-nah Def: Safe from danger or harm; marked by or given to feelings of confident certainty. What is firm. \{Strong's: 545, 546, 548\}\hfill{}\\

\textbf{SURELY} Heb: {\large\H אכן} a-kheyn Def: In a sure manner. To be firm in something. \{Strong's: 389, 403\}\hfill{}\\

\textbf{SURROUNDED.BY.A.WALL} Heb: {\large\H חצרון} hhets-ron Def: To be surrounded, encompassed, by a wall of stone or thorns for protection. \{Strong's: n/a\}\hfill{}\\

\textbf{SURVIVE} Heb: {\large\H סריד} {[}X{]} Def: What is left behind. \{Strong's: 8300\}\hfill{}\\

\textbf{SUSTAIN (Verb)} Heb: {\large\H כול} k.w.l Def: To provide what is needed to make someone or something whole or complete. \{Strong's: 3557\}\hfill{}\\

\textbf{SWALLOW (Verb)} Heb: {\large\H בלע} b.l.ah Def: To pass through the mouth and move into the esophagus to the stomach. \{Strong's: 1104\}\hfill{}\\

\textbf{SWALLOWED} Heb: {\large\H בלע} {[}X{]} Def: {[}X{]} \{Strong's: 1105\}\hfill{}\\

\textbf{SWARM (Verb)} Heb: {\large\H שרץ} sh.r.ts Def: To move, as a large mass of creatures. \{Strong's: 8317\}\hfill{}\\

\textbf{SWARMER} Heb: {\large\H שרץ} she-rets Def: The creature(s) of a large swarm. \{Strong's: 8318\}\hfill{}\\

\textbf{SWARMING.LOCUST} Heb: {\large\H ארבה} ar-beh Def: A six legged insect having short antennae and commonly migrating in swarms that strip the vegetation from large areas. \{Strong's: 697\}\hfill{}\\

\textbf{SWEAR (Verb)} Heb: {\large\H שבע} sh.b.ah Def: To completely submit to a promise or oath with words and spoken seven times. \{Strong's: 7650\}\hfill{}\\

\textbf{SWEARING} Heb: {\large\H שבועה} she-vu-ah Def: The act of taking an oath. \{Strong's: 7621\}\hfill{}\\

\textbf{SWEAT} Heb: {\large\H זעה} ze-ah Def: To excrete moisture in visible quantities through the pores of the skin. \{Strong's: 2188\}\hfill{}\\

\textbf{SWEEP (Verb)} Heb: {\large\H גוז} g.w.z Def: The sweeping away of something. \{Strong's: 1468\}\hfill{}\\

\textbf{SWEET} Heb: {\large\H ניחוח} ni-hho-ahh Def: Pleasing to the taste. Not sour, bitter or salty. Something that smells pleasing. \{Strong's: 5207, 5208\}\hfill{}\\

\textbf{SWEET.SPICE} Heb: {\large\H בוסם} bo-sem Def: An aromatic spice that is pleasing to the nose. \{Strong's: 1314\}\hfill{}\\

\textbf{SWEETNESS} Heb: {\large\H מתק} {[}X{]} \textbf{\textbackslash{}} {\large\H מתקה} mit-qah Def: {[}X{]} \{Strong's: 4986\}\hfill{}\\

\textbf{SWELL (Verb)} Heb: {\large\H צבה} ts.b.h Def: {[}X{]} \{Strong's: 6638\}\hfill{}\\

\textbf{SWELL.UP (Verb)} Heb: {\large\H בצק} b.ts.q Def: {[}X{]} \{Strong's: 1216\}\hfill{}\\

\textbf{SWELLING} Heb: {\large\H צבה} {[}X{]} Def: {[}X{]} \{Strong's: 6639\}\hfill{}\\

\textbf{SWIFTNESS} Heb: {\large\H פלת} pe-let Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{SWINE} Heb: {\large\H חזיר} {[}X{]} Def: {[}X{]} \{Strong's: 2386\}\hfill{}\\

\textbf{SWORD} Heb: {\large\H חרב} hhe-rev Def: A weapon with a long blade for cutting or thrusting. \{Strong's: 2719\}\hfill{}\\

\textbf{TABLE} Heb: {\large\H שולחן} shul-hhan Def: A flat surface, usually made of wood and with four legs, for laying out the meal to be eaten. \{Strong's: 7979\}\hfill{}\\

\textbf{TAHHASH} Heb: {\large\H תחש} ta-hhash Def: An unknown species of animal. \{Strong's: 8476\}\hfill{}\\

\textbf{TAHHMAS} Heb: {\large\H תחמס} {[}X{]} Def: An unknown bird. \{Strong's: 8464\}\hfill{}\\

\textbf{TAIL} Heb: {\large\H זנב} na-nav Def: The hindmost flexible appendage of an animal. \{Strong's: 2180\}\hfill{}\\

\textbf{TAKE (Verb)} Heb: {\large\H לקח} l.q.hh Def: To receive what is given; to gain possession by seizing. \{Strong's: 3947\}\hfill{}\\

\textbf{TAKE.A.FIFTH (Verb)} Heb: {\large\H חמש} hh.m.sh Def: To separate out one equal portion out of five. \{Strong's: 2567\}\hfill{}\\

\textbf{TAKE.ABACK (Verb)} Heb: {\large\H חתת} hh.t.t Def: To beat or shatter into pieces; to fear or be in terror in the sense of being shattered. \{Strong's: 2865\}\hfill{}\\

\textbf{TAKE.AS.A.PLEDGE (Verb)} Heb: {\large\H חבל} hh.b.l Def: To receive an object in exchange for a promise. \{Strong's: 2254, 2255\}\hfill{}\\

\textbf{TAKE.AWAY (Verb)} Heb: {\large\H גרע} g.r.ah Def: To scrape off or clip. To impair or degrade. \{Strong's: 1639\}\hfill{}\\

\textbf{TAKE.HEED (Verb)} Heb: {\large\H סכת} s.k.t Def: To be silent. \{Strong's: 5535\}\hfill{}\\

\textbf{TAKE.HOLD (Verb)} Heb: {\large\H אחז} a.hh.z Def: To have possession or ownership of; to keep in restraint; to have or maintain in one's grasp; to grab something and keep hold of it. \{Strong's: 270\}\hfill{}\\

\textbf{TAKE.UPON (Verb)} Heb: {\large\H יאל} y.a.l Def: The placing of a yoke on the shoulders to perform work or undertake a task. \{Strong's: 2974\}\hfill{}\\

\textbf{TALEBEARER} Heb: {\large\H רכיל} {[}X{]} Def: A traveler selling stories and songs. As a talebearer. \{Strong's: 7400\}\hfill{}\\

\textbf{TALK (Verb)} Heb: {\large\H מלל} m.l.l Def: To deliver or express in spoken words. \{Strong's: 4448, 4449\}\hfill{}\\

\textbf{TAMARISK} Heb: {\large\H אשל} a-shal Def: The tree or a grove of desert shrubs and trees with masses of minute flowers.. \{Strong's: 815\}\hfill{}\\

\textbf{TAMBOURINE} Heb: {\large\H תוף} toph Def: A shallow, one-headed drum with loose disks at the sides played by shaking, striking with the hand, or rubbing with the thumb. \{Strong's: 8596\}\hfill{}\\

\textbf{TAR} Heb: {\large\H חמר} hhey-mar Def: A dark and thick liquid that floats to the surface of water and is used as a waterproof covering for boats. \{Strong's: 2561, 2562, 2564\}\hfill{}\\

\textbf{TASK.WORK} Heb: {\large\H מס} mas Def: A forced labor or service. \{Strong's: 4522, 4523\}\hfill{}\\

\textbf{TASSEL} Heb: {\large\H גדיל} {[}X{]} Def: Something that is made from twisted fibers. \{Strong's: 1434\}\hfill{}\\

\textbf{TASTE.SWEET (Verb)} Heb: {\large\H מתק} m.t.q Def: To have a pleasant taste to the mouth. \{Strong's: 4985, 4988\}\hfill{}\\

\textbf{TASTY.FOOD} Heb: {\large\H מעדן} ma-a-dan Def: Having a marked and pleasing flavor. As a pleasurable thing. \{Strong's: 4574\}\hfill{}\\

\textbf{TATTOO} Heb: {\large\H קעקע} {[}X{]} Def: {[}X{]} \{Strong's: 7085\}\hfill{}\\

\textbf{TAUNT (Verb)} Heb: {\large\H גדף} g.d.p Def: {[}X{]} \{Strong's: 1442\}\hfill{}\\

\textbf{TEACHING} Heb: {\large\H תורה} to-rah Def: Acquired knowledge or skills that mark the direction one is to take in life. A straight direction. Knowledge passed from one person to another. \{Strong's: 8451\}\hfill{}\\

\textbf{TEAR (Verb)} Heb: {\large\H קרע} q.r.ah Def: To rip into pieces. \{Strong's: 7167\}\hfill{}\\

\textbf{TEAR.AWAY (Verb)} Heb: {\large\H נסח} n.s.hh Def: {[}X{]} \{Strong's: 5255, 5256\}\hfill{}\\

\textbf{TEAR.INTO.PIECES (Verb)} Heb: {\large\H טרף} t.r.p Def: To tear into pieces as a predator does to its prey; to rip a cloth into pieces. \{Strong's: 2963\}\hfill{}\\

\textbf{TEAR.OFF (Verb)} Heb: {\large\H פרק} p.r.q Def: To remove reluctantly. \{Strong's: 6561, 6562\}\hfill{}\\

\textbf{TEAT} Heb: {\large\H דד} {[}X{]} Def: {[}X{]} \{Strong's: 1717\}\hfill{}\\

\textbf{TEN} Heb: {\large\H עשרה} a-sa-rah \textbf{\textbackslash{}} {\large\H עשר} e-ser Def: A cardinal number. \{Strong's: 6235, 6236, 6240, 6242, 6243\}\hfill{}\\

\textbf{TENDER} Heb: {\large\H רך} rakh \textbf{\textbackslash{}} {\large\H רכה} ra-kah Def: Having a soft or yielding texture; easily broken, cut, or damaged. From the tenderness of the loins. \{Strong's: 7390\}\hfill{}\\

\textbf{TENDERNESS} Heb: {\large\H רוך} {[}X{]} Def: {[}X{]} \{Strong's: 7391\}\hfill{}\\

\textbf{TENT} Heb: {\large\H אוהל} o-hel Def: The black, goat hair dwelling of the nomad. \{Strong's: 168\}\hfill{}\\

\textbf{TENT.CURTAIN} Heb: {\large\H פרוכת} pa-ro-khet Def: A wall of fabric or hung from the roof to make a dividing of a room. \{Strong's: 6532\}\hfill{}\\

\textbf{TENT.PEG} Heb: {\large\H יתד} ya-teyd Def: An instrument used to secure the corners and sides of the tent to the ground. \{Strong's: 3489\}\hfill{}\\

\textbf{TENT.WALL} Heb: {\large\H יריעה} ye-ri-a Def: The goat hair curtain that forms the walls of the tent. \{Strong's: 3407\}\hfill{}\\

\textbf{TENTH} Heb: {\large\H עשירי} a-si-ri Def: An ordinal number. \{Strong's: 6224\}\hfill{}\\

\textbf{TENTH.ONE} Heb: {\large\H עשור} a-sor Def: That which occupies the tenth position in a sequence. \{Strong's: 6218\}\hfill{}\\

\textbf{TENTH.PART} Heb: {\large\H מעסר} ma-a-seyr Def: One portion of a whole divided into ten equal portions. \{Strong's: 4643\}\hfill{}\\

\textbf{TE'O} Heb: {\large\H תאו} {[}X{]} Def: An unknown animal. \{Strong's: 8377\}\hfill{}\\

\textbf{TERMINATE (Verb)} Heb: {\large\H חדל} hh.d.l Def: To stop or refrain from continuing an action. \{Strong's: 2308\}\hfill{}\\

\textbf{TERRIFY (Verb)} Heb: {\large\H ערץ} ah.r.ts Def: {[}X{]} \{Strong's: 6206\}\hfill{}\\

\textbf{TERROR} Heb: {\large\H אימה} ey-mah Def: A state of intense fear. \{Strong's: 367\}\hfill{}\\

\textbf{TEST (Verb)} Heb: {\large\H נסה} n.s.h Def: A critical examination, observation, or evaluation; trial. \{Strong's: 5254\}\hfill{}\\

\textbf{TESTICLES} Heb: {\large\H אשך} {[}X{]} Def: {[}X{]} \{Strong's: 810\}\hfill{}\\

\textbf{THANKS} Heb: {\large\H תודה} {[}X{]} Def: An expression of gratitude or acknowledgement toward another. In the sense of raising up the hands. \{Strong's: 8426\}\hfill{}\\

\textbf{THANKSGIVING} Heb: {\large\H יהודה} ye-hu-dah Def: An expression of thanks through shouting. \{Strong's: n/a\}\hfill{}\\

\textbf{THAT} Heb: {\large\H מען} ma-an Def: The person, thing, or idea indicated, mentioned, or understood from the situation. A close watching. \{Strong's: 4616\}\hfill{}\\

\textbf{THAT.ONE} Heb: {\large\H מו} mo Def: Being the person, thing, or idea specified, mentioned, or understood. \{Strong's: 1119, 3644, 3926\}\hfill{}\\

\textbf{THEFT} Heb: {\large\H גנבה} ge-ney-vah Def: The unlawful taking of another's property. \{Strong's: 1591\}\hfill{}\\

\textbf{THEN} Heb: {\large\H אפו} ey-pho Def: An inquiry of a time or place. \{Strong's: 645\}\hfill{}\\

\textbf{THERE} Heb: {\large\H שם} sham Def: Used to identify another place. \{Strong's: 8033, 8536\}\hfill{}\\

\textbf{THERE.IS} Heb: {\large\H יש} yeysh Def: Something that exists. \{Strong's: 786, 3426\}\hfill{}\\

\textbf{THESE} Heb: {\large\H אלה} ey-lah Def: The persons, things, or ideas present or near in place, time, or thought or just mentioned. A grammatical tool used to identify something specific in the sense of looking toward a sight. \{Strong's: 411, 412, 428, 429, 459, 479\}\hfill{}\\

\textbf{THEY(f)} Heb: {\large\H הנה} hey-nah Def: The plural of ``she.'' \{Strong's: 2007, 3860\}\hfill{}\\

\textbf{THEY(m)} Heb: {\large\H המה} hey-mah Def: The plural of ``he.'' \{Strong's: 1992, 1994\}\hfill{}\\

\textbf{THICK} Heb: {\large\H עב} av Def: Heavily compacted material, such as a cloud, forest or thicket, and is filled with darkness. \{Strong's: 5645\}\hfill{}\\

\textbf{THICK.CORD} Heb: {\large\H עבות} a-vot Def: A rope or other woven object that is tightly wrapped. \{Strong's: 5687, 5688\}\hfill{}\\

\textbf{THICK.DARKNESS} Heb: {\large\H ערפל} a-ra-phel Def: A heavy darkness that can be felt. \{Strong's: 6205\}\hfill{}\\

\textbf{THICK.GLOOMINESS} Heb: {\large\H אפלה} a-phey-lah Def: A heavy darkness that brings about sadness or depression. \{Strong's: 653\}\hfill{}\\

\textbf{THIEF} Heb: {\large\H גנב} ga-nav Def: One who steals the property of another. \{Strong's: 1590\}\hfill{}\\

\textbf{THIGH} Heb: {\large\H שוק} shuq Def: The upper part of the leg of a man or animal. Also a street. \{Strong's: 7784, 7785\}\hfill{}\\

\textbf{THIN} Heb: {\large\H רק} raq Def: Not dense in distribution; not well-fleshed. \{Strong's: 7534\}\hfill{}\\

\textbf{THIN.BREAD} Heb: {\large\H רקיק} ra-qiq Def: Dough that has been spread thin before baked. \{Strong's: 7550\}\hfill{}\\

\textbf{THING.WRITTEN} Heb: {\large\H מכתב} mikh-tav Def: A composition that has been recorded by the written words. \{Strong's: 4385\}\hfill{}\\

\textbf{THINK (Verb)} Heb: {\large\H חשב} hh.sh.b Def: To plan or design a course of action, item or invention. \{Strong's: 2803, 2804\}\hfill{}\\

\textbf{THIRD} Heb: {\large\H שלישי} she-li-shi Def: An ordinal number. \{Strong's: 7992, 8523\}\hfill{}\\

\textbf{THIRD.GENERATION} Heb: {\large\H שילש} shi-leysh Def: The third increment within the sequence. \{Strong's: 8029\}\hfill{}\\

\textbf{THIRST} Heb: {\large\H צמא} tsa-mey \textbf{\textbackslash{}} {\large\H צמאה} tsa-mah Def: The lack of sufficient water. \{Strong's: 6771, 6772, 6773\}\hfill{}\\

\textbf{THIRST (Verb)} Heb: {\large\H צמא} ts.m.a Def: To lack sufficient water. \{Strong's: 6770\}\hfill{}\\

\textbf{THIRSTY.LAND} Heb: {\large\H צימאון} {[}X{]} Def: A thirsty land. \{Strong's: 6774\}\hfill{}\\

\textbf{THIS} Heb: {\large\H זה} zeh \textbf{\textbackslash{}} {\large\H זאת} zot Def: A person, thing, or idea present or near in place, time, or thought or just mentioned. As prominent or pointed out. \{Strong's: 1454, 1668, 1768, 1791, 1797, 1836, 2063, 2088, 2090, 2097\}\hfill{}\\

\textbf{THIS.ONE} Heb: {\large\H הלזה} ha-la-zeh Def: The one nearer or more immediately under observation or discussion. \{Strong's: 1976\}\hfill{}\\

\textbf{THISTLE} Heb: {\large\H דרדר} dar-dar Def: A prickly plant used by the shepherd to build a corral around the flock at night. \{Strong's: 1863\}\hfill{}\\

\textbf{THORN.BUSH} Heb: {\large\H סנה} se-neh Def: A plant, bush or tree, that grows thorns. \{Strong's: 5572\}\hfill{}\\

\textbf{THOUGH} Heb: {\large\H הן} heyn Def: However; nevertheless. In spite of the fact of. A possible or desired location. To bring attention to an event. \{Strong's: 581, 2004, 2005, 2006, 3861\}\hfill{}\\

\textbf{THOUGHT} Heb: {\large\H יצר} yey-tser Def: The forming of ideas in the mind. \{Strong's: 3336\}\hfill{}\\

\textbf{THOUSAND} Heb: {\large\H אלף} e-leph Def: Ten times one hundred in amount or number. \{Strong's: 505, 506\}\hfill{}\\

\textbf{THREAD} Heb: {\large\H חוט} hhut Def: A filament of fibers twisted together by spinning and used for sewing or tying items together. \{Strong's: 2339\}\hfill{}\\

\textbf{THREE} Heb: {\large\H שלושה} she-lo-shah \textbf{\textbackslash{}} {\large\H שלוש} she-losh Def: A cardinal number. \{Strong's: 7969, 7970\}\hfill{}\\

\textbf{THREE.DAYS.AGO} Heb: {\large\H שילשום} shil-shom Def: Literally the day before yesterday, but used as an idiom for the past. \{Strong's: 8032\}\hfill{}\\

\textbf{THRESH (Verb)} Heb: {\large\H אדש} a.d.sh Def: {[}X{]} \{Strong's: 156\}\hfill{}\\

\textbf{THRESHER} Heb: {\large\H דישון} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{THRESHING} Heb: {\large\H דיש} {[}X{]} Def: {[}X{]} \{Strong's: 1786\}\hfill{}\\

\textbf{THROW (Verb)} Heb: {\large\H ירה} y.r.h Def: To propel through the air by a forward motion; to drizzle as a throwing down of water; to teach in the sense of throwing or pointing a finger in a straight line as the direction one is to walk. The hiphil (causative) form means ``teach.'' \{Strong's: 3384\}\hfill{}\\

\textbf{THROW.DOWN (Verb)} Heb: {\large\H רמה} r.m.h Def: To lead astray; to deliver to an enemy by treachery; to reveal unintentionally. \{Strong's: 7411, 7412\}\hfill{}\\

\textbf{THROW.OUT (Verb)} Heb: {\large\H שלך} sh.l.k Def: To remove from a place, usually in a sudden or unexpected manner; to cast out, down or away. \{Strong's: 7993\}\hfill{}\\

\textbf{THROW.STONES (Verb)} Heb: {\large\H רגם} r.g.m Def: To throw stones for execution. \{Strong's: 7275\}\hfill{}\\

\textbf{THROW.THE.HAND (Verb)} Heb: {\large\H ידה} y.d.h Def: To stretch out the hand to grab; to show praise or confession. \{Strong's: 1911, 3029, 3034\}\hfill{}\\

\textbf{THROWING} Heb: {\large\H מידד} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{THRUST (Verb)} Heb: {\large\H תקע} t.q.ah Def: To push or drive with force a pole into the ground, such as when setting up the tent; to blow the trumpet in the sense of throwing out the sound. \{Strong's: 8628\}\hfill{}\\

\textbf{THUMB} Heb: {\large\H בוהן} bo-hen Def: The opposable digit of the hand. Also the big toe of the foot. Perceived as the builder because of its unique abilities. \{Strong's: 931\}\hfill{}\\

\textbf{TIE (Verb)} Heb: {\large\H קשר} q.sh.r Def: To fasten, attach, or close by means of a string or cord; to tie around; to conspire in the sense of tying up. \{Strong's: 7194\}\hfill{}\\

\textbf{TIE.ON (Verb)} Heb: {\large\H רכס} r.k.s Def: To attach or bind one object to another by tying them together. \{Strong's: 7405\}\hfill{}\\

\textbf{TIE.UP (Verb)} Heb: {\large\H אסר} a.s.r Def: To wrap or fasten with a cord. \{Strong's: 631\}\hfill{}\\

\textbf{TIGHTLY.WRAPPED} Heb: {\large\H לוט} {[}X{]} Def: {[}X{]} \{Strong's: 3875\}\hfill{}\\

\textbf{TIME} Heb: {\large\H מונה} mo-neh Def: The measured or measurable period during which an action, process or condition exists or continues. A counting or reckoning of time. \{Strong's: 4489\}\hfill{}\\

\textbf{TIME.OF.WEEPING} Heb: {\large\H בכית} be-khit Def: A period of sadness or mourning. \{Strong's: 1068\}\hfill{}\\

\textbf{TIN} Heb: {\large\H בדיל} {[}X{]} Def: A metal separated out by smelting. \{Strong's: 913\}\hfill{}\\

\textbf{TINSHEMET} Heb: {\large\H תנשמת} {[}X{]} Def: An unknown animal. \{Strong's: 8580\}\hfill{}\\

\textbf{TINY} Heb: {\large\H צוער} tso-ar Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{TIP} Heb: {\large\H תנוך} te-nuk Def: The pointed end of an object. \{Strong's: 8571\}\hfill{}\\

\textbf{TIRED} Heb: {\large\H עיף} a-yeyph Def: Drained of strength and energy; fatigued. \{Strong's: 5889\}\hfill{}\\

\textbf{TITLE} Heb: {\large\H שם} sheym Def: A word given to an individual or place denoting its character. The character of an individual or place. \{Strong's: 8034, 8036\}\hfill{}\\

\textbf{TO} Heb: {\large\H אל} el Def: Used as a function word to indicate movement or an action or condition suggestive of progress toward a place, person, or thing reached. \{Strong's: 413\}\hfill{}\\

\textbf{TO.THE.RIGHT} Heb: {\large\H תימן} tey-man Def: A Southern direction, which is to the right when facing the rising sun. \{Strong's: 8486\}\hfill{}\\

\textbf{TO.THIS.POINT} Heb: {\large\H הנה} hey-nah Def: A precise moment in time or a specific location. \{Strong's: 2008\}\hfill{}\\

\textbf{TOGETHER} Heb: {\large\H יחד} ya-hhad Def: In or into one place, mass, collection, or group. \{Strong's: 3162\}\hfill{}\\

\textbf{TOIL} Heb: {\large\H יגיע} ye-gi-a Def: To work hard and long. \{Strong's: 3018, 3019\}\hfill{}\\

\textbf{TOKEN} Heb: {\large\H ערבון} ey-ra-von Def: Something given as a promise as an exchange. \{Strong's: 6162\}\hfill{}\\

\textbf{TOMORROW} Heb: {\large\H מחר} ma-hhar Def: The next day. At a time following. \{Strong's: 4279\}\hfill{}\\

\textbf{TONG} Heb: {\large\H מלקח} mel-qahh Def: An instrument used for grasping, having two arms working together. A tool for taking coals out of the fire. \{Strong's: 4457\}\hfill{}\\

\textbf{TONGUE} Heb: {\large\H לשון} la-shon Def: A fleshy moveable process on the floor of the mouth used in speaking and eating. Also, language as a tongue. \{Strong's: 3956\}\hfill{}\\

\textbf{TOOTH} Heb: {\large\H שן} sheyn Def: Hard bony appendages on the jaws used for chewing food and forming of sounds when talking. \{Strong's: 8127, 8128\}\hfill{}\\

\textbf{TOP.OF.THE.HEAD} Heb: {\large\H קדקוד} {[}X{]} Def: The crown of the head. \{Strong's: 6936\}\hfill{}\\

\textbf{TOPAZ} Heb: {\large\H תרשיש} tar-shish Def: Possibly the Topaz, which may be yellow, gray, white, pink, green or blue in color. Other possible translations are Beryl, Lapis Lazuli, Amber, Jasper, Serpentine, Olivine, or Flint. \{Strong's: 8658\}\hfill{}\\

\textbf{TOPPLE (Verb)} Heb: {\large\H כשל} k.sh.l Def: To fall over in death or from being pushed. \{Strong's: 3782\}\hfill{}\\

\textbf{TORCH} Heb: {\large\H לפיד} la-pid Def: A burning stick of resinous wood. Also, lightning as a torch in the night sky. \{Strong's: 3940\}\hfill{}\\

\textbf{TORN} Heb: {\large\H טרפה} te-rey-phah Def: Pulled apart. Flesh that is torn. \{Strong's: 2966\}\hfill{}\\

\textbf{TOSS (Verb)} Heb: {\large\H נדד} n.d.d Def: To heave or fling about; to throw with a quick, light, or careless motion; to be thrown about or wander around as nodding the head. \{Strong's: 5074, 5075\}\hfill{}\\

\textbf{TOSS.OUT (Verb)} Heb: {\large\H כור} k.w.r Def: To look deeply. \{Strong's: 952, 6979\}\hfill{}\\

\textbf{TOTTER (Verb)} Heb: {\large\H מוט} m.w.t Def: To waver as a green branch. \{Strong's: 4131\}\hfill{}\\

\textbf{TOUCH (Verb)} Heb: {\large\H נגע} n.g.ah Def: To lay hands upon; to touch or strike; to be touched by a plague. \{Strong's: 5060\}\hfill{}\\

\textbf{TOUR (Verb)} Heb: {\large\H תור} t.w.r Def: To travel an area from border to border. \{Strong's: 7788, 8446\}\hfill{}\\

\textbf{TOWER} Heb: {\large\H מגדל} mig-dal Def: A structure higher than its diameter and high relative to its surroundings. Place of great size. \{Strong's: 4026\}\hfill{}\\

\textbf{TOWN} Heb: {\large\H חוה} hha-wah Def: A small village. \{Strong's: 2333\}\hfill{}\\

\textbf{TRADE (Verb)} Heb: {\large\H סחר} s.hh.r Def: The business of buying and selling or bartering commodities. To go about as a merchant trading goods. In Psalm 38:11 this word is used for the beating of the heart in the sense of going about to and fro. \{Strong's: 5503\}\hfill{}\\

\textbf{TRAMPLE.DOWN (Verb)} Heb: {\large\H בוס} b.w.s Def: To purposely destroy by stomping upon to break or smash. \{Strong's: 947\}\hfill{}\\

\textbf{TRANCE} Heb: {\large\H תרדמה} tar-dey-mah Def: A state of partly suspended animation or inability to function. A deep sleep or unconsciousness. \{Strong's: 8639\}\hfill{}\\

\textbf{TRANQUILITY} Heb: {\large\H שילוה} shi-loh Def: A state of rest. \{Strong's: 7886\}\hfill{}\\

\textbf{TRANSGRESS (Verb)} Heb: {\large\H מעל} m.ah.l Def: To commit an unintentional or treacherous act that results in error. \{Strong's: 4603\}\hfill{}\\

\textbf{TRANSGRESSION} Heb: {\large\H מעל} {[}X{]} Def: An unintentional or treacherous act that results in error. \{Strong's: 4604\}\hfill{}\\

\textbf{TRAP (Verb)} Heb: {\large\H לכד} l.k.d Def: To forcefully take or seize. \{Strong's: 3920\}\hfill{}\\

\textbf{TRAPPINGS} Heb: {\large\H עדי} a-di Def: Articles of dress or adornment that often witness to a person's position or rank. \{Strong's: 5716\}\hfill{}\\

\textbf{TREAD (Verb)} Heb: {\large\H רמס} r.m.s Def: To trample under foot. \{Strong's: 7429, 7430\}\hfill{}\\

\textbf{TREAD.ABOUT (Verb)} Heb: {\large\H רגל} r.g.l Def: To be on foot walking through a foreign land, usually in the sense of spying; to trample another with the tongue. \{Strong's: 7270, 8637\}\hfill{}\\

\textbf{TREADER} Heb: {\large\H רמס} re-mes Def: A creature that crawls or creeps on something. \{Strong's: 7431\}\hfill{}\\

\textbf{TREASURE} Heb: {\large\H מטמון} mat-mon Def: Wealth hoarded up or stored. What is hidden. \{Strong's: 4301\}\hfill{}\\

\textbf{TREASURY} Heb: {\large\H צפנת} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{TREE} Heb: {\large\H עץ} eyts Def: A woody perennial plant with a supporting stem or trunk and multiple branches. Meaning ``wood'' when written in the plural form. \{Strong's: 636, 6086, 6097\}\hfill{}\\

\textbf{TREMBLE (Verb)} Heb: {\large\H חרד} hh.r.d Def: To shake involuntarily; shiver. \{Strong's: 2729\}\hfill{}\\

\textbf{TREMBLING} Heb: {\large\H חרד} {[}X{]} \textbf{\textbackslash{}} {\large\H חרדה} hha-ra-dah Def: An involuntary shaking or shivering out of fear or awe. \{Strong's: 2730, 2731\}\hfill{}\\

\textbf{TREMBLING.IN.FEAR} Heb: {\large\H חת} hhet Def: A physical reaction, such as shivering, in fear or dread. \{Strong's: 2844\}\hfill{}\\

\textbf{TRIAL} Heb: {\large\H מסה} ma-sah Def: The act of trying, testing, or putting to the proof. \{Strong's: 4530\}\hfill{}\\

\textbf{TRIBAL} Heb: {\large\H עםון} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{TRIBE} Heb: {\large\H אומה} u-mah Def: A social group consisting of numerous families, clans or generations together. A family lineage as bound together. \{Strong's: 523, 524\}\hfill{}\\

\textbf{TRIBUTARY} Heb: {\large\H פלג} {[}X{]} Def: As a division of the waters. Split into two. \{Strong's: 6387, 6388\}\hfill{}\\

\textbf{TRIBUTE} Heb: {\large\H מכס} {[}X{]} Def: An assessment based on a number. \{Strong's: 4371\}\hfill{}\\

\textbf{TRICKLING} Heb: {\large\H זילפה} {[}X{]} Def: To set aside a time for a special occasion. \{Strong's: n/a\}\hfill{}\\

\textbf{TROUBLE} Heb: {\large\H תלאה} te-la-ah Def: A difficulty that brings about weariness. \{Strong's: 8513\}\hfill{}\\

\textbf{TROUBLED} Heb: {\large\H זעון} ze-ah Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{TROUGH} Heb: {\large\H רהט} ra-hat Def: A long, shallow often V-shaped receptacle for the drinking water or food of domestic animals. \{Strong's: 7298\}\hfill{}\\

\textbf{TRUMPET} Heb: {\large\H יובל} yo-vel Def: An instrument of flowing air to make a sound. Also, the horn of a ram as used as a trumpet. \{Strong's: 3104\}\hfill{}\\

\textbf{TRUTH} Heb: {\large\H אמת} e-met Def: The state of being the case. Fact. What is firm. Accurately so. \{Strong's: 571\}\hfill{}\\

\textbf{TUB} Heb: {\large\H סף} saph Def: A container with a lip. The lip of the door. \{Strong's: 5592\}\hfill{}\\

\textbf{TUMULT} Heb: {\large\H מהומה} {[}X{]} Def: {[}X{]} \{Strong's: 4103\}\hfill{}\\

\textbf{TUMULTUOUS} Heb: {\large\H משא} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{TUNIC} Heb: {\large\H כתונת} ke-to-net Def: A simple slip-on garment with or without sleeves. \{Strong's: 3801\}\hfill{}\\

\textbf{TURBAN} Heb: {\large\H מצנפת} mits-ne-phet Def: A cloth that is wrapped around the head. \{Strong's: 4701\}\hfill{}\\

\textbf{TURN (Verb)} Heb: {\large\H פנה} p.n.h Def: To rotate or revolve; to face another direction; to turn the face; to turn directions; to turn something back or away. \{Strong's: 6437\}\hfill{}\\

\textbf{TURN.ASIDE (Verb)} Heb: {\large\H סור} s.w.r Def: To change the location, position, station, or residence; to remove. The hiphil (causative) form means ``remove.'' \{Strong's: 5493, 7787\}\hfill{}\\

\textbf{TURN.AWAY (Verb)} Heb: {\large\H סרה} s.r.h Def: To deviate from the correct path toward another direction. \{Strong's: 8280\}\hfill{}\\

\textbf{TURN.BACK (Verb)} Heb: {\large\H שוב} sh.w.b Def: To return to a previous place or state. \{Strong's: 7725, 8421\}\hfill{}\\

\textbf{TURN.OVER (Verb)} Heb: {\large\H עטף} ah.t.p Def: To turn aside in fainting or hiding. \{Strong's: 5848\}\hfill{}\\

\textbf{TURNING.ASIDE} Heb: {\large\H סורה} {[}X{]} Def: A change in location, position, station or residence, usually as a revolt. \{Strong's: 5627\}\hfill{}\\

\textbf{TURQUOISE} Heb: {\large\H נופך} no-phek Def: Possibly the Turquoise, a blue to green stone that was commonly mined in the Near East. The Septuagint has Anthrax meaning coal. Other possible translations are Carbuncle, Garnet, Emerald and Malachite. \{Strong's: 5306\}\hfill{}\\

\textbf{TURTLEDOVE} Heb: {\large\H תור} tor Def: A small wild pigeon. \{Strong's: 8449\}\hfill{}\\

\textbf{TWIG} Heb: {\large\H סריג} sa-rig Def: A secondary shoot or stem arising from a main trunk or axis.. \{Strong's: 8299\}\hfill{}\\

\textbf{TWILIGHT} Heb: {\large\H עלטה} a-la-tah Def: The light from the sky between full night and sunrise; or between sunset and full night. \{Strong's: 5939\}\hfill{}\\

\textbf{TWIN} Heb: {\large\H תאום} ta-om Def: Born with one other or as a pair at birth. \{Strong's: 8380\}\hfill{}\\

\textbf{TWIRL (Verb)} Heb: {\large\H נדף} n.d.p Def: To toss back and forth. \{Strong's: 5086\}\hfill{}\\

\textbf{TWIST} Heb: {\large\H עוי} {[}X{]} \textbf{\textbackslash{}} {\large\H עוה} {[}X{]} Def: {[}X{]} \{Strong's: 5754\}\hfill{}\\

\textbf{TWIST (Verb)} Heb: {\large\H חול} hh.w.l Def: A winding or wrapping together; entwined in pain or joy. \{Strong's: 2342\}\hfill{}\\

\textbf{TWIST.AROUND} Heb: {\large\H חוילה} hhu-il Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{TWIST.BACKWARDS (Verb)} Heb: {\large\H סלף} s.l.p Def: A path that winds back on itself. To twist words or actions away from their proper context. \{Strong's: 5557\}\hfill{}\\

\textbf{TWIST.TOGETHER (Verb)} Heb: {\large\H שזר} sh.z.r Def: To wrap separate pieces together forming one unit. \{Strong's: 7806\}\hfill{}\\

\textbf{TWISTED} Heb: {\large\H פתלתל} {[}X{]} Def: {[}X{]} \{Strong's: 6618\}\hfill{}\\

\textbf{TWISTEDNESS} Heb: {\large\H עוון} a-won Def: Gross injustice; wickedness. The result of twisted actions. \{Strong's: 5771\}\hfill{}\\

\textbf{TWO} Heb: {\large\H שנים} she-na-yim \textbf{\textbackslash{}} {\large\H שתים} she-ta-yim Def: A cardinal number. \{Strong's: 8147, 8578, 8648\}\hfill{}\\

\textbf{TWO.WELLS} Heb: {\large\H דותן} {[}X{]} Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{ULCER} Heb: {\large\H יבלת} {[}X{]} Def: A flowing lesion. \{Strong's: 2990\}\hfill{}\\

\textbf{UNAWARE} Heb: {\large\H בלי} be-li Def: Without design, attention, preparation, or premeditation. \{Strong's: 1097\}\hfill{}\\

\textbf{UNCIRCUMCISED} Heb: {\large\H ערל} a-reyl Def: A male with a foreskin. \{Strong's: 6189\}\hfill{}\\

\textbf{UNCLEAN} Heb: {\large\H טמא} ta-mey \textbf{\textbackslash{}} {\large\H טמאה} ta-mey-ah Def: What is morally or physically impure; dirty, filthy. \{Strong's: 2931, 2932\}\hfill{}\\

\textbf{UNCOVER (Verb)} Heb: {\large\H ערה} ah.r.h Def: To remove the covering. \{Strong's: 6168\}\hfill{}\\

\textbf{UNDER} Heb: {\large\H תחת} ta-hhat Def: Beneath. Below or underneath. Also, to be underneath in the sense of being in place of something else. \{Strong's: 8478, 8479\}\hfill{}\\

\textbf{UNDERGARMENT} Heb: {\large\H מכנס} mikh-nas Def: Garment worn under another garment that is bundled up. \{Strong's: 4370\}\hfill{}\\

\textbf{UNDERSTAND (Verb)} Heb: {\large\H בין} b.y.n Def: To grasp the meaning of; to have comprehension. \{Strong's: 995\}\hfill{}\\

\textbf{UNDERSTANDING} Heb: {\large\H בינה} {[}X{]} Def: A comprehension of the construction of a structure or thought. \{Strong's: 998, 999\}\hfill{}\\

\textbf{UNDERWORLD} Heb: {\large\H שאול} she-ol Def: The place of the dead. \{Strong's: 7585\}\hfill{}\\

\textbf{UNFILLED} Heb: {\large\H בוהו} bo-hu Def: Empty. As an empty box that needs to be filled. \{Strong's: 922\}\hfill{}\\

\textbf{UNINHABITED} Heb: {\large\H גזרה} {[}X{]} Def: A place cut off. \{Strong's: 1509, 1510\}\hfill{}\\

\textbf{UNIQUE} Heb: {\large\H קדוש} qa-dosh Def: Someone or something that has, or has been given the quality of specialness, and has been separated from the rest for a special purpose. \{Strong's: 6918\}\hfill{}\\

\textbf{UNIT} Heb: {\large\H אחד} e-hhad \textbf{\textbackslash{}} {\large\H אחת} e-hhat Def: A unit within the whole, a unified group. A single quantity. \{Strong's: 259\}\hfill{}\\

\textbf{UNITE (Verb)} Heb: {\large\H יחד} y.hh.d Def: To put together to form a single unit. \{Strong's: 3161\}\hfill{}\\

\textbf{UNLEAVENED.BREAD} Heb: {\large\H מצה} mats-tsah Def: A hard and flat bread or cake made without yeast. \{Strong's: 4682\}\hfill{}\\

\textbf{UNLESS} Heb: {\large\H לואא} lu-a Def: Except on the condition that. \{Strong's: 3884\}\hfill{}\\

\textbf{UNNATURAL.MIX} Heb: {\large\H תבל} {[}X{]} Def: An action that lacks any results. \{Strong's: 8397\}\hfill{}\\

\textbf{UNPROTECTED} Heb: {\large\H ערוער} {[}X{]} Def: {[}X{]} \{Strong's: 6176\}\hfill{}\\

\textbf{UNSEASONED} Heb: {\large\H תפל} {[}X{]} Def: {[}X{]} \{Strong's: 8602\}\hfill{}\\

\textbf{UNTIL} Heb: {\large\H עד} ad Def: The conclusion of a determinate period of time. Also, again; a repetition of time, either definite or indefinite; another time; once more. \{Strong's: 5703, 5704, 5705\}\hfill{}\\

\textbf{UPHOLD (Verb)} Heb: {\large\H תמך} t.m.k Def: To give support or to steady. \{Strong's: 8551\}\hfill{}\\

\textbf{UPON} Heb: {\large\H על} al Def: To be on or over in the sense of the yoke that is placed on the neck of the ox. \{Strong's: 5921, 5922\}\hfill{}\\

\textbf{UPPER} Heb: {\large\H עליון} el-yon Def: Higher than the others. \{Strong's: 5945, 5946\}\hfill{}\\

\textbf{UPPER.LEG} Heb: {\large\H שובל} {[}X{]} Def: As the leg of a stream. \{Strong's: 7640\}\hfill{}\\

\textbf{UPPER.LIP} Heb: {\large\H ספם} {[}X{]} Def: {[}X{]} \{Strong's: 8222\}\hfill{}\\

\textbf{UPRISING} Heb: {\large\H מנסאת} ma-se-eyt Def: Violence in defiance of something. Something that is lifted up such as a burden, gift or flame. \{Strong's: 4864\}\hfill{}\\

\textbf{UPSIDE.DOWN} Heb: {\large\H תהפכה} {[}X{]} Def: {[}X{]} \{Strong's: 8419\}\hfill{}\\

\textbf{UPWARD} Heb: {\large\H מעל} ma-al Def: In a direction from lower to higher. \{Strong's: 4605\}\hfill{}\\

\textbf{USURY} Heb: {\large\H נשך} ne-shek Def: The lending or practice of lending money at an exorbitant interest. \{Strong's: 5392\}\hfill{}\\

\textbf{UTTER (Verb)} Heb: {\large\H בטא} b.t.a Def: {[}X{]} \{Strong's: 981\}\hfill{}\\

\textbf{UTTERANCE} Heb: {\large\H מבטא} {[}X{]} Def: Words spoken out of rashness. \{Strong's: 4008\}\hfill{}\\

\textbf{VACANT} Heb: {\large\H בוקי} {[}X{]} \textbf{\textbackslash{}} {\large\H בוקה} {[}X{]} Def: {[}X{]} \{Strong's: 950\}\hfill{}\\

\textbf{VALIANT} Heb: {\large\H אביר} a-vir Def: Possessing or acting with bravery or boldness. The mighty power of a bird in flight. Anything or anyone of great mental or physical strength. \{Strong's: 46, 47\}\hfill{}\\

\textbf{VALLEY} Heb: {\large\H עמק} ey-meq Def: An elongated depression between ranges of hills or mountains. As deep. Obscure, in the sense of dark. \{Strong's: 6010, 6012\}\hfill{}\\

\textbf{VALUE} Heb: {\large\H מכר} {[}X{]} Def: {[}X{]} \{Strong's: 4377\}\hfill{}\\

\textbf{VANITY} Heb: {\large\H הבל} {[}X{]} Def: The state of being empty of contents or usefulness. \{Strong's: 1892\}\hfill{}\\

\textbf{VEHICLE} Heb: {\large\H רכב} re-khev Def: A wheeled transport such as a wagon or chariot used for transportation. Also, the top millstone as a wheel that rides on top of the lower millstone. \{Strong's: 7393, 7395\}\hfill{}\\

\textbf{VEIL} Heb: {\large\H צעיף} tsa-iph Def: To cover, provide, obscure, or conceal with or as if with a cloth. \{Strong's: 6809\}\hfill{}\\

\textbf{VENGEANCE} Heb: {\large\H נקם} {[}X{]} \textbf{\textbackslash{}} {\large\H נקמה} {[}X{]} Def: The desire for revenge. \{Strong's: 5359, 5360\}\hfill{}\\

\textbf{VENOM} Heb: {\large\H רואש} {[}X{]} Def: The poison of serpents that comes sacks located in the head. Also by extension any type of poison. \{Strong's: 7219\}\hfill{}\\

\textbf{VERTICAL} Heb: {\large\H קוממיות} {[}X{]} Def: {[}X{]} \{Strong's: 6968\}\hfill{}\\

\textbf{VESSEL} Heb: {\large\H תבה} tey-vah Def: A floating container for holding items. Used for the basket that carried Mosheh down the Nile river and the boat made by Noah. \{Strong's: 8392\}\hfill{}\\

\textbf{VIGOR} Heb: {\large\H און} on Def: Active bodily or mental strength or force. The power within the belly or loins for reproduction or creative work. \{Strong's: 202\}\hfill{}\\

\textbf{VILLAGE} Heb: {\large\H פרזי} {[}X{]} \textbf{\textbackslash{}} {\large\H פרזה} {[}X{]} Def: A town or village without walls of protection. \{Strong's: 6519, 6521\}\hfill{}\\

\textbf{VINE} Heb: {\large\H זמורה} {[}X{]} Def: From where grapes are plucked. \{Strong's: 2156\}\hfill{}\\

\textbf{VINEGAR} Heb: {\large\H חומץ} {[}X{]} Def: Made by souring grapes. \{Strong's: 2558\}\hfill{}\\

\textbf{VINEYARD} Heb: {\large\H כרם} ke-rem Def: A planting of grapevines. \{Strong's: 3754\}\hfill{}\\

\textbf{VINTAGE} Heb: {\large\H בצור} {[}X{]} Def: The gathered crop of grapes. \{Strong's: 1208\}\hfill{}\\

\textbf{VIOLENCE} Heb: {\large\H חמס} hha-mas Def: Exertion of physical force so as to injure or abuse. A violent shaking. \{Strong's: 2555\}\hfill{}\\

\textbf{VIRGIN} Heb: {\large\H בתולה} be-tu-lah Def: An unmarried young woman who is absolutely chaste. \{Strong's: 1330\}\hfill{}\\

\textbf{VIRGINITY} Heb: {\large\H בתול} {[}X{]} Def: {[}X{]} \{Strong's: 1331\}\hfill{}\\

\textbf{VISION} Heb: {\large\H מחזה} ma-hha-zeh Def: Something seen in a dream, trance, or ecstasy. \{Strong's: 4236\}\hfill{}\\

\textbf{VISUALIZE (Verb)} Heb: {\large\H חלם} hh.l.m Def: To see or form a mental image of; to dream dreams. \{Strong's: 2492\}\hfill{}\\

\textbf{VOICE} Heb: {\large\H קול} qol Def: The faculty of utterance. Sound of a person, musical instrument, the wind, thunder, etc. \{Strong's: 6963\}\hfill{}\\

\textbf{VOMIT} Heb: {\large\H זרא} za-ra Def: {[}X{]} \{Strong's: 2214\}\hfill{}\\

\textbf{VOMIT (Verb)} Heb: {\large\H קוא} q.w.a Def: {[}X{]} \{Strong's: 6958\}\hfill{}\\

\textbf{VOW} Heb: {\large\H נדר} ne-der Def: To promise solemnly. \{Strong's: 5088\}\hfill{}\\

\textbf{WADI} Heb: {\large\H נחל} na-hhal Def: The bed or valley of a stream. A choice piece of land desired in an inheritance because of its fertility. \{Strong's: 5158\}\hfill{}\\

\textbf{WAFER} Heb: {\large\H צפיחית} tsa-pi-hhit Def: Small thinly baked bread. \{Strong's: 6838\}\hfill{}\\

\textbf{WAGE} Heb: {\large\H שכר} se-kher Def: The reward or price paid for one's labor. \{Strong's: 7938, 7939\}\hfill{}\\

\textbf{WAGES} Heb: {\large\H אתנן} {[}X{]} Def: What is brought to a harlot as a gift. \{Strong's: 868\}\hfill{}\\

\textbf{WAGON} Heb: {\large\H צב} {[}X{]} Def: A walled wagon for transport. From its shell as a wagon. \{Strong's: 6632\}\hfill{}\\

\textbf{WAIST} Heb: {\large\H מתן} ma-ten Def: The slender part of the body above the hips. \{Strong's: 4975\}\hfill{}\\

\textbf{WALK (Verb)} Heb: {\large\H הלך} h.l.k Def: To move along on foot; walk a journey; to go. Also, customs as a lifestyle that is walked or lived. \{Strong's: 1946, 1980, 1981, 3212\}\hfill{}\\

\textbf{WALL} Heb: {\large\H קיר} qir Def: A permanent upright construction having a length much greater than the thickness and presenting a continuous surface, may be constructed of a curtain, earth, rocks or hewed stones. Used for shelter, protection, or privacy, or to subdivide interior space. \{Strong's: 2426, 7023\}\hfill{}\\

\textbf{WANDER (Verb)} Heb: {\large\H תעה} t.ah.h Def: To go astray due to deception or an outside influence. To staggar, as from being intoxicated. \{Strong's: 8582\}\hfill{}\\

\textbf{WANTING} Heb: {\large\H חוסר} {[}X{]} Def: {[}X{]} \{Strong's: 2640\}\hfill{}\\

\textbf{WARN (Verb)} Heb: {\large\H זהר} z.h.r Def: To urge or advise to be careful. To caution. \{Strong's: 2094, 2095\}\hfill{}\\

\textbf{WARP} Heb: {\large\H שתי} {[}X{]} Def: A tool used for weaving, an activity performed while sitting down. \{Strong's: 8358, 8359\}\hfill{}\\

\textbf{WARRIOR} Heb: {\large\H גבר} ge-ver Def: One of great strength in battle, such as a warrior. One who is strong in authority, such as a master. \{Strong's: 1397, 1399, 1400\}\hfill{}\\

\textbf{WASH (Verb)} Heb: {\large\H כבס} k.b.s Def: To immerse articles of clothing into a cleaning solution and agitate them, usually by treading upon them, to clean them; to clean the body. \{Strong's: 3526\}\hfill{}\\

\textbf{WASTELAND} Heb: {\large\H חרבה} hhar-bah Def: A dry or desolate place. Barren or uncultivated land. Also a dry land. \{Strong's: 2720, 2723, 2724\}\hfill{}\\

\textbf{WATCHER} Heb: {\large\H ציפיון} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{WATCHMAN} Heb: {\large\H צף} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{WATCHTOWER} Heb: {\large\H מצפה} {[}X{]} Def: A place for watching. \{Strong's: 4707\}\hfill{}\\

\textbf{WATER} Heb: {\large\H מה} mah Def: The Liquid of streams, ponds and seas or stored in cisterns or jars. The necessary liquid that is drank. \{Strong's: 4325\}\hfill{}\\

\textbf{WATERCOURSE} Heb: {\large\H יבל} {[}X{]} Def: A flowing body of water. \{Strong's: 2988\}\hfill{}\\

\textbf{WATERED} Heb: {\large\H רוה} {[}X{]} Def: {[}X{]} \{Strong's: 7302\}\hfill{}\\

\textbf{WATERING.TROUGH} Heb: {\large\H שוקת} sho-qet Def: A trench for bringing water into the village. A place for domestic animals to quench thirst. \{Strong's: 8268\}\hfill{}\\

\textbf{WAVE (Verb)} Heb: {\large\H נוף} n.w.p Def: To move an object, such as hammer or a sacrifice, back and forth. \{Strong's: 5130\}\hfill{}\\

\textbf{WAVER (Verb)} Heb: {\large\H אזל} a.z.l Def: To go about in a shaking motion. \{Strong's: 235, 236\}\hfill{}\\

\textbf{WAVING} Heb: {\large\H תנופה} te-nu-phah Def: The action of moving an object, such as hammer or a sacrifice, back and forth. \{Strong's: 8573\}\hfill{}\\

\textbf{WAYWARDNESS} Heb: {\large\H רישעה} {[}X{]} Def: {[}X{]} \{Strong's: 7564\}\hfill{}\\

\textbf{WE} Heb: {\large\H אנו} a-nu Def: I and the rest of a group. \{Strong's: 580, 586, 587, 5168\}\hfill{}\\

\textbf{WEAK} Heb: {\large\H דל} dal Def: One who dangles the head in poverty or hunger. \{Strong's: 1800\}\hfill{}\\

\textbf{WEAKEN (Verb)} Heb: {\large\H חלש} hh.l.sh Def: To reduce in strength. \{Strong's: 2522\}\hfill{}\\

\textbf{WEALTHY} Heb: {\large\H חשמן} {[}X{]} \textbf{\textbackslash{}} {\large\H חשמנה} {[}X{]} Def: {[}X{]} \{Strong's: 2831\}\hfill{}\\

\textbf{WEAR (Verb)} Heb: {\large\H לבש} l.b.sh Def: To cover with cloth or clothing; to provide with clothing; put on clothing. The hiphil (causative) form means ``clothe.'' \{Strong's: 3847, 3848\}\hfill{}\\

\textbf{WEAR.OUT (Verb)} Heb: {\large\H בלה} b.l.h Def: To make useless, especially by long or hard usage. \{Strong's: 1086, 1089\}\hfill{}\\

\textbf{WEARY} Heb: {\large\H יגע} {[}X{]} Def: {[}X{]} \{Strong's: 3022, 3023\}\hfill{}\\

\textbf{WEAVE (Verb)} Heb: {\large\H שבץ} sh.b.ts Def: To interlace (threads, yarns, strips, fibrous material, etc.) so as to form a fabric or material. \{Strong's: 7660\}\hfill{}\\

\textbf{WEEK} Heb: {\large\H שבוע} sha-vu-a Def: A period of time consisting of seven days or seven years. \{Strong's: 7620\}\hfill{}\\

\textbf{WEEP (Verb)} Heb: {\large\H בכה} b.k.h Def: To express deep sorrow, especially by shedding tears. \{Strong's: 1058\}\hfill{}\\

\textbf{WEEPING} Heb: {\large\H בכי} be-khi Def: The act of expressing sorrow by shedding tears. \{Strong's: 1065\}\hfill{}\\

\textbf{WEIGH (Verb)} Heb: {\large\H שקל} sh.q.l Def: To ascertain the heaviness of by a balance or scale. Weigh out, usually of silver for payment. \{Strong's: 8254\}\hfill{}\\

\textbf{WEIGHT} Heb: {\large\H משקל} mish-qal Def: The amount a thing weighs. Relative heaviness. \{Strong's: 4948\}\hfill{}\\

\textbf{WELL} Heb: {\large\H באר} be-eyr Def: A dug-out hole, usually a well or cistern. \{Strong's: 875\}\hfill{}\\

\textbf{WELLNESS} Heb: {\large\H יטבה} ya-ta-vah Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{WHAT} Heb: {\large\H מה} mah Def: Interrogative expressing inquiry about the identity, nature, or value of an object. Something that is unknown; can also be why, when or how. \{Strong's: 3964, 4100, 4101, 4479\}\hfill{}\\

\textbf{WHEAT} Heb: {\large\H חיטה} hhi-tah Def: A cereal grain that yields a fine white flour, the chief ingredient of bread. \{Strong's: 2406, 2591\}\hfill{}\\

\textbf{WHEEL} Heb: {\large\H אופן} o-phen Def: A circular frame or disk arranged to revolve on an axis, as on a wagon or chariot. \{Strong's: 212\}\hfill{}\\

\textbf{WHELP} Heb: {\large\H גור} gur \textbf{\textbackslash{}} {\large\H גורה} {[}X{]} Def: Usually a young lion. \{Strong's: 1482, 1484\}\hfill{}\\

\textbf{WHERE} Heb: {\large\H אי} ey Def: At, in, or to what place. \{Strong's: 335, 346, 351, 375\}\hfill{}\\

\textbf{WHEREIN} Heb: {\large\H זו} zu Def: A person, thing, or idea present or near in place, time, or thought or just mentioned. \{Strong's: 2098\}\hfill{}\\

\textbf{WHEREVER} Heb: {\large\H אן} an Def: Anywhere at all. A search for a person, place or time. \{Strong's: 575\}\hfill{}\\

\textbf{WHET (Verb)} Heb: {\large\H שנן} sh.n.n Def: To sharpen a knife or other cutting edge with a stone. \{Strong's: 8150\}\hfill{}\\

\textbf{WHICH} Heb: {\large\H אשר} a-sheyr Def: Or who, what or that. This word links the action of the sentence to the one doing the action. \{Strong's: 834\}\hfill{}\\

\textbf{WHIP} Heb: {\large\H פרך} pe-rek Def: To strike, in punishment or anger with a rope or cord. \{Strong's: 6531\}\hfill{}\\

\textbf{WHIRLWIND} Heb: {\large\H סופה} {[}X{]} Def: A circling wind that devours what is on the land in its mouth. \{Strong's: 5492\}\hfill{}\\

\textbf{WHISPER (Verb)} Heb: {\large\H רגן} r.g.n Def: {[}X{]} \{Strong's: 7279\}\hfill{}\\

\textbf{WHITE} Heb: {\large\H לבן} la-van \textbf{\textbackslash{}} {\large\H לבנה} le-va-nah Def: Free from color. \{Strong's: 3836\}\hfill{}\\

\textbf{WHITE.ONE} Heb: {\large\H לבנון} lev-non Def: \{Strong's: n/a\}\hfill{}\\

\textbf{WHITE.SPOT} Heb: {\large\H בהרת} {[}X{]} Def: A light colored blemish or spot on the skin and a possible sign of leprosy. \{Strong's: 934\}\hfill{}\\

\textbf{WHO} Heb: {\large\H מי} mi Def: What or which person or persons. Someone that is unknown. \{Strong's: 4310\}\hfill{}\\

\textbf{WHOLE} Heb: {\large\H תמים} ta-mim \textbf{\textbackslash{}} {\large\H תמימה} {[}X{]} Def: Free of wound or injury; free of defect or impairment; having all its proper parts or components. \{Strong's: 8549\}\hfill{}\\

\textbf{WHOREDOM} Heb: {\large\H זנות} {[}X{]} Def: As paid with food. \{Strong's: 2184\}\hfill{}\\

\textbf{WHY} Heb: {\large\H מדוע} ma-du-a Def: For what cause, purpose or reason for which. \{Strong's: 4069\}\hfill{}\\

\textbf{WICKED} Heb: {\large\H עול} ul Def: {[}X{]} \{Strong's: 5766, 5767\}\hfill{}\\

\textbf{WICKEDNESS} Heb: {\large\H עלוה} {[}X{]} Def: {[}X{]} \{Strong's: 5932\}\hfill{}\\

\textbf{WICKER.BASKET} Heb: {\large\H סל} sal Def: A receptacle made of interwoven materials such as reeds. \{Strong's: 5536\}\hfill{}\\

\textbf{WIDE} Heb: {\large\H רחב} ra-hhav Def: Having great extent or breadth. \{Strong's: 7338, 7342\}\hfill{}\\

\textbf{WIDE.OPEN (Verb)} Heb: {\large\H שתם} sh.t.m Def: {[}X{]} \{Strong's: 8365\}\hfill{}\\

\textbf{WIDEN (Verb)} Heb: {\large\H רחב} r.hh.b Def: To increase the size of an area wide; large; roomy. \{Strong's: 7337\}\hfill{}\\

\textbf{WIDOW} Heb: {\large\H אלמנה} al-ma-nah Def: A woman who has lost her husband by death. As bound in grief. \{Strong's: 490\}\hfill{}\\

\textbf{WIDOWHOOD} Heb: {\large\H אלמנות} al-me-nut Def: The quality of being a widow. As bound in grief. \{Strong's: 491\}\hfill{}\\

\textbf{WIDTH} Heb: {\large\H רוחב} ro-hhav Def: Largeness of extent or scope. From the width of a road. \{Strong's: 7341\}\hfill{}\\

\textbf{WILD.ASS} Heb: {\large\H פרא} pe-re Def: A wild animal as prolific. \{Strong's: 6501\}\hfill{}\\

\textbf{WILD.DONKEY} Heb: {\large\H ערד} {[}X{]} Def: {[}X{]} \{Strong's: 6167\}\hfill{}\\

\textbf{WILD.GOAT} Heb: {\large\H אקו} {[}X{]} Def: {[}X{]} \{Strong's: 689\}\hfill{}\\

\textbf{WILDERNESS} Heb: {\large\H מדבר} mid-bar Def: A tract or region uncultivated and uninhabited by human beings. Place of order, a sanctuary. \{Strong's: 4057\}\hfill{}\\

\textbf{WILLING} Heb: {\large\H נדיב} na-div Def: To give honor or offering out of one's own free will. \{Strong's: 5081\}\hfill{}\\

\textbf{WIND} Heb: {\large\H רוח} ru-ahh Def: A natural movement of air; breath. The breath of man, animal or God. The character. A space in between. \{Strong's: 7305, 7307\}\hfill{}\\

\textbf{WINDOW} Heb: {\large\H חלון} hha-lon Def: A hole in the wall that admits light and a view of the other side. \{Strong's: 2474\}\hfill{}\\

\textbf{WINE} Heb: {\large\H יין} ya-yin Def: Fermented juice of fresh grapes. From the mire in the wine. \{Strong's: 3196\}\hfill{}\\

\textbf{WINE.TROUGH} Heb: {\large\H יקב} {[}X{]} Def: {[}X{]} \{Strong's: 3342\}\hfill{}\\

\textbf{WINESKIN} Heb: {\large\H אוב} ov Def: A leather bag that holds wine and is hung from the pole of the tent. Can also mean ``medium'' as one who evokes the dead, a ghost, possibly from their mumbling like the sound of wine poured out of the wineskin. \{Strong's: 178\}\hfill{}\\

\textbf{WING} Heb: {\large\H כנף} ka-naph Def: An appendage that allows an animal, bird or insect to fly. Also, the wings of a garment. \{Strong's: 3671\}\hfill{}\\

\textbf{WINTER} Heb: {\large\H חורף} hho-reph Def: The season between summer and spring. Time of the piercing cold and relative bleakness. \{Strong's: 2779\}\hfill{}\\

\textbf{WIPE.AWAY (Verb)} Heb: {\large\H מחה} m.hh.h Def: To remove by drying or sweeping away through rubbing; to polish in the sense of a vigorous rubbing; erase. \{Strong's: 4229\}\hfill{}\\

\textbf{WIRE} Heb: {\large\H פח} pahh Def: A slender, string-like piece or filament of relatively rigid or flexible metal often used for snares. \{Strong's: 6341\}\hfill{}\\

\textbf{WITH} Heb: {\large\H עים} im Def: Through the idea of being together in a group. \{Strong's: 5868, 5973, 5974\}\hfill{}\\

\textbf{WITHDRAW (Verb)} Heb: {\large\H חבא} hh.b.a Def: To take back or withhold what is cherished; to turn away or move back. \{Strong's: 2244\}\hfill{}\\

\textbf{WITHER (Verb)} Heb: {\large\H צנם} ts.n.m Def: To become dry and sapless; to shrivel. \{Strong's: 6798\}\hfill{}\\

\textbf{WITHHOLD (Verb)} Heb: {\large\H מנע} m.n.ah Def: To hold back from action. \{Strong's: 4513\}\hfill{}\\

\textbf{WITHHOLDING} Heb: {\large\H תמנע} ma-na Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{WITHIN} Heb: {\large\H קרב} qe-rev Def: In the sense of being close or in the interior of. An approaching. \{Strong's: 7130, 7131\}\hfill{}\\

\textbf{WITHOUT} Heb: {\large\H אין} a-yin Def: A lacking of something or the inability to do or have something. The search for a place of unknown origin. \{Strong's: 369, 370, 371\}\hfill{}\\

\textbf{WITHOUT.EXCEPTION} Heb: {\large\H זולה} {[}X{]} Def: An exception in the sense of shaking everything out except one. \{Strong's: 2108\}\hfill{}\\

\textbf{WITNESS} Heb: {\large\H עד} eyd Def: Attestation of a fact or event. An object, person or group that affords evidence. \{Strong's: 5707\}\hfill{}\\

\textbf{WOLF} Heb: {\large\H זאב} ze-eyv Def: A yellowish colored animal. \{Strong's: 2061\}\hfill{}\\

\textbf{WOMAN} Heb: {\large\H אישה} i-shah Def: An adult female person. As mortal. \{Strong's: 802\}\hfill{}\\

\textbf{WOMB} Heb: {\large\H בטן} be-ten Def: An organ where something is generated or grows before birth. \{Strong's: 990\}\hfill{}\\

\textbf{WONDER} Heb: {\large\H מופת} mo-phet Def: An amazing sight or event that causes one to be dismayed. Something out of the ordinary. \{Strong's: 4159\}\hfill{}\\

\textbf{WOOD.BAR} Heb: {\large\H בריח} be-ri-ahh Def: Round wooden dowels. \{Strong's: 1280, 1281\}\hfill{}\\

\textbf{WOOL} Heb: {\large\H צמר} {[}X{]} Def: {[}X{]} \{Strong's: 6785\}\hfill{}\\

\textbf{WORD} Heb: {\large\H דבר} da-var Def: An arrangement of words, ideas or concepts to form sentences. A promise in the sense of being “ones word.” An action in the sense of acting out an arrangement. A plague as an act. A matter or thing. \{Strong's: 1697\}\hfill{}\\

\textbf{WORK} Heb: {\large\H מעשה} ma-a-seh Def: Activity where one exerts strength or faculties to do or perform something. An action. \{Strong's: 4639\}\hfill{}\\

\textbf{WORK.OVER (Verb)} Heb: {\large\H עלל} ah.l.l Def: To carefully and thoroughly perform a task such as gleaning a field. Also, to mock or abuse in the sense of walking over another. \{Strong's: 5953, 5954\}\hfill{}\\

\textbf{WORKING} Heb: {\large\H אצבון} {[}X{]} Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{WORKINGS} Heb: {\large\H עלילה} {[}X{]} Def: {[}X{]} \{Strong's: 5949\}\hfill{}\\

\textbf{WORKS} Heb: {\large\H מעלל} {[}X{]} Def: What is done or performed. \{Strong's: 4611\}\hfill{}\\

\textbf{WORTH} Heb: {\large\H מכסה} mikh-sah Def: The number assigned according to its amount, importance or need. \{Strong's: 4373\}\hfill{}\\

\textbf{WORTHLESS} Heb: {\large\H לאיא} {[}X{]} Def: A god or being without power. \{Strong's: 457\}\hfill{}\\

\textbf{WOULD.THAT} Heb: {\large\H לו} lu Def: In the sense of joining. A yearning for certain direction or action. \{Strong's: 3863\}\hfill{}\\

\textbf{WOUND} Heb: {\large\H פצע} pe-tsah Def: An injury involving rupture of small blood vessels and discoloration without a skin break. The dark coloring of the skin caused by being hit or smashed. \{Strong's: 6482\}\hfill{}\\

\textbf{WOUND (Verb)} Heb: {\large\H פצע} p.ts.ah Def: {[}X{]} \{Strong's: 6481\}\hfill{}\\

\textbf{WOVEN.BASKET} Heb: {\large\H צינצנת} tsin-tse-net Def: A container made from multiple pieces of material entwined together into one unit. \{Strong's: 6803\}\hfill{}\\

\textbf{WOVEN.MATERIAL} Heb: {\large\H תשבץ} tash-beyts Def: Material made from weaving threads of fibers together to become a solid piece. \{Strong's: 8665\}\hfill{}\\

\textbf{WRAP (Verb)} Heb: {\large\H עלף} ah.l.p Def: To envelop and secure for transport or storage. Also, meaning to faint. \{Strong's: 5968\}\hfill{}\\

\textbf{WRAP.AROUND (Verb)} Heb: {\large\H עוד} ah.w.d Def: To enclose; to repeat or do again what has been said or done. The hiphil (causative) form means ``warn.'' \{Strong's: 5749\}\hfill{}\\

\textbf{WRAPPER} Heb: {\large\H לוטן} {[}X{]} Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{WRATH} Heb: {\large\H עברה} ev-rah Def: Strong vengeful anger. As crossing over from peace. \{Strong's: 5678, 5679\}\hfill{}\\

\textbf{WREATH} Heb: {\large\H עטרה} {[}X{]} Def: As encircling the head. Used as a sign of authority like a crown. \{Strong's: 5850\}\hfill{}\\

\textbf{WRESTLING} Heb: {\large\H נפתול} naph-tul Def: To contend by grappling with to throw one's opponent off balance. \{Strong's: 5319\}\hfill{}\\

\textbf{WRING (Verb)} Heb: {\large\H מלק} m.l.q Def: To wring the neck. \{Strong's: 4454\}\hfill{}\\

\textbf{WRIST} Heb: {\large\H פס} pas Def: The joint between the hand and arm. Also, a garment with sleeves that reaches to the wrist. \{Strong's: 6446, 6447\}\hfill{}\\

\textbf{WRITE (Verb)} Heb: {\large\H כתב} k.t.b Def: To inscribe a story, thoughts or instructions on in a variety of mediums including stone, papyrus, leather or parchment. \{Strong's: 3789, 3790\}\hfill{}\\

\textbf{WRITING} Heb: {\large\H כתובת} {[}X{]} Def: {[}X{]} \{Strong's: 3793\}\hfill{}\\

\textbf{YA'ANAH} Heb: {\large\H יענה} {[}X{]} Def: An unknown bird. \{Strong's: 3284\}\hfill{}\\

\textbf{YAHHMOR} Heb: {\large\H יחמור} {[}X{]} Def: An unknown animal, probably from its dark color. \{Strong's: 3180\}\hfill{}\\

\textbf{YANSHOPH} Heb: {\large\H ינשוף} {[}X{]} Def: An unknown bird. \{Strong's: 3244\}\hfill{}\\

\textbf{YARN} Heb: {\large\H מטוה} mat-weh Def: Fibers that are spun together to form one strand. \{Strong's: 4299\}\hfill{}\\

\textbf{YEAR} Heb: {\large\H שנה} sha-neyh Def: The period of around 365 solar days. \{Strong's: 8140, 8141\}\hfill{}\\

\textbf{YEARN} Heb: {\large\H אוה} e-veh Def: To long persistently, wistfully, or sadly. What is desired, whether good or bad. \{Strong's: n/a\}\hfill{}\\

\textbf{YEARN (Verb)} Heb: {\large\H אוה} a.w.h Def: To have an earnest or strong desire; long. \{Strong's: 183\}\hfill{}\\

\textbf{YEARNING} Heb: {\large\H תאוה} ta-a-wah Def: To long persistently, wistfully, or sadly. What is desired, whether good or bad. \{Strong's: 8378\}\hfill{}\\

\textbf{YELL} Heb: {\large\H זעק} za-aq Def: A vehement protest; a loud cry. \{Strong's: 2201\}\hfill{}\\

\textbf{YELL.OUT (Verb)} Heb: {\large\H זעק} z.ah.q Def: To call out in a louder than normal voice; to declare; to cry out for help. \{Strong's: 2199, 2200\}\hfill{}\\

\textbf{YELLOW} Heb: {\large\H זהוב} {[}X{]} Def: {[}X{]} \{Strong's: 6669\}\hfill{}\\

\textbf{YESTERDAY} Heb: {\large\H תמול} te-mul Def: On the day last past. Idiomatic for a time past. \{Strong's: 8543\}\hfill{}\\

\textbf{YET.AGAIN} Heb: {\large\H עוד} od Def: A repeating of something. \{Strong's: 5750, 5751\}\hfill{}\\

\textbf{YIELD (Verb)} Heb: {\large\H גמל} g.m.l Def: To produce or be productive. \{Strong's: 1580\}\hfill{}\\

\textbf{YOKE} Heb: {\large\H עול} ul Def: A wooden bar or frame by which two draft animals are joined at the heads or necks for working together. \{Strong's: 5923\}\hfill{}\\

\textbf{YOKE.BREAKER} Heb: {\large\H תדעל} da-phaq Def: {[}X{]} \{Strong's: n/a\}\hfill{}\\

\textbf{YOU(FP)} Heb: {\large\H אתן} a-ten Def: Pronoun, second person, feminine plural. \{Strong's: 859\}\hfill{}\\

\textbf{YOU(FS)} Heb: {\large\H את} at Def: Pronoun, second person, feminine singular \{Strong's: 859\}\hfill{}\\

\textbf{YOU(MP)} Heb: {\large\H אתם} a-tem Def: Pronoun, second person, masculine plural. \{Strong's: 859\}\hfill{}\\

\textbf{YOU(MS)} Heb: {\large\H אתה} a-tah Def: Pronoun, second person, masculine singular. \{Strong's: 607, 608\}\hfill{}\\

\textbf{YOUNG.AGE} Heb: {\large\H נעור} na-ur Def: A person of short life. \{Strong's: 5271\}\hfill{}\\

\textbf{YOUNG.BOY} Heb: {\large\H ענר} {[}X{]} Def: A word of uncertain meaning. \{Strong's: n/a\}\hfill{}\\

\textbf{YOUNG.CAMEL} Heb: {\large\H בכר} {[}X{]} Def: A young camel. \{Strong's: 1070\}\hfill{}\\

\textbf{YOUNG.MAIDEN} Heb: {\large\H עלמה} al-mah Def: A young female of marriageable age or newly married as at the prime age for work. \{Strong's: 5959\}\hfill{}\\

\textbf{YOUNG.MAN} Heb: {\large\H נער} na-ar Def: A male that has moved from youth to young adulthood. \{Strong's: 5288, 5289\}\hfill{}\\

\textbf{YOUNG.PIGEON} Heb: {\large\H גוזל} go-zal Def: A young featherless bird as plucked. \{Strong's: 1469\}\hfill{}\\

\textbf{YOUNG.SHEEP} Heb: {\large\H עשתרה} {[}X{]} Def: A young one of the flock. \{Strong's: 6251\}\hfill{}\\

\textbf{YOUNG.WOMAN} Heb: {\large\H נערה} na-a-rah Def: A female that has moved from youth to young adulthood. \{Strong's: 5291\}\hfill{}\\

\textbf{YOUTH} Heb: {\large\H בחורות} {[}X{]} Def: A young age. \{Strong's: 979\}\hfill{}\\

\textbf{YOUTHFULNESS} Heb: {\large\H צעירה} tse-i-rah Def: Young acting no matter the age. \{Strong's: 6812\}\hfill{}\\

\textbf{ZEALOUS} Heb: {\large\H קנא} qa-nah Def: Someone who is insistent on reaching the desired outcome. Single minded. One who is protective over someone or something. \{Strong's: 7067\}\hfill{}\\

\textbf{ZEALOUSNESS} Heb: {\large\H קנאה} {[}X{]} Def: A protective or suspicious nature. \{Strong's: 7068\}\hfill{}\\

\textbf{ZEMER} Heb: {\large\H זמר} {[}X{]} Def: An unknown species of animal. \{Strong's: 2169\}\hfill{}\\

\newpage
\begin{center}
{\Large{}Names}\phantomsection{}\label{page:dictionary:names}
\end{center}

\vspace{-2ex}
\textbf{Adah} Heb: {\large\H עדה} a-dah Def: ADORNMENT \{Strong's: 5711\}\hfill{}\\

\textbf{Adbe'el} Heb: {\large\H אדבאל} ad-be-eyl Def: MIST\textasciitilde{}+\textasciitilde{}in\textasciitilde{}MIGHTY.ONE \{Strong's: 110\}\hfill{}\\

\textbf{Admah} Heb: {\large\H אדמה} ad-mah Def: GROUND \{Strong's: 126, 128\}\hfill{}\\

\textbf{Adonai} Heb: {\large\H אדוני} a-do-ni Def: LORD\textasciitilde{}s\textasciitilde{}me(cs) \{Strong's: 136\}\hfill{}\\

\textbf{Adulam} Heb: {\large\H עדולם} a-du-lam Def: WITNESS\textasciitilde{}+\textasciitilde{}and\textasciitilde{}SHEPHERD.STAFF \{Strong's: 5725, 5726\}\hfill{}\\

\textbf{Agag} Heb: {\large\H אגג} a-gag Def: I(cs)\textasciitilde{}will\textasciitilde{}OVERTOP (V) \{Strong's: 90\}\hfill{}\\

\textbf{Ahalivamah} Heb: {\large\H אהליבמה} a-ha-li-va-mah Def: TENT\textasciitilde{}of\textasciitilde{}+\textasciitilde{}PLATFORM \{Strong's: 173\}\hfill{}\\

\textbf{Ahaliyav} Heb: {\large\H אהליאב} a-ha-li-av Def: TENT\textasciitilde{}of\textasciitilde{}+\textasciitilde{}FATHER \{Strong's: 171\}\hfill{}\\

\textbf{Aharon} Heb: {\large\H אהרון} a-ha-ron Def: LIGHT.BRINGER \{Strong's: 175\}\hfill{}\\

\textbf{Ahhi'ezer} Heb: {\large\H אחיעזר} a-hhi-e-zer Def: BROTHER\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}HELP \{Strong's: 295\}\hfill{}\\

\textbf{Ahhihud} Heb: {\large\H אחיהוד} a-hhi-hud Def: BROTHER\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}SPLENDOR \{Strong's: 282\}\hfill{}\\

\textbf{Ahhiman} Heb: {\large\H אחימן} a-hhi-man Def: BROTHER\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}SHARE \{Strong's: 289\}\hfill{}\\

\textbf{Ahhira} Heb: {\large\H אחירע} a-hhi-ra Def: BROTHER\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}DYSFUNCTIONAL \{Strong's: 299\}\hfill{}\\

\textbf{Ahhiram} Heb: {\large\H אחירם} a-hhi-ram Def: BROTHER\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}RAISED \{Strong's: 297, 298\}\hfill{}\\

\textbf{Ahhiysamahh} Heb: {\large\H אחיסמך} a-hhi-sa-mak Def: BROTHER\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}he\textasciitilde{}did\textasciitilde{}SUPPORT (V) \{Strong's: 294\}\hfill{}\\

\textbf{Ahhuzat} Heb: {\large\H אחוזת} a-hhu-zat Def: HOLDINGS \{Strong's: 276\}\hfill{}\\

\textbf{Akad} Heb: {\large\H אכד} a-kad Def: DELICATE \{Strong's: 390\}\hfill{}\\

\textbf{Akhbor} Heb: {\large\H עכבור} akh-bor Def: MOUSE \{Strong's: 5907\}\hfill{}\\

\textbf{Akhran} Heb: {\large\H עכרן} akh-ran Def: DISTURBED.ONE \{Strong's: 5918\}\hfill{}\\

\textbf{Almodad} Heb: {\large\H אלמודד} al-mo-dad Def: MIGHTY.ONE\textasciitilde{}+\textasciitilde{}MEASURING \{Strong's: 486\}\hfill{}\\

\textbf{Almon} Heb: {\large\H עלמון} al-mon Def: OUT.OF.SIGHT \{Strong's: 5960, 5963\}\hfill{}\\

\textbf{Alon-Bakhut} Heb: {\large\H אלון.בכות} a-lon ba-khut Def: GREAT.TREE\textasciitilde{}+\textasciitilde{}WEEPING \{Strong's: 439\}\hfill{}\\

\textbf{Alush} Heb: {\large\H אלוש} a-lush Def: I(cs)\textasciitilde{}will\textasciitilde{}KNEAD (V) \{Strong's: 442\}\hfill{}\\

\textbf{Alwah} Heb: {\large\H עלוה} al-wah Def: WICKEDNESS \{Strong's: 5933\}\hfill{}\\

\textbf{Alwan} Heb: {\large\H עלון} al-wan Def: LOFT \{Strong's: 5935\}\hfill{}\\

\textbf{Amaleq} Heb: {\large\H עמלק} a-me-leq Def: PEOPLE\textasciitilde{}+\textasciitilde{}GATHERED.UP \{Strong's: 6002, 6003\}\hfill{}\\

\textbf{Ami'eyl} Heb: {\large\H עמיאל} a-mi-eyl Def: PEOPLE\textasciitilde{}of\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 5988\}\hfill{}\\

\textbf{Amihud} Heb: {\large\H עמיהוד} a-mi-hud Def: PEOPLE\textasciitilde{}of\textasciitilde{}+\textasciitilde{}SPLENDOR \{Strong's: 5989\}\hfill{}\\

\textbf{Amishadai} Heb: {\large\H עמישדי} a-mi-sha-dai Def: PEOPLE\textasciitilde{}of\textasciitilde{}+\textasciitilde{}BREAST\textasciitilde{}s\textasciitilde{}me(cs) \{Strong's: 5996\}\hfill{}\\

\textbf{Amiynadav} Heb: {\large\H עמינדב} a-mi-na-dav Def: PEOPLE\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}OFFERED.WILLINGLY \{Strong's: 5992\}\hfill{}\\

\textbf{Amon} Heb: {\large\H עמון} a-mon Def: TRIBAL \{Strong's: 5983, 5984, 5985\}\hfill{}\\

\textbf{Amram} Heb: {\large\H עמרם} am-ram Def: PEOPLE\textasciitilde{}+\textasciitilde{}RAISED \{Strong's: 6019\}\hfill{}\\

\textbf{Amraphel} Heb: {\large\H אמרפל} am-ra-phel Def: SAYERFALL \{Strong's: 569\}\hfill{}\\

\textbf{Anah} Heb: {\large\H ענה} a-nah Def: ANSWERED \{Strong's: 6034\}\hfill{}\\

\textbf{Anam} Heb: {\large\H ענם} a-nam Def: AFFLICTION\textasciitilde{}+\textasciitilde{}WATER\textasciitilde{}s2 \{Strong's: 6047\}\hfill{}\\

\textbf{Anaq} Heb: {\large\H ענק} a-naq Def: NECK.BAND \{Strong's: 6061, 6062\}\hfill{}\\

\textbf{Aner} Heb: {\large\H ענר} a-ner Def: YOUNG.BOY \{Strong's: 6063\}\hfill{}\\

\textbf{Aqan} Heb: {\large\H עקן} a-qan Def: SHARP.SIGHTED \{Strong's: 6130\}\hfill{}\\

\textbf{Ar} Heb: {\large\H ער} ar Def: ENEMY \{Strong's: 6144\}\hfill{}\\

\textbf{Arad} Heb: {\large\H ערד} a-rad Def: WILD.DONKEY \{Strong's: 6166\}\hfill{}\\

\textbf{Aram} Heb: {\large\H ארם} a-ram Def: PALACE \{Strong's: 758\}\hfill{}\\

\textbf{Aram-Nahara'im} Heb: {\large\H ארם.נהרים} a-ram na-ha-ra-yim Def: PALACE\textasciitilde{}+\textasciitilde{}RIVER\textasciitilde{}s2 \{Strong's: 763\}\hfill{}\\

\textbf{Aran} Heb: {\large\H ארן} a-ran Def: I(cs)\textasciitilde{}will\textasciitilde{}SHOUT.ALOUD (V) \{Strong's: 765\}\hfill{}\\

\textbf{Araq} Heb: {\large\H ערק} a-raq Def: GNAWED \{Strong's: 6208\}\hfill{}\\

\textbf{Ararat} Heb: {\large\H אררט} a-ra-rat Def: HIGH.LAND \{Strong's: 780\}\hfill{}\\

\textbf{Ard} Heb: {\large\H ארד} ard Def: I(cs)\textasciitilde{}will\textasciitilde{}GO.DOWN (V) \{Strong's: 714\}\hfill{}\\

\textbf{Areliy} Heb: {\large\H אראלי} ar-ey-li Def: LION\textasciitilde{}+\textasciitilde{}MIGHTY.ONE\textasciitilde{}me(cs) \{Strong's: 692\}\hfill{}\\

\textbf{Argov} Heb: {\large\H ארגוב} ar-gov Def: I(cs)\textasciitilde{}will\textasciitilde{}CLOD (V) \{Strong's: 709\}\hfill{}\\

\textbf{Arnon} Heb: {\large\H ארנון} ar-non Def: I(cs)\textasciitilde{}will\textasciitilde{}SHOUT.ALOUD (V) \{Strong's: 769\}\hfill{}\\

\textbf{Arodiy} Heb: {\large\H ארודי} a-ro-di Def: ROAMING\textasciitilde{}me(cs) \{Strong's: 722\}\hfill{}\\

\textbf{Aro'eyr} Heb: {\large\H ערוער} ar-o-eyr Def: UNPROTECTED \{Strong's: 6177\}\hfill{}\\

\textbf{Arpakhshad} Heb: {\large\H ארפכשד} ar-pakh-shad Def: I(cs)\textasciitilde{}will\textasciitilde{}DECLINE (V)\textasciitilde{}+\textasciitilde{}BREAST \{Strong's: 775\}\hfill{}\\

\textbf{Arwad} Heb: {\large\H ארוד} ar-wad Def: ROAMING \{Strong's: 719, 721\}\hfill{}\\

\textbf{Aryokh} Heb: {\large\H אריוך} a-ri-okh Def: LION.LIKE \{Strong's: 746\}\hfill{}\\

\textbf{Ashbeyl} Heb: {\large\H אשבל} ash-beyl Def: I(cs)\textasciitilde{}will\textasciitilde{}EXCHANGE (V) \{Strong's: 788\}\hfill{}\\

\textbf{Asher} Heb: {\large\H אשר} a-sher Def: HAPPY \{Strong's: 836\}\hfill{}\\

\textbf{Ashkanaz} Heb: {\large\H אשכנז} ash-ke-naz Def: FIRE\textasciitilde{}+\textasciitilde{}SPRINKLED \{Strong's: 813\}\hfill{}\\

\textbf{Ashterot-Qar'nayim} Heb: {\large\H עשתרות.קרנים} ash-te-rot qar-na-yim Def: YOUNG.SHEEP\textasciitilde{}s\textasciitilde{}+\textasciitilde{}HORN\textasciitilde{}s2 \{Strong's: 6255\}\hfill{}\\

\textbf{Ashur} Heb: {\large\H אשור} a-shur Def: HAPPY \{Strong's: 804\}\hfill{}\\

\textbf{Asiyr} Heb: {\large\H אסיר} a-sir Def: PRISONER \{Strong's: 617\}\hfill{}\\

\textbf{Asnat} Heb: {\large\H אסנת} as-nat Def: BELONGING.TO.NAT \{Strong's: 621\}\hfill{}\\

\textbf{Asri'eyl} Heb: {\large\H אסריאל} as-ri-eyl Def: HAPPY (V)\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 844, 845\}\hfill{}\\

\textbf{Atarot} Heb: {\large\H עטרות} a-ta-rot Def: WREATH\textasciitilde{}s \{Strong's: 5852\}\hfill{}\\

\textbf{Atsmon} Heb: {\large\H עצמון} ats-mon Def: ABUNDANT.ONE \{Strong's: 6111\}\hfill{}\\

\textbf{Aveyl-Mitsrayim} Heb: {\large\H אבל.מצרים} a-veyl mits-ra-yim Def: MOURNING\textasciitilde{}+\textasciitilde{}STRAIT\textasciitilde{}s2 \{Strong's: 67\}\hfill{}\\

\textbf{Avida} Heb: {\large\H אבידע} a-viy-da Def: FATHER\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}he\textasciitilde{}did\textasciitilde{}KNOW (V) \{Strong's: 28\}\hfill{}\\

\textbf{Avidan} Heb: {\large\H אבידן} a-vi-dan Def: FATHER\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}MODERATOR \{Strong's: 27\}\hfill{}\\

\textbf{Avihha'il} Heb: {\large\H אביחיל} a-vi-hha-yil Def: FATHER\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}FORCE \{Strong's: 32\}\hfill{}\\

\textbf{Aviram} Heb: {\large\H אבירם} a-vi-ram Def: FATHER\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}RAISED \{Strong's: 48\}\hfill{}\\

\textbf{Aviyasaph} Heb: {\large\H אביאסף} a-vi-a-saph Def: FATHER\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}he\textasciitilde{}did\textasciitilde{}GATHER (V) \{Strong's: 23\}\hfill{}\\

\textbf{Aviyhu} Heb: {\large\H אביהוא} a-vi-hu Def: FATHER\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}HE \{Strong's: 30\}\hfill{}\\

\textbf{Aviyma'el} Heb: {\large\H אבימאל} a-vi-ma-eyl Def: FATHER\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}from\textasciitilde{}MIGHTY.ONE \{Strong's: 39\}\hfill{}\\

\textbf{Aviymelekh} Heb: {\large\H אבימלך} a-viy-me-lekh Def: FATHER\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}KING \{Strong's: 40\}\hfill{}\\

\textbf{Avraham} Heb: {\large\H אברהם} av-ra-ham Def: FATHER\textasciitilde{}+\textasciitilde{}LIFTED \{Strong's: 85\}\hfill{}\\

\textbf{Avram} Heb: {\large\H אברם} av-ram Def: FATHER\textasciitilde{}+\textasciitilde{}RAISED \{Strong's: 87\}\hfill{}\\

\textbf{Awi} Heb: {\large\H עוי} a-wi Def: TWIST \{Strong's: 5757, 5761\}\hfill{}\\

\textbf{Awit} Heb: {\large\H עיות} a-wit Def: RUINED.HEAP\textasciitilde{}s \{Strong's: 5762\}\hfill{}\\

\textbf{Ay} Heb: {\large\H עי} ai Def: RUINED.HEAP \{Strong's: 5857\}\hfill{}\\

\textbf{Ayah} Heb: {\large\H איה} ai-yah Def: HAWK \{Strong's: 345\}\hfill{}\\

\textbf{Azan} Heb: {\large\H עזן} a-zan Def: STRONG.ONE \{Strong's: 5821\}\hfill{}\\

\textbf{Azazeyl} Heb: {\large\H עזאזל} a-za-zeyl Def: STRONG\textasciitilde{}+\textasciitilde{}>\textasciitilde{}WAVER (V) \{Strong's: 5799\}\hfill{}\\

\textbf{Azni} Heb: {\large\H אזני} az-ni Def: EAR\textasciitilde{}me(cs) \{Strong's: 241, 244\}\hfill{}\\

\textbf{Ba'al} Heb: {\large\H בעל} ba-al Def: MASTER \{Strong's: 1168\}\hfill{}\\

\textbf{Ba'al-Hhanan} Heb: {\large\H בעל.חנן} ba-al hha-nan Def: MASTER\textasciitilde{}+\textasciitilde{}BEAUTY \{Strong's: 1177\}\hfill{}\\

\textbf{Ba'al-Tsephon} Heb: {\large\H בעל.צפון} ba-al tse-phon Def: MASTER\textasciitilde{}+\textasciitilde{}NORTH \{Strong's: 1189\}\hfill{}\\

\textbf{Balaq} Heb: {\large\H בלק} ba-laq Def: he\textasciitilde{}did\textasciitilde{}LAY.WASTE (V) \{Strong's: 1111\}\hfill{}\\

\textbf{Barneya} Heb: {\large\H ברנע} bar-ney-a Def: GRAIN\textasciitilde{}+\textasciitilde{}RATTLE \{Strong's: 6947\}\hfill{}\\

\textbf{Bashan} Heb: {\large\H בשן} ba-shan Def: SHAME \{Strong's: 1316\}\hfill{}\\

\textbf{Basmat} Heb: {\large\H בסמת} bas-mat Def: FRAGRANCE \{Strong's: 1315\}\hfill{}\\

\textbf{Bavel} Heb: {\large\H בבל} ba-vel Def: MIXED.UP \{Strong's: 894\}\hfill{}\\

\textbf{Bedad} Heb: {\large\H בדד} be-dad Def: ALONE \{Strong's: 911\}\hfill{}\\

\textbf{Be'eri} Heb: {\large\H בארי} be-ey-ri Def: WELL\textasciitilde{}me(cs) \{Strong's: 882\}\hfill{}\\

\textbf{Be'er-Lahhiy-Ro'iy} Heb: {\large\H באר.לחי.רואי} be-eyr la-hhai ro-iy Def: WELL\textasciitilde{}+\textasciitilde{}to\textasciitilde{}LIVING\textasciitilde{}+\textasciitilde{}SEE (V)\textasciitilde{}ing(ms)\textasciitilde{}me(cs) \{Strong's: 883\}\hfill{}\\

\textbf{Bekher} Heb: {\large\H בכר} be-kher Def: YOUNG.CAMEL \{Strong's: 1071\}\hfill{}\\

\textbf{Bela} Heb: {\large\H בלע} be-la Def: SWALLOWED \{Strong's: 1106\}\hfill{}\\

\textbf{Beli'ya'al} Heb: {\large\H בליעל} be-li-ya-al Def: UNAWARE\textasciitilde{}+\textasciitilde{}he\textasciitilde{}will\textasciitilde{}RISE.ABOVE (V) \{Strong's: 1100\}\hfill{}\\

\textbf{Ben-Amiy} Heb: {\large\H בן.עמי} ben a-miy Def: SON\textasciitilde{}+\textasciitilde{}PEOPLE\textasciitilde{}me(cs) \{Strong's: 1151\}\hfill{}\\

\textbf{Ben-Oni} Heb: {\large\H בן.אוני} ben o-niy Def: SON\textasciitilde{}+\textasciitilde{}VIGOR\textasciitilde{}me(cs) \{Strong's: 1126\}\hfill{}\\

\textbf{Be'on} Heb: {\large\H בעון} be-on Def: in\textasciitilde{}COHABITATION \{Strong's: 1194\}\hfill{}\\

\textbf{Be'or} Heb: {\large\H בעור} be-or Def: IGNITING \{Strong's: 1160\}\hfill{}\\

\textbf{Bera} Heb: {\large\H ברע} be-ra Def: in\textasciitilde{}DYSFUNCTIONAL \{Strong's: 1298\}\hfill{}\\

\textbf{Bered} Heb: {\large\H ברד} be-red Def: HAILSTONES \{Strong's: 1260\}\hfill{}\\

\textbf{Beri'ah} Heb: {\large\H בריעה} be-ri-ah Def: in\textasciitilde{}COMPANION \{Strong's: 1283\}\hfill{}\\

\textbf{B'er-Sheva} Heb: {\large\H באר.שבע} be-er she-va Def: WELL\textasciitilde{}+\textasciitilde{}SEVEN \{Strong's: 884\}\hfill{}\\

\textbf{Betsaleyl} Heb: {\large\H בצלאל} be-tsa-leyl Def: in\textasciitilde{}SHADOW\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 1212\}\hfill{}\\

\textbf{Betser} Heb: {\large\H בצר} be-tser Def: PRECIOUS.METAL \{Strong's: 1221\}\hfill{}\\

\textbf{Betu'el} Heb: {\large\H בתואל} be-tu-eyl Def: HOUSE\textasciitilde{}them(mp)\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 1328\}\hfill{}\\

\textbf{Beyt-El} Heb: {\large\H בית.אל} beyt eyl Def: HOUSE\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 1008\}\hfill{}\\

\textbf{Beyt-Lehhem} Heb: {\large\H בית.לחם} beyt le-hhem Def: HOUSE\textasciitilde{}+\textasciitilde{}BREAD \{Strong's: 1035\}\hfill{}\\

\textbf{Bilam} Heb: {\large\H בילעם} bil-am Def: NONE\textasciitilde{}+\textasciitilde{}PEOPLE \{Strong's: 1109\}\hfill{}\\

\textbf{Bilhah} Heb: {\large\H בילהה} bil-hah Def: DISMAY \{Strong's: 1090\}\hfill{}\\

\textbf{Bilhan} Heb: {\large\H בילהן} bil-han Def: DISMAY\textasciitilde{}them(fp) \{Strong's: 1092\}\hfill{}\\

\textbf{Binyamin} Heb: {\large\H בינימין} bin-ya-min Def: SON\textasciitilde{}+\textasciitilde{}RIGHT.HAND \{Strong's: 1144\}\hfill{}\\

\textbf{Birsha} Heb: {\large\H ברשע} bir-sha Def: in\textasciitilde{}LOST \{Strong's: 1306\}\hfill{}\\

\textbf{Botsrah} Heb: {\large\H בוצרה} bots-rah Def: SHEEP.PEN \{Strong's: 1224\}\hfill{}\\

\textbf{Buqi} Heb: {\large\H בוקי} bu-qi Def: VACANT \{Strong's: 1231\}\hfill{}\\

\textbf{Buz} Heb: {\large\H בוז} buz Def: DESPISED \{Strong's: 938\}\hfill{}\\

\textbf{Dameseq} Heb: {\large\H דמסק} dam-seq Def: BLOOD\textasciitilde{}+\textasciitilde{}SACK \{Strong's: 1834\}\hfill{}\\

\textbf{Dan} Heb: {\large\H דן} dan Def: MODERATOR \{Strong's: 1835\}\hfill{}\\

\textbf{Daphqah} Heb: {\large\H דפקה} daph-qah Def: she\textasciitilde{}did\textasciitilde{}BEAT.OUT (V) \{Strong's: 1850\}\hfill{}\\

\textbf{Datan} Heb: {\large\H דתן} da-tan Def: TWO.WELLS \{Strong's: 1885\}\hfill{}\\

\textbf{Dedan} Heb: {\large\H דדן} de-dan Def: LOW.COUNTRY \{Strong's: 1719\}\hfill{}\\

\textbf{De'u'eyl} Heb: {\large\H דעואל} de-u-eyl Def: they(cp)\textasciitilde{}did\textasciitilde{}KNOW (V)\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 1845\}\hfill{}\\

\textbf{Devorah} Heb: {\large\H דבורה} de-vo-rah Def: BEE \{Strong's: 1683\}\hfill{}\\

\textbf{Di} Heb: {\large\H די} di Def: SUFFICIENT \{Strong's: 1774\}\hfill{}\\

\textbf{Dibon} Heb: {\large\H דיבון} di-bon Def: BROODING \{Strong's: 1769\}\hfill{}\\

\textbf{Dinah} Heb: {\large\H דינה} di-nah Def: PLEA \{Strong's: 1783\}\hfill{}\\

\textbf{Dinhavah} Heb: {\large\H דינהבה} din-ha-vah Def: PLEA\textasciitilde{}+\textasciitilde{}GIFT.OFFERING \{Strong's: 1838\}\hfill{}\\

\textbf{Diqlah} Heb: {\large\H דיקלה} diq-lah Def: PALM.GROVE \{Strong's: 1853\}\hfill{}\\

\textbf{Dishan} Heb: {\large\H דישן} di-shan Def: THRESHER \{Strong's: 1789\}\hfill{}\\

\textbf{Dishon} Heb: {\large\H דישון} di-shon Def: THRESHER \{Strong's: 1787\}\hfill{}\\

\textbf{Divlatayim} Heb: {\large\H דבלתים} div-la-ta-yim Def: CAKE\textasciitilde{}s2 \{Strong's: 2583\}\hfill{}\\

\textbf{Dodan} Heb: {\large\H דודן} do-dan Def: LOW.COUNTRY \{Strong's: 1721\}\hfill{}\\

\textbf{Dotan} Heb: {\large\H דותן} do-tan Def: TWO.WELLS \{Strong's: 1886\}\hfill{}\\

\textbf{Dumah} Heb: {\large\H דומה} du-mah Def: SILENCED \{Strong's: 1746\}\hfill{}\\

\textbf{Eden} Heb: {\large\H עדן} e-den Def: PLEASURE \{Strong's: 5731\}\hfill{}\\

\textbf{Edom} Heb: {\large\H אדום} e-dom Def: RED \{Strong's: 123, 130\}\hfill{}\\

\textbf{Ed're'i} Heb: {\large\H אדרעי} ed-re-i Def: ROBE\textasciitilde{}+\textasciitilde{}RUINED.HEAP \{Strong's: 154\}\hfill{}\\

\textbf{Ehyeh} Heb: {\large\H אהיה} eh-yeh Def: I(cs)\textasciitilde{}will\textasciitilde{}EXIST (V) \{Strong's: n/a\}\hfill{}\\

\textbf{Elaley} Heb: {\large\H אלעלא} el-a-ley Def: MIGHTY.ONE\textasciitilde{}+\textasciitilde{}>\textasciitilde{}GO.UP (V) \{Strong's: 500\}\hfill{}\\

\textbf{Elam} Heb: {\large\H עילם} e-lam Def: ANCIENT \{Strong's: 5867\}\hfill{}\\

\textbf{Elasar} Heb: {\large\H אלסר} el-la-sar Def: MIGHTY.ONE\textasciitilde{}+\textasciitilde{}NOBLE \{Strong's: 495\}\hfill{}\\

\textbf{Elazar} Heb: {\large\H אלעזר} el-a-zar Def: MIGHTY.ONE\textasciitilde{}+\textasciitilde{}he\textasciitilde{}did\textasciitilde{}HELP (V) \{Strong's: 499\}\hfill{}\\

\textbf{El-Beyt-El} Heb: {\large\H אל.בית.אל} eyl beyt eyl Def: MIGHTY.ONE\textasciitilde{}+\textasciitilde{}HOUSE\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 416\}\hfill{}\\

\textbf{Elda'ah} Heb: {\large\H אלדעה} el-da-ah Def: MIGHTY.ONE\textasciitilde{}+\textasciitilde{}he\textasciitilde{}did\textasciitilde{}KNOW (V) \{Strong's: 420\}\hfill{}\\

\textbf{Eldad} Heb: {\large\H אלדד} el-dad Def: MIGHTY.ONE\textasciitilde{}+\textasciitilde{}TEAT \{Strong's: 419\}\hfill{}\\

\textbf{El-Elohey-Yisra'el} Heb: {\large\H אל.אלהי.יסראל} eyl e-lo-hey yis-ra-eyl\\\hspace{0.25in}Def: MIGHTY.ONE\textasciitilde{}+\textasciitilde{}POWER\textasciitilde{}s\textasciitilde{}+\textasciitilde{}he\textasciitilde{}will\textasciitilde{}TURN.ASIDE (V)\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 415\}\hfill{}\\

\textbf{Eli'av} Heb: {\large\H אליאב} e-li-av Def: MIGHTY.ONE\textasciitilde{}+\textasciitilde{}FATHER \{Strong's: 446\}\hfill{}\\

\textbf{Elidad} Heb: {\large\H אלידד} e-li-dad Def: MIGHTY.ONE\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}TEAT \{Strong's: 449\}\hfill{}\\

\textbf{Eli'ezer} Heb: {\large\H אליעזר} e-li-e-zer Def: MIGHTY.ONE\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}he\textasciitilde{}did\textasciitilde{}HELP (V) \{Strong's: 461\}\hfill{}\\

\textbf{Eliphaz} Heb: {\large\H אליפז} e-li-phaz Def: MIGHTY.ONE\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}PURE.GOLD \{Strong's: 464\}\hfill{}\\

\textbf{Elishah} Heb: {\large\H אלישה} e-li-shah Def: MIGHTY.ONE\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}EQUATED \{Strong's: 473\}\hfill{}\\

\textbf{Elishama} Heb: {\large\H אלישמע} e-li-sha-ma Def: MIGHTY.ONE\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}he\textasciitilde{}did\textasciitilde{}HEAR (V) \{Strong's: 476\}\hfill{}\\

\textbf{Elitsaphan} Heb: {\large\H אליצפן} e-li-tsa-phan Def: MIGHTY.ONE\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}he\textasciitilde{}did\textasciitilde{}CONCEAL (V) \{Strong's: 469\}\hfill{}\\

\textbf{Elitsur} Heb: {\large\H אליצור} e-li-tsur Def: MIGHTY.ONE\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}BOULDER \{Strong's: 468\}\hfill{}\\

\textbf{Eliysheva} Heb: {\large\H אלישבע} e-li-she-va Def: MIGHTY.ONE\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}he\textasciitilde{}did\textasciitilde{}SWEAR (V) \{Strong's: 472\}\hfill{}\\

\textbf{Elohiym} Heb: {\large\H אלוהים} e-lo-him Def: POWER\textasciitilde{}s \{Strong's: 430\}\hfill{}\\

\textbf{Elqanah} Heb: {\large\H אלקנה} el-qa-nah Def: MIGHTY.ONE\textasciitilde{}+\textasciitilde{}he\textasciitilde{}did\textasciitilde{}PURCHASE (V) \{Strong's: 511\}\hfill{}\\

\textbf{El-Ra'iy} Heb: {\large\H אל.ראי} el ra-iy Def: MIGHTY.ONE\textasciitilde{}+\textasciitilde{}he\textasciitilde{}did\textasciitilde{}SEE (V)\textasciitilde{}me(cs) \{Strong's: n/a\}\hfill{}\\

\textbf{El'tsaphan} Heb: {\large\H אלצפן} el-tsa-phan Def: MIGHTY.ONE\textasciitilde{}+\textasciitilde{}he\textasciitilde{}did\textasciitilde{}CONCEAL (V) \{Strong's: 469\}\hfill{}\\

\textbf{Elyasaph} Heb: {\large\H אליסף} el-ya-saph Def: MIGHTY.ONE\textasciitilde{}+\textasciitilde{}he\textasciitilde{}did\textasciitilde{}ADD (V) \{Strong's: 460\}\hfill{}\\

\textbf{Emor} Heb: {\large\H אמור} e-mor Def: SAYER \{Strong's: 567\}\hfill{}\\

\textbf{Enosh} Heb: {\large\H אנוש} e-nosh Def: PERSON \{Strong's: 583\}\hfill{}\\

\textbf{Epher} Heb: {\large\H עפר} e-pher Def: POWDER \{Strong's: 6081\}\hfill{}\\

\textbf{Ephrat} Heb: {\large\H אפרת} eph-rat Def: I(cs)\textasciitilde{}will\textasciitilde{}INTERPRET (V) \{Strong's: 672\}\hfill{}\\

\textbf{Ephrayim} Heb: {\large\H אפרים} eph-ra-yim Def: ASH\textasciitilde{}s2 \{Strong's: 669\}\hfill{}\\

\textbf{Ephron} Heb: {\large\H עפרון} eph-ron Def: POWDERY \{Strong's: 6085\}\hfill{}\\

\textbf{Erekh} Heb: {\large\H ארך} e-rekh Def: SLOW \{Strong's: 751\}\hfill{}\\

\textbf{Esaw} Heb: {\large\H עסו} e-saw Def: DOING \{Strong's: 6215\}\hfill{}\\

\textbf{Eseq} Heb: {\large\H עסק} e-seq Def: STRIFE \{Strong's: 6230\}\hfill{}\\

\textbf{Eshban} Heb: {\large\H אשבן} esh-ban Def: I(cs)\textasciitilde{}will\textasciitilde{}GROW (V) \{Strong's: 790\}\hfill{}\\

\textbf{Eshkol} Heb: {\large\H אשכול} esh-kol Def: CLUSTER \{Strong's: 812\}\hfill{}\\

\textbf{Etsbon} Heb: {\large\H אצבון} ets-bon Def: WORKING \{Strong's: 675\}\hfill{}\\

\textbf{Etsi'on} Heb: {\large\H עציון} e-tsi-on Def: BACKBONE \{Strong's: 6100\}\hfill{}\\

\textbf{Ever} Heb: {\large\H עבר} e-ver Def: OTHER.SIDE \{Strong's: 5677, 5680, 5681, 5682\}\hfill{}\\

\textbf{Evronah} Heb: {\large\H עברונה} ev-ro-nah Def: CROSSING.ONE \{Strong's: 5684\}\hfill{}\\

\textbf{Ewi} Heb: {\large\H אוי} e-wi Def: YEARN\textasciitilde{}me(cs) \{Strong's: 189\}\hfill{}\\

\textbf{Eyhhiy} Heb: {\large\H אחי} a-hhi Def: BROTHER\textasciitilde{}me(cs) \{Strong's: 278\}\hfill{}\\

\textbf{Eylah} Heb: {\large\H אלה} ey-lah Def: OAK \{Strong's: 425\}\hfill{}\\

\textbf{Eyliym} Heb: {\large\H אילים} ey-lim Def: BUCK\textasciitilde{}s \{Strong's: 362\}\hfill{}\\

\textbf{Eylon} Heb: {\large\H אילון} ey-lon Def: OAK.TREE \{Strong's: 356\}\hfill{}\\

\textbf{Eylot} Heb: {\large\H אילות} ey-lot Def: DOE\textasciitilde{}s \{Strong's: 359\}\hfill{}\\

\textbf{Eyl-Paran} Heb: {\large\H איל.פארן} eyl pa-ran Def: BUCK\textasciitilde{}+\textasciitilde{}DECORATED \{Strong's: 364\}\hfill{}\\

\textbf{Eym} Heb: {\large\H אים} eym Def: TERROR \{Strong's: 368\}\hfill{}\\

\textbf{Eynan} Heb: {\large\H עינן} ey-nan Def: HAVING.AN.EYE \{Strong's: 5851\}\hfill{}\\

\textbf{Eynayim} Heb: {\large\H עינים} ey-na-yim Def: EYE\textasciitilde{}s2 \{Strong's: 5879\}\hfill{}\\

\textbf{Eyn-Mishpat} Heb: {\large\H עין.משפט} eyn mish-pat Def: EYE\textasciitilde{}+\textasciitilde{}DECISION \{Strong's: 5880\}\hfill{}\\

\textbf{Eyphah} Heb: {\large\H עיפה} ey-phah Def: MURKINESS \{Strong's: 5891\}\hfill{}\\

\textbf{Eyr} Heb: {\large\H ער} eyr Def: BARE.SKIN \{Strong's: 6147\}\hfill{}\\

\textbf{Eyran} Heb: {\large\H ערן} ey-ran Def: BARE.ONE \{Strong's: 6197\}\hfill{}\\

\textbf{Eyriy} Heb: {\large\H ערי} ey-ri Def: BARE.SKIN\textasciitilde{}me(cs) \{Strong's: 6179, 6180\}\hfill{}\\

\textbf{Eyshdat} Heb: {\large\H אשדת} eysh-dat Def: FIRE\textasciitilde{}+\textasciitilde{}LAW \{Strong's: 799+1881\}\hfill{}\\

\textbf{Eytam} Heb: {\large\H אתם} ey-tam Def: PLOWSHARE\textasciitilde{}them(mp) \{Strong's: 864\}\hfill{}\\

\textbf{Eytser} Heb: {\large\H אצר} ey-tser Def: he\textasciitilde{}did\textasciitilde{}STORE.UP (V) \{Strong's: 687\}\hfill{}\\

\textbf{Eyval} Heb: {\large\H עיבל} ey-val Def: ROUND.STONE \{Strong's: 5858\}\hfill{}\\

\textbf{Gad} Heb: {\large\H גד} gad Def: FORTUNE \{Strong's: 1410\}\hfill{}\\

\textbf{Gadi'eyl} Heb: {\large\H גדיאל} ga-di-eyl Def: FORTUNE\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 1427\}\hfill{}\\

\textbf{Gahham} Heb: {\large\H גחם} ga-hham Def: BURNT \{Strong's: 1514\}\hfill{}\\

\textbf{Galeyd} Heb: {\large\H גלעד} gal-eyd Def: MOUND\textasciitilde{}+\textasciitilde{}WITNESS \{Strong's: 1567\}\hfill{}\\

\textbf{Gamli'eyl} Heb: {\large\H גמליאל} gam-li-eyl Def: CAMEL\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 1583\}\hfill{}\\

\textbf{Gatam} Heb: {\large\H געתם} ga-tam Def: BURNT.VALLEY \{Strong's: 1609\}\hfill{}\\

\textbf{Gemali} Heb: {\large\H גמלי} ge-ma-li Def: CAMEL\textasciitilde{}me(cs) \{Strong's: 1582\}\hfill{}\\

\textbf{Gera} Heb: {\large\H גרא} gey-ra Def: SEED.OF.GRAIN \{Strong's: 1617\}\hfill{}\\

\textbf{Gerar} Heb: {\large\H גרר} ge-rar Def: CHEWED \{Strong's: 1642\}\hfill{}\\

\textbf{Gerizim} Heb: {\large\H גרזים} ge-ri-zim Def: CUTTING\textasciitilde{}s \{Strong's: 1630\}\hfill{}\\

\textbf{Gershom} Heb: {\large\H גרשום} ger-shom Def: EVICTED \{Strong's: 1647\}\hfill{}\\

\textbf{Gershon} Heb: {\large\H גרשון} ger-shon Def: EVICTED \{Strong's: 1648\}\hfill{}\\

\textbf{Geshur} Heb: {\large\H גשור} ge-shur Def: PROUD.BEHOLDER \{Strong's: 1650, 1651\}\hfill{}\\

\textbf{Getar} Heb: {\large\H גתר} ge-ter Def: AGITATED \{Strong's: 1666\}\hfill{}\\

\textbf{Ge'u'eyl} Heb: {\large\H גאואל} ge-u-eyl Def: !(ms)\textasciitilde{}RISE.UP (V)\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 1345\}\hfill{}\\

\textbf{Ghamorah} Heb: {\large\H עמורה} gha-mo-rah Def: SUBMERSION \{Strong's: 6017\}\hfill{}\\

\textbf{Ghaza} Heb: {\large\H עזה} gha-za Def: SHE.GOAT \{Strong's: 5804\}\hfill{}\\

\textbf{Ghir} Heb: {\large\H עיר} ghir Def: CITY \{Strong's: 5893\}\hfill{}\\

\textbf{Gidgad} Heb: {\large\H גידגד} gid-gad Def: FORTUNES \{Strong's: 2735\}\hfill{}\\

\textbf{Gidoni} Heb: {\large\H גדעוני} gid-o-ni Def: HEWN.ONE\textasciitilde{}me(cs) \{Strong's: 1441\}\hfill{}\\

\textbf{Gil'ad} Heb: {\large\H גילעד} gil-ad Def: DANCING.AROUND\textasciitilde{}+\textasciitilde{}WITNESS \{Strong's: 1568\}\hfill{}\\

\textbf{Gilgal} Heb: {\large\H גילגל} gil-gal Def: ROLLING.THING \{Strong's: 1537\}\hfill{}\\

\textbf{Girgash} Heb: {\large\H גירגש} gir-gash Def: STRANGER\textasciitilde{}+\textasciitilde{}CLAYEY.SOIL \{Strong's: 1622\}\hfill{}\\

\textbf{Giyhhon} Heb: {\large\H גיחון} gi-hhon Def: BURSTING.FORTH \{Strong's: 1521\}\hfill{}\\

\textbf{Golan} Heb: {\large\H גולן} go-lan Def: RISING\textasciitilde{}them(fp) \{Strong's: 1474\}\hfill{}\\

\textbf{Gomer} Heb: {\large\H גומר} go-mer Def: CONCLUDED \{Strong's: 1586\}\hfill{}\\

\textbf{Goren-Ha'atad} Heb: {\large\H גורן.האטד} goren ha'atad Def: FLOOR\textasciitilde{}+\textasciitilde{}the\textasciitilde{}BRAMBLE.THORN \{Strong's: 329, 1637\}\hfill{}\\

\textbf{Goshen} Heb: {\large\H גושן} go-shen Def: DRAWING.NEAR \{Strong's: 1657\}\hfill{}\\

\textbf{Goyim} Heb: {\large\H גוים} go-yim Def: NATION\textasciitilde{}s \{Strong's: 1471\}\hfill{}\\

\textbf{Gudgodah} Heb: {\large\H גודגודה} gud-go-dah Def: FORTUNES \{Strong's: 1412\}\hfill{}\\

\textbf{Guni} Heb: {\large\H גוני} gu-ni Def: DEFENDER\textasciitilde{}me(cs) \{Strong's: 1476\}\hfill{}\\

\textbf{Hadad} Heb: {\large\H הדד} ha-dad Def: the\textasciitilde{}TEAT \{Strong's: 1908\}\hfill{}\\

\textbf{Hadar} Heb: {\large\H הדר} ha-dar Def: HONOR \{Strong's: 1924\}\hfill{}\\

\textbf{Hadoram} Heb: {\large\H הדורם} ha-do-ram Def: HONOR\textasciitilde{}them(mp) \{Strong's: 1913\}\hfill{}\\

\textbf{Hagar} Heb: {\large\H הגר} ha-gar Def: the\textasciitilde{}STRANGER \{Strong's: 1904\}\hfill{}\\

\textbf{Ham} Heb: {\large\H הם} ham Def: ROARING \{Strong's: 1990\}\hfill{}\\

\textbf{Haradah} Heb: {\large\H הרדה} ha-ra-dah Def: TREMBLING \{Strong's: 2732\}\hfill{}\\

\textbf{Haran} Heb: {\large\H הרן} ha-ran Def: HILL.COUNTRY \{Strong's: 2039\}\hfill{}\\

\textbf{Hata'awah} Heb: {\large\H התאוה} ha-ta-a-wah Def: the\textasciitilde{}YEARNING \{Strong's: 6914\}\hfill{}\\

\textbf{Hayishmot} Heb: {\large\H הישמות} ha-yish-mot Def: THERE.IS\textasciitilde{}+\textasciitilde{}DEATH \{Strong's: 1020\}\hfill{}\\

\textbf{Hevel} Heb: {\large\H הבל} he-vel Def: VANITY \{Strong's: 1893\}\hfill{}\\

\textbf{Heymam} Heb: {\large\H הימם} hey-mam Def: CONFUSED \{Strong's: 1967\}\hfill{}\\

\textbf{Hhadad} Heb: {\large\H חדד} hha-dad Def: he\textasciitilde{}did\textasciitilde{}SHARP (V) \{Strong's: 2316\}\hfill{}\\

\textbf{Hhagi} Heb: {\large\H חגי} hha-gi Def: FEAST\textasciitilde{}me(cs) \{Strong's: 2291\}\hfill{}\\

\textbf{Hhaglah} Heb: {\large\H חגלה} hhag-lah Def: PARTRIDGE \{Strong's: 2295\}\hfill{}\\

\textbf{Hham} Heb: {\large\H חם} hham Def: FATHER.IN.LAW \{Strong's: 2526\}\hfill{}\\

\textbf{Hhamat} Heb: {\large\H חמת} hha-mat Def: SKIN.BAG \{Strong's: 2574, 2575, 2577\}\hfill{}\\

\textbf{Hhamor} Heb: {\large\H חמור} hha-mor Def: DONKEY \{Strong's: 2544\}\hfill{}\\

\textbf{Hhamul} Heb: {\large\H חמול} hha-mul Def: PITIED \{Strong's: 2538, 2539\}\hfill{}\\

\textbf{Hhani'eyl} Heb: {\large\H חניאל} hha-ni-eyl Def: BEAUTY\textasciitilde{}of\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 2592\}\hfill{}\\

\textbf{Hhanokh} Heb: {\large\H חנוך} hha-nokh Def: DEVOTED \{Strong's: 2585\}\hfill{}\\

\textbf{Hharan} Heb: {\large\H חרן} hha-ran Def: FLAMING.WRATH \{Strong's: 2771\}\hfill{}\\

\textbf{Hharmah} Heb: {\large\H חרמה} hhar-mah Def: PERFORATED \{Strong's: 2767\}\hfill{}\\

\textbf{Hhashmonah} Heb: {\large\H חשמונה} hhash-mo-nah Def: WEALTHY \{Strong's: 2832\}\hfill{}\\

\textbf{Hhatsar} Heb: {\large\H חצר} hha-tsar Def: COURTYARD \{Strong's: 2704\}\hfill{}\\

\textbf{Hhatsarmawet} Heb: {\large\H חצרמות} hha-tsa-ma-wet Def: COURTYARD\textasciitilde{}+\textasciitilde{}DEATH \{Strong's: 2700\}\hfill{}\\

\textbf{Hhats'tson-Tamar} Heb: {\large\H חצצון.תמר} hhats-tson ta-mar Def: DIVIDING\textasciitilde{}+\textasciitilde{}DATE.PALM \{Strong's: 2688\}\hfill{}\\

\textbf{Hhawah} Heb: {\large\H חוה} hha-wah Def: TOWN \{Strong's: 2332\}\hfill{}\\

\textbf{Hhawilah} Heb: {\large\H חוילה} hha-wi-lah Def: TWIST.AROUND \{Strong's: 2341\}\hfill{}\\

\textbf{Hhawot} Heb: {\large\H חות} hha-wot Def: TOWN\textasciitilde{}s \{Strong's: 2334\}\hfill{}\\

\textbf{Hhazo} Heb: {\large\H חזו} hha-zo Def: LOOK.INTO\textasciitilde{}him \{Strong's: 2375\}\hfill{}\\

\textbf{Hheleq} Heb: {\large\H חלק} hhe-leq Def: PORTION \{Strong's: 2507, 2516\}\hfill{}\\

\textbf{Hhemdan} Heb: {\large\H חמדן} hhem-dan Def: DESIRED \{Strong's: 2533\}\hfill{}\\

\textbf{Hhermon} Heb: {\large\H חרמון} hher-mon Def: PERFORATED.ONE \{Strong's: 2768\}\hfill{}\\

\textbf{Hheshbon} Heb: {\large\H חשבון} hhesh-bon Def: REASON \{Strong's: 2809\}\hfill{}\\

\textbf{Hhet} Heb: {\large\H חת} hhet Def: TREMBLING.IN.FEAR \{Strong's: 2845, 2850\}\hfill{}\\

\textbf{Hhetsron} Heb: {\large\H חצרון} hhets-ron Def: SURROUNDED.BY.A.WALL \{Strong's: 2696\}\hfill{}\\

\textbf{Hhever} Heb: {\large\H חבר} hhe-ver Def: COUPLE \{Strong's: 2268\}\hfill{}\\

\textbf{Hhevron} Heb: {\large\H חברון} hhev-ron Def: ASSOCIATION \{Strong's: 2275, 2276\}\hfill{}\\

\textbf{Hheylon} Heb: {\large\H חלון} hhey-lon Def: WINDOW \{Strong's: 2497\}\hfill{}\\

\textbf{Hheypher} Heb: {\large\H חפר} hhey-pher Def: DUG.OUT.WELL \{Strong's: 2660\}\hfill{}\\

\textbf{Hhideqel} Heb: {\large\H חידקל} hhi-de-qel Def: RAPID \{Strong's: 2313\}\hfill{}\\

\textbf{Hhirot} Heb: {\large\H חירות} hhi-rot Def: CISTERN\textasciitilde{}s \{Strong's: 6367\}\hfill{}\\

\textbf{Hhiw} Heb: {\large\H חיו} hhiw Def: TOWN \{Strong's: 2340\}\hfill{}\\

\textbf{Hhiyrah} Heb: {\large\H חירה} hhi-rah Def: NOBILITY \{Strong's: 2437\}\hfill{}\\

\textbf{Hhor} Heb: {\large\H חור} hhor Def: CISTERN \{Strong's: 2752\}\hfill{}\\

\textbf{Hhorev} Heb: {\large\H חורב} hho-rev Def: PARCHING.HEAT \{Strong's: 2722\}\hfill{}\\

\textbf{Hhoriy} Heb: {\large\H חורי} hho-ri Def: CISTERN\textasciitilde{}me(cs) \{Strong's: 2753\}\hfill{}\\

\textbf{Hhovah} Heb: {\large\H חובה} hho-vah Def: HIDING.PLACE \{Strong's: 2327\}\hfill{}\\

\textbf{Hhovav} Heb: {\large\H חובב} hho-vav Def: CHERISH (V)\textasciitilde{}ing(ms) \{Strong's: 2246\}\hfill{}\\

\textbf{Hhul} Heb: {\large\H חול} hhul Def: SAND \{Strong's: 2343\}\hfill{}\\

\textbf{Hhupham} Heb: {\large\H חופם} hhu-pham Def: SHORE\textasciitilde{}them(mp) \{Strong's: 2349\}\hfill{}\\

\textbf{Hhupim} Heb: {\large\H חופים} hhu-pim Def: SHORE\textasciitilde{}s \{Strong's: 2650\}\hfill{}\\

\textbf{Hhur} Heb: {\large\H חור} hhur Def: CISTERN \{Strong's: 2354\}\hfill{}\\

\textbf{Hhush} Heb: {\large\H חוש} hhush Def: HASTY \{Strong's: 2366\}\hfill{}\\

\textbf{Hhusham} Heb: {\large\H חושם} hhu-sham Def: HASTILY \{Strong's: 2367\}\hfill{}\\

\textbf{Hhutsot} Heb: {\large\H חוצות} hhu-tsot Def: OUTSIDE\textasciitilde{}s \{Strong's: 7155\}\hfill{}\\

\textbf{Hor} Heb: {\large\H הור} hor Def: HILL \{Strong's: 2023\}\hfill{}\\

\textbf{Hosheya} Heb: {\large\H הושע} ho-shey-a Def: !(ms)\textasciitilde{}make\textasciitilde{}RESCUE (V) \{Strong's: 1954\}\hfill{}\\

\textbf{I'ezer} Heb: {\large\H איעזר} i-e-zer Def: ISLAND\textasciitilde{}+\textasciitilde{}HELP \{Strong's: 372, 373\}\hfill{}\\

\textbf{Irad} Heb: {\large\H עירד} i-rad Def: FLEET \{Strong's: 5897\}\hfill{}\\

\textbf{Iyim} Heb: {\large\H עיים} i-yim Def: PILE.OF.RUINS\textasciitilde{}s \{Strong's: 5863\}\hfill{}\\

\textbf{Iyram} Heb: {\large\H עירם} i-ram Def: CITY\textasciitilde{}them(mp) \{Strong's: 5902\}\hfill{}\\

\textbf{Iytamar} Heb: {\large\H איתמר} it-mar Def: ISLAND\textasciitilde{}+\textasciitilde{}DATE.PALM \{Strong's: 385\}\hfill{}\\

\textbf{Kalahh} Heb: {\large\H כלח} ka-lahh Def: FULL.AGE \{Strong's: 3625\}\hfill{}\\

\textbf{Kaleyv} Heb: {\large\H כלב} ka-leyv Def: DOG \{Strong's: 3612\}\hfill{}\\

\textbf{Kalneh} Heb: {\large\H כלנה} kal-neh Def: FORTRESS.OF.ANU \{Strong's: 3641\}\hfill{}\\

\textbf{Kaphtor} Heb: {\large\H כפתור} kaph-tor Def: KNOB \{Strong's: 3731, 3732\}\hfill{}\\

\textbf{Karmi} Heb: {\large\H כרמי} kar-mi Def: VINEYARD\textasciitilde{}me(cs) \{Strong's: 3756\}\hfill{}\\

\textbf{Kasluhh} Heb: {\large\H כסלוח} kas-luhh Def: FORTIFIED \{Strong's: 3695\}\hfill{}\\

\textbf{Kazbi} Heb: {\large\H כזבי} kaz-bi Def: LIE\textasciitilde{}me(cs) \{Strong's: 3579\}\hfill{}\\

\textbf{Kedarla'omer} Heb: {\large\H כדרלעומר} ke-dar-la-o-mer Def: FIGHTING\textasciitilde{}+\textasciitilde{}to\textasciitilde{}the\textasciitilde{}SHEAF \{Strong's: 3540\}\hfill{}\\

\textbf{Kemosh} Heb: {\large\H כמוש} ke-mosh Def: SUBDUER \{Strong's: 3645\}\hfill{}\\

\textbf{Kena'an} Heb: {\large\H כנען} ke-na-an Def: LOWERED \{Strong's: 3667, 3669\}\hfill{}\\

\textbf{Keran} Heb: {\large\H כרן} ke-ran Def: LYRE \{Strong's: 3763\}\hfill{}\\

\textbf{Kesed} Heb: {\large\H כסד} ke-sed Def: INCREASING \{Strong's: 3777, 3778, 3779\}\hfill{}\\

\textbf{Keziv} Heb: {\large\H כזיב} ke-ziv Def: LIE \{Strong's: 3580\}\hfill{}\\

\textbf{Kineret} Heb: {\large\H כנרת} ki-ne-ret Def: HARP \{Strong's: 3672\}\hfill{}\\

\textbf{Kislon} Heb: {\large\H כיסלון} kis-lon Def: CONFIDENT.ONE \{Strong's: 3692\}\hfill{}\\

\textbf{Kit} Heb: {\large\H כית} kit Def: BRUISER \{Strong's: 3794\}\hfill{}\\

\textbf{Kush} Heb: {\large\H כוש} kush Def: BLACKISH \{Strong's: 3568, 3569, 3571\}\hfill{}\\

\textbf{Lamekh} Heb: {\large\H למך} la-mekh Def: DESPAIRING \{Strong's: 3929\}\hfill{}\\

\textbf{Lavan} Heb: {\large\H לבן} la-van Def: WHITE \{Strong's: 3837\}\hfill{}\\

\textbf{Le'ah} Heb: {\large\H לאה} ley-ah Def: IMPATIENT \{Strong's: 3812\}\hfill{}\\

\textbf{Lehav} Heb: {\large\H להב} le-hav Def: GLIMMER \{Strong's: 3853\}\hfill{}\\

\textbf{Lesha} Heb: {\large\H לשע} le-sha Def: CRACK.OPEN \{Strong's: 3962\}\hfill{}\\

\textbf{Letush} Heb: {\large\H לטוש} le-tush Def: SHARPENED \{Strong's: 3912\}\hfill{}\\

\textbf{Le'um} Heb: {\large\H לאום} le-um Def: COMMUNITY \{Strong's: 3817\}\hfill{}\\

\textbf{Levanon} Heb: {\large\H לבנון} le-va-non Def: WHITE.ONE \{Strong's: 3844\}\hfill{}\\

\textbf{Lewi} Heb: {\large\H לוי} le-wi Def: JOINING\textasciitilde{}me(cs) \{Strong's: 3878, 3879, 3881\}\hfill{}\\

\textbf{Livnah} Heb: {\large\H לבנה} liv-nah Def: BRICK \{Strong's: 3841\}\hfill{}\\

\textbf{Liyvniy} Heb: {\large\H ליבני} liv-ni Def: WHITE\textasciitilde{}me(cs) \{Strong's: 3845\}\hfill{}\\

\textbf{Lot} Heb: {\large\H לוט} lot Def: TIGHTLY.WRAPPED \{Strong's: 3876\}\hfill{}\\

\textbf{Lotan} Heb: {\large\H לוטן} lo-tan Def: WRAPPER \{Strong's: 3877\}\hfill{}\\

\textbf{Lud} Heb: {\large\H לוד} lud Def: NATIVITY \{Strong's: 3865, 3866\}\hfill{}\\

\textbf{Luz} Heb: {\large\H לוז} luz Def: HAZEL \{Strong's: 3870\}\hfill{}\\

\textbf{Ma'akhah} Heb: {\large\H מעכה} ma-a-khah Def: FIRMLY.PRESSED \{Strong's: 4601\}\hfill{}\\

\textbf{Madai} Heb: {\large\H מדי} ma-dai Def: LONG.GARMENT\textasciitilde{}s\textasciitilde{}me(cs) \{Strong's: 4074\}\hfill{}\\

\textbf{Magdi'eyl} Heb: {\large\H מגדיאל} mag-di-eyl Def: PRECIOUS\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 4025\}\hfill{}\\

\textbf{Magog} Heb: {\large\H מגוג} ma-gog Def: ROOFING \{Strong's: 4031\}\hfill{}\\

\textbf{Mahalalel} Heb: {\large\H מהללאל} ma-ha-la-lel Def: SHINE\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 4111\}\hfill{}\\

\textbf{Mahhalat} Heb: {\large\H מחלת} ma-hha-lat Def: SICKENED \{Strong's: 4257, 4258\}\hfill{}\\

\textbf{Mahhanayim} Heb: {\large\H מחנים} ma-hha-na-yim Def: CAMPSITE\textasciitilde{}s2 \{Strong's: 4266\}\hfill{}\\

\textbf{Mahhlah} Heb: {\large\H מחלה} mahh-lah Def: SICKNESS \{Strong's: 4244\}\hfill{}\\

\textbf{Mahh'liy} Heb: {\large\H מחלי} mahh-li Def: SICKNESS\textasciitilde{}me(cs) \{Strong's: 4249\}\hfill{}\\

\textbf{Mahn} Heb: {\large\H מן} mahn Def: SHARE \{Strong's: 4478\}\hfill{}\\

\textbf{Makhi} Heb: {\large\H מכי} ma-khi Def: BEING.LOW \{Strong's: 4352\}\hfill{}\\

\textbf{Makhir} Heb: {\large\H מכיר} ma-khir Def: PRICE \{Strong's: 4353\}\hfill{}\\

\textbf{Makhpelah} Heb: {\large\H מכפלה} makh-pe-lah Def: DOUBLED \{Strong's: 4375\}\hfill{}\\

\textbf{Malki'el} Heb: {\large\H מלכיאל} mal-ki-eyl Def: KING\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 4439\}\hfill{}\\

\textbf{Malkiy-Tsedeq} Heb: {\large\H מלכי.צדק} mal-ki tse-deq Def: KING\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}STEADFAST \{Strong's: 4442\}\hfill{}\\

\textbf{Mamre} Heb: {\large\H ממרא} mam-rey Def: FATNESS \{Strong's: 4471\}\hfill{}\\

\textbf{Manahhat} Heb: {\large\H מנחת} ma-na-hhat Def: OASIS \{Strong's: 4506\}\hfill{}\\

\textbf{Maqheylot} Heb: {\large\H מקהלות} maq-hey-lot Def: PASTURE\textasciitilde{}s \{Strong's: 4722\}\hfill{}\\

\textbf{Marah} Heb: {\large\H מרה} ma-rah Def: BITTER \{Strong's: 4785\}\hfill{}\\

\textbf{Masa} Heb: {\large\H מסא} ma-sa Def: LOAD \{Strong's: 4854\}\hfill{}\\

\textbf{Masah} Heb: {\large\H מסה} ma-sah Def: TRIAL \{Strong's: 4532\}\hfill{}\\

\textbf{Mash} Heb: {\large\H מש} mash Def: DRAWN.OUT \{Strong's: 4851\}\hfill{}\\

\textbf{Masreyqah} Heb: {\large\H מסרקה} mas-rey-qah Def: CHOICE.VINEYARD \{Strong's: 4957\}\hfill{}\\

\textbf{Matanah} Heb: {\large\H מתנה} ma-ta-nah Def: CONTRIBUTION \{Strong's: 4980\}\hfill{}\\

\textbf{Matreyd} Heb: {\large\H מטרד} mat-reyd Def: CONTINUOUS \{Strong's: 4308\}\hfill{}\\

\textbf{Medan} Heb: {\large\H מדן} me-dan Def: DISCORD \{Strong's: 4091\}\hfill{}\\

\textbf{Meheytaveyl} Heb: {\large\H מהיטבאל} me-hey-tav-eyl Def: FAVORED\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 4105\}\hfill{}\\

\textbf{Mehhuya'el} Heb: {\large\H מחויאל} me-huu-ya-eyl Def: BATTERING.RAM\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 4232\}\hfill{}\\

\textbf{Menasheh} Heb: {\large\H מנשה} me-na-sheh Def: CAUSING.TO.OVERLOOK \{Strong's: 4519\}\hfill{}\\

\textbf{Me'on} Heb: {\large\H מעון} me-on Def: HABITATION \{Strong's: 1186\}\hfill{}\\

\textbf{Merari} Heb: {\large\H מררי} me-ra-ri Def: BITTERNESS\textasciitilde{}me(cs) \{Strong's: 4847\}\hfill{}\\

\textbf{Meriyvah} Heb: {\large\H מריבה} me-ri-vah Def: CONTENTION \{Strong's: 4809\}\hfill{}\\

\textbf{Mesha} Heb: {\large\H משא} mey-sha Def: TUMULTUOUS \{Strong's: 4852\}\hfill{}\\

\textbf{Meshek} Heb: {\large\H משך} me-shek Def: ACQUIRING \{Strong's: 4902\}\hfill{}\\

\textbf{Metusha'el} Heb: {\large\H מתושאל} me-tu-sha-eyl Def: DEATH\textasciitilde{}him\textasciitilde{}+\textasciitilde{}he\textasciitilde{}did\textasciitilde{}ENQUIRE (V) \{Strong's: 4967\}\hfill{}\\

\textbf{Metushelahh} Heb: {\large\H מתושלח} me-tu-sha-lahh Def: DEATH\textasciitilde{}him\textasciitilde{}+\textasciitilde{}he\textasciitilde{}did\textasciitilde{}SEND (V) \{Strong's: 4968\}\hfill{}\\

\textbf{Meydad} Heb: {\large\H מידד} mey-dad Def: THROWING \{Strong's: 4312\}\hfill{}\\

\textbf{Meydva} Heb: {\large\H מידבא} meyd-va Def: WATER\textasciitilde{}+\textasciitilde{}DEMISE \{Strong's: 4311\}\hfill{}\\

\textbf{Mey-Zahav} Heb: {\large\H מי.זהב} mey za-hav Def: WATER\textasciitilde{}s2GOLD \{Strong's: 4314\}\hfill{}\\

\textbf{Mid'yan} Heb: {\large\H מידין} mid-yan Def: QUARREL \{Strong's: 4080\}\hfill{}\\

\textbf{Migdal-Eyder} Heb: {\large\H מגדל.עדר} mig-dal ey-der Def: TOWER\textasciitilde{}+\textasciitilde{}DROVE \{Strong's: 4029\}\hfill{}\\

\textbf{Migdol} Heb: {\large\H מגדול} mig-dol Def: TOWER \{Strong's: 4024\}\hfill{}\\

\textbf{Mika'eyl} Heb: {\large\H מיכאל} mi-ka-eyl Def: WHO\textasciitilde{}+\textasciitilde{}like\textasciitilde{}MIGHTY.ONE \{Strong's: 4317\}\hfill{}\\

\textbf{Milkah} Heb: {\large\H מלכה} mil-kah Def: QUEEN \{Strong's: 4435\}\hfill{}\\

\textbf{Mir'yam} Heb: {\large\H מירים} mir-yam Def: BITTER\textasciitilde{}+\textasciitilde{}SEA \{Strong's: 4813\}\hfill{}\\

\textbf{Mishma} Heb: {\large\H משמע} mish-ma Def: HEARING \{Strong's: 4927\}\hfill{}\\

\textbf{Mitqah} Heb: {\large\H מתקה} mit-qah Def: SWEETNESS \{Strong's: 4989\}\hfill{}\\

\textbf{Mitspah} Heb: {\large\H מצפה} mits-pah Def: WATCHTOWER \{Strong's: 4708, 4709\}\hfill{}\\

\textbf{Mits'rayim} Heb: {\large\H מצרים} mits-ra-yim Def: STRAIT\textasciitilde{}s2 \{Strong's: 4713, 4714\}\hfill{}\\

\textbf{Mivsam} Heb: {\large\H מבסם} miv-sam Def: SPICE.PLACE \{Strong's: 4017\}\hfill{}\\

\textbf{Mivtsar} Heb: {\large\H מבצר} miv-tsar Def: FENCE \{Strong's: 4014\}\hfill{}\\

\textbf{Miysha'eyl} Heb: {\large\H מישאל} mi-sha-eyl Def: WHO\textasciitilde{}+\textasciitilde{}he\textasciitilde{}did\textasciitilde{}ENQUIRE (V) \{Strong's: 4332\}\hfill{}\\

\textbf{Miz'zah} Heb: {\large\H מזה} miz-zah Def: SUCKED.OUT \{Strong's: 4199\}\hfill{}\\

\textbf{Mo'av} Heb: {\large\H מואב} mo-av Def: THAT.ONE\textasciitilde{}+\textasciitilde{}FATHER \{Strong's: 4124\}\hfill{}\\

\textbf{Molekh} Heb: {\large\H מולך} mo-lekh Def: REIGN (V)\textasciitilde{}ing(ms) \{Strong's: 4432\}\hfill{}\\

\textbf{Moreh} Heb: {\large\H מורה} mo-reh Def: THROW (V)\textasciitilde{}ing(ms) \{Strong's: 4176\}\hfill{}\\

\textbf{Moriyah} Heb: {\large\H מוריה} mo-ri-yah Def: THROW (V)\textasciitilde{}ing(ms)\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}EXISTING \{Strong's: 4179\}\hfill{}\\

\textbf{Moseyrah} Heb: {\large\H מוסרה} mo-sey-rah Def: STRAP \{Strong's: 4149\}\hfill{}\\

\textbf{Mosheh} Heb: {\large\H מושה} mo-sheh Def: PLUCKED.OUT \{Strong's: 4872\}\hfill{}\\

\textbf{Mupim} Heb: {\large\H מופים} mu-qim Def: SNAKE\textasciitilde{}s \{Strong's: 4649\}\hfill{}\\

\textbf{Mushiy} Heb: {\large\H מושי} mu-shi Def: MOVING\textasciitilde{}me(cs) \{Strong's: 4187\}\hfill{}\\

\textbf{Na'amah} Heb: {\large\H נעמה} na-a-mah Def: DELIGHTFUL \{Strong's: 5279\}\hfill{}\\

\textbf{Na'aman} Heb: {\large\H נעמן} na-a-man Def: PLEASANTNESS \{Strong's: 5283\}\hfill{}\\

\textbf{Nadav} Heb: {\large\H נדב} na-dav Def: he\textasciitilde{}did\textasciitilde{}OFFER.WILLINGLY (V) \{Strong's: 5070\}\hfill{}\\

\textbf{Nahhali'eyl} Heb: {\large\H נחליאל} na-hha-li-eyl Def: WADI\textasciitilde{}of\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 5160\}\hfill{}\\

\textbf{Nahhat} Heb: {\large\H נחת} na-hhat Def: QUIETNESS \{Strong's: 5184\}\hfill{}\\

\textbf{Nahhbi} Heb: {\large\H נחבי} nahh-bi Def: HIDDEN \{Strong's: 5147\}\hfill{}\\

\textbf{Nahhor} Heb: {\large\H נחור} na-hhor Def: SNORTING \{Strong's: 5152\}\hfill{}\\

\textbf{Nahhshon} Heb: {\large\H נחשון} nahh-shon Def: DIVINER \{Strong's: 5177\}\hfill{}\\

\textbf{Naphish} Heb: {\large\H נפיש} na-phish Def: DEEP.BREATH \{Strong's: 5305\}\hfill{}\\

\textbf{Naphtali} Heb: {\large\H נפתלי} naph-ta-li Def: WRESTLING\textasciitilde{}me(cs) \{Strong's: 5321\}\hfill{}\\

\textbf{Naphtuhh} Heb: {\large\H נפתוח} naph-tu-ahh Def: DOORWAY \{Strong's: 5320\}\hfill{}\\

\textbf{Nataneyl} Heb: {\large\H נתנאל} na-tan-eyl Def: >\textasciitilde{}GIVE (V)\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 5417\}\hfill{}\\

\textbf{Negev} Heb: {\large\H נגב} ne-gev Def: PARCHED \{Strong's: 5045\}\hfill{}\\

\textbf{Nemu'eyl} Heb: {\large\H נמואל} ne-mu-eyl Def: SEA\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 5241\}\hfill{}\\

\textbf{Nepheg} Heb: {\large\H נפג} ne-pheg Def: SPROUT.UP \{Strong's: 5298\}\hfill{}\\

\textbf{Nephilim} Heb: {\large\H נפילים} ne-phi-lim Def: make\textasciitilde{}FALL (V)\textasciitilde{}ing(mp) \{Strong's: 5303\}\hfill{}\\

\textbf{Nevayot} Heb: {\large\H נביות} ne-va-yot Def: FLOURISHED\textasciitilde{}s \{Strong's: 5032\}\hfill{}\\

\textbf{Nevo} Heb: {\large\H נבו} ne-vo Def: FLOURISHED\textasciitilde{}him \{Strong's: 5015\}\hfill{}\\

\textbf{Nimrah} Heb: {\large\H נמרה} nim-rah Def: LEOPARD \{Strong's: 1039\}\hfill{}\\

\textbf{Nimrod} Heb: {\large\H נימרוד} nim-rod Def: REBELLING \{Strong's: 5248\}\hfill{}\\

\textbf{Ninweh} Heb: {\large\H נינוה} nin-weh Def: ABODE.OF.NINUS \{Strong's: 5210\}\hfill{}\\

\textbf{No'ah} Heb: {\large\H נועה} no-ah Def: STAGGERING \{Strong's: 5270\}\hfill{}\\

\textbf{No'ahh} Heb: {\large\H נוח} no-ahh Def: REST \{Strong's: 5146\}\hfill{}\\

\textbf{Nod} Heb: {\large\H נוד} nod Def: NODDING \{Strong's: 5113\}\hfill{}\\

\textbf{Nophahh} Heb: {\large\H נופח} no-phahh Def: EXHALE (V)\textasciitilde{}ing(ms) \{Strong's: 5302\}\hfill{}\\

\textbf{Novahh} Heb: {\large\H נובח} no-vahh Def: BARK (V)\textasciitilde{}ing(ms) \{Strong's: 5025\}\hfill{}\\

\textbf{Nun} Heb: {\large\H נון} nun Def: CONTINUE \{Strong's: 5126\}\hfill{}\\

\textbf{Og} Heb: {\large\H עוג} og Def: BREAD.CAKE \{Strong's: 5747\}\hfill{}\\

\textbf{Ohad} Heb: {\large\H אוהד} o-had Def: SHOUTING \{Strong's: 161\}\hfill{}\\

\textbf{Omar} Heb: {\large\H אומר} o-mar Def: MATTER \{Strong's: 201\}\hfill{}\\

\textbf{On} Heb: {\large\H און} on Def: VIGOR \{Strong's: 204\}\hfill{}\\

\textbf{Onam} Heb: {\large\H אונם} o-nam Def: COMPLAINER \{Strong's: 208\}\hfill{}\\

\textbf{Onan} Heb: {\large\H אונן} o-nan Def: COMPLAINER \{Strong's: 209\}\hfill{}\\

\textbf{Ophir} Heb: {\large\H אופיר} o-phir Def: REDUCED.TO.ASHES \{Strong's: 211\}\hfill{}\\

\textbf{Ovot} Heb: {\large\H אובות} o-vot Def: WINESKIN\textasciitilde{}s \{Strong's: 88\}\hfill{}\\

\textbf{Padan} Heb: {\large\H פדן} pa-dan Def: SUET \{Strong's: 6307\}\hfill{}\\

\textbf{Padan-Aram} Heb: {\large\H פדן.ארם} pa-dan a-ram Def: SUET\textasciitilde{}+\textasciitilde{}PALACE \{Strong's: 6307\}\hfill{}\\

\textbf{Pagi'eyl} Heb: {\large\H פגעיאל} pag-i-eyl Def: ENCOUNTER\textasciitilde{}of\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 6295\}\hfill{}\\

\textbf{Palti} Heb: {\large\H פלטי} pal-ti Def: ESCAPING\textasciitilde{}me(cs) \{Strong's: 6406\}\hfill{}\\

\textbf{Palti'eyl} Heb: {\large\H פלטיאל} pal-ti-eyl Def: ESCAPING\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 6409\}\hfill{}\\

\textbf{Palu} Heb: {\large\H פלוא} pa-lu Def: PERFORMING \{Strong's: 6396\}\hfill{}\\

\textbf{Paran} Heb: {\large\H פארן} pa-ran Def: DECORATED \{Strong's: 6290\}\hfill{}\\

\textbf{Parnakh} Heb: {\large\H פרנך} par-nakh Def: FRAGILE \{Strong's: 6535\}\hfill{}\\

\textbf{Paroh} Heb: {\large\H פרעוה} par-oh Def: GREAT.HOUSE \{Strong's: 6547\}\hfill{}\\

\textbf{Patros} Heb: {\large\H פתרוס} pat-ros Def: SOUTHERN.REGION \{Strong's: 6624, 6625\}\hfill{}\\

\textbf{Pa'u} Heb: {\large\H פעו} pa-u Def: SCREAMING \{Strong's: 6464\}\hfill{}\\

\textbf{Pedah} Heb: {\large\H פדה} pe-dah Def: RANSOMED \{Strong's: 6301\}\hfill{}\\

\textbf{Pedah'eyl} Heb: {\large\H פדהאל} pe-dah-eyl Def: RANSOMED\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 6300\}\hfill{}\\

\textbf{Pedatsur} Heb: {\large\H פדהצור} pe-dah-tsur Def: RANSOMED\textasciitilde{}+\textasciitilde{}BOULDER \{Strong's: 6301\}\hfill{}\\

\textbf{Peleg} Heb: {\large\H פלג} pe-leg Def: TRIBUTARY \{Strong's: 6389\}\hfill{}\\

\textbf{Peleshet} Heb: {\large\H פלשת} pe-le-shet Def: IMMIGRANT \{Strong's: 6429, 6430\}\hfill{}\\

\textbf{Pelet} Heb: {\large\H פלת} pe-let Def: SWIFTNESS \{Strong's: 6431\}\hfill{}\\

\textbf{Peni'el} Heb: {\large\H פניאל} pe-ni-eyl Def: FACE\textasciitilde{}s\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 6439\}\hfill{}\\

\textbf{Pe'or} Heb: {\large\H פעור} pe-or Def: OPENED.WIDE \{Strong's: 1187, 6465\}\hfill{}\\

\textbf{Perat} Heb: {\large\H פרת} pe-rat Def: FRUITFULNESS \{Strong's: 6578\}\hfill{}\\

\textbf{Perets} Heb: {\large\H פרץ} pe-rets Def: BREACH \{Strong's: 6557\}\hfill{}\\

\textbf{Perez} Heb: {\large\H פרז} pe-rez Def: PEASANT \{Strong's: 6522\}\hfill{}\\

\textbf{Pesahh} Heb: {\large\H פסח} pe-sahh Def: HOPPING \{Strong's: 6453\}\hfill{}\\

\textbf{Petor} Heb: {\large\H פתור} pe-tor Def: INTERPRETING \{Strong's: 6604\}\hfill{}\\

\textbf{Pikhol} Heb: {\large\H פיכול} pi-khol Def: MOUTH\textasciitilde{}+\textasciitilde{}ALL \{Strong's: 6369\}\hfill{}\\

\textbf{Pildash} Heb: {\large\H פילדש} pil-dash Def: FLAME.OF.FIRE \{Strong's: 6394\}\hfill{}\\

\textbf{Pinon} Heb: {\large\H פינון} pi-non Def: AROUND.THE.CORNER \{Strong's: 6373\}\hfill{}\\

\textbf{Pisgah} Heb: {\large\H פיסגה} pis-gah Def: CLEFT \{Strong's: 6449\}\hfill{}\\

\textbf{Pishon} Heb: {\large\H פישון} pi-shon Def: SCATTERED \{Strong's: 6376\}\hfill{}\\

\textbf{Pitom} Heb: {\large\H פיתום} pi-tom Def: CITY.OF.JUSTICE \{Strong's: 6619\}\hfill{}\\

\textbf{Piy-Hahhiyrot} Heb: {\large\H פי.החירות} pi ha-hhi-rot Def: MOUTH\textasciitilde{}+\textasciitilde{}the\textasciitilde{}CISTERN\textasciitilde{}s \{Strong's: 6367\}\hfill{}\\

\textbf{Piynhhas} Heb: {\large\H פינחס} pin-hhas Def: MOUTH\textasciitilde{}+\textasciitilde{}SERPENT \{Strong's: 6372\}\hfill{}\\

\textbf{Potee-Phera} Heb: {\large\H פוטי.פרע} po-ti phe-ra Def: BELONGING\textasciitilde{}of\textasciitilde{}+\textasciitilde{}LONG.HAIR \{Strong's: 6319\}\hfill{}\\

\textbf{Potiphar} Heb: {\large\H פוטיפר} po-ti-phar Def: BELONGING\textasciitilde{}of\textasciitilde{}+\textasciitilde{}BULL \{Strong's: 6318\}\hfill{}\\

\textbf{Pu'ah} Heb: {\large\H פואה} pu-ah Def: BLOWN \{Strong's: 6312\}\hfill{}\\

\textbf{Pu'ah} Heb: {\large\H פועה} pu-ah Def: SPLENDID \{Strong's: 6326\}\hfill{}\\

\textbf{Pun} Heb: {\large\H פון} pun Def: DISTRACTED \{Strong's: 6325\}\hfill{}\\

\textbf{Punon} Heb: {\large\H פונון} pu-non Def: DISTRACTED.ONE \{Strong's: 6325\}\hfill{}\\

\textbf{Put} Heb: {\large\H פוט} put Def: BELONGING \{Strong's: 6316\}\hfill{}\\

\textbf{Putiy'eyl} Heb: {\large\H פוטיאל} pu-ti-eyl Def: BELONGING\textasciitilde{}of\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 6317\}\hfill{}\\

\textbf{Qadesh} Heb: {\large\H קדש} qa-desh Def: MALE.PROSTITUTE \{Strong's: 6946\}\hfill{}\\

\textbf{Qadmon} Heb: {\large\H קדמון} qad-mon Def: EASTERN \{Strong's: 6935\}\hfill{}\\

\textbf{Qayin} Heb: {\large\H קין} qa-yin Def: SPEARHEAD \{Strong's: 7014, 7017, 8423\}\hfill{}\\

\textbf{Qedar} Heb: {\large\H קדר} qe-dar Def: GRAY \{Strong's: 6938\}\hfill{}\\

\textbf{Qedeymot} Heb: {\large\H קדמות} qe-dey-mot Def: PAST.TIME\textasciitilde{}s \{Strong's: 6932\}\hfill{}\\

\textbf{Qedmah} Heb: {\large\H קדמה} qed-mah Def: PAST.TIME \{Strong's: 6929\}\hfill{}\\

\textbf{Qehat} Heb: {\large\H קהת} qe-hat Def: ALLIED \{Strong's: 6955\}\hfill{}\\

\textbf{Qemu'el} Heb: {\large\H קמואל} qe-mu-eyl Def: !(ms)\textasciitilde{}RISE (V)\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 7055\}\hfill{}\\

\textbf{Qenat} Heb: {\large\H קנת} qe-nat Def: PURCHASED \{Strong's: 7079\}\hfill{}\\

\textbf{Qenaz} Heb: {\large\H קנז} qe-naz Def: STALKER \{Strong's: 7073, 7074\}\hfill{}\\

\textbf{Qeturah} Heb: {\large\H קטורה} qe-tu-rah Def: BURN.INCENSE (V)\textasciitilde{}ed(fs) \{Strong's: 6989\}\hfill{}\\

\textbf{Qeynan} Heb: {\large\H קינן} qey-nan Def: NESTING \{Strong's: 7018\}\hfill{}\\

\textbf{Qiryat-Arba} Heb: {\large\H קירית.ארבע} qir-yat ar-ba Def: WALL\textasciitilde{}+\textasciitilde{}FOUR \{Strong's: 7153\}\hfill{}\\

\textbf{Qiryatayim} Heb: {\large\H קריתים} qir-ya-ta-yim Def: METROPOLIS\textasciitilde{}s2 \{Strong's: 7156\}\hfill{}\\

\textbf{Qivrot} Heb: {\large\H קברות} qiv-rot Def: GRAVE\textasciitilde{}s \{Strong's: 6914\}\hfill{}\\

\textbf{Qorahh} Heb: {\large\H קורח} qo-rahh Def: BALDING \{Strong's: 7141\}\hfill{}\\

\textbf{Rahhel} Heb: {\large\H רחל} ra-hheyl Def: EWE \{Strong's: 7354\}\hfill{}\\

\textbf{Ramah} Heb: {\large\H רעמה} ra-mah Def: MANE.OF.A.HORSE \{Strong's: 7484\}\hfill{}\\

\textbf{Ra'meses} Heb: {\large\H רעמסס} ra-me-ses Def: CHILD.OF.THE.SUN \{Strong's: 7486\}\hfill{}\\

\textbf{Ramot} Heb: {\large\H ראמות} ra-mot Def: CORAL\textasciitilde{}s \{Strong's: 7216\}\hfill{}\\

\textbf{Rapha} Heb: {\large\H רפא} ra-pha Def: DEAD \{Strong's: 7497\}\hfill{}\\

\textbf{Raphu} Heb: {\large\H רפוא} ra-phu Def: HEAL (V)\textasciitilde{}ed(ms) \{Strong's: 7505\}\hfill{}\\

\textbf{Ravah} Heb: {\large\H רבה} ra-vah Def: ABUNDANT \{Strong's: 7237\}\hfill{}\\

\textbf{Rehhov} Heb: {\large\H רחוב} re-hhov Def: STREET \{Strong's: 7340\}\hfill{}\\

\textbf{Rehhovot} Heb: {\large\H רחובות} re-hho-vot Def: STREET\textasciitilde{}s \{Strong's: 7344\}\hfill{}\\

\textbf{Rehhovot-Ghir} Heb: {\large\H רחובות.עיר} re-hho-vot ghir Def: STREET\textasciitilde{}s\textasciitilde{}+\textasciitilde{}CITY \{Strong's: 7344, 5892\}\hfill{}\\

\textbf{Rephiydiym} Heb: {\large\H רפידים} re-phi-dim Def: PILLAR.BASE \{Strong's: 7508\}\hfill{}\\

\textbf{Reqem} Heb: {\large\H רקם} re-qem Def: EMBROIDERY \{Strong's: 7552\}\hfill{}\\

\textbf{Resen} Heb: {\large\H רסן} re-sen Def: HALTER \{Strong's: 7449\}\hfill{}\\

\textbf{Re'u} Heb: {\large\H רעו} re'u Def: COMPANION \{Strong's: 7466\}\hfill{}\\

\textbf{Re'u'el} Heb: {\large\H רעואל} re-u-eyl Def: COMPANION\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 7467\}\hfill{}\\

\textbf{Re'umah} Heb: {\large\H ראומה} re-u-mah Def: ELEVATED \{Strong's: 7208\}\hfill{}\\

\textbf{Re'uven} Heb: {\large\H ראובן} re-u-veyn Def: !(ms)\textasciitilde{}SEE (V)\textasciitilde{}+\textasciitilde{}SON \{Strong's: 7205\}\hfill{}\\

\textbf{Riphat} Heb: {\large\H ריפת} ri-phat Def: SPOKEN \{Strong's: 7384\}\hfill{}\\

\textbf{Risah} Heb: {\large\H ריסה} ri-sah Def: OVERTHROWN \{Strong's: 7446\}\hfill{}\\

\textbf{Ritmah} Heb: {\large\H רתמה} rit-mah Def: JUNIPER \{Strong's: 7575\}\hfill{}\\

\textbf{Rivlah} Heb: {\large\H ריבלה} riv-lah Def: FRUITFUL \{Strong's: 7247\}\hfill{}\\

\textbf{Rivqah} Heb: {\large\H ריבקה} riv-qah Def: FATTENING \{Strong's: 7259\}\hfill{}\\

\textbf{Rosh} Heb: {\large\H רואש} rosh Def: HEAD \{Strong's: 7220\}\hfill{}\\

\textbf{Salkah} Heb: {\large\H סלכה} sal-kah Def: MIGRATION \{Strong's: 5548\}\hfill{}\\

\textbf{Salu} Heb: {\large\H סלוא} sa-lu Def: COMPARE (V)\textasciitilde{}ed(ms) \{Strong's: 5543\}\hfill{}\\

\textbf{Samlah} Heb: {\large\H סמלה} sam-lah Def: APPAREL \{Strong's: 8072\}\hfill{}\\

\textbf{Sarah} Heb: {\large\H סרה} sa-rah Def: NOBLEWOMAN \{Strong's: 8297\}\hfill{}\\

\textbf{Sarai} Heb: {\large\H סרי} sa-rai Def: PRINCESS \{Strong's: 8283\}\hfill{}\\

\textbf{Savtah} Heb: {\large\H סבתה} sav-tah Def: GO.ABOUT \{Strong's: 5454\}\hfill{}\\

\textbf{Savtekha} Heb: {\large\H סבתכא} sav-ke-kha Def: HITTING \{Strong's: 5455\}\hfill{}\\

\textbf{Sedom} Heb: {\large\H סדום} se-dom Def: SCORCHING \{Strong's: 5467\}\hfill{}\\

\textbf{Se'iyr} Heb: {\large\H סעיר} se-ir Def: HAIRY \{Strong's: 8165\}\hfill{}\\

\textbf{Senir} Heb: {\large\H סניר} se-nir Def: SNOW.MOUNTAIN \{Strong's: 8149\}\hfill{}\\

\textbf{Sephar} Heb: {\large\H ספר} se-phar Def: SCROLL \{Strong's: 5611\}\hfill{}\\

\textbf{Serahh} Heb: {\large\H סרח} se-rahh Def: OVERHANG \{Strong's: 8294\}\hfill{}\\

\textbf{Sered} Heb: {\large\H סרד} se-red Def: BRAIDED.WORK \{Strong's: 5624\}\hfill{}\\

\textbf{Serug} Heb: {\large\H סרוג} se-rug Def: TWIG \{Strong's: 8286\}\hfill{}\\

\textbf{Setur} Heb: {\large\H סתור} se-tur Def: HIDE (V)\textasciitilde{}ed(ms) \{Strong's: 5639\}\hfill{}\\

\textbf{Seva} Heb: {\large\H סבא} se-va Def: DRUNKARD \{Strong's: 5434\}\hfill{}\\

\textbf{Sevam} Heb: {\large\H סבם} se-vam Def: BALSAM \{Strong's: 7643\}\hfill{}\\

\textbf{Shaddai} Heb: {\large\H שדי} shad-dai Def: BREAST\textasciitilde{}s\textasciitilde{}me(cs) \{Strong's: 7706\}\hfill{}\\

\textbf{Shalem} Heb: {\large\H שלם} sha-lem Def: COMPLETE \{Strong's: 8004\}\hfill{}\\

\textbf{Sham'mah} Heb: {\large\H שממה} sham-mah Def: DESOLATE \{Strong's: 8048\}\hfill{}\\

\textbf{Shamu'a} Heb: {\large\H שמוע} sha-mu-a Def: HEAR (V)\textasciitilde{}ed(ms) \{Strong's: 8051\}\hfill{}\\

\textbf{Shaphat} Heb: {\large\H שפט} sha-phat Def: he\textasciitilde{}did\textasciitilde{}DECIDE (V) \{Strong's: 8202\}\hfill{}\\

\textbf{Shaphtan} Heb: {\large\H שפטן} shiph-tan Def: JUDICIAL \{Strong's: 8204\}\hfill{}\\

\textbf{Sha'ul} Heb: {\large\H שאול} sha-ul Def: ENQUIRE (V)\textasciitilde{}ed(ms) \{Strong's: 7586\}\hfill{}\\

\textbf{Shaweh} Heb: {\large\H שוה} sha-weh Def: EQUAL \{Strong's: 7740\}\hfill{}\\

\textbf{Shaweh-Qiryatayim} Heb: {\large\H שוה.קיריתים} sha-weh qir-ya-ta-yim Def: EQUAL\textasciitilde{}s\textasciitilde{}+\textasciitilde{}WALL\textasciitilde{}s \{Strong's: 7741\}\hfill{}\\

\textbf{Shedeyur} Heb: {\large\H שדיאור} she-dey-ur Def: BREAST\textasciitilde{}s\textasciitilde{}+\textasciitilde{}LIGHT (V) \{Strong's: 7707\}\hfill{}\\

\textbf{Shekhem} Heb: {\large\H שכם} she-khem Def: SHOULDER \{Strong's: 7927, 7928\}\hfill{}\\

\textbf{Shelahh} Heb: {\large\H שלח} she-lahh Def: PROJECTILE \{Strong's: 7974\}\hfill{}\\

\textbf{Sheleph} Heb: {\large\H שלף} she-leph Def: PULLED.OUT \{Strong's: 8026\}\hfill{}\\

\textbf{Shelumi'eyl} Heb: {\large\H שלומיאל} she-lu-mi-eyl Def: COMPLETENESS\textasciitilde{}of\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 8017\}\hfill{}\\

\textbf{Shem} Heb: {\large\H שם} shem Def: TITLE \{Strong's: 8035\}\hfill{}\\

\textbf{Shemever} Heb: {\large\H שמאבר} shem-ey-ver Def: TITLE\textasciitilde{}+\textasciitilde{}LONG.WINGED \{Strong's: 8038\}\hfill{}\\

\textbf{Shemida} Heb: {\large\H שמידע} she-mi-da Def: TITLE\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}OPINION \{Strong's: 8061, 8062\}\hfill{}\\

\textbf{Shemu'eyl} Heb: {\large\H שמואל} she-mu-eyl Def: TITLE\textasciitilde{}him\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 8050\}\hfill{}\\

\textbf{Shepham} Heb: {\large\H שפם} she-pham Def: SCRAPED.BARE \{Strong's: 8221\}\hfill{}\\

\textbf{Shepho} Heb: {\large\H שפו} she-pho Def: BARE.PLACE \{Strong's: 8195\}\hfill{}\\

\textbf{Sheshupham} Heb: {\large\H שפופם} she-phu-pham Def: ADDER \{Strong's: 7781, 8197\}\hfill{}\\

\textbf{Shet} Heb: {\large\H שת} shet Def: BUTTOCKS \{Strong's: 8352\}\hfill{}\\

\textbf{Sheva} Heb: {\large\H שבא} she-va Def: SEVEN \{Strong's: 7614\}\hfill{}\\

\textbf{Sheylah} Heb: {\large\H שלה} shey-lah Def: REQUEST \{Strong's: 7956\}\hfill{}\\

\textbf{Sheyshai} Heb: {\large\H ששי} shey-shai Def: LINEN\textasciitilde{}s\textasciitilde{}me(cs) \{Strong's: 8344\}\hfill{}\\

\textbf{Shilem} Heb: {\large\H שילם} shi-lem Def: RECOMPENSE \{Strong's: 8006\}\hfill{}\\

\textbf{Shimon} Heb: {\large\H שימעון} shi-mon Def: HEARER \{Strong's: 8095\}\hfill{}\\

\textbf{Shimron} Heb: {\large\H שימרון} im-ron Def: GUARD \{Strong's: 8110\}\hfill{}\\

\textbf{Shinar} Heb: {\large\H שינער} shi-nar Def: COUNTRY.OF.TWO.RIVERS \{Strong's: 8152\}\hfill{}\\

\textbf{Shinav} Heb: {\large\H שינאב} shi-nav Def: TOOTH\textasciitilde{}+\textasciitilde{}FATHER \{Strong's: 8134\}\hfill{}\\

\textbf{Shiphrah} Heb: {\large\H שיפרה} shiph-rah Def: BRIGHTNESS \{Strong's: 8236\}\hfill{}\\

\textbf{Shivah} Heb: {\large\H שיבעה} shi-vah Def: SEVENFOLD \{Strong's: 7656\}\hfill{}\\

\textbf{Shiymiy} Heb: {\large\H שימעי} shi-mi Def: REPORT\textasciitilde{}me(cs) \{Strong's: 8096\}\hfill{}\\

\textbf{Shophan} Heb: {\large\H שופן} sho-phan Def: SHAPHAN \{Strong's: 5855\}\hfill{}\\

\textbf{Shoval} Heb: {\large\H שובל} sho-val Def: UPPER.LEG \{Strong's: 7732\}\hfill{}\\

\textbf{Shu'a} Heb: {\large\H שוע} shu-ahh Def: SHOUTING.OUT \{Strong's: 7770\}\hfill{}\\

\textbf{Shu'ahh} Heb: {\large\H שוח} shu-ahh Def: SINKING \{Strong's: 7744\}\hfill{}\\

\textbf{Shuhham} Heb: {\large\H שוחם} shu-hham Def: PIT.DIGGER \{Strong's: 7748, 7749\}\hfill{}\\

\textbf{Shuni} Heb: {\large\H שוני} shu-ni Def: FORTUNATE\textasciitilde{}of \{Strong's: 7764\}\hfill{}\\

\textbf{Shur} Heb: {\large\H שור} shur Def: ROCK.WALL \{Strong's: 7793\}\hfill{}\\

\textbf{Shutelahh} Heb: {\large\H שותלח} shu-te-lahh Def: SET.DOWN (V)\textasciitilde{}ed(ms)\textasciitilde{}+\textasciitilde{}MOIST \{Strong's: 7803, 8364\}\hfill{}\\

\textbf{Sidim} Heb: {\large\H סידים} si-dim Def: FIELD\textasciitilde{}s \{Strong's: 7708\}\hfill{}\\

\textbf{Sihhon} Heb: {\large\H סיחון} si-hhon Def: MEDITATING.ONE \{Strong's: 5511\}\hfill{}\\

\textbf{Sin} Heb: {\large\H סין} sin Def: SHARP.THORN \{Strong's: 5513\}\hfill{}\\

\textbf{Sinai} Heb: {\large\H סיני} si-nai Def: SHARP.THORN\textasciitilde{}s\textasciitilde{}me(cs) \{Strong's: 5514\}\hfill{}\\

\textbf{Si'on} Heb: {\large\H סיאון} si-on Def: HIGH.ONE \{Strong's: 7865\}\hfill{}\\

\textbf{Siryon} Heb: {\large\H סיריון} sir-yon Def: HARNESS \{Strong's: 8303\}\hfill{}\\

\textbf{Sitnah} Heb: {\large\H סטנה} sit-nah Def: OPPOSITION \{Strong's: 7856\}\hfill{}\\

\textbf{Sitriy} Heb: {\large\H סיתרי} sit-ri Def: PROTECTION\textasciitilde{}me(cs) \{Strong's: 5644\}\hfill{}\\

\textbf{Sodi} Heb: {\large\H סודי} so-di Def: CONFIDENCE\textasciitilde{}me(cs) \{Strong's: 5476\}\hfill{}\\

\textbf{Sukhot} Heb: {\large\H סוכות} su-khot Def: BOOTH\textasciitilde{}s \{Strong's: 5523\}\hfill{}\\

\textbf{Suphah} Heb: {\large\H סופה} su-phah Def: WHIRLWIND \{Strong's: 5492\}\hfill{}\\

\textbf{Tahhan} Heb: {\large\H תחן} ta-hhan Def: CAMP \{Strong's: 8465, 8470\}\hfill{}\\

\textbf{Tahhash} Heb: {\large\H תחש} ta-hhash Def: TAHHASH \{Strong's: 8477\}\hfill{}\\

\textbf{Talmai} Heb: {\large\H תלמי} tal-mai Def: FURROW\textasciitilde{}s\textasciitilde{}me(cs) \{Strong's: 8526\}\hfill{}\\

\textbf{Tamar} Heb: {\large\H תמר} ta-mar Def: DATE.PALM \{Strong's: 8559\}\hfill{}\\

\textbf{Tarshish} Heb: {\large\H תרשיש} tar-shish Def: TOPAZ \{Strong's: 8659\}\hfill{}\\

\textbf{Taveyrah} Heb: {\large\H תבערה} tav-ey-rah Def: KINDLED \{Strong's: 8404\}\hfill{}\\

\textbf{Terahh} Heb: {\large\H תרח} te-rahh Def: STATIONED \{Strong's: 8646\}\hfill{}\\

\textbf{tevahh} Heb: {\large\H טבח} te-vahh Def: SLAUGHTERING \{Strong's: 2875\}\hfill{}\\

\textbf{Teyma} Heb: {\large\H תימא} tey-ma Def: DESERT.REGION \{Strong's: 8485\}\hfill{}\\

\textbf{Teyman} Heb: {\large\H תימן} tey-man Def: TO.THE.RIGHT \{Strong's: 8487, 8489\}\hfill{}\\

\textbf{Tidal} Heb: {\large\H תדעל} ti-dal Def: YOKE.BREAKER \{Strong's: 8413\}\hfill{}\\

\textbf{Timna} Heb: {\large\H תימנע} tim-na Def: WITHHOLDING \{Strong's: 8555\}\hfill{}\\

\textbf{Timnat} Heb: {\large\H תימנת} tim-nat Def: TO.THE.RIGHT \{Strong's: 8553\}\hfill{}\\

\textbf{Tiras} Heb: {\large\H תירס} ti-ras Def: DESIRABLE \{Strong's: 8494\}\hfill{}\\

\textbf{Tirtsah} Heb: {\large\H תירצה} tir-tsah Def: you(ms)\textasciitilde{}will\textasciitilde{}ACCEPT (V) \{Strong's: 8656\}\hfill{}\\

\textbf{Togarmah} Heb: {\large\H תוגרמה} to-gar-mah Def: you(ms)\textasciitilde{}will\textasciitilde{}GNAW (V)\textasciitilde{}her \{Strong's: 8425\}\hfill{}\\

\textbf{Tola} Heb: {\large\H תולע} to-la Def: KERMES \{Strong's: 8439\}\hfill{}\\

\textbf{Tophel} Heb: {\large\H תופל} to-phel Def: UNSEASONED \{Strong's: 8603\}\hfill{}\\

\textbf{Tsalmonah} Heb: {\large\H צלמונה} tsal-mo-nah Def: IMAGING \{Strong's: 6758\}\hfill{}\\

\textbf{Tsaphnat-Paneyahh} Heb: {\large\H צפנת.פענח} tsaph-nat pa-ney-ahh Def: TREASURY\textasciitilde{}+\textasciitilde{}GLORIOUS.REST \{Strong's: 6847\}\hfill{}\\

\textbf{Tsaphon} Heb: {\large\H צפון} tsa-phon Def: NORTH \{Strong's: 6827\}\hfill{}\\

\textbf{Tsedad} Heb: {\large\H צדד} tse-dad Def: MOUNTAIN.SIDE \{Strong's: 6657\}\hfill{}\\

\textbf{Tselaph'hhad} Heb: {\large\H צלפחד} tse-laph-hhad Def: SHADOW\textasciitilde{}+\textasciitilde{}AWE \{Strong's: 6765\}\hfill{}\\

\textbf{Tsemar} Heb: {\large\H צמר} tse-mar Def: WOOL \{Strong's: 6786\}\hfill{}\\

\textbf{Tsepho} Heb: {\large\H צפו} tse-pho Def: WATCHMAN\textasciitilde{}him \{Strong's: 6825\}\hfill{}\\

\textbf{Tseviim} Heb: {\large\H צביים} tse-vi-im Def: GAZELLE\textasciitilde{}s \{Strong's: 6636\}\hfill{}\\

\textbf{Tsidon} Heb: {\large\H צידון} tsi-don Def: HUNTING \{Strong's: 6721\}\hfill{}\\

\textbf{Tsilah} Heb: {\large\H צילה} tsi-lah Def: SHADOW \{Strong's: 6741\}\hfill{}\\

\textbf{Tsin} Heb: {\large\H צין} tsin Def: FLOCKS \{Strong's: 6790\}\hfill{}\\

\textbf{Tsiphyon} Heb: {\large\H ציפיון} tsiph-yon Def: WATCHER \{Strong's: 6837\}\hfill{}\\

\textbf{Tsiporah} Heb: {\large\H ציפורה} tsi-po-rah Def: BIRD \{Strong's: 6855\}\hfill{}\\

\textbf{Tsiv'on} Heb: {\large\H ציבעון} tsiv-on Def: SPLASHED \{Strong's: 6649\}\hfill{}\\

\textbf{Tso'an} Heb: {\large\H צוען} tso-an Def: REMOVED \{Strong's: 6814\}\hfill{}\\

\textbf{Tso'ar} Heb: {\large\H צוער} tso-ar Def: TINY \{Strong's: 6820\}\hfill{}\\

\textbf{Tsohhar} Heb: {\large\H צוחר} tso-hhar Def: REDDISH.GRAY \{Strong's: 6714\}\hfill{}\\

\textbf{Tsophim} Heb: {\large\H צופים} tso-phim Def: KEEP.WATCH (V)\textasciitilde{}ed(mp) \{Strong's: 6839\}\hfill{}\\

\textbf{Tsur} Heb: {\large\H צור} tsur Def: BOULDER \{Strong's: 6701\}\hfill{}\\

\textbf{Tsuri'eyl} Heb: {\large\H צוריאל} tsu'ri'eyl Def: BOULDER\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 6700\}\hfill{}\\

\textbf{Tsurishadai} Heb: {\large\H צורישדי} tsu-ri-sha-dai Def: BOULDER\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}BREAST\textasciitilde{}s\textasciitilde{}me(cs) \{Strong's: 6701\}\hfill{}\\

\textbf{Tumiym} Heb: {\large\H תומים} tu-mim Def: FULL.STRENGTH\textasciitilde{}s \{Strong's: 8550\}\hfill{}\\

\textbf{Tuval} Heb: {\large\H תובל} tu-val Def: you(ms)\textasciitilde{}will\textasciitilde{}BRING (V) \{Strong's: 8422\}\hfill{}\\

\textbf{Tuval-Qayin} Heb: {\large\H תובל.קין} tu-val qa-yin Def: you(ms)\textasciitilde{}will\textasciitilde{}BRING (V)\textasciitilde{}+\textasciitilde{}SPEARHEAD \{Strong's: 8423\}\hfill{}\\

\textbf{Ur} Heb: {\large\H אור} ur Def: LIGHT \{Strong's: 218\}\hfill{}\\

\textbf{Uriy} Heb: {\large\H אורי} u-ri Def: LIGHT\textasciitilde{}me(cs) \{Strong's: 221\}\hfill{}\\

\textbf{Uriym} Heb: {\large\H אורים} u-rim Def: LIGHT\textasciitilde{}s \{Strong's: 224\}\hfill{}\\

\textbf{Uts} Heb: {\large\H עוץ} uts Def: ADVICE \{Strong's: 5780\}\hfill{}\\

\textbf{Uval} Heb: {\large\H עובל} u-val Def: ROUNDED \{Strong's: 5745\}\hfill{}\\

\textbf{Uzal} Heb: {\large\H אוזל} u-zal Def: I(cs)\textasciitilde{}will\textasciitilde{}BE.LAVISH (V)\textasciitilde{}ed(ms) \{Strong's: 187\}\hfill{}\\

\textbf{Uziy'eyl} Heb: {\large\H עוזיאל} u-zi-eyl Def: BOLDNESS\textasciitilde{}me(cs)\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 5816\}\hfill{}\\

\textbf{Waheyv} Heb: {\large\H והב} wa-heyv Def: and\textasciitilde{}GIFT.OFFERING \{Strong's: 2052\}\hfill{}\\

\textbf{Waphsi} Heb: {\large\H ופסי} waph-si Def: and\textasciitilde{}WRIST\textasciitilde{}me(cs) \{Strong's: 2058\}\hfill{}\\

\textbf{Ya'aqov} Heb: {\large\H יעקוב} ya-a-qov Def: he\textasciitilde{}will\textasciitilde{}RESTRAIN (V) \{Strong's: 3290\}\hfill{}\\

\textbf{Yaboq} Heb: {\large\H יבוק} ya-boq Def: he\textasciitilde{}will\textasciitilde{}EMPTY.OUT (V) \{Strong's: 2999\}\hfill{}\\

\textbf{Yagbahah} Heb: {\large\H יגבהה} yag-ba-hah Def: he\textasciitilde{}will\textasciitilde{}BE.HIGH (V)\textasciitilde{}her \{Strong's: 3011\}\hfill{}\\

\textbf{Yagli} Heb: {\large\H יגלי} yag-li Def: he\textasciitilde{}will\textasciitilde{}REMOVE.THE.COVER (V) \{Strong's: 3020\}\hfill{}\\

\textbf{Yah} Heb: {\large\H יה} yah Def: EXISTING \{Strong's: 3050\}\hfill{}\\

\textbf{Yahats} Heb: {\large\H יהץ} ya-hats Def: STAMPED.DOWN \{Strong's: 3096\}\hfill{}\\

\textbf{Yahh'le'el} Heb: {\large\H יחלאל} yahh-le-eyl Def: he\textasciitilde{}will\textasciitilde{}STAY (V)\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 3177, 3178\}\hfill{}\\

\textbf{Yahhtse'el} Heb: {\large\H יחצאל} yahh-tse-eyl Def: he\textasciitilde{}will\textasciitilde{}DIVIDE (V)\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 3183\}\hfill{}\\

\textbf{Ya'ir} Heb: {\large\H יאיר} ya-ir Def: he\textasciitilde{}will\textasciitilde{}make\textasciitilde{}LIGHT (V) \{Strong's: 2971\}\hfill{}\\

\textbf{Yakhin} Heb: {\large\H יכין} ya-khin Def: he\textasciitilde{}will\textasciitilde{}PREPARE (V) \{Strong's: 3199\}\hfill{}\\

\textbf{Yalam} Heb: {\large\H יעלם} ya-lam Def: he\textasciitilde{}will\textasciitilde{}BE.OUT.OF.SIGHT (V) \{Strong's: 3281\}\hfill{}\\

\textbf{Yamin} Heb: {\large\H ימין} ya-min Def: RIGHT.HAND \{Strong's: 3226\}\hfill{}\\

\textbf{Yaphet} Heb: {\large\H יפת} ya-phat Def: WONDER \{Strong's: 3315\}\hfill{}\\

\textbf{Yaq'shan} Heb: {\large\H יקשן} yaq-shan Def: SNARER \{Strong's: 3370\}\hfill{}\\

\textbf{Yaqtan} Heb: {\large\H יקטן} yaq-tan Def: he\textasciitilde{}will\textasciitilde{}BE.SMALL (V) \{Strong's: 3355\}\hfill{}\\

\textbf{Yarden} Heb: {\large\H ירדן} yar-den Def: DESCENDER \{Strong's: 3383\}\hfill{}\\

\textbf{Yared} Heb: {\large\H ירד} ya-red Def: he\textasciitilde{}will\textasciitilde{}GO.DOWN (V) \{Strong's: 3382\}\hfill{}\\

\textbf{Yashuv} Heb: {\large\H ישוב} ya-shuv Def: he\textasciitilde{}will\textasciitilde{}TURN.BACK (V) \{Strong's: 3102, 3437\}\hfill{}\\

\textbf{Yatvatah} Heb: {\large\H יטבתה} yat-va-tah Def: WELLNESS\textasciitilde{}her \{Strong's: 3193\}\hfill{}\\

\textbf{Yaval} Heb: {\large\H יבל} ya-val Def: WATERCOURSE \{Strong's: 2989\}\hfill{}\\

\textbf{Yawan} Heb: {\large\H יון} ya-wan Def: MIRE \{Strong's: 3120\}\hfill{}\\

\textbf{Yazeyr} Heb: {\large\H יעזר} ya-zeyr Def: he\textasciitilde{}will\textasciitilde{}HELP (V) \{Strong's: 3270\}\hfill{}\\

\textbf{Yegar-Sa'haduta} Heb: {\large\H יגר.סהדותא} ye-gar sa-ha-du-ta Def: AFRAID\textasciitilde{}+\textasciitilde{}RECORD \{Strong's: 3026\}\hfill{}\\

\textbf{Yehoshu'a} Heb: {\large\H יהושוע} ye-ho-shu-a Def: EXISTING\textasciitilde{}+\textasciitilde{}he\textasciitilde{}will\textasciitilde{}RESCUE (V) \{Strong's: 3091\}\hfill{}\\

\textbf{Yehudah} Heb: {\large\H יהודה} ye-hu-dah Def: THANKSGIVING \{Strong's: 3063\}\hfill{}\\

\textbf{Yehudit} Heb: {\large\H יהודית} ye-hu-dit Def: THANKSGIVING \{Strong's: 3067\}\hfill{}\\

\textbf{Ye'ish} Heb: {\large\H יעיש} ye-ish Def: he\textasciitilde{}will\textasciitilde{}MAKE.HASTE (V) \{Strong's: 3274\}\hfill{}\\

\textbf{Yemu'el} Heb: {\large\H ימואל} ye-mu-eyl Def: DAY\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 3223\}\hfill{}\\

\textbf{Yephunah} Heb: {\large\H יפונה} ye-phu-nah Def: he\textasciitilde{}will\textasciitilde{}be\textasciitilde{}TURN (V) \{Strong's: 3312\}\hfill{}\\

\textbf{Yerahh} Heb: {\large\H ירח} ye-rahh Def: MOON \{Strong's: 3392\}\hfill{}\\

\textbf{Yereyhho} Heb: {\large\H ירחו} ye-rey-hho Def: MOON\textasciitilde{}him \{Strong's: 3405\}\hfill{}\\

\textbf{Yeshurun} Heb: {\large\H ישורון} ye-shu-run Def: STRAIGHT.ONE \{Strong's: 3484\}\hfill{}\\

\textbf{Yeter} Heb: {\large\H יתר} ye-ter Def: REMAINDER \{Strong's: n/a\}\hfill{}\\

\textbf{Yetet} Heb: {\large\H יתת} ye-tet Def: NAIL \{Strong's: 3509\}\hfill{}\\

\textbf{Yetser} Heb: {\large\H יצר} ye-tser Def: THOUGHT \{Strong's: 3337\}\hfill{}\\

\textbf{Yetur} Heb: {\large\H יטור} ye-tur Def: he\textasciitilde{}will\textasciitilde{}ROW (V) \{Strong's: 3195\}\hfill{}\\

\textbf{Yevus} Heb: {\large\H יבוס} ye-vus Def: he\textasciitilde{}will\textasciitilde{}TRAMPLE.DOWN (V) \{Strong's: 2982, 2983\}\hfill{}\\

\textbf{Yhwh} Heb: {\large\H יהוה} yhwh Def: he\textasciitilde{}will\textasciitilde{}BE (V) \{Strong's: 3068\}\hfill{}\\

\textbf{Yhwh-Nisiy} Heb: {\large\H יהוה.ניסי} yhwh ni-si Def: he\textasciitilde{}will\textasciitilde{}BE (V)\textasciitilde{}+\textasciitilde{}STANDARD\textasciitilde{}me(cs) \{Strong's: 3071\}\hfill{}\\

\textbf{Yhwh-Yireh} Heb: {\large\H יהוה.יראה} yhwh yi-reh Def: he\textasciitilde{}will\textasciitilde{}BE (V)\textasciitilde{}+\textasciitilde{}he\textasciitilde{}will\textasciitilde{}SEE (V) \{Strong's: 3070\}\hfill{}\\

\textbf{Yidlap} Heb: {\large\H ידלף} yid-lap Def: he\textasciitilde{}will\textasciitilde{}DRIP (V) \{Strong's: 3044\}\hfill{}\\

\textbf{Yimnah} Heb: {\large\H ימנה} yim-nah Def: he\textasciitilde{}will\textasciitilde{}RECKON (V) \{Strong's: 3232\}\hfill{}\\

\textbf{Yish'baq} Heb: {\large\H ישבק} yish-baq Def: he\textasciitilde{}will\textasciitilde{}LEAVE.ALONE (V) \{Strong's: 3435\}\hfill{}\\

\textbf{Yishma'el} Heb: {\large\H ישמעאל} yish-ma-eyl Def: he\textasciitilde{}will\textasciitilde{}HEAR (V)\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 3458\}\hfill{}\\

\textbf{Yishwah} Heb: {\large\H ישוה} yish-wah Def: he\textasciitilde{}will\textasciitilde{}EQUATE (V) \{Strong's: 3438\}\hfill{}\\

\textbf{Yishwiy} Heb: {\large\H ישוי} yish-wi Def: he\textasciitilde{}will\textasciitilde{}EQUATE (V)\textasciitilde{}me(cs) \{Strong's: 3440, 3441\}\hfill{}\\

\textbf{Yiskah} Heb: {\large\H יסכה} {[}X{]} Def: he\textasciitilde{}will\textasciitilde{}LOOK.FORTH (V) \{Strong's: 3252\}\hfill{}\\

\textbf{Yisra'el} Heb: {\large\H יסראל} yis-ra-eyl Def: he\textasciitilde{}will\textasciitilde{}TURN.ASIDE (V)\textasciitilde{}+\textasciitilde{}MIGHTY.ONE \{Strong's: 3478, 3479\}\hfill{}\\

\textbf{Yis'sas'khar} Heb: {\large\H יססכר} yeysh-sa-khar Def: THERE.IS\textasciitilde{}+\textasciitilde{}WAGE \{Strong's: 3485\}\hfill{}\\

\textbf{Yitran} Heb: {\large\H יתרן} yit-ran Def: RESERVER \{Strong's: 3506\}\hfill{}\\

\textbf{Yitro} Heb: {\large\H יתרו} yit-ro Def: REMAINDER\textasciitilde{}him \{Strong's: 3503\}\hfill{}\\

\textbf{Yits'har} Heb: {\large\H יצהר} yits-har Def: he\textasciitilde{}will\textasciitilde{}PRESS.OUT.OIL (V) \{Strong's: 3324\}\hfill{}\\

\textbf{Yits'hhaq} Heb: {\large\H יצחק} yits-hhaq Def: he\textasciitilde{}will\textasciitilde{}LAUGH (V) \{Strong's: 3327\}\hfill{}\\

\textbf{Yokheved} Heb: {\large\H יוכבד} yo-khe-ved Def: EXISTING\textasciitilde{}+\textasciitilde{}HEAVY \{Strong's: 3115\}\hfill{}\\

\textbf{Yoseph} Heb: {\large\H יוסף} yo-seph Def: ADD (V)\textasciitilde{}ing(ms) \{Strong's: 3130\}\hfill{}\\

\textbf{Yovav} Heb: {\large\H יובב} yo-vav Def: HOWL (V)\textasciitilde{}ing(ms) \{Strong's: 3103\}\hfill{}\\

\textbf{Yuval} Heb: {\large\H יובל} yu-val Def: CREEK \{Strong's: 3106\}\hfill{}\\

\textbf{Za'awan} Heb: {\large\H זעון} za-a-wan Def: TROUBLED \{Strong's: 2190\}\hfill{}\\

\textbf{Zakur} Heb: {\large\H זכור} za-kur Def: REMEMBER (V)\textasciitilde{}ed(ms) \{Strong's: 2139\}\hfill{}\\

\textbf{Zamzum} Heb: {\large\H זמזום} zam-zum Def: MISCHIEFOUS \{Strong's: 2157\}\hfill{}\\

\textbf{Zerahh} Heb: {\large\H זרח} ze-rahh Def: RISING.SUN \{Strong's: 2226, 2227\}\hfill{}\\

\textbf{Zered} Heb: {\large\H זרד} ze-red Def: EXUBERANT \{Strong's: 2218\}\hfill{}\\

\textbf{Zevulun} Heb: {\large\H זבולון} ze-vu-lun Def: RESIDENT \{Strong's: 2074\}\hfill{}\\

\textbf{Zikh'riy} Heb: {\large\H זיכרי} zikh-ri Def: MEMORY\textasciitilde{}me(cs) \{Strong's: 2147\}\hfill{}\\

\textbf{Zilpah} Heb: {\large\H זילפה} zil-pah Def: TRICKLING \{Strong's: 2153\}\hfill{}\\

\textbf{Zimran} Heb: {\large\H זימרן} zim-ran Def: MUSICIAN \{Strong's: 2175\}\hfill{}\\

\textbf{Zimri} Heb: {\large\H זימרי} zim-ri Def: SINGER\textasciitilde{}me(cs) \{Strong's: 2174\}\hfill{}\\

\textbf{Ziphron} Heb: {\large\H זיפרון} ziph-ron Def: FRAGRANT.ONE \{Strong's: 2202\}\hfill{}\\

\textbf{Zuz} Heb: {\large\H זוז} zuz Def: ENTRYWAY \{Strong's: 2104\}\hfill{}\\

\newpage
\begin{center}
{\Large{}Prefixes and Suffixes}\phantomsection{}\label{page:dictionary:pre-n-suf}
\end{center}

\vspace{-1ex}
\textbf{!(fp)\textasciitilde{}} Def: Identifies the verb as a feminine plural imperative.\hfill{}\\

\textbf{!(fs)\textasciitilde{}} Def: Identifies the verb as a feminine singular imperative.\hfill{}\\

\textbf{!(mp)\textasciitilde{}} Def: Identifies the verb as a masculine plural imperative.\hfill{}\\

\textbf{!(ms)\textasciitilde{}} Def: Identifies the verb as a masculine singular imperative.\hfill{}\\

\textbf{?\textasciitilde{}} Def: The interrogative hey converting the sentence into a question.\hfill{}\\

\textbf{\textasciitilde{}{\char`\^}} Def: Paragogic Hey; added to the ordinary forms of words, to express additional emphasis, or some change in the sense.\hfill{}\\

\textbf{\textasciitilde{}+\textasciitilde{}} Def: Identifies a compound name (used in the translation of names only).\hfill{}\\

\textbf{\textasciitilde{}ed(fp)} Def: Feminine plural verb passive participle denoting an action (such as baked).\hfill{}\\

\textbf{\textasciitilde{}ed(fs)} Def: Feminine singular verb passive participle denoting an action (such as baked).\hfill{}\\

\textbf{\textasciitilde{}ed(mp)} Def: Masculine plural verb passive participle denoting an action (such as baked).\hfill{}\\

\textbf{\textasciitilde{}ed(ms)} Def: Masculine singular verb passive participle denoting an action (such as baked).\hfill{}\\

\textbf{\textasciitilde{}her} Def: Third person feminine singular pronoun (her) also used as a possessive pronoun (of him or his).\hfill{}\\

\textbf{\textasciitilde{}him} Def: Third person masculine singular pronoun (him) also used as a possessive pronoun (of him or his).\hfill{}\\

\textbf{\textasciitilde{}ing(fp)} Def: Feminine plural verb participle denoting an action (such as baking) or one of action (such as a bakers).\hfill{}\\

\textbf{\textasciitilde{}ing(fs)} Def: Feminine singular verb participle denoting an action (such as baking) or one of action (such as a baker).\hfill{}\\

\textbf{\textasciitilde{}ing(mp)} Def: Masculine plural verb participle denoting an action (such as baking) or one of action (such as a bakers).\hfill{}\\

\textbf{\textasciitilde{}ing(ms)} Def: Masculine singular verb participle denoting an action (such as baking) or one of action (such as a baker).\hfill{}\\

\textbf{\textasciitilde{}me(cs)} Def: First person common singular pronoun (me), also used as a possessive pronoun (of me or my).\hfill{}\\

\textbf{\textasciitilde{}must} Def: Paragogic Nun; emphasises the intensity of action of the verb.\hfill{}\\

\textbf{\textasciitilde{}of} Def: Identifies the noun as possessive.\hfill{}\\

\textbf{\textasciitilde{}s} Def: Identifies the noun as a quantitative or qualitative plural.\hfill{}\\

\textbf{\textasciitilde{}s2} Def: Identifies the noun as a dual plural.\hfill{}\\

\textbf{\textasciitilde{}them(fp)} Def: Third person feminine plural pronoun (them) also used as a possessive pronoun (of them or their).\hfill{}\\

\textbf{\textasciitilde{}them(mp)} Def: Third person masculine plural pronoun (them) also used as a possessive pronoun (of them or their).\hfill{}\\

\textbf{\textasciitilde{}unto} Def: Directional Hey; implies movement toward the location identified in the word this suffix is attached to.\hfill{}\\

\textbf{\textasciitilde{}us(cp)} Def: First person common plural pronoun (we), also used as a possessive pronoun (of us or our).\hfill{}\\

\textbf{\textasciitilde{}you(fp)} Def: Second person feminine plural pronoun (you), also used as a possessive pronoun (of you or your).\hfill{}\\

\textbf{\textasciitilde{}you(fs)} Def: Second person feminine singular pronoun (you), alsoused as a possessive pronoun (of you or your).\hfill{}\\

\textbf{\textasciitilde{}you(mp)} Def: Second person masculine plural pronoun (you), also used as a possessive pronoun (of you or your).\hfill{}\\

\textbf{\textasciitilde{}you(ms)} Def: Second person masculine singular pronoun (you), also used as a possessive pronoun (of you or your).\hfill{}\\

\textbf{>\textasciitilde{}} Def: Identifies the verb form as infinitive.\hfill{}\\

\textbf{and\textasciitilde{}} Def: The conjunction meaning and. Often used as the vav consecutive meaning that when prefixed to a verb it will usually reverse the tense of the verb.\hfill{}\\

\textbf{be\textasciitilde{}} Def: Identifies the voice of the verb as passive.\hfill{}\\

\textbf{did\textasciitilde{}} Def: Identifies the tense of the verb as perfect.\hfill{}\\

\textbf{from\textasciitilde{}} Def: A preposition meaning from.\hfill{}\\

\textbf{he\textasciitilde{}} Def: Identifies the subject of the verb as third person masculine singular.\hfill{}\\

\textbf{I(cs)\textasciitilde{}} Def: Identifies the subject of the verb as first person common singular.\hfill{}\\

\textbf{in\textasciitilde{}} Def: A preposition meaning in or with.\hfill{}\\

\textbf{like\textasciitilde{}} Def: A preposition meaning like.\hfill{}\\

\textbf{make\textasciitilde{}} Def: Identifies the the mood of the verb as causative.\hfill{}\\

\textbf{much\textasciitilde{}} Def: Identifies the the mood of the verb as intensive.\hfill{}\\

\textbf{self\textasciitilde{}} Def: Identifies the voice of the verb as reflexive.\hfill{}\\

\textbf{she\textasciitilde{}} Def: Identifies the subject of the verb as third person feminine singular.\hfill{}\\

\textbf{the\textasciitilde{}} Def: The definite article meaning "the". \hfill{}\\

\textbf{they(cp)\textasciitilde{}} Def: Identifies the subject of the verb as third person common plural.\hfill{}\\

\textbf{they(fp)\textasciitilde{}} Def: Identifies the subject of the verb as third person feminine plural.\hfill{}\\

\textbf{they(mp)\textasciitilde{}} Def: Identifies the subject of the verb as third person masculine plural.\hfill{}\\

\textbf{to\textasciitilde{}} Def: A preposition meaning to or for.\hfill{}\\

\textbf{we(cp)\textasciitilde{}} Def: Identifies the subject of the verb as first person common plural.\hfill{}\\

\textbf{which\textasciitilde{}} Def: A preposition meaning which or who.\hfill{}\\

\textbf{will\textasciitilde{}} Def: Identifies the tense of the verb as imperfect.\hfill{}\\

\textbf{you(fp)\textasciitilde{}} Def: Identifies the subject of the verb as second person feminine plural.\hfill{}\\

\textbf{you(fs)\textasciitilde{}} Def: Identifies the subject of the verb as second person feminine singular.\hfill{}\\

\textbf{you(mp)\textasciitilde{}} Def: Identifies the subject of the verb as second person masculine plural.\hfill{}\\

\textbf{you(ms)\textasciitilde{}} Def: Identifies the subject of the verb as second person masculine singular.\hfill{}\\

}
